### 2017-02-11 doc/paper.tex
Add Tex file

\documentclass[12pt,final,fleqn]{article}

% basic packages
\usepackage[margin=1in] { geometry }
\usepackage{amssymb,amsmath, bm}
\usepackage{verbatim}
\usepackage[latin1]{inputenc}
%\usepackage[OT1]{fontenc}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage[font={bf}]{caption}
%\usepackage{pgfplots}
%\usepackage[font={bf}]{caption}
\usepackage{setspace}
\usepackage{latexsym}
%\usepackage{euscript}
\usepackage{graphicx}
\usepackage{marvosym}
%\usepackage[varg]{txfonts}  Older version of ``g'' in math.

% bibliography packages
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
\bibliographystyle{apsr}
\renewcommand{\bibname}{References}

% hyperref options
\usepackage{color}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={blue!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\newcommand*{\Appendixautorefname}{Appendix}
\renewcommand*{\sectionautorefname}{Section}
\renewcommand*{\subsectionautorefname}{Section}
\newcommand{\aref}[1]{\hyperref[#1]{Appendix~\ref{#1}}}

% packages for tables
\usepackage{longtable}
\usepackage{booktabs, threeparttable}
\usepackage{threeparttablex}
%\usepackage{tabularx}
% dcolumn package
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\captionsetup{belowskip=10pt,aboveskip=-5pt}
\usepackage{multirow}
% rotating package
\usepackage[figuresright]{rotating}
\usepackage{pdflscape}
\usepackage{subcaption}

% packages for figures
\usepackage{grffile}
\usepackage{afterpage}
\usepackage{float}
\usepackage[section]{placeins}

% theorem package
\usepackage{theorem}
\theoremstyle{plain}
\theoremheaderfont{\scshape}
\newtheorem{theorem}{Theorem}
\newtheorem{algorithm}{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newcommand{\qed}{\hfill \ensuremath{\Box}}
\newcommand\indep{\protect\mathpalette{\protect\independenT}{\perp}}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\argmin}{arg\min}
\DeclareMathOperator{\argmax}{arg\max}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\providecommand{\norm}[1]{\lVert#1\rVert}
\renewcommand\r{\right}
\renewcommand\l{\left}
\newcommand\E{\mathbb{E}}
\newcommand\dist{\buildrel\rm d\over\sim}
\newcommand\iid{\stackrel{\rm i.i.d.}{\sim}}
\newcommand\ind{\stackrel{\rm indep.}{\sim}}
\newcommand\cov{{\rm Cov}}
\newcommand\var{{\rm Var}}
\newcommand\SD{{\rm SD}}
\newcommand\bone{\mathbf{1}}
\newcommand\bzero{\mathbf{0}}

% dotted lines in tables
%\usepackage{arydshln}

\usepackage{pdflscape}

% spacing between sections and subsections
\usepackage[compact]{titlesec}

% times new roman
%\usepackage{times}

% appendix settings
\usepackage[toc,page,header]{appendix}
\renewcommand{\appendixpagename}{\centering Appendices}
\usepackage{chngcntr}
\usepackage{etoolbox}
\usepackage{lipsum}

% file paths and definitions
\makeatletter
\newcommand*\ExpandableInput[1]{\@@input#1 }
\makeatother

\setlength{\mathindent}{1cm}
\allowdisplaybreaks[4]
\doublespacing
%\special{pdf: pagesize width 8.5truein height 11.0truein}

\titleformat{\subsection}
  {\itshape\large}{\thesubsection}{1em}{}

\setcounter{tocdepth}{1}
\begin{document}
\author{Devin Incerti and Trevor Incerti}
\title{\textbf{Political Instability and Financial Markets}}
\date{\today}
\maketitle

\singlespacing
\begin{abstract}
We examine the relationship between political instability and the daily returns of national stock indices. Financial volatility increases dramatically following (and just before) ``irregular'' regime changes caused by coup d'état, assassinations, and resignations. Some of the pre-resignation volatility occurs because of public protests such as riots and popular demonstrations that helped spawn the resignation in the first place. However, these irregular regime changes have disparate effects on the direction of stock returns. Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%). The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'état attempt result in positive abnormal returns of 20\% or more.
\end{abstract}
\doublespacing

\section{Introduction} \label{sec:Introduction}
Investors, firms and development agencies are all concerned with political risk in emerging markets. Government's can reduce asset returns, firm profits and overall economic performance by implementing unfavorable policies. In the 2011 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the most important constraint for foreign direct investment (FDI) in developing countries over the next three years. The most pressing risks involved government regulatory policies and failed commitments, although political violence was also a concern. \footnote{The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.}

A common hypothesis is that political instability discourages investment and reduces economic growth by increasing policy uncertainty. Some cross country empirical evidence is consistent with this hypothesis: political instability, as measured by regime change frequency or political violence, is negatively correlated with investment, GDP growth and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}. In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups. On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.

Of course, a change in government might promote growth if the new regime adopts better economic policies or is less corrupt than its predecessors. \citet{alesina1996political} takes this possibility seriously but argues that the negative effects of policy uncertainty dominate the positive effects of coups staged by pro growth factions. Conversely, \citet{londregan1990poverty} present evidence suggestive of a bimodal distribution of coups in which neither the effects of pro-growth or anti-growth coups dominate.

As in \citet{alesina1996political}, We use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability. The major innovation of this paper is that, in contrast to the aforementioned cross country studies, We analyze the impact of political instability using daily financial data. To the extent that these irregular transfers of power are unpredictable and unrelated events do not bias the results, this allows me to use market expectations to quantify the economic impact of regime changes. The advantage of this event study approach is that it allows me to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.

My main finding is that financial volatility increases dramatically following (and just before) coup d'état, assassinations, and resignations. However, these irregular regime changes have disparate effects on the direction of stock returns.  Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%). The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'état attempt result in positive abnormal returns of 20\% or more. We also present evidence showing that volatility increases during public protests such as riots and popular demonstrations that cause leaders to resign. These findings provide important insights into the expected impact of episodes of political instability on economic performance.

This paper is most closely related to four branches of literature. The first analyzes the economic impact of political instability. This area contains a number of theoretical models in addition to the empirical work already mentioned. These models tend to focus on government policy instruments that affect private rates of return on investment. The general idea is that political instability causes governments to act myopically and adopt inefficient policies. For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high. Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes. The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.

The second strand examines the impact of leaders on political and economic outcomes. \citet{jones2005leaders} identify plausibly exogenous leadership transitions using the deaths of leaders from either natural causes or accidents. Their results indicate that leaders influence policy outcomes (particularly monetary policy) and economic growth. \citet{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats. Other work has focused on leaders in the private sector. In particular, \citet{bertrand2003managing} estimate CEO fixed effects and show that private sector leaders have important effects on the profits of firms.

The third uses event studies to assess political phenomenon. A growing body of work uses political events to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}. Other studies in ``forensic economics" have used political events to study illicit transactions such as insider trading \citep{dube2011coups}. \citet{guidolin2007diamonds} used the sudden death of rebel leader, Jonas Savimbi, to show that Angolan diamond mining companies benefited from the Angolan civil war. \citet{dellavigna2010detecting} detect illegal arms trading by identifying events that increase or decrease conflict intensity.

The fourth looks at how the variance of stock market returns reacts to political events. \citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain. \citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies, Luiz Inácio Lula da Silva, increased the volatility (but not the mean return) of the Brazilian stock market.

\section{Data}
Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'état dataset and Coup d'état Events handbook. The Coup d'état dataset incudes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots. We focus on successful coups because it is difficult to classify failed coups. \citet[p. 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''

The Coup d'état Events handbook provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority. Daily financial data is available for countries in categories 4 and 5, so We supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes. The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.

We further supplement the CSP data with leadership data from Archigos Version 2.9, which allows me to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g. coups, revolts and assassinations).

Financial data are from the Global Financial Data database, which includes the longest available time series of stock prices. We collect data on national equity indices and two global equity indices, the S\&P/IFC Emerging Market Investable Composite and the Morgan Stanley Capital International (MSCI) World Index. The S\&P/IFC index includes securities from emerging markets while the MSCI index includes securities from developed markets only. We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}. Coup attempts are those in category 2 in the CSP Coup d'état dataset.}The longest available time series for these stock indices are listed in \autoref{tab:stock list}.

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of stock indices}\label{tab:stock list}\\
\vspace{-5pt}\\
\hline
\hline
\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Stock Index}&\multicolumn{1}{c}{Begin Date}&\multicolumn{1}{c}{End Date}\\
\hline
\endfirsthead
\multicolumn{4}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Stock Index}&\multicolumn{1}{c}{Begin Date}&\multicolumn{1}{c}{End Date}\\
\hline
\endhead
\hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
Argentina & Beunos Aires SE General Index & Dec-66 & Jan-13\\
Australia & Australia ASX All Ordinaries & Jan-58 & Jan-13\\
Bangladesh & Dhaka SE Index & Jan-90 & Apr-09\\
Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-13\\
Chile & Santiago IGBC General Index & Jan-75 & Jan-13\\
Colombia & Colombia IGBC General Index & Jan-92 & Jan-13\\
Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Nov-11\\
Egypt & Cairo SE Index & Dec-92 & Jan-13\\
Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-13\\
France & France CAC All-Tradable Index & Sep-68 & Jan-13\\
Greece & Athens SE General Index & Oct-88 & Jan-13\\
India & Bombday SE SENSEX & Apr-79 & Jan-13\\
Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-13\\
Iran & Tehran SE Price Index & Jan-95 & Mar-12\\
Israel & Tel Aviv 100 Index & May-87 & Jan-13\\
Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-13\\
Latin America & Dow Jones Latin America Index & Jan-92 & Jan-13\\
Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-13\\
Nepal & Nepal NEPSE Stock Index & Jul-97 & Jul-99\\
Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-13\\
Pakistan & Karachi SE 100 Index & Jan-89 & Jan-13\\
Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
Peru & Lima SE General Index & Jan-82 & Jan-13\\
Philippines & Manila SE Composite Index & Jan-86 & Jan-13\\
Portugal & Oporto PSI-20 Index & Jan-86 & Jan-13\\
Singapore & Singapore FTSE ST Index & Jul-65 & Jan-13\\
South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-13\\
Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-13\\
Spain & Madrid SE General Index & Aug-71 & Jan-13\\
Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-13\\
Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-13\\
Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-13\\
Thailand & Thailand SET General Index & Apr-75 & Jan-13\\
Tunisia & Tunisia SE Index & Dec-97 & Jan-13\\
Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-13\\
Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-13\\
United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-13\\
United States & Dow Jones Industrial Average & Feb-1885 & Jan-13\\
Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jan-13\\
Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
Venezuela & Caracas SE General Index & Jan-94 & Jan-13\\
World & MSCI World Price Index & Jan-76 & Jan-13\\
Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
Zambia & Zambia LuSE Index & Jan-02 & Apr-06\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

To gain perspective on the relationship between irregular regime changes and the stock market, \autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events. Returns are for 250 trading days---approximately one calendar year---before and after regime changes.

The absolute value of returns on the event day (trading day 0) are significantly larger than on any other day. In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after it. This suggests that financial volatility increase during the days surrounding regime changes, although it does not provide any evidence on mean returns.

\autoref{sec: Irregular Regime Changes} tests these results more formally. It will first analyze coups, assassinations and resignations separately and determine whether they increase mean returns. It will then combine all irregular regime changes and estimate the effect of regime changes on the variance of returns.

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Absolute value of daily returns}
\label{fig:AV-DR}
\end{figure}

\section{Irregular Regime Changes} \label{sec: Irregular Regime Changes}
\subsection{Abnormal Returns} \label{subsec: Abnormal Returns}
We begin our analysis by studying the effect of irregular regime changes on stock returns. We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}. Normal performance is measured with a constant mean return model\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations (plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995 respectively). That said, results are insensitive to the use of a market model.},
\begin{align} \label{eqn:market-model}
R_{it}=\mu_{i}+\epsilon_{it},
\end{align}
where $R_{it}$ is the logged return of national stock index $i$ on trading day $t$ and $\epsilon_{it}$ is the error term. We calculate abnormal returns (ARs), in an ``event window'' surrounding the date of each coup, $AR_{i\tau}=R_{i\tau}-\widehat{\mu}_i$, where $\tau$ is a date in the event window, and $\widehat{\mu}_i$ is estimated in an ``estimation window'' preceding the event window with \autoref{eqn:market-model}. We use a 41 day event window (i.e. 20 pre-event trading days, the event day, and 20 post-event trading days). The estimation window is the 250 trading days prior to the start of the event window. The abnormal returns are then used to generate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.

We define the event date as the first trading day in which the market could have reacted to news of the event. For example, during the October 12, 1999 coup d'état in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm. We code October 14th, the day in which the market re-opened, as the event day. When events occurred on weekends, We change the event date to the following Monday.

$(0,\tau-1)$ is used to denote the $\tau$-day period beginning with the event day and $(-1,\tau)$ to denote the negative $\tau$-day period beginning with the day prior to the event day. In other words, for cumulative abnormal returns prior to the event date, We aggregate backwards starting at the day of the event. For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.

We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns. \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'état.
Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}. \footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}

\begin{table}[!ht]
\caption{Abnormal returns following coups} \label{tab:AR-coups}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car.txt}
  \hline
  \textbf{Means} &  &  &  &  &  &  \\
\ExpandableInput{../tables/artable-coups-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
\end{threeparttable}
\end{center}
\end{table}

Event day ARs are negative for all coups except the 1971 and 1976 coups in Argentina. The 1976 coup in Argentina appears to be somewhat of an anomaly.  The ARs on the event day are larger than for any other regime change in the sample (28\%). It is also the only coup with statistically significant (and extremely large) 7-day and 20-day pre-event CARs. Finally, although the event day abnormal return is large and positive, the 7-day and 20-day post-event CARs are negative.

Event day ARs for the 1970 coup in Argentina, the 1979 coup in South Korea, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero. Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero.

If the 1976 coup in Argentina is dropped from the sample, the average coup has a $-2.7\%$ event day AR. Even so, markets usually recovered quickly: the market returned to its pre-coup level following a negative event day stock return within 5 trading days in all but one case.

Although it is tempting to dismiss the 1976 Argentina coup as an outlier, there is reason to to believe that coups can in fact result in large positive abnormal returns. The 2002 failed coup d'état attempt against Hugo Chavez is a case in point. On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him. Pedro Carmona, a Venezuelan business leader, was named the transitional President of Venezuela. Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.

The event is a perfect natural experiment because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated. It provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime. It is therefore a good example of the impact of a shift from a left-wing populist government to a pro business regime on the value of the largest firms in an emerging market.

\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt. The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals. The daily ARs and corresponding confidence intervals are displayed in the bottom panel. The abnormal return on April 12, the first trading day in which investors could react to the coup, was 19.5\%. The market reacted similarly, albeit in the opposite direction, to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -14\%.

\begin{figure}[!ht]
\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'état attempt}
\label{fig:AR-Ven}
\end{figure}

The results in the figure are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days. The only other day in which the ARs are statistically different from zero is on the third trading day after the coup attempt.

The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot. The unexpected nature of the event means that the abnormal returns capture the true value of the regime change from Chavez to Carmona more accurately than they otherwise would.

The results in \autoref{tab:AR-ass} are produced from analyses identical to those table \autoref{tab:AR-coups} but for successful assassinations rather than coups. Like coups, there is some evidence that assassinations decrease stock prices. The mean event day abnormal return is negative and statistically different than zero. However, the result is driven almost entirely by three events: the shooting of U.S. President William McKinley on September 6, 1901; the assassination of U.S. President John F. Kennedy on November 22, 1963; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.

\begin{table}[!ht]
\caption{Abnormal returns following assassinations} \label{tab:AR-ass}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-ass-car.txt}
  \hline
\ExpandableInput{../tables/artable-ass-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level. The mean days to rebound excludes the assassination of William McKinley on November 6, 1901.
\end{threeparttable}
\end{center}
\end{table}

There is no evidence of post or pre-event CARs in almost any of the assassinations. As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low. One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days, or almost 4 calendar years. However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death (although the assassination may have exacerbated the panic). In any case, the length of this time period is so long that we omitted it when calculating the mean days to rebound in the figure.

As shown in \autoref{tab:AR-resignations}, and in contrast to coups and assassinations, abnormal returns following resignations are large and positive. The mean event day abnormal return is a little over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011). But positive stock returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.

\begin{table}[!ht]
\caption{Abnormal returns following resignations} \label{tab:AR-resignations}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-res-car.txt}
  \hline
\ExpandableInput{../tables/artable-res-car-mean.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
\end{threeparttable}
\end{center}
\end{table}

The positive event day abnormal return following resignations is not surprising since resignations occurred because of ``poor performance and/or loss of authority.'' Leaders were often ousted following corruption charges, financial crises, and/or political violence. For example, consider Suharto's resignation from office as the President of Indonesia on May 1998, just after the 1997 Asian Financial Crisis.

Prior to the crisis, the Indonesian economy suffered from a number of ailments including crony capitalism, poor corporate governance, growing short-term debt and a corrupt banking system \citep{radelet2000onset}. In addition, Suharto's ill health created considerable policy uncertainty, which only added to the financial panic in Indonesia. Indonesia was also hesitant to adopt structural reforms which further weakened its economic image. As a result, the crisis gave additional ammo to opposition leaders and public opposition culminated in riots in mid-May 1998. Suharto eventually lost his military support and was forced to resign.

\subsection{Volatility} \label{subsec: Volatility}
Although irregular regime changes have disparate effects on the direction of stock returns, the results from \autoref{subsec: Abnormal Returns} suggest that all of these political events increase financial volatility. However, since stock volatility is not directly observable, one must decide how to best estimate volatility. My estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days. As in \citet{jensen2005market} and \citet{leblang2005government}, We use the GARCH (1,1) specification. In particular, for national stock index $i$,
\begin{align*}
R_{it}=\mu_i + \epsilon_{it},\hspace{1cm} \epsilon_{it}\sim \mathcal{N}\left(0,\sigma_{it}^2\right),
\end{align*}
where $\mu_i$ is a constant and,
\begin{align*}
\sigma_{it}^2&=\gamma_{i}+\alpha_{i}\epsilon_{i,t-1}^2+\beta_{i}\sigma_{i,t-1}^2.
\end{align*}
The key parameter of interest is the conditional variance, $\sigma_{it}^2$. The one-period-ahead volatility forecasts, $\sigma_{it}$, are larger when $\epsilon_{i,t-1}^2$ and $\sigma_{i,t-1}^2$ are larger. In other words, the model predicts that large shocks will be followed by other large shocks.

\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 30 trading days prior to and 30 days after each event. Volatility appears to increase slowly just before the regime change, which suggests that investors sometimes have information about the events before they occur. Nonetheless, there is still an enormous volatility jump on the day of the regime change. Volatility then decreases to normal levels within a month of the event.

The smaller figure within \autoref{fig:volatility} expands the volatility estimates to the 250 trading days before and after each regime change. As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.

\begin{figure}[htb]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Mean of volatility estimates from GARCH(1,1) models}
\label{fig:volatility}
\end{figure}

\subsection{Robustness} \label{subsec: Robustness}
There are three potential concerns with the results in \autoref{subsec: Abnormal Returns}. First, the abnormal returns could have been driven by factors unrelated to the regime changes. Second, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate. Third, the true effects of irregular regime changes on firm value may be underestimated if investors had apriori information.

To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}. Each country is given a weight which represents its influence in the synthetic control portfolio. The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window. The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock list}.\footnote{See the appendix for a more formal explanation.}

The second concern is addressed using non-parametric statistical techniques, which are free from distributional assumptions. we employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.

\autoref{tab:non-parametric} compares event day ARs as well as ``abnormal absolute returns'' between the event country and the synthetic control portfolio using the non-parametric methods discussed above. The ``abnormal absolute returns'' are abnormal returns for the absolute value of stock returns. This is done to combine events since resignations tend to increase returns while assassinations and coups tend to decrease them. The idea that the absolute value of returns might increase during irregular regime changes is similar to the finding that volatility increases and consistent with \autoref{fig:AV-DR}.

\begin{table}[!ht]
\caption{Non-parametric tests of the impact of regime changes} \label{tab:non-parametric}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
&\multicolumn{3}{c}{Regime Change Country}&\multicolumn{3}{c}{Synthetic Control Portfolio}&\multicolumn{1}{c}{\multirow{2}{*}{Wilcoxon}}\\
\cmidrule(r){2-4} \cmidrule(r){5-7}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Sign}
&\multicolumn{1}{c}{Rank Test}\\
\multicolumn{1}{c}{Event Type}&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{CAR (0,0)}&\multicolumn{1}{c}{p-value}&\multicolumn{1}{c}{p-value}
&\multicolumn{1}{c}{p-Value}\\
  \hline
Coups & -0.182 & 0.008 & 0.083 & 0.235 & 0.980 & 1.000 & 0.034  \\
Assassinations & -1.101 & 0.043 & 0.157 & -2.342 & 0.236 & 0.157 & 0.688  \\
Resignations & 6.146 & 0.000 & 0.020 & 0.486 & 0.217 & 0.796 & 0.007 \\
All (Absolute Value) & 3.725 & 0.000 & 0.004 & 0.335 & 0.144 & 0.612 & 0.001 \\
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes:
\end{threeparttable}
\end{center}
\end{table}

As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 5\% level using the rank test statistic and the abnormal returns for coups and resignations are significant at at least the 10\% level using the sign test. In addition, abnormal absolute returns for all events are statistically significant at the 1\% level using both the rank and sign statistics. On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level. Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups, resignations and all events combined when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec: Abnormal Returns} are not an artifact of deviations from normality or confounding world events.

The third concern, which is that the political events in this paper are not unexpected, is addressed in a number of ways. First, one can note that neither the 7-day or the 20-day mean CAR from tables \autoref{tab:AR-coups}, \autoref{tab:AR-ass} or \autoref{tab:AR-resignations} are statistically different than zero at even the 10\% level. Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do do not always move in the same direction. For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rúa of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Mean cumulative abnormal returns surrounding regime changes}
\label{fig:CAR-mean}
\end{figure}

Second, since the direction of the pre-trends is unclear, we examine whether there are different pre-trends for events with positive stock reactions than for events with negative stock reactions. As shown in \autoref{fig:CAR-mean}, neither the ``positive'' nor ``negative'' events have pre-event CAR's that are statistically different from 0.

It is also worth noting that the post-event CAR(1,k) for $k\in(2,19)$ is not statistically significant for either the ``positive'' or the ``negative'' events. Almost all of the stock-market reaction occurs on the first day that the market could react to the event which suggests that markets respond quickly to political events. This, in turn, implies that markets are reacting to news efficiently and that an event-driven trading strategy would not be profitable.

To check for the possibility that my previous results were spurious, a final placebo check examines whether there are abnormal absolute returns on the event day when the event day is shifted forward and backwards in time. Events are shifted backwards by 5, 10, 15, 20, 25 and 30 trading days and forwards by 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55 and 60 trading days.\footnote{Event days are not shifted backwards by more than 30 trading days to ensure than every country in the sample can be included. When events are shifted backwards by more than 30 trading days mean abnormal absolute returns continue to cluster around 0.} Figure~\autoref{fig:time-placebos} graphs the abnormal absolute returns (labeled CAR(0,0) in the figure) against the number of days shifted.

The largest CAR(0,0) occurs when the events have not been shifted in time. Moreover, the backwards shifted event day abnormal absolute return is only statistically different from zero when the event day is shifted backwards by 5 days. On the other hand, the forwards shifted CAR(0,0) is statistically significant when the event day is shifted forward by 5, 10, 15 and 20 days. These findings are consistent with figure~\autoref{fig:volatility}, in which volatility began increasing around 5 trading days before the event and then started decreasing quickly about 20 trading days therafter.

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\vspace{-50pt}
\caption{Time-shifed placebos for absolute abnormal returns}
\label{fig:time-placebos}
\end{figure}

\section{Public Protests} \label{sec: Public Protests}
The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests. While the previous section showed that the resignations themselves had large effects on stock returns and volatility, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets. Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.

The most recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more. The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership. Examples of public discontent included demonstrations, marches, riots and non-violent civil disobedience, and labor strikes.

While the Egyptian Revolution may have positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous. As shown in \autoref{fig:CAR-Egypt}, abnormal returns the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after. To prevent further decline during the uprising, the Egyptian Stock Exchanged closed at the end of trading on January 27th. President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.

\begin{figure}[!ht]
\includegraphics{../figs/daily_mean_absreturn.pdf}
\caption{Cumulative abnormal returns during the Egyptian revolution}
\label{fig:CAR-Egypt}
\end{figure}

An important question is whether other popular uprisings have had similar adverse economic consequences. To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'état Events Handbook or the Archigos Version 2.9 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent. These events are listed in \autoref{tab:protest-list} in the appendix.

The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively. Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'état Events Handbook and Archigos Version 2.9. Additional Lexis Nexis searches were used to verify these descriptions. Start dates were determined through similar means.

In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices. The variable, \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive are and 0 otherwise. Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}

Column (1) suggests that public protests have no effect on stock returns. However, this occurs because some political movements increase stock prices while others decrease them. As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests. These estimates would be biased if protest dates are correlated with higher world or regional stock market indices. To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index. The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests. Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.

\begin{table}[!ht]
\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
  \hline
  \hline
\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
 & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
  \hline
Protest & 0.282 & 2.113*** & 1.961*** & 1.148*** \\
   & (0.781) & (0.648) & (0.643) & (0.385) \\
  Emerging Market &  &  & 0.216* &  \\
  Index &  &  & (0.129) &  \\
  \hline
  Event Fixed Effect? & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\
  Observations & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{2676} & \multicolumn{1}{c}{3537} \\
  Events & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{11} \\
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors clustered by event are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
\end{threeparttable}
\end{center}
\end{table}

\section{Conclusion}
This paper has examined the economic effects of irregular regime changes. It uses an event study approach to show that investors expect irregular regime changes to have large effects on equity returns. This methodology is less susceptible to endogeneity biases than studies that use cross country data.

The results are consistent with the idea that government competence is a random walk and that government changes have large impacts on investor confidence. Financial volatility surrounding regime changes, which is often characterized by large positive \textit{and} negative stock returns, suggests that irregular regime changes increase policy uncertainty. The variation in the direction of abnormal returns is consistent with the idea that not all governments are created equally. Abnormal returns are likely positive following resignations because those leaders were the most likely to be ``bad'' leaders.

Although this study is based on only 35 events, the size of the effects suggests that it should not be dismissed. Irregular regime changes are important economic events than can drastically alter the economic landscape. For instance, the 21.26\% increase in the Venezuelan Stock Index following the temporary ousting of Hugo Chavez in 2002 is its 4th largest increase since 1994. In comparison, the Hong Kong Stock Index (Hang Seng Index) decreased by 21.7\% following the 1989 massacre of Chinese protestors in Tiananmen square and the Dow Jones Industrial Average in the United States fell by 22.61\% on Black Monday (1997), the largest one-day drop in its history.

\appendix
\setcounter{table}{0}
\renewcommand\thetable{\Alph{section}.\arabic{table}}
\section{Appendix} \label{Appendix}
\begin{table}[!ht]
\caption{List of public protests preceding resignations} \label{tab:protest-list}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}llll}
  \hline
    \hline
\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Name}&\multicolumn{1}{c}{Start Date}&\multicolumn{1}{c}{End Date}\\
  \hline
Philippines & EDSA 1/Yellow Revolution & 2/22/1986 & 2/25/1986\\
Bangladesh & Bangladeshi Spring of 1990 & 11/27/1990 & 12/7/1990\\
Thailand & Black May & 5/17/1992 & 5/20/1992\\
Indonesia & Indonesian Riots & 5/12/1998 & 5/21/1998\\
Philippines & EDSA II & 1/17/2001 & 1/20/2001\\
Argentina & Argentina Riots & 12/16/2001 & 12/20/2001\\
Ukraine & Orange Revolution & 11/22/2004 & 1/23/2005\\
Ecuador & Ecuadorian Protests & 4/13/2005 & 4/20/2005\\
Nepal & Nepalese People's Revolution & 4/6/2006 & 4/24/2006\\
Tunisia & Tunisian Revolution & 12/18/2010 & 1/14/2011\\
Egypt & Egyptian Revolution & 1/25/2011 & 2/11/2001\\
   \hline
   \hline
\end{tabular*}
\scriptsize
\end{threeparttable}
\end{center}
\end{table}

\subsection{Synthetic Control Portfolio}
Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock list}. Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}

\pdfbookmark[1]{References}{References}
\bibliography{bibliography}

\end{document}

### 2017-02-11 code/03-ar.R

@@ -1,4 +1,5 @@
 rm(list = ls())
+library("xtable")
 load("data/data-clean.RData")
 source("code/func.R")
 
@@ -20,7 +21,7 @@ for (i in 1:ncol(ar)){
                                             .(date, p)],
                           event_date = regime.change$stock_date[i])
 }
-td.ew <- seq(-event.window, event.window -1 )
+td.ew <- seq(-event.window, event.window -1)
 
 # ABNORMAL RETURNS TABLES ------------------------------------------------------
 # coups
@@ -30,6 +31,8 @@ artable.coups <- ar_table(td = td.ew, ar = ar[, coup.index],
                           country = regime.change[coup.index, country],
                           date = regime.change[coup.index, stock_date], 
                           coup = TRUE)
+myprint.xtable(artable.coups$car, file = "tables/artable-coups-car.txt")
+myprint.xtable(artable.coups$car.mean, file = "tables/artable-coups-car-mean.txt")
 
 # assassinations
 ass.index <- which(regime.change$type == "Assassination")
@@ -37,6 +40,8 @@ artable.ass <- ar_table(td = td.ew, ar = ar[, ass.index],
                         sigma = sigma[ass.index], dtr = dtr[ass.index],
                         country = regime.change[ass.index, country],
                         date = regime.change[ass.index, stock_date])
+myprint.xtable(artable.ass$car, file = "tables/artable-ass-car.txt")
+myprint.xtable(artable.ass$car.mean, file = "tables/artable-ass-car-mean.txt")
 
 # resignations
 res.index <- which(regime.change$type == "Resignation")
@@ -44,6 +49,8 @@ artable.res <- ar_table(td = td.ew, ar = ar[, res.index],
                         sigma = sigma[res.index], dtr = dtr[res.index],
                         country = regime.change[res.index, country],
                         date = regime.change[res.index, stock_date])
+myprint.xtable(artable.res$car, file = "tables/artable-res-car.txt")
+myprint.xtable(artable.res$car.mean, file = "tables/artable-res-car-mean.txt")
 
 # VENEZUELA PARTIAL COUP -------------------------------------------------------
 ven <- event[ticker == "_IBCD" & stock_date == "2002-04-12"]

### 2017-02-11 code/func.R

@@ -1,5 +1,13 @@
+# xtable print -----------------------------------------------------------------
+myprint.xtable <- function(x, file){
+  print(xtable(x), 
+        include.rownames = FALSE, include.colnames = FALSE,
+        only.contents = TRUE, sanitize.text.function = identity, hline.after = NULL,
+        file = file)
+}
+
 # MATRIX WITH PARENTHESES IN STANDARD ERRORS -----------------------------------
-MatrixSE <- function(est, se){
+matrix_se <- function(est, se){
   m <- matrix(as.vector(rbind(as.vector(est), 
                               paste0("(", as.vector(se), ")"))),
               nrow= 2 * nrow(est))
@@ -34,17 +42,18 @@ return_by_td <- function(stockdata, event_date, pre_event, post_event){
 # DAYS TO REBOUND --------------------------------------------------------------
 days_to_rebound <- function(stockdata, event_date){
   # Note: first column of stockdata is a date and second is price
-  setnames(stockdata, c("date", "p"))
+  x = copy(stockdata)
+  setnames(x, c("date", "p"))
   
   # trading days
-  stockdata[, n := seq(1, .N)]
-  event.td <- which.max(stockdata$date - event_date >= 0) 
-  stockdata[, td := n - event.td]
+  x[, n := seq(1, .N)]
+  event.td <- which.max(x$date - event_date >= 0) 
+  x[, td := n - event.td]
   
   # days to rebound
-  p.init <- stockdata[td == -1, p]
-  if (stockdata[td == 0, p]/p.init < 1){
-    return(which.max(stockdata[td >= 0, p] >= p.init))
+  p.init <- x[td == -1, p]
+  if (x[td == 0, p]/p.init < 1){
+    return(which.max(x[td >= 0, p] >= p.init))
   } else{
     return(NA)
   }
@@ -76,10 +85,17 @@ event_study <- function(stockdata, event_window, estimation_window, event_date,
 }  
 
 # ABNORMAL RETURN TABLE --------------------------------------------------------
+# LaTeX table of abnormal returns
+#
+# Args:
+#   td: vector of trading days relative to event day for abnormal returns.
+#   ar: matrix of abnormal returns.
+#   sigma: standard error returns.
+#   dtr: days to rebound.
[…]

### 2017-02-12 code/01-clean.R
Add code for protest regression

@@ -22,9 +22,14 @@ leaders <- fread("data-raw/leaders_duration.csv")
 
 # revolution dates
 rev <- fread("data-raw/revolutions.csv")
-rev[, num := seq(1, length(Country), 1)]
+rev[, num := seq(1, length(country), 1)]
+rev[, start_date := as.Date(start_date,"%m/%d/%Y")]
+rev[, end_date := as.Date(end_date,"%m/%d/%Y")]
 
 # CLEAN DATA -------------------------------------------------------------------
+# inflation adjusted returns
+#indices[, dr := (real_p - shift(real_p))/shift(real_p), by = "ticker"]
+
 ## continuously compounded returns
 indices[, dr := 100 * log(dr+1)]
 indices[, abs_dr := abs(dr)]
@@ -70,5 +75,5 @@ regime.change <- event[type == "Coup" | type == "Assassination" |
                        .(country, ticker, stock_date, type)]
 
 # SAVE DATA --------------------------------------------------------------------
-save(country.lookup, event, index, regime.change, 
+save(country.lookup, event, index, regime.change, rev,
      file = "data/data-clean.RData")

### 2017-02-12 code/func.R

@@ -10,7 +10,7 @@ myprint.xtable <- function(x, file){
 matrix_se <- function(est, se){
   m <- matrix(as.vector(rbind(as.vector(est), 
                               paste0("(", as.vector(se), ")"))),
-              nrow= 2 * nrow(est))
+              nrow = 2 * nrow(est))
   return(m)
 }
 
@@ -42,18 +42,17 @@ return_by_td <- function(stockdata, event_date, pre_event, post_event){
 # DAYS TO REBOUND --------------------------------------------------------------
 days_to_rebound <- function(stockdata, event_date){
   # Note: first column of stockdata is a date and second is price
-  x = copy(stockdata)
-  setnames(x, c("date", "p"))
+  setnames(stockdata, c("date", "p"))
   
   # trading days
-  x[, n := seq(1, .N)]
-  event.td <- which.max(x$date - event_date >= 0) 
-  x[, td := n - event.td]
+  stockdata[, n := seq(1, .N)]
+  event.td <- which.max(stockdata$date - event_date >= 0) 
+  stockdata[, td := n - event.td]
   
   # days to rebound
-  p.init <- x[td == -1, p]
+  p.init <- stockdata[td == -1, p]
   if (x[td == 0, p]/p.init < 1){
-    return(which.max(x[td >= 0, p] >= p.init))
+    return(which.max(stockdata[td >= 0, p] >= p.init))
   } else{
     return(NA)
   }

### 2017-02-12 main.R

@@ -3,5 +3,8 @@ source("code/func.R")
 if (!file.exists("data/data-clean.RData")){
   source("code/01-clean.R")
 }
-source("code/02-desc_stats.R")
+source("code/02-desc-stats.R")
 source("code/03-ar.R")
+source("code/04-volatility.R")
+source("code/05-sensitivity.R")
+source("code/06-protests.R")

### 2017-02-12 code/06-protests.R
Add code for protest regression

@@ -1,0 +1,26 @@
+rm(list = ls())
+load("data/data-clean.RData")
+source("code/func.R")
+library("plm")
+
+# EFFECT OF PUBLIC PROTESTS ON STOCK DATA --------------------------------------
+# data 
+index.rev <- vector(mode = "list", length(rev$ticker))
+for (i in 1:length(rev$ticker)){
+  index.rev[[i]] <- index[ticker == rev$ticker[i] & date >= (rev$start_date[i] - 250)
+                          & date <= (rev$end_date[i] + 250)]
+  index.rev[[i]][, rev_no := i]
+  index.rev[[i]][, event := ifelse(date >= rev$start_date[i] & 
+                                     date <= rev$end_date[i], 1, 0)]
+}
+index.rev <- rbindlist(index.rev)
+index.rev <- pdata.frame(index.rev, index = c("rev_no", "date"))
+
+# regressions
+revfit1 <- plm(dr ~ event, data = index.rev, model = "within")
+revfit2 <- plm(abs_dr ~ event, data = index.rev, model = "within")
+revfit3 <- plm(abs_dr ~ event + emerg_abs_dr, data = index.rev, model = "within")
+
+# table of results
+coef <- 2
+#coeftest(model.plm, vcov=vcovHC(model.plm,type="HC0",cluster="group"))

### 2017-02-13 doc/paper.tex
Code for protest regression table

@@
   \hline
-Protest & 0.282 & 2.113*** & 1.961*** & 1.148*** \\
-   & (0.781) & (0.648) & (0.643) & (0.385) \\
-  Emerging Market &  &  & 0.216* &  \\
-  Index &  &  & (0.129) &  \\
-  \hline
-  Event Fixed Effect? & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\
-  Observations & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{3537} & \multicolumn{1}{c}{2676} & \multicolumn{1}{c}{3537} \\
-  Events & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{11} \\
+\ExpandableInput{../tables/protest-regtable.txt}
    \hline

### 2017-02-13 code/06-protests.R

@@ -2,6 +2,8 @@ rm(list = ls())
 load("data/data-clean.RData")
 source("code/func.R")
 library("plm")
+library("lmtest")
+library("broom")
 
 # EFFECT OF PUBLIC PROTESTS ON STOCK DATA --------------------------------------
 # data 
@@ -20,7 +22,23 @@ index.rev <- pdata.frame(index.rev, index = c("rev_no", "date"))
 revfit1 <- plm(dr ~ event, data = index.rev, model = "within")
 revfit2 <- plm(abs_dr ~ event, data = index.rev, model = "within")
 revfit3 <- plm(abs_dr ~ event + emerg_abs_dr, data = index.rev, model = "within")
+revfit <- list(revfit1, revfit2, revfit3)
+nfits <- length(revfit)
 
 # table of results
-coef <- 2
-#coeftest(model.plm, vcov=vcovHC(model.plm,type="HC0",cluster="group"))
+vars <- c("event", "emerg_abs_dr")
+varsl <- c("Protest", "Emerging market index")
+lookup <- data.frame(term = vars, varname = varsl, id = seq(1, length(vars)))
+revfit.table <- reg_table(models = revfit, lookup = lookup)
+n <- nrow(revfit.table)
+fe.lab <- rep(paste0("\\multicolumn{1}{c}{", "Yes}"), nfits)
+fe.lab <- c("Event fixed effect?", fe.lab)
+revfit.table <- rbind(revfit.table[1:(n-1), ], fe.lab, revfit.table[n, ])
+events <- rep(NA, nfits)
+for (i in 1:length(events)){
+  events[i] <- pdim(revfit[[i]]$model)$nT$n
+}
+events <- paste0("\\multicolumn{1}{c}{", events, "}")
+revfit.table <- rbind(revfit.table, c("Events", events))
+myprint.xtable(revfit.table, file = "tables/protest-regtable.txt")
+

### 2017-02-13 code/func.R

@@ -8,9 +8,12 @@ myprint.xtable <- function(x, file){
 
 # MATRIX WITH PARENTHESES IN STANDARD ERRORS -----------------------------------
 matrix_se <- function(est, se){
+  est <- gsub(" ", "", est)
+  se <- gsub(" ", "", se)
   m <- matrix(as.vector(rbind(as.vector(est), 
                               paste0("(", as.vector(se), ")"))),
               nrow = 2 * nrow(est))
+  m <- gsub("\\()", "", m)
   return(m)
 }
 
@@ -163,5 +166,57 @@ Car <- function(td, ar, sigma){
   car <- c(car.b, car.f)
   car.se <- c(car.b.se, car.f.se)
   return(list(car = car, car.se = car.se))
+}
+
+# REGRESSION TABLE WITH STANDARD ERRORS IN PARENTEHSES--------------------------
+# Regression table with standard errors in parentheses
+#
+# Args:
+#   models: List of models
+#   lookup: Option data.frame to lookup variable names. First column is term, the name
+#           of variables in the model. Second column is varname, the name of the variable
+#           to display in the LaTex table. Third column is id, which is the order to display
+#           the variables.
+#   digits: Digits to round coefficients and standard errors to
+#
+# Returns: 
+#   LaTeX table with coefficients (se's in parentheses) and number of observations for each
+#   model listed.
+reg_table <- function(models, lookup = NULL, digits = 3){
+  n.est <- length(models)
+  coef <- se <- vector(mode = "list", length = n.est)
+  obs <- rep(NA, n.est)
+  #r2 <- rep(NA, n.est)
+  for (i in 1:n.est){
+    est <- coeftest(models[[i]], vcov = vcovHC(models[[i]], type = "HC0",
+                                                   cluster="group"))
+    est <- data.frame(tidy(est))
+    colnames(est) <- c("term", paste0(colnames(est)[-1], i))
+    if (!is.null(lookup)){
+      est <- merge(est, lookup, by = "term", all.x = TRUE)
+      est$term <- est$varname
+      est$varname <- NULL
+    }
+    coef[[i]] <- est[, c("term", "id", paste0("estimate", i))]
+    se[[i]] <- est[, c("term", "id", paste0("std.error", i))]
+    obs[i] <- nobs(models[[i]])
+  }
[…]

### 2017-02-14 code/03-ar.R
CAR during Egyptian revolution

@@ -54,11 +54,10 @@ myprint.xtable(artable.res$car.mean, file = "tables/artable-res-car-mean.txt")
 
 # VENEZUELA PARTIAL COUP -------------------------------------------------------
 ven <- event[ticker == "_IBCD" & stock_date == "2002-04-12"]
-ven.es <- event_study(stockdata = index[ticker == ven$ticker, 
-                                       .(date, dr)],
+ven.es <- event_study(stockdata = index[ticker == ven$ticker, .(date, dr)],
                      event_window = event.window, estimation_window = est.window,
                      event_date = ven$stock_date, model = "constant")  
-ven.es <- c(ven.es, Car(td = td.ew, ar = ven.es$ar, sigma = ven.es$sigma))
+ven.es <- c(ven.es, car(td = td.ew, ar = ven.es$ar, sigma = ven.es$sigma))
 tmp <- data.table(td = td.ew,  ar = ven.es$ar, ar.se = ven.es$sigma)
 tmp[, lower := ar - qnorm(.975) * ar.se]
 tmp[, upper := ar + qnorm(.975) * ar.se]

### 2017-02-14 code/06-protests.R

@@ -1,11 +1,47 @@
 rm(list = ls())
 load("data/data-clean.RData")
 source("code/func.R")
+library("data.table")
 library("plm")
 library("lmtest")
 library("broom")
 
-# EFFECT OF PUBLIC PROTESTS ON STOCK DATA --------------------------------------
+# EGYPTIAN REVOLUTION ----------------------------------------------------------
+egypt.es <-  event_study(stockdata = index[ticker == "_EFGID", .(date, dr)],
+                    event_window = 20, estimation_window = 200,
+                    event_date = rev[name == "Egyptian Revolution", start_date],
+                    model = "constant")   
+egypt.es <- c(egypt.es, car(td = egypt.es$td, ar = egypt.es$ar, sigma = egypt.es$sigma))
+egypt.es <- data.table(date = egypt.es$date, td = egypt.es$td,  car = egypt.es$car, 
+                  car.se = egypt.es$car.se)
+egypt.es[, lcar := car - qnorm(.975) * car.se]
+egypt.es[, ucar := car + qnorm(.975) * car.se]
+p <- ggplot(egypt.es, aes(x = date, y = car)) + geom_line() +
+  geom_point(size = .8) +
+  geom_ribbon(aes(ymin = lcar, ymax = ucar), alpha=0.2) +
+  xlab("Date") + ylab("CAR (%)") +
+  geom_hline(aes(yintercept = 0), linetype = 2) + 
+  annotate("text", x = as.Date("02/10/2011", "%m/%d/%Y"), 
+           y = 5, label = "Jan 25: uprising begins", size = 3) +
+  geom_segment(aes(x = as.Date("02/07/2011", "%m/%d/%Y"), y = 4, 
+                   xend = as.Date("01/25/2011", "%m/%d/%Y") , 
+                   yend = 0),
+               arrow = arrow(length = unit(0.01, "npc"))) +
+  annotate("text", x = as.Date("02/25/2011", "%m/%d/%Y"), 
+           y = -14, label = "Feb 11: Mubarak resigns", size = 3) +
+  geom_segment(aes(x = as.Date("02/25/2011", "%m/%d/%Y"), y = -15, 
+                   xend = as.Date("02/11/2011", "%m/%d/%Y") , 
+                   yend = -20),
+               arrow = arrow(length = unit(0.01, "npc"))) +
+  annotate("text", x = as.Date("03/15/2011", "%m/%d/%Y"), 
[…]

### 2017-02-14 code/func.R

@@ -54,7 +54,7 @@ days_to_rebound <- function(stockdata, event_date){
   
   # days to rebound
   p.init <- stockdata[td == -1, p]
-  if (x[td == 0, p]/p.init < 1){
+  if (stockdata[td == 0, p]/p.init < 1){
     return(which.max(stockdata[td >= 0, p] >= p.init))
   } else{
     return(NA)
@@ -80,10 +80,10 @@ event_study <- function(stockdata, event_window, estimation_window, event_date,
   }
   
   # abnormal returns
-  event.data <- stockdata[td >= -event_window & td < event_window, .(td, r)]
+  event.data <- stockdata[td >= -event_window & td < event_window, .(date, td, r)]
   ar <- event.data$r - predict(lm, event.data)
   sigma <- summary(lm)$sigma
-  return(list(ar = ar, sigma = sigma))
+  return(list(date = event.data$date, td = event.data$td, ar = ar, sigma = sigma))
 }  
 
 # ABNORMAL RETURN TABLE --------------------------------------------------------
@@ -158,14 +158,17 @@ ar_table <- function(td, ar, sigma, dtr, country, date, coup = FALSE){
 }
 
 # CUMULATIVE ABNORMAL RETURNS --------------------------------------------------
-Car <- function(td, ar, sigma){
-  car.b <- rev(cumsum(rev(ar[which(td < 0)])))
+car <- function(td, ar, sigma){
+  car.b <- rev(cumsum(rev(ar[which(td < -1)])))
   car.b.se <- rev(sigma * sqrt(seq(1, length(car.b))))
   car.f <- cumsum(ar[which(td >= 0)])
   car.f.se <- sigma * sqrt(seq(1, length(car.f)))
-  car <- c(car.b, car.f)
-  car.se <- c(car.b.se, car.f.se)
-  return(list(car = car, car.se = car.se))
+  car.fixed <- ar[which(td == -1)]
+  car.fixed.se <- 0
+  car <- c(car.b, car.fixed, car.f)
+  car <- car - car.fixed
+  car.se <- c(car.b.se, car.fixed.se, car.f.se)
+  return(list(car = car, car.se =  car.se))
 }
 
 # REGRESSION TABLE WITH STANDARD ERRORS IN PARENTEHSES--------------------------

### 2017-02-14 code/03-ar.R
Calculate CAR within event_study function

@@ -1,6 +1,9 @@
 rm(list = ls())
 library("xtable")
+library("data.table")
+library("ggplot2")
 load("data/data-clean.RData")
+theme_set(theme_bw())
 source("code/func.R")
 
 # EVENT STUDY ------------------------------------------------------------------
@@ -9,6 +12,7 @@ event.window <- 20
 est.window <- 200
 sigma <- rep(NA, nrow(regime.change))
 ar <- matrix(NA, nrow = 2 * event.window, ncol = nrow(regime.change))
+car <- car.se <-  ar
 dtr <- rep(NA, nrow(regime.change))
 for (i in 1:ncol(ar)){
   tmp <-  event_study(stockdata = index[ticker == regime.change$ticker[i], 
@@ -17,11 +21,15 @@ for (i in 1:ncol(ar)){
                      event_date = regime.change$stock_date[i], model = "constant")   
   sigma[i] <- tmp$sigma
   ar[, i] <- tmp$ar
+  car[, i] <- tmp$car
+  car.se[, i] <- tmp$car.se
   dtr[i] <- days_to_rebound(stockdata = index[ticker == regime.change$ticker[i], 
                                             .(date, p)],
                           event_date = regime.change$stock_date[i])
 }
 td.ew <- seq(-event.window, event.window -1)
+regime.change.es <- list(td = td.ew, sigma = sigma, car = car, car.se = car.se) 
+save(regime.change.es, file = "output/regime-change-event-study.RData")
 
 # ABNORMAL RETURNS TABLES ------------------------------------------------------
 # coups
@@ -57,12 +65,11 @@ ven <- event[ticker == "_IBCD" & stock_date == "2002-04-12"]
 ven.es <- event_study(stockdata = index[ticker == ven$ticker, .(date, dr)],
                      event_window = event.window, estimation_window = est.window,
                      event_date = ven$stock_date, model = "constant")  
-ven.es <- c(ven.es, car(td = td.ew, ar = ven.es$ar, sigma = ven.es$sigma))
-tmp <- data.table(td = td.ew,  ar = ven.es$ar, ar.se = ven.es$sigma)
-tmp[, lower := ar - qnorm(.975) * ar.se]
-tmp[, upper := ar + qnorm(.975) * ar.se]
[…]

### 2017-02-14 code/05-sensitivity.R

@@ -1,0 +1,7 @@
+rm(list = ls())
+load("output/regime-change-event-study.RData")
+library("data.table")
+source("code/func.R")
+theme_set(theme_bw())
+
+# CAR SURROUNDING REGIME CHANGES -----------------------------------------------

### 2017-02-14 code/06-protests.R

@@ -5,13 +5,13 @@ library("data.table")
 library("plm")
 library("lmtest")
 library("broom")
+theme_set(theme_bw())
 
 # EGYPTIAN REVOLUTION ----------------------------------------------------------
 egypt.es <-  event_study(stockdata = index[ticker == "_EFGID", .(date, dr)],
                     event_window = 20, estimation_window = 200,
                     event_date = rev[name == "Egyptian Revolution", start_date],
                     model = "constant")   
-egypt.es <- c(egypt.es, car(td = egypt.es$td, ar = egypt.es$ar, sigma = egypt.es$sigma))
 egypt.es <- data.table(date = egypt.es$date, td = egypt.es$td,  car = egypt.es$car, 
                   car.se = egypt.es$car.se)
 egypt.es[, lcar := car - qnorm(.975) * car.se]

### 2017-02-14 code/func.R

@@ -83,7 +83,9 @@ event_study <- function(stockdata, event_window, estimation_window, event_date,
   event.data <- stockdata[td >= -event_window & td < event_window, .(date, td, r)]
   ar <- event.data$r - predict(lm, event.data)
   sigma <- summary(lm)$sigma
-  return(list(date = event.data$date, td = event.data$td, ar = ar, sigma = sigma))
+  car <- calc_car(event.data$td, ar, sigma)
+  return(list(date = event.data$date, td = event.data$td, ar = ar, sigma = sigma,
+              car = car$car, car.se = car$car.se))
 }  
 
 # ABNORMAL RETURN TABLE --------------------------------------------------------
@@ -158,7 +160,7 @@ ar_table <- function(td, ar, sigma, dtr, country, date, coup = FALSE){
 }
 
 # CUMULATIVE ABNORMAL RETURNS --------------------------------------------------
-car <- function(td, ar, sigma){
+calc_car <- function(td, ar, sigma){
   car.b <- rev(cumsum(rev(ar[which(td < -1)])))
   car.b.se <- rev(sigma * sqrt(seq(1, length(car.b))))
   car.f <- cumsum(ar[which(td >= 0)])

### 2017-02-16 code/03-ar.R
Sensitivity positive/negative CAR

@@ -21,14 +21,15 @@ for (i in 1:ncol(ar)){
                      event_date = regime.change$stock_date[i], model = "constant")   
   sigma[i] <- tmp$sigma
   ar[, i] <- tmp$ar
-  car[, i] <- tmp$car
-  car.se[, i] <- tmp$car.se
+  tmp.car <- car_prepost(tmp$td, tmp$ar, tmp$sigma)
+  car[, i] <- tmp.car$car
+  car.se[, i] <- tmp.car$car.se
   dtr[i] <- days_to_rebound(stockdata = index[ticker == regime.change$ticker[i], 
                                             .(date, p)],
                           event_date = regime.change$stock_date[i])
 }
 td.ew <- seq(-event.window, event.window -1)
-regime.change.es <- list(td = td.ew, sigma = sigma, car = car, car.se = car.se) 
+regime.change.es <- list(td = td.ew, sigma = sigma, ar = ar) 
 save(regime.change.es, file = "output/regime-change-event-study.RData")
 
 # ABNORMAL RETURNS TABLES ------------------------------------------------------
@@ -70,6 +71,6 @@ ven.es[, lar := ar - qnorm(.975) * ar.se]
 ven.es[, uar := ar + qnorm(.975) * ar.se]
 p <- ggplot(ven.es[abs(td) <= 10], aes(x = td, y = ar)) + 
   geom_pointrange(aes(ymin = lar, ymax = uar), size = .2) +
-  xlab("Days") + ylab("AR (%)") +
+  xlab("Trading days") + ylab("AR (%)") +
   geom_hline(aes(yintercept = 0), linetype = 2)
 ggsave("figs/venezuela_coup_attempt_2002.pdf", p, height = 5, width = 7)

### 2017-02-16 code/05-sensitivity.R

@@ -1,7 +1,36 @@
 rm(list = ls())
 load("output/regime-change-event-study.RData")
 library("data.table")
+library("ggplot2")
 source("code/func.R")
 theme_set(theme_bw())
 
 # CAR SURROUNDING REGIME CHANGES -----------------------------------------------
+td0.indx <- which(regime.change.es$td == 0)
+pos.events <- which(regime.change.es$ar[td0.indx, ] >= 0)
+neg.events <- which(regime.change.es$ar[td0.indx, ] < 0)
+
+# positive events
+car.mean.pos <- mean_car_prepost(ar = regime.change.es$ar[, pos.events],
+                         sigma = regime.change.es$sigma[pos.events], 
+                         td = regime.change.es$td)
+car.mean.pos[, lcar_mean := car_mean - qnorm(.975) * car_mean_se]
+car.mean.pos[, ucar_mean := car_mean + qnorm(.975) * car_mean_se]
+car.mean.pos[, lab := "Positive event"]
+
+# negative events
+car.mean.neg <- mean_car_prepost(ar = regime.change.es$ar[, neg.events],
+                                 sigma = regime.change.es$sigma[neg.events], 
+                                 td = regime.change.es$td)
+car.mean.neg[, lcar_mean := car_mean - qnorm(.975) * car_mean_se]
+car.mean.neg[, ucar_mean := car_mean + qnorm(.975) * car_mean_se]
+car.mean.neg[, lab := "Negative event"]
+
+# plot
+car.mean <- rbind(car.mean.neg, car.mean.pos)
+p.meancar <- ggplot(car.mean, aes(x = td, y = car_mean)) + geom_line() +
+  geom_point(size = .8) + facet_wrap(~lab) +
+  geom_ribbon(aes(ymin = lcar_mean, ymax = ucar_mean), alpha = 0.2) +
+  xlab("Trading days") + ylab("Mean CAR (%)") +
+  geom_hline(aes(yintercept = 0), linetype = 2)
+ggsave("figs/mean-car-pos-neg.pdf", p.meancar, height = 5, width = 7)

### 2017-02-16 code/06-protests.R

@@ -12,6 +12,7 @@ egypt.es <-  event_study(stockdata = index[ticker == "_EFGID", .(date, dr)],
                     event_window = 20, estimation_window = 200,
                     event_date = rev[name == "Egyptian Revolution", start_date],
                     model = "constant")   
+egypt.es <- c(egypt.es, car_prepost(egypt.es$td, egypt.es$ar, egypt.es$sigma))
 egypt.es <- data.table(date = egypt.es$date, td = egypt.es$td,  car = egypt.es$car, 
                   car.se = egypt.es$car.se)
 egypt.es[, lcar := car - qnorm(.975) * car.se]

### 2017-02-16 code/func.R

@@ -62,6 +62,8 @@ days_to_rebound <- function(stockdata, event_date){
 }
 
 # EVENT STUDY ------------------------------------------------------------------
+# Returns: list of date, trading day, standard error of regression, and
+#          abnormal return
 event_study <- function(stockdata, event_window, estimation_window, event_date,
                        model = "constant"){
   # Note: first column of stockdata must be a date variable
@@ -83,9 +85,7 @@ event_study <- function(stockdata, event_window, estimation_window, event_date,
   event.data <- stockdata[td >= -event_window & td < event_window, .(date, td, r)]
   ar <- event.data$r - predict(lm, event.data)
   sigma <- summary(lm)$sigma
-  car <- calc_car(event.data$td, ar, sigma)
-  return(list(date = event.data$date, td = event.data$td, ar = ar, sigma = sigma,
-              car = car$car, car.se = car$car.se))
+  return(list(date = event.data$date, td = event.data$td, ar = ar, sigma = sigma))
 }  
 
 # ABNORMAL RETURN TABLE --------------------------------------------------------
@@ -160,7 +160,7 @@ ar_table <- function(td, ar, sigma, dtr, country, date, coup = FALSE){
 }
 
 # CUMULATIVE ABNORMAL RETURNS --------------------------------------------------
-calc_car <- function(td, ar, sigma){
+car_prepost <- function(td, ar, sigma){
   car.b <- rev(cumsum(rev(ar[which(td < -1)])))
   car.b.se <- rev(sigma * sqrt(seq(1, length(car.b))))
   car.f <- cumsum(ar[which(td >= 0)])
@@ -172,6 +172,29 @@ calc_car <- function(td, ar, sigma){
   car.se <- c(car.b.se, car.fixed.se, car.f.se)
   return(list(car = car, car.se =  car.se))
 }
+
+# MEAN CAR ---------------------------------------------------------------------
+car_mean <- function(ar, sigma) {
+  ar.mean <- apply(ar, 1, mean)
+  car.mean <- cumsum(ar.mean)
+  ar.mean.var <- 1/nrow(ar)^2 * sum(sigma^2)
+  car.mean.se <- sqrt(ar.mean.var * seq(1, nrow(ar)))
+  return(data.table(car_mean = car.mean, car_mean_se = car.mean.se))
+}
+
[…]

### 2017-02-16 code/05-sensitivity.R
Add rank test for AR

@@ -1,9 +1,31 @@
 rm(list = ls())
 load("output/regime-change-event-study.RData")
+load("data/data-clean.RData")
 library("data.table")
 library("ggplot2")
 source("code/func.R")
 theme_set(theme_bw())
+
+# NON-PARAMETRIC TESTS ---------------------------------------------------------
+ed <- which(regime.change.es$td == 0)
+
+# coups 
+coup.index <- which(regime.change$type == "Coup")
+ar.mean.coup <- mean(regime.change.es$ar[ed, coup.index])
+ranktest.coup <- rank_test(regime.change.es$ar[, coup.index], 
+                              regime.change.es$td)
+
+# assassinations
+ass.index <- which(regime.change$type == "Assassination")
+ar.mean.ass <- mean(regime.change.es$ar[ed, ass.index])
+ranktest.ass <- rank_test(regime.change.es$ar[, ass.index], 
+                           regime.change.es$td)
+
+# resignations
+res.index <- which(regime.change$type == "Resignation")
+ar.mean.res <- mean(regime.change.es$ar[ed, res.index])
+ranktest.res <- rank_test(regime.change.es$ar[, res.index], 
+                          regime.change.es$td)
 
 # CAR SURROUNDING REGIME CHANGES -----------------------------------------------
 td0.indx <- which(regime.change.es$td == 0)

### 2017-02-16 code/func.R

@@ -196,7 +196,7 @@ mean_car_prepost <- function(ar, sigma, td){
 }
   
 
-# REGRESSION TABLE WITH STANDARD ERRORS IN PARENTEHSES--------------------------
+# REGRESSION TABLE WITH STANDARD ERRORS IN PARENTEHSES -------------------------
 # Regression table with standard errors in parentheses
 #
 # Args:
@@ -248,3 +248,15 @@ reg_table <- function(models, lookup = NULL, digits = 3){
   return(table)
 }
   
+# RANK TEST --------------------------------------------------------------------
+rank_test <- function(ar, td){
+  L2 <- nrow(ar)
+  exp.rank <- (L2 + 1)/2
+  ar.rank <- apply(ar, 2, rank)
+  diff <- ar.rank - exp.rank
+  diff.mean <- apply(diff, 1, mean)
+  sk <- sqrt(mean(diff.mean^2))
+  theta <- diff.mean[which(td == 0)]/sk
+  pval <- 2 * (1 - pnorm(abs(theta)))
+  return(pval)
+}

### 2017-02-17 code/03-ar.R
Add sign test

@@ -10,17 +10,23 @@ source("code/func.R")
 # calculate abnormal returns and days to rebound
 event.window <- 20
 est.window <- 200
-sigma <- rep(NA, nrow(regime.change))
-ar <- matrix(NA, nrow = 2 * event.window, ncol = nrow(regime.change))
+sigma <- sigma.abs <- rep(NA, nrow(regime.change))
+ar <- ar.abs <- matrix(NA, nrow = 2 * event.window, ncol = nrow(regime.change))
 car <- car.se <-  ar
 dtr <- rep(NA, nrow(regime.change))
 for (i in 1:ncol(ar)){
-  tmp <-  event_study(stockdata = index[ticker == regime.change$ticker[i], 
+  tmp <- event_study(stockdata = index[ticker == regime.change$ticker[i], 
                                        .(date, dr)],
                      event_window = event.window, estimation_window = est.window,
-                     event_date = regime.change$stock_date[i], model = "constant")   
+                     event_date = regime.change$stock_date[i], model = "constant") 
+  tmp.abs <- event_study(stockdata = index[ticker == regime.change$ticker[i], 
+                                           .(date, abs(dr))],
+                         event_window = event.window, estimation_window = est.window,
+                         event_date = regime.change$stock_date[i], model = "constant")
   sigma[i] <- tmp$sigma
+  sigma.abs[i] <- tmp.abs$sigma
   ar[, i] <- tmp$ar
+  ar.abs[, i] <- tmp.abs$ar
   tmp.car <- car_prepost(tmp$td, tmp$ar, tmp$sigma)
   car[, i] <- tmp.car$car
   car.se[, i] <- tmp.car$car.se
@@ -30,7 +36,8 @@ for (i in 1:ncol(ar)){
 }
 td.ew <- seq(-event.window, event.window -1)
 regime.change.es <- list(td = td.ew, sigma = sigma, ar = ar) 
-save(regime.change.es, file = "output/regime-change-event-study.RData")
+regime.change.es.abs <- list(td = td.ew, sigma = sigma.abs, ar = ar.abs)
+save(regime.change.es, regime.change.es.abs, file = "output/regime-change-event-study.RData")
 
 # ABNORMAL RETURNS TABLES ------------------------------------------------------
 # coups

### 2017-02-17 code/05-sensitivity.R

@@ -12,20 +12,29 @@ ed <- which(regime.change.es$td == 0)
 # coups 
 coup.index <- which(regime.change$type == "Coup")
 ar.mean.coup <- mean(regime.change.es$ar[ed, coup.index])
-ranktest.coup <- rank_test(regime.change.es$ar[, coup.index], 
+rankpval.coup <- rank_test(regime.change.es$ar[, coup.index], 
                               regime.change.es$td)
+signpval.coup <- sign_test(regime.change.es$ar[ed, coup.index], "negative")
 
 # assassinations
 ass.index <- which(regime.change$type == "Assassination")
 ar.mean.ass <- mean(regime.change.es$ar[ed, ass.index])
 ranktest.ass <- rank_test(regime.change.es$ar[, ass.index], 
                            regime.change.es$td)
+signpval.ass <- sign_test(regime.change.es$ar[ed, ass.index], "negative")
 
 # resignations
 res.index <- which(regime.change$type == "Resignation")
 ar.mean.res <- mean(regime.change.es$ar[ed, res.index])
 ranktest.res <- rank_test(regime.change.es$ar[, res.index], 
                           regime.change.es$td)
+signpval.res <- sign_test(regime.change.es$ar[ed, res.index], "positive")
+
+# absolute value
+ar.mean.abs <- mean(regime.change.es.abs$ar[ed, ])
+ranktest.res <- rank_test(regime.change.es.abs$ar, 
+                          regime.change.es.abs$td)
+signpval.res <- sign_test(regime.change.es.abs$ar[ed, ], "positive")
 
 # CAR SURROUNDING REGIME CHANGES -----------------------------------------------
 td0.indx <- which(regime.change.es$td == 0)

### 2017-02-17 code/func.R

@@ -260,3 +260,18 @@ rank_test <- function(ar, td){
   pval <- 2 * (1 - pnorm(abs(theta)))
   return(pval)
 }
+
+# SIGN TEST --------------------------------------------------------------------
+sign_test <- function(ar0, direction = c("positive", "negative")){
+  direction = match.arg(direction)
+  n <- length(ar0)
+  if (direction == "positive"){
+    x <- sum(ar0 > 0)
+  } else{
+    x <- sum(ar0 < 0)
+  }
+  #binom.test <- binom.test(x, n, p = .5)
+  theta <- ((x/n) - 0.5)*(sqrt(n)/0.5)
+  pval <- 2 * (1 - pnorm(abs(theta)))
+  return(pval)
+}

### 2017-02-19 code/02-desc-stats.R
Add synthetic controls

@@ -9,14 +9,17 @@ theme_set(theme_bw())
 pre <- post <- 200
 dr <- matrix(NA, nrow = pre + post + 1, ncol = nrow(regime.change))
 for (i in 1:nrow(regime.change)){
-  dr[, i] <- return_by_td(stockdata = index[ticker == regime.change$ticker[i], .(date, dr)],
+  dr[, i] <- return_by_td(stockdata = index,
+                        event_ticker = regime.change$ticker[i],
                         event_date = regime.change$stock_date[i], pre_event = pre, 
                         post_event = post)  
 }
 
-# note: 2 events don't have complete data and are excluded
+# exclude 2 events that don't have complete data 
 dr.na <- apply(dr, 2, function (x) sum(1 * is.na(x)))
-abs.dr.mean <- apply(abs(dr[, which(dr.na==0)]), 1, mean)
+abs.dr.mean <- apply(abs(dr[, which(dr.na == 0)]), 1, mean)
+
+# plot
 tmp <- data.table(dr = abs.dr.mean, td = seq(-pre, post))
 p <- ggplot(tmp, aes(x = td, y = dr)) + 
   geom_segment(mapping = aes(xend = td, yend = 0)) +

### 2017-02-19 code/03-ar.R

@@ -1,83 +1,0 @@
-rm(list = ls())
-library("xtable")
-library("data.table")
-library("ggplot2")
-load("data/data-clean.RData")
-theme_set(theme_bw())
-source("code/func.R")
-
-# EVENT STUDY ------------------------------------------------------------------
-# calculate abnormal returns and days to rebound
-event.window <- 20
-est.window <- 200
-sigma <- sigma.abs <- rep(NA, nrow(regime.change))
-ar <- ar.abs <- matrix(NA, nrow = 2 * event.window, ncol = nrow(regime.change))
-car <- car.se <-  ar
-dtr <- rep(NA, nrow(regime.change))
-for (i in 1:ncol(ar)){
-  tmp <- event_study(stockdata = index[ticker == regime.change$ticker[i], 
-                                       .(date, dr)],
-                     event_window = event.window, estimation_window = est.window,
-                     event_date = regime.change$stock_date[i], model = "constant") 
-  tmp.abs <- event_study(stockdata = index[ticker == regime.change$ticker[i], 
-                                           .(date, abs(dr))],
-                         event_window = event.window, estimation_window = est.window,
-                         event_date = regime.change$stock_date[i], model = "constant")
-  sigma[i] <- tmp$sigma
-  sigma.abs[i] <- tmp.abs$sigma
-  ar[, i] <- tmp$ar
-  ar.abs[, i] <- tmp.abs$ar
-  tmp.car <- car_prepost(tmp$td, tmp$ar, tmp$sigma)
-  car[, i] <- tmp.car$car
-  car.se[, i] <- tmp.car$car.se
-  dtr[i] <- days_to_rebound(stockdata = index[ticker == regime.change$ticker[i], 
-                                            .(date, p)],
-                          event_date = regime.change$stock_date[i])
-}
-td.ew <- seq(-event.window, event.window -1)
-regime.change.es <- list(td = td.ew, sigma = sigma, ar = ar) 
-regime.change.es.abs <- list(td = td.ew, sigma = sigma.abs, ar = ar.abs)
-save(regime.change.es, regime.change.es.abs, file = "output/regime-change-event-study.RData")
-
-# ABNORMAL RETURNS TABLES ------------------------------------------------------
-# coups
-coup.index <- which(regime.change$type == "Coup")
-artable.coups <- ar_table(td = td.ew, ar = ar[, coup.index],
-                          sigma = sigma[coup.index], dtr = dtr[coup.index],
[…]

### 2017-02-19 code/04-ar.R

@@ -1,0 +1,54 @@
+rm(list = ls())
+library("xtable")
+library("data.table")
+library("ggplot2")
+load("data/data-clean.RData")
+load("output/regime-change-event-study.RData")
+theme_set(theme_bw())
+source("code/func.R")
+
+# ABNORMAL RETURNS TABLES ------------------------------------------------------
+# coups
+coup.index <- which(regime.change$type == "Coup")
+artable.coups <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, coup.index],
+                          sigma = rc.es$sigma.treat[coup.index], 
+                          dtr = rc.es$dtr.treat[coup.index],
+                          country = regime.change[coup.index, country],
+                          date = regime.change[coup.index, stock_date], 
+                          coup = TRUE)
+myprint.xtable(artable.coups$car, file = "tables/artable-coups-car.txt")
+myprint.xtable(artable.coups$car.mean, file = "tables/artable-coups-car-mean.txt")
+
+# assassinations
+ass.index <- which(regime.change$type == "Assassination")
+artable.ass <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, ass.index],
+                        sigma = rc.es$sigma.treat[ass.index], 
+                        dtr = rc.es$dtr.treat[ass.index],
+                        country = regime.change[ass.index, country],
+                        date = regime.change[ass.index, stock_date])
+myprint.xtable(artable.ass$car, file = "tables/artable-ass-car.txt")
+myprint.xtable(artable.ass$car.mean, file = "tables/artable-ass-car-mean.txt")
+
+# resignations
+res.index <- which(regime.change$type == "Resignation")
+artable.res <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, res.index],
+                        sigma = rc.es$sigma.treat[res.index], 
+                        dtr = rc.es$dtr.treat[res.index],
+                        country = regime.change[res.index, country],
+                        date = regime.change[res.index, stock_date])
+myprint.xtable(artable.res$car, file = "tables/artable-res-car.txt")
+myprint.xtable(artable.res$car.mean, file = "tables/artable-res-car-mean.txt")
+
+# VENEZUELA PARTIAL COUP -------------------------------------------------------
+ven <- event[ticker == "_IBCD" & stock_date == "2002-04-12"]
[…]

### 2017-02-19 code/05-sensitivity.R

@@ -1,67 +1,0 @@
-rm(list = ls())
-load("output/regime-change-event-study.RData")
-load("data/data-clean.RData")
-library("data.table")
-library("ggplot2")
-source("code/func.R")
-theme_set(theme_bw())
-
-# NON-PARAMETRIC TESTS ---------------------------------------------------------
-ed <- which(regime.change.es$td == 0)
-
-# coups 
-coup.index <- which(regime.change$type == "Coup")
-ar.mean.coup <- mean(regime.change.es$ar[ed, coup.index])
-rankpval.coup <- rank_test(regime.change.es$ar[, coup.index], 
-                              regime.change.es$td)
-signpval.coup <- sign_test(regime.change.es$ar[ed, coup.index], "negative")
-
-# assassinations
-ass.index <- which(regime.change$type == "Assassination")
-ar.mean.ass <- mean(regime.change.es$ar[ed, ass.index])
-ranktest.ass <- rank_test(regime.change.es$ar[, ass.index], 
-                           regime.change.es$td)
-signpval.ass <- sign_test(regime.change.es$ar[ed, ass.index], "negative")
-
-# resignations
-res.index <- which(regime.change$type == "Resignation")
-ar.mean.res <- mean(regime.change.es$ar[ed, res.index])
-ranktest.res <- rank_test(regime.change.es$ar[, res.index], 
-                          regime.change.es$td)
-signpval.res <- sign_test(regime.change.es$ar[ed, res.index], "positive")
-
-# absolute value
-ar.mean.abs <- mean(regime.change.es.abs$ar[ed, ])
-ranktest.res <- rank_test(regime.change.es.abs$ar, 
-                          regime.change.es.abs$td)
-signpval.res <- sign_test(regime.change.es.abs$ar[ed, ], "positive")
-
-# CAR SURROUNDING REGIME CHANGES -----------------------------------------------
-td0.indx <- which(regime.change.es$td == 0)
-pos.events <- which(regime.change.es$ar[td0.indx, ] >= 0)
-neg.events <- which(regime.change.es$ar[td0.indx, ] < 0)
-
-# positive events
-car.mean.pos <- mean_car_prepost(ar = regime.change.es$ar[, pos.events],
-                         sigma = regime.change.es$sigma[pos.events], 
-                         td = regime.change.es$td)
[…]

### 2017-02-19 code/06-sensitivity.R

@@ -1,0 +1,140 @@
+rm(list = ls())
+load("output/regime-change-event-study.RData")
+load("data/data-clean.RData")
+library("data.table")
+library("ggplot2")
+source("code/func.R")
+theme_set(theme_bw())
+
+# NON-PARAMETRIC TESTS ---------------------------------------------------------
+ed <- which(rc.es$td == 0)
+tab.np <- matrix(NA, nrow = 4, ncol = 7)
+colnames(tab.np) <- c("mean_ar_treat", "rank_pval_treat", "sign_pval_treat",
+                      "mean_ar_control", "rank_pval_control", "sign_pval_control",
+                      "wilcoxon_rank_pval")
+indx <- list(coup.index = which(regime.change$type == "Coup"),
+             ass.index = which(regime.change$type == "Assassination"),
+             res.index = which(regime.change$type == "Resignation"))
+sign.dir <- c("negative", "negative", "positive")
+
+## Treatment
+# mean abnormal return
+for (i in 1:3){
+  tab.np[i, 1] <- mean(rc.es$ar.treat[ed, indx[[i]]])
+}
+tab.np[4, 1] <-  mean(rc.abs.es$ar.treat[ed, ])
+
+# rank test p-value
+for (i in 1:3){
+  tab.np[i, 2] <- rank_test(rc.es$ar.treat[, indx[[i]]], rc.es$td)
+}
+tab.np[4, 2] <-  rank_test(rc.abs.es$ar.treat[, indx[[i]]], rc.abs.es$td)
+
+# sign test p-value
+for (i in 1:3){
+  tab.np[i, 3] <- sign_test(rc.es$ar.treat[ed, indx[[i]]], sign.dir[i])
+}
+tab.np[4, 3] <-  sign_test(rc.abs.es$ar.treat[ed, indx[[i]]], sign.dir[i])
+
+## Control
+# mean abnormal return
+for (i in 1:3){
+  tab.np[i, 4] <- mean(rc.es$ar.control[ed, indx[[i]]], na.rm = TRUE)
+}
+tab.np[4, 4] <-  mean(rc.abs.es$ar.control[ed, ], na.rm = TRUE)
+
+# rank test p-value
+for (i in 1:3){
+  tab.np[i, 5] <- rank_test(rc.es$ar.control[, indx[[i]]] , rc.es$td)
+}
[…]

### 2017-02-19 code/07-protests.R

@@ -8,13 +8,15 @@ library("broom")
 theme_set(theme_bw())
 
 # EGYPTIAN REVOLUTION ----------------------------------------------------------
-egypt.es <-  event_study(stockdata = index[ticker == "_EFGID", .(date, dr)],
+egypt.es <-  event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                         event_ticker = "_EFGID",
                     event_window = 20, estimation_window = 200,
                     event_date = rev[name == "Egyptian Revolution", start_date],
-                    model = "constant")   
-egypt.es <- c(egypt.es, car_prepost(egypt.es$td, egypt.es$ar, egypt.es$sigma))
-egypt.es <- data.table(date = egypt.es$date, td = egypt.es$td,  car = egypt.es$car, 
-                  car.se = egypt.es$car.se)
+                    model = "constant", control = FALSE)   
+egypt.es <- c(egypt.es, car_prepost(egypt.es$ar.treat$td, egypt.es$ar.treat$ar,
+                                    egypt.es$sigma.treat))
+egypt.es <- data.table(date = egypt.es$ar.treat$date, td = egypt.es$ar.treat$td,  
+                       car = egypt.es$car, car.se = egypt.es$car.se)
 egypt.es[, lcar := car - qnorm(.975) * car.se]
 egypt.es[, ucar := car + qnorm(.975) * car.se]
 p <- ggplot(egypt.es, aes(x = date, y = car)) + geom_line() +

### 2017-02-19 code/func.R

@@ -1,4 +1,9 @@
-# xtable print -----------------------------------------------------------------
+# CONVERT STRING DATE TO R DATE ------------------------------------------------
+mydate <- function(strdate){
+  return(as.Date(strdate, "%m/%d/%Y"))
+}
+
+# xtable PRINT -----------------------------------------------------------------
 myprint.xtable <- function(x, file){
   print(xtable(x), 
         include.rownames = FALSE, include.colnames = FALSE,
@@ -17,20 +22,38 @@ matrix_se <- function(est, se){
   return(m)
 }
 
+# CALCULATE TRADING DAYS IN EVENT WINDOW ---------------------------------------
+calc_td <- function(stockdata, event_date){
+  stockdata[, n := seq(1, .N), by = "ticker"]
+  if (length(unique(stockdata$ticker)) == 1) {
+      # scenario 1: only 1 ticker 
+      event.td <- which.max(stockdata$date - event_date >= 0) # first trading day on or after event
+      stockdata[, td := n - event.td]
+  } else { 
+      # scenario 2: many tickers (i.e. for control portfolio)
+      stockdata[, event_td := which.max(date - event_date >= 0), by = "ticker"]
+      stockdata[, td := n - event_td]
+      stockdata[, date_diff := date - event_date]
+      stockdata[, date_diff0 := ifelse(td == 0, date_diff, NA)]
+      stockdata[, date_diff0 := mean(date_diff0, na.rm = TRUE), by = "ticker"]
+      stockdata <- stockdata[abs(date_diff0) <= 5]
+      stockdata[, c("event_td", "date_diff", "date_diff0") := NULL]
+  }
+  return(stockdata)
+}
+
 # DAILY RETURNS BY TRADING DAY -------------------------------------------------
-return_by_td <- function(stockdata, event_date, pre_event, post_event){
+return_by_td <- function(stockdata, event_ticker, event_date, pre_event, post_event){
   # Note: first column of stockdata must be a date variable
-  setnames(stockdata, c("date", "r"))
+  stockdata <- stockdata[ticker == event_ticker, .(ticker, date, dr)]
   
   # trading days
-  stockdata[, n := seq(1, .N)]
-  event.td <- which.max(stockdata$date - event_date >= 0) # first trading day on or after event
-  stockdata[, td := n - event.td]
+  stockdata <- calc_td(stockdata, event_date)
   
   # trading window surrounding event
[…]

### 2017-02-19 main.R

@@ -4,7 +4,8 @@ if (!file.exists("data/data-clean.RData")){
   source("code/01-clean.R")
 }
 source("code/02-desc-stats.R")
-source("code/03-ar.R")
-source("code/04-volatility.R")
-source("code/05-sensitivity.R")
-source("code/06-protests.R")
+source("code/03-event-studies.R")
+source("code/04-ar.R")
+source("code/05-volatility.R")
+source("code/06-sensitivity.R")
+source("code/07-protests.R")

### 2017-02-19 code/03-event-studies.R
Add synthetic controls

@@ -1,0 +1,63 @@
+rm(list = ls())
+library("xtable")
+library("data.table")
+load("data/data-clean.RData")
+theme_set(theme_bw())
+source("code/func.R")
+
+# EVENT STUDY ------------------------------------------------------------------
+# calculate abnormal returns and days to rebound
+event.window <- 20
+est.window <- 200
+n.es <- nrow(regime.change)
+es <- es.abs <- vector(mode = "list", n.es)
+dtr.treat <- rep(NA, n.es)
+
+# loop
+for (i in 1:n.es){
+  # no controls for 1901
+  if(regime.change$stock_date[i] == mydate("09/07/1901")){
+      controli <- FALSE
+  } else{
+      controli <- TRUE
+  }
+  
+  # use custom V in synth to deal with singular matrix in optim
+  if (regime.change$stock_date[i] == mydate("10/4/2002")){
+      custom.v.i <- rep(1, 2)
+  } else{
+      custom.v.i <- NULL
+  }
+  
+  # run event study
+  es[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                     event_ticker = regime.change$ticker[i],
+                     event_window = event.window, estimation_window = est.window,
+                     event_date = regime.change$stock_date[i], model = "constant",
+                     control = controli, custom_v = custom.v.i) 
+  es.abs[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = abs(index$dr),
+                         event_ticker = regime.change$ticker[i],
+                         event_window = event.window, estimation_window = est.window,
+                         event_date = regime.change$stock_date[i], model = "constant",
+                         control = controli, custom_v = custom.v.i)
+  
+  # days to rebound
+  dtr.treat[i] <- days_to_rebound(ticker = index$ticker, date = index$date, price = index$p,
+                                  event_ticker = regime.change$ticker[i],
+                                  event_date = regime.change$stock_date[i])
+  
+  # print
+  print(i)
+}
+
+# combine event studies
+rc.es <- combine_event_studies(es, event_country = regime.change$country,
+                                          event_type = regime.change$type, 
+                                          event_date = regime.change$stock_date)
+rc.es <- c(rc.es, list(dtr.treat = dtr.treat))
+rc.abs.es <- combine_event_studies(es.abs, event_country = regime.change$country,
+                                          event_type = regime.change$type, 
+                                          event_date = regime.change$stock_date)
+
[…]

### 2017-02-19 code/do.R

@@ -1,82 +1,0 @@
-
-# SET UP -----------------------------------------------------------------------
-regime.change <- event[type == "Coup" | type == "Assassination" |
-                         type == "Resignation", 
-                       .(country, ticker, stock_date, type)]
-
-# ABSOLUTE VALUE OF DAILY STOCK RETURNS BY DAYS FROM EVENT ---------------------
-pre <- post <- 200
-dr <- matrix(NA, nrow = pre + post + 1, ncol = nrow(regime.change))
-for (i in 1:nrow(regime.change)){
-  dr[, i] <- ReturnByTD(stockdata = index[ticker == regime.change$ticker[i], .(date, dr)],
-                        event.date = regime.change$stock_date[i], pre.event = pre, 
-                        post.event = post)  
-}
-# note: 2 events don't have complete data and are excluded
-dr.na <- apply(dr, 2, function (x) sum(1 * is.na(x)))
-abs.dr.mean <- apply(abs(dr[, which(dr.na==0)]), 1, mean)
-tmp <- data.table(dr = abs.dr.mean, td = seq(-pre, post))
-p <- ggplot(tmp, aes(x = td, y = dr)) + 
-  geom_segment(mapping = aes(xend = td, yend = 0)) +
-  xlab("Trading days") + ylab("Absolute value of daily return (%)")
-ggsave("figs/daily_mean_absreturn.pdf", p, height = 5, width = 7)
-
-# EVENT STUDY ------------------------------------------------------------------
-# calculate abnormal returns and days to rebound
-event.window <- 20
-est.window <- 200
-sigma <- rep(NA, nrow(regime.change))
-ar <- matrix(NA, nrow = 2 * event.window, ncol = nrow(regime.change))
-dtr <- rep(NA, nrow(regime.change))
-for (i in 1:ncol(ar)){
-  tmp <-  EventStudy(stockdata = index[ticker == regime.change$ticker[i], 
-                                       .(date, dr)],
-                     event.window = event.window, estimation.window = est.window,
-                     event.date = regime.change$stock_date[i], model = "constant")   
-  sigma[i] <- tmp$sigma
-  ar[, i] <- tmp$ar
-  dtr[i] <- DaysToRebound(stockdata = index[ticker == regime.change$ticker[i], 
-                                            .(date, p)],
-                          event.date = regime.change$stock_date[i])
-}
-td.ew <- seq(-event.window, event.window -1 )
-
-# ABNORMAL RETURNS TABLES ------------------------------------------------------
[…]

### 2017-02-20 doc/paper.tex
Add Egypt plot to tex file
Sensitivity positive/negative CAR
Change to real returns

@@
   \hline
-  \textbf{Means} &  &  &  &  &  &  \\
 \ExpandableInput{../tables/artable-coups-car-mean.txt}
@@
 \begin{figure}[htb]
-\includegraphics{../figs/daily_mean_absreturn.pdf}
+\includegraphics{../figs/mean-volatility.pdf}
 \caption{Mean of volatility estimates from GARCH(1,1) models}
@@
   \hline
-Coups & -0.182 & 0.008 & 0.083 & 0.235 & 0.980 & 1.000 & 0.034  \\
-Assassinations & -1.101 & 0.043 & 0.157 & -2.342 & 0.236 & 0.157 & 0.688  \\
-Resignations & 6.146 & 0.000 & 0.020 & 0.486 & 0.217 & 0.796 & 0.007 \\
-All (Absolute Value) & 3.725 & 0.000 & 0.004 & 0.335 & 0.144 & 0.612 & 0.001 \\
+\ExpandableInput{../tables/non-parametric-ar0.txt}
    \hline
@@
 \scriptsize
-Notes:
+Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available. 
 \end{threeparttable}
@@
 \begin{figure}[!ht]
-\includegraphics{../figs/daily_mean_absreturn.pdf}
+\includegraphics{../figs/mean-car-pos-neg.pdf}
 \caption{Mean cumulative abnormal returns surrounding regime changes}
@@
 
-To check for the possibility that my previous results were spurious, a final placebo check examines whether there are abnormal absolute returns on the event day when the event day is shifted forward and backwards in time.
-Events are shifted backwards by 5, 10, 15, 20, 25 and 30 trading days and forwards by 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55 and 60 trading days.\footnote{Event days are not shifted backwards by more than 30 trading days to ensure than every country in the sample can be included.
-When events are shifted backwards by more than 30 trading days mean abnormal absolute returns continue to cluster around 0.} Figure~\autoref{fig:time-placebos} graphs the abnormal absolute returns (labeled CAR(0,0) in the figure) against the number of days shifted.
-
-The largest CAR(0,0) occurs when the events have not been shifted in time.
-Moreover, the backwards shifted event day abnormal absolute return is only statistically different from zero when the event day is shifted backwards by 5 days.
-On the other hand, the forwards shifted CAR(0,0) is statistically significant when the event day is shifted forward by 5, 10, 15 and 20 days.
-These findings are consistent with figure~\autoref{fig:volatility}, in which volatility began increasing around 5 trading days before the event and then started decreasing quickly about 20 trading days therafter.
-
-\begin{figure}[!ht]
-\includegraphics{../figs/daily_mean_absreturn.pdf}
-\vspace{-50pt}
-\caption{Time-shifed placebos for absolute abnormal returns}
-\label{fig:time-placebos}
-\end{figure}
+Fianlly, to check whether our results are sensitive to model specificaiton, we estimated market models in addition to the baseline constant returns model.
+We used the MSCI World Index as a proxy for ther market return.
+[To do: add table for this]
 
@@
 \begin{figure}[!ht]
-\includegraphics{../figs/daily_mean_absreturn.pdf}
+\includegraphics{../figs/egypt-revolution-2011.pdf}
 \caption{Cumulative abnormal returns during the Egyptian revolution}

### 2017-02-20 code/01-clean.R

@@ -28,7 +28,7 @@ rev[, end_date := as.Date(end_date,"%m/%d/%Y")]
 
 # CLEAN DATA -------------------------------------------------------------------
 # inflation adjusted returns
-#indices[, dr := (real_p - shift(real_p))/shift(real_p), by = "ticker"]
+indices[, dr := (real_p - shift(real_p))/shift(real_p), by = "ticker"]
 
 ## continuously compounded returns
 indices[, dr := 100 * log(dr+1)]

### 2017-02-20 code/04-ar.R

@@ -15,7 +15,7 @@ artable.coups <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, coup.index],
                           dtr = rc.es$dtr.treat[coup.index],
                           country = regime.change[coup.index, country],
                           date = regime.change[coup.index, stock_date], 
-                          coup = TRUE)
+                          coup = FALSE)
 myprint.xtable(artable.coups$car, file = "tables/artable-coups-car.txt")
 myprint.xtable(artable.coups$car.mean, file = "tables/artable-coups-car-mean.txt")
 

### 2017-02-20 code/05-volatility.R

@@ -1,0 +1,46 @@
+rm(list = ls())
+library("xtable")
+library("data.table")
+library("ggplot2")
+library("rugarch")
+load("data/data-clean.RData")
+theme_set(theme_bw())
+source("code/func.R")
+
+# DATA SETUP -------------------------------------------------------------------
+post.days <- pre.days <- 1000
+n.rc <- nrow(regime.change)
+dat <- vector(mode = "list", n.rc)
+for (i in 1:n.rc){
+  dat[[i]] <- index[ticker == regime.change$ticker[i], .(ticker, date, dr)]
+  dat[[i]] <- calc_td(stockdata = dat[[i]], 
+                            event_date = regime.change$stock_date[i])
+  dat[[i]] <- dat[[i]][td >= -pre.days & td <= post.days]
+  dat[[i]] <- dat[[i]][complete.cases(dat[[i]])]
+  dat[[i]]$event_date <- regime.change$stock_date[i]
+  dat[[i]]$event_num <- i
+} 
+nobs <- do.call("c", lapply(dat, nrow))
+
+# GARCH MODEL ------------------------------------------------------------------
+# model spects
+garch.spec <- ugarchspec(mean.model = list(armaOrder = c(0,0)), 
+                         distribution.model = "norm")
+
+# run models
+for (i in 1:n.rc){
+  rc.garchfit <- ugarchfit(spec = garch.spec, data = dat[[i]]$dr)
+  dat[[i]]$garch_volatility <- rc.garchfit@fit$sigma
+  print(i)
+}
+
+# VOLATILITY PLOTS -------------------------------------------------------------
+dat <- rbindlist(dat, fill = TRUE)
+volatility.mean <- dat[, .(mean_garch_volatility = mean(garch_volatility, na.rm = TRUE)),
+                             by = c("td")]
+p.volatility <- ggplot(volatility.mean[td >= -250 & td <= 250],
+                       aes(x = td, y = mean_garch_volatility)) + 
+  geom_line() + xlab("Trading days") + ylab("Mean volatility")
+ggsave("figs/mean-volatility.pdf", p.volatility, height = 5, width = 7)
+
+

### 2017-02-20 code/07-protests.R

@@ -45,7 +45,7 @@ p <- ggplot(egypt.es, aes(x = date, y = car)) + geom_line() +
 ggsave("figs/egypt-revolution-2011.pdf", p, height = 5, width = 7)
 
 # EFFECT OF PUBLIC PROTESTS ON STOCK PRICES ------------------------------------
-# data 
+# data
 index.rev <- vector(mode = "list", length(rev$ticker))
 for (i in 1:length(rev$ticker)){
   index.rev[[i]] <- index[ticker == rev$ticker[i] & date >= (rev$start_date[i] - 250)
@@ -53,15 +53,28 @@ for (i in 1:length(rev$ticker)){
   index.rev[[i]][, rev_no := i]
   index.rev[[i]][, event := ifelse(date >= rev$start_date[i] & 
                                      date <= rev$end_date[i], 1, 0)]
+  index.rev[[i]] <- index.rev[[i]][!is.na(dr)]
+}
+
+# volatility
+garch.spec <- ugarchspec(mean.model = list(armaOrder = c(0,0)), 
+                         distribution.model = "norm")
+for (i in 1:length(rev$ticker)){
+  rc.garchfit <- ugarchfit(spec = garch.spec, data = index.rev[[i]]$dr)
+  index.rev[[i]]$garch_volatility <- rc.garchfit@fit$sigma
+  print(i)
 }
 index.rev <- rbindlist(index.rev)
+
+# panel data
 index.rev <- pdata.frame(index.rev, index = c("rev_no", "date"))
 
 # regressions
 revfit1 <- plm(dr ~ event, data = index.rev, model = "within")
 revfit2 <- plm(abs_dr ~ event, data = index.rev, model = "within")
 revfit3 <- plm(abs_dr ~ event + emerg_abs_dr, data = index.rev, model = "within")
-revfit <- list(revfit1, revfit2, revfit3)
+revfit4 <- plm(garch_volatility ~ event, data = index.rev, model = "within")
+revfit <- list(revfit1, revfit2, revfit3, revfit4)
 nfits <- length(revfit)
 
 # table of results

### 2017-02-20 code/func.R

@@ -433,3 +433,21 @@ combine_event_studies <- function(x, event_country, event_type, event_date){
             car.control = car.control, car.control.se = car.control.se)
   return(l)
 }
+
+# VOLATILITY DATA --------------------------------------------------------------
+volatility_data <- function(stockdata, event_ticker, event_date, 
+                            date_start = NULL, date_end = NULL<
+                            pre_days, post_days){
+  n <- length(event_ticker)
+  dat <- vector(mode = "list", n)
+  for (i in 1:n){
+    dat[[i]] <- stockdata[ticker == event_ticker[i], .(ticker, date, dr)]
+    dat[[i]] <- calc_td(dat[[i]], 
+                        event_date = event_date[i])
+    dat[[i]] <- dat[[i]][td >= -pre_days & td <= post_days]
+    dat[[i]] <- dat[[i]][complete.cases(dat[[i]])]
+    dat[[i]]$event_date <- event_date[i]
+    dat[[i]]$event_num <- i
+  }
+  return(dat)
+}

### 2017-02-20 doc/paper.tex
Tex file update

@@
 Notes: Standard errors are in parentheses.
-Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
 \end{threeparttable}
@@
 Notes: Standard errors are in parentheses.
-Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level.
-The mean days to rebound excludes the assassination of William McKinley on November 6, 1901.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
 \end{threeparttable}

### 2017-02-20 code/02-desc-stats.R
Trevor Working Branch
Updated visuals for daily mean absolute returns plot

@@ -9,19 +9,33 @@ theme_set(theme_bw())
 pre <- post <- 200
 dr <- matrix(NA, nrow = pre + post + 1, ncol = nrow(regime.change))
 for (i in 1:nrow(regime.change)){
-  dr[, i] <- return_by_td(stockdata = index,
-                        event_ticker = regime.change$ticker[i],
-                        event_date = regime.change$stock_date[i], pre_event = pre, 
-                        post_event = post)  
+  dr[, i] <- return_by_td(stockdata = index[ticker == regime.change$ticker[i], .(date, dr)],
+                          event_date = regime.change$stock_date[i], pre_event = pre, 
+                          post_event = post)  
 }
 
-# exclude 2 events that don't have complete data 
+# note: 2 events don't have complete data and are excluded
 dr.na <- apply(dr, 2, function (x) sum(1 * is.na(x)))
-abs.dr.mean <- apply(abs(dr[, which(dr.na == 0)]), 1, mean)
-
-# plot
+abs.dr.mean <- apply(abs(dr[, which(dr.na==0)]), 1, mean)
 tmp <- data.table(dr = abs.dr.mean, td = seq(-pre, post))
+
+# Create plot
 p <- ggplot(tmp, aes(x = td, y = dr)) + 
-  geom_segment(mapping = aes(xend = td, yend = 0)) +
-  xlab("Trading days") + ylab("Absolute value of daily return (%)")
+  geom_area(color="gray48", fill='gray48', size = .1) +
+  xlab("Trading days") + ylab("Absolute value of daily return (%)") +  
+  
+  theme(
+    plot.background = element_blank()
+    ,panel.grid.major = element_blank()
+    ,panel.grid.minor = element_blank()
+    ,panel.border = element_blank()) +
+  
+  theme(axis.line.x = element_line(color="black"),
+        axis.line.y = element_line(color="black"),
+        axis.ticks = element_blank()) +
+  
+  theme(plot.margin=unit(c(0.5,0.5,0.5,0.5),"cm")) +
+  
+  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))
+
 ggsave("figs/daily_mean_absreturn.pdf", p, height = 5, width = 7)

### 2017-07-09 doc/paper.tex
Add empty data directory

@@
 We examine the relationship between political instability and the daily returns of national stock indices.
-Financial volatility increases dramatically following (and just before) ``irregular'' regime changes caused by coup d'état, assassinations, and resignations.
+Financial volatility increases dramatically following (and just before) ``irregular'' regime changes caused by coup d'?tat, assassinations, and resignations.
 Some of the pre-resignation volatility occurs because of public protests such as riots and popular demonstrations that helped spawn the resignation in the first place.
@@
 Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'état attempt result in positive abnormal returns of 20\% or more.
+The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'?tat attempt result in positive abnormal returns of 20\% or more.
 \end{abstract}
@@
 
-My main finding is that financial volatility increases dramatically following (and just before) coup d'état, assassinations, and resignations.
+My main finding is that financial volatility increases dramatically following (and just before) coup d'?tat, assassinations, and resignations.
 However, these irregular regime changes have disparate effects on the direction of stock returns.
 Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'état attempt result in positive abnormal returns of 20\% or more.
+The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'?tat attempt result in positive abnormal returns of 20\% or more.
 We also present evidence showing that volatility increases during public protests such as riots and popular demonstrations that cause leaders to resign.
@@
 \citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
-\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies, Luiz Inácio Lula da Silva, increased the volatility (but not the mean return) of the Brazilian stock market.
+\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies, Luiz In?cio Lula da Silva, increased the volatility (but not the mean return) of the Brazilian stock market.
 
 \section{Data}
-Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'état dataset and Coup d'état Events handbook.
-The Coup d'état dataset incudes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
+Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'?tat dataset and Coup d'?tat Events handbook.
+The Coup d'?tat dataset incudes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
 We focus on successful coups because it is difficult to classify failed coups.
@@
 
-The Coup d'état Events handbook provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
+The Coup d'?tat Events handbook provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
 Daily financial data is available for countries in categories 4 and 5, so We supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
@@
 We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
-Coup attempts are those in category 2 in the CSP Coup d'état dataset.}The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
+Coup attempts are those in category 2 in the CSP Coup d'?tat dataset.}The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
 
@@
 We define the event date as the first trading day in which the market could have reacted to news of the event.
-For example, during the October 12, 1999 coup d'état in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
+For example, during the October 12, 1999 coup d'?tat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
 We code October 14th, the day in which the market re-opened, as the event day.
@@
 We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
-\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'état.
+\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'?tat.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.
@@
 Although it is tempting to dismiss the 1976 Argentina coup as an outlier, there is reason to to believe that coups can in fact result in large positive abnormal returns.
-The 2002 failed coup d'état attempt against Hugo Chavez is a case in point.
+The 2002 failed coup d'?tat attempt against Hugo Chavez is a case in point.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 \includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'état attempt}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'?tat attempt}
 \label{fig:AR-Ven}
@@
 Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do do not always move in the same direction.
-For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rúa of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.
+For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la R?a of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.
 
@@
 An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'état Events Handbook or the Archigos Version 2.9 data set with available financial data.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'?tat Events Handbook or the Archigos Version 2.9 data set with available financial data.
 In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
@@
 The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
-Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'état Events Handbook and Archigos Version 2.9.
+Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'?tat Events Handbook and Archigos Version 2.9.
 Additional Lexis Nexis searches were used to verify these descriptions.

### 2017-08-07 doc/paper.tex
Updates to introduction and bibliography

@@
 \begin{abstract}
-We examine the relationship between political instability and the daily returns of national stock indices.
-Financial volatility increases dramatically following (and just before) ``irregular'' regime changes caused by coup d'?tat, assassinations, and resignations.
-Some of the pre-resignation volatility occurs because of public protests such as riots and popular demonstrations that helped spawn the resignation in the first place.
+We examine the relationship between political instability and daily returns of national stock indices.
+Financial volatility increases dramatically following (and immediately before) ``irregular'' regime changes caused by coup d'etat, assassinations, and resignations.
+Some of the pre-resignation volatility occurs due to actions that precede the resignation such as public protests, riots, and popular demonstrations.
 However, these irregular regime changes have disparate effects on the direction of stock returns.
 Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'?tat attempt result in positive abnormal returns of 20\% or more.
+The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup attempt result in positive abnormal returns of 20\% or more.
 \end{abstract}
@@
 \section{Introduction} \label{sec:Introduction}
-Investors, firms and development agencies are all concerned with political risk in emerging markets.
-Government's can reduce asset returns, firm profits and overall economic performance by implementing unfavorable policies.
-In the 2011 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the most important constraint for foreign direct investment (FDI) in developing countries over the next three years.
-The most pressing risks involved government regulatory policies and failed commitments, although political violence was also a concern.
+For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.
+In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability) \citet{wipr2013}.
+In 2011 and 2012, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
 \footnote{The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.}
@@
 A common hypothesis is that political instability discourages investment and reduces economic growth by increasing policy uncertainty.
-Some cross country empirical evidence is consistent with this hypothesis: political instability, as measured by regime change frequency or political violence, is negatively correlated with investment, GDP growth and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.
-In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.
-
-Of course, a change in government might promote growth if the new regime adopts better economic policies or is less corrupt than its predecessors.
-\citet{alesina1996political} takes this possibility seriously but argues that the negative effects of policy uncertainty dominate the positive effects of coups staged by pro growth factions.
-Conversely, \citet{londregan1990poverty} present evidence suggestive of a bimodal distribution of coups in which neither the effects of pro-growth or anti-growth coups dominate.
+This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.
+\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
+On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
+Not all political instability is equivalent - resignations, assassinations, and coups are each examples of political instability, but may have disparate effects on financial returns.
+Further, political instability may be seen as a \textit{positive} event if the current regime is regarded as strongly anti-business or anti-global.
+\citet{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
 
 As in \citet{alesina1996political}, We use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
-The major innovation of this paper is that, in contrast to the aforementioned cross country studies, We analyze the impact of political instability using daily financial data.
-To the extent that these irregular transfers of power are unpredictable and unrelated events do not bias the results, this allows me to use market expectations to quantify the economic impact of regime changes.
-The advantage of this event study approach is that it allows me to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.
+The major innovation of this paper is that, in contrast to the aforementioned cross country studies, we analyze the impact of political instability using daily financial data.
+This enables us to use market expectations to quantify the economic impact of each individual type of regime change.
+The advantage of this event study approach is that it allows us to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.
 
-My main finding is that financial volatility increases dramatically following (and just before) coup d'?tat, assassinations, and resignations.
+Our main finding is that financial volatility increases dramatically following (and just before) coup d'etat, assassinations, and resignations.
 However, these irregular regime changes have disparate effects on the direction of stock returns.
 Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'?tat attempt result in positive abnormal returns of 20\% or more.
-We also present evidence showing that volatility increases during public protests such as riots and popular demonstrations that cause leaders to resign.
-These findings provide important insights into the expected impact of episodes of political instability on economic performance.
+The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'etat attempt result in positive abnormal returns of 20\% or more.
+This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore coups should not be expected to lead to increased economic development and therefore positive market returns (cite).
+However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
 
-This paper is most closely related to four branches of literature.
+This paper is closely related to four branches of literature.
 The first analyzes the economic impact of political instability.
@@
 These models tend to focus on government policy instruments that affect private rates of return on investment.
-The general idea is that political instability causes governments to act myopically and adopt inefficient policies.
-For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+The general argument is that political instability causes governments to act myopically and adopt inefficient policies.
+\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
 Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.
+The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
 
-The second strand examines the impact of leaders on political and economic outcomes.
-\citet{jones2005leaders} identify plausibly exogenous leadership transitions using the deaths of leaders from either natural causes or accidents.
-Their results indicate that leaders influence policy outcomes (particularly monetary policy) and economic growth.
+The second looks at how the variance of stock market returns reacts to political events.
+\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
+\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
+
+The third strand examines the impact of leaders on political and economic outcomes.
+\citet{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
+Their results indicate that leaders influence monetary policy and economic growth.
 \citet{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
-Other work has focused on leaders in the private sector.
-In particular, \citet{bertrand2003managing} estimate CEO fixed effects and show that private sector leaders have important effects on the profits of firms.
 
-The third uses event studies to assess political phenomenon.
+The fourth uses event studies to assess political phenomenon.
 A growing body of work uses political events to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Other studies in ``forensic economics" have used political events to study illicit transactions such as insider trading \citep{dube2011coups}.
-\citet{guidolin2007diamonds} used the sudden death of rebel leader, Jonas Savimbi, to show that Angolan diamond mining companies benefited from the Angolan civil war.
+Studies in ``forensic economics" have used political events to examine illicit transactions such as insider trading \citep{dube2011coups}.
+\citet{guidolin2007diamonds} used the sudden death of rebel leader to show that Angolan diamond mining companies benefited from the Angolan civil war.
 \citet{dellavigna2010detecting} detect illegal arms trading by identifying events that increase or decrease conflict intensity.
-
-The fourth looks at how the variance of stock market returns reacts to political events.
-\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
-\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies, Luiz In?cio Lula da Silva, increased the volatility (but not the mean return) of the Brazilian stock market.
 

### 2017-08-07 doc/paper.tex
Updates to introduction and bibliography

@@
 For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.
-In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability) \citet{wipr2013}.
+In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability) \citep{wipr2013}.
 In 2011 and 2012, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
@@
 This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.
-\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
+\footnote{In particular, \citep{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
+On the other hand, \citep{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
 Not all political instability is equivalent - resignations, assassinations, and coups are each examples of political instability, but may have disparate effects on financial returns.
 Further, political instability may be seen as a \textit{positive} event if the current regime is regarded as strongly anti-business or anti-global.
-\citet{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+\citep{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
 
-As in \citet{alesina1996political}, We use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
+As in \citep{alesina1996political}, we use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
 The major innovation of this paper is that, in contrast to the aforementioned cross country studies, we analyze the impact of political instability using daily financial data.
@@
 
+\bigskip
+
 This paper is closely related to four branches of literature.
@@
 The general argument is that political instability causes governments to act myopically and adopt inefficient policies.
-\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
-Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+\footnote{For instance, \citep{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+Similarly, \citep{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
 The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
@@
 The second looks at how the variance of stock market returns reacts to political events.
-\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
-\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
+\citep{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
+\citep{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
 
 The third strand examines the impact of leaders on political and economic outcomes.
-\citet{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
+\citep{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
 Their results indicate that leaders influence monetary policy and economic growth.
-\citet{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
+\citep{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
 
@@
 A growing body of work uses political events to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used political events to examine illicit transactions such as insider trading \citep{dube2011coups}.
-\citet{guidolin2007diamonds} used the sudden death of rebel leader to show that Angolan diamond mining companies benefited from the Angolan civil war.
-\citet{dellavigna2010detecting} detect illegal arms trading by identifying events that increase or decrease conflict intensity.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.
 
@@
 We focus on successful coups because it is difficult to classify failed coups.
-\citet[p.
+\citep[p.
 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''
@@
 The Coup d'?tat Events handbook provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
-Daily financial data is available for countries in categories 4 and 5, so We supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
+Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
 The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.
 
-We further supplement the CSP data with leadership data from Archigos Version 2.9, which allows me to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
+We further supplement the CSP data with leadership data from Archigos Version 2.9, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
 coups, revolts and assassinations).
@@
 The S\&P/IFC index includes securities from emerging markets while the MSCI index includes securities from developed markets only.
-We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
+We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citep{jones2009hit}.
 Coup attempts are those in category 2 in the CSP Coup d'?tat dataset.}The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
@@
 We begin our analysis by studying the effect of irregular regime changes on stock returns.
-We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
+We follow the standard event study methodology as presented by, among others, \citep{mackinlay1997event} and \citep{campbell1997econometrics}.
 Normal performance is measured with a constant mean return model\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations (plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995 respectively).
@@
 We code October 14th, the day in which the market re-opened, as the event day.
-When events occurred on weekends, We change the event date to the following Monday.
+When events occurred on weekends, we change the event date to the following Monday.
 
 $(0,\tau-1)$ is used to denote the $\tau$-day period beginning with the event day and $(-1,\tau)$ to denote the negative $\tau$-day period beginning with the day prior to the event day.
-In other words, for cumulative abnormal returns prior to the event date, We aggregate backwards starting at the day of the event.
+In other words, for cumulative abnormal returns prior to the event date, we aggregate backwards starting at the day of the event.
 For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'?tat.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.
 \footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
@@
 My estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
-As in \citet{jensen2005market} and \citet{leblang2005government}, We use the GARCH (1,1) specification.
+As in \citep{jensen2005market} and \citep{leblang2005government}, we use the GARCH (1,1) specification.
 In particular, for national stock index $i$,
@@
 
-To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
+To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citep{abadie2003economic} and \citep{abadie2010synthetic}.
 Each country is given a weight which represents its influence in the synthetic control portfolio.
@@
 The second concern is addressed using non-parametric statistical techniques, which are free from distributional assumptions.
-we employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
+we employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citep{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
 
@@
 Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citep{abadie2003economic} for further details.}
 

### 2017-08-12 doc/paper.tex
Updates to section 1 and 2, new table in section 2.

@@
 
-Our main finding is that financial volatility increases dramatically following (and just before) coup d'etat, assassinations, and resignations.
+We find that financial volatility increases dramatically following (and just before) coup d'etat, assassinations, and resignations.
 However, these irregular regime changes have disparate effects on the direction of stock returns.
@@
 The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'etat attempt result in positive abnormal returns of 20\% or more.
-This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore coups should not be expected to lead to increased economic development and therefore positive market returns (cite).
+This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore coups should not be expected to lead to increased economic development and therefore positive market returns \citep{derpanopoulos2015coups}.
 However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+
+Our main finding is therefore that the \textit{type} of political event is less important to the direction of abnormal returns than the \textit{nature} of the event.
+Events expected to lead to more stable governance, economic liberalization or democratization are associated with positive returns, while those that consolidate authoritarian rule or poor economic policies have the opposite effect.
 
@@
 \section{Data}
-Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'?tat dataset and Coup d'?tat Events handbook.
-The Coup d'?tat dataset incudes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups.
-\citep[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''
+Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
+The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
+We focus on successful coups because it is difficult to classify failed coups.\footnote{\citep[p.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g.
+a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome in \autoref{tab:coup list} below.
 
-The Coup d'?tat Events handbook provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
+\singlespacing
+\footnotesize
+\begin{center}
+\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
+\caption{List of Coup d'Etat}
+\label{tab:coup list}\\
+\vspace{-5pt}\\
+\hline
+\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
+\endfirsthead
+\multicolumn{3}{c}%
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+\hline
+\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
+\hline
+\endhead
+\hline 
+\multicolumn{3}{r}{\textit{Continued on next page}} \\
+\endfoot
+\hline
+\endlastfoot
+06/08/1970 & Argentina & Authoritarian to authoritarian\\
+03/22/1971 & Argentina & Authoritarian to democratic\\
+03/24/1976 & Argentina & Democratic to authoritarian\\
+10/06/1976 & Thailand & Democratic to authoritarian\\
+10/20/1977 & Thailand & Authoritarian to authoritarian\\
+12/12/1979 & South Korea & Authoritarian to authoritarian\\
+02/23/1991 & Thailand & Democratic to authoritarian\\
+04/05/1992 & Peru & Democratic to authoritarian\\
+10/12/1999 & Pakistan & Democratic to authoritarian\\
+10/04/2002 & Nepal & Democratic to authoritarian\\
+09/19/2006 & Thailand & Democratic to authoritarian\\
+01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
+04/11/2002 & Venezuela & Failed authoritarian to democratic\\
+\hline
+\hline
+\end{longtable}
+\end{center}
+\doublespacing
+\normalsize
+
+The Coup d'etat Events handbook also provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
 Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
@@
 We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citep{jones2009hit}.
-Coup attempts are those in category 2 in the CSP Coup d'?tat dataset.}The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
+Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
 

### 2017-08-20 doc/paper.tex
Additional updates to sections 1, 2, and 3 (rewriting prose and reframing argument).

@@
 We find that financial volatility increases dramatically following (and just before) coup d'etat, assassinations, and resignations.
-However, these irregular regime changes have disparate effects on the direction of stock returns.
+However, unlike the previously mentioned studies, we find that these irregular regime changes have disparate effects on the direction of stock returns.
 Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup d'etat attempt result in positive abnormal returns of 20\% or more.
-This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore coups should not be expected to lead to increased economic development and therefore positive market returns \citep{derpanopoulos2015coups}.
+The impact of coups tends to be negative, but some events result in positive abnormal returns of 20\% or more.
+This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups}.
 However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
 
-Our main finding is therefore that the \textit{type} of political event is less important to the direction of abnormal returns than the \textit{nature} of the event.
-Events expected to lead to more stable governance, economic liberalization or democratization are associated with positive returns, while those that consolidate authoritarian rule or poor economic policies have the opposite effect.
+Our main finding is therefore that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule, exacerbate poor economic policies, or merely increase policy uncertainty have the opposite effect.
 
@@
 06/08/1970 & Argentina & Authoritarian to authoritarian\\
-03/22/1971 & Argentina & Authoritarian to democratic\\
+03/22/1971 & Argentina & Authoritarian to authoritarian\\
 03/24/1976 & Argentina & Democratic to authoritarian\\
@@
 We define the event date as the first trading day in which the market could have reacted to news of the event.
-For example, during the October 12, 1999 coup d'?tat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
+For example, during the October 12, 1999 coup d'etat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
 We code October 14th, the day in which the market re-opened, as the event day.
@@
 We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
-\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'?tat.
+\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.
@@
 ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
 \end{threeparttable}
@@
 
-Event day ARs are negative for all coups except the 1971 and 1976 coups in Argentina.
-The 1976 coup in Argentina appears to be somewhat of an anomaly.
-The ARs on the event day are larger than for any other regime change in the sample (28\%).
-It is also the only coup with statistically significant (and extremely large) 7-day and 20-day pre-event CARs.
-Finally, although the event day abnormal return is large and positive, the 7-day and 20-day post-event CARs are negative.
-
+The average coup has a $-2.5\%$ event day AR.
 Event day ARs for the 1970 coup in Argentina, the 1979 coup in South Korea, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
 Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero.
+In all of these cases, the coup in question either overthrew a democratically elected government or changed governance from one military ruler to another.
+The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.
 
-If the 1976 coup in Argentina is dropped from the sample, the average coup has a $-2.7\%$ event day AR.
-Even so, markets usually recovered quickly: the market returned to its pre-coup level following a negative event day stock return within 5 trading days in all but one case.
+Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez.
+These results provide evidence that that coups can in fact result in positive abnormal returns.
+While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
+The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
 
-Although it is tempting to dismiss the 1976 Argentina coup as an outlier, there is reason to to believe that coups can in fact result in large positive abnormal returns.
-The 2002 failed coup d'?tat attempt against Hugo Chavez is a case in point.
+The failed coup attempt against Hugo Chavez is a perfect natural experiment because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
-Pedro Carmona, a Venezuelan business leader, was named the transitional President of Venezuela.
+Pedro Carmona, a Venezuelan economist and business leader, was named the transitional President of Venezuela.
 Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.
-
-The event is a perfect natural experiment because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
-It provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
-It is therefore a good example of the impact of a shift from a left-wing populist government to a pro business regime on the value of the largest firms in an emerging market.
+This provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
+By extension, it provides an estimate of the impact of a shift from a left-wing populist government to a pro business regime in an emerging market.
 
@@
 \includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'?tat attempt}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'etat attempt}
 \label{fig:AR-Ven}
@@
 The results in \autoref{tab:AR-ass} are produced from analyses identical to those table \autoref{tab:AR-coups} but for successful assassinations rather than coups.
-Like coups, there is some evidence that assassinations decrease stock prices.
+Like the majority of coups, there is evidence that assassinations decrease stock prices.
 The mean event day abnormal return is negative and statistically different than zero.
@@
 Kennedy on November 22, 1963; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.
+
+These results are consistent with our hypothesis that the nature of the political event and its expect impact on policy matters.
+While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
+Unlike a coup, an assassination is typically a random event that will not necessarily cause immediate change in economic policy.
+As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
 
@@
 There is no evidence of post or pre-event CARs in almost any of the assassinations.
-As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.
-One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days, or almost 4 calendar years.
+This is consistent with expectations as assassinations are typically not predictable.
+As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days, or almost 4 calendar years.
 However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death (although the assassination may have exacerbated the panic).
-In any case, the length of this time period is so long that we omitted it when calculating the mean days to rebound in the figure.
+In any case, the length of this time period is so long that we omitted it when calculating the mean days to rebound in the figure.}
 
-As shown in \autoref{tab:AR-resignations}, and in contrast to coups and assassinations, abnormal returns following resignations are large and positive.
-The mean event day abnormal return is a little over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011).
-But positive stock returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.
+In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
+The mean event day abnormal return is over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011).
+However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.
 
@@
 
+These results are also consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns.
 The positive event day abnormal return following resignations is not surprising since resignations occurred because of ``poor performance and/or loss of authority.'' Leaders were often ousted following corruption charges, financial crises, and/or political violence.
@@
 Indonesia was also hesitant to adopt structural reforms which further weakened its economic image.
-As a result, the crisis gave additional ammo to opposition leaders and public opposition culminated in riots in mid-May 1998.
+As a result, the crisis gave additional ammunition to opposition leaders, and public opposition culminated in riots in mid-May 1998.
 Suharto eventually lost his military support and was forced to resign.
@@
 \subsection{Volatility} \label{subsec: Volatility}
-Although irregular regime changes have disparate effects on the direction of stock returns, the results from \autoref{subsec: Abnormal Returns} suggest that all of these political events increase financial volatility.
+Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, the results from \autoref{subsec: Abnormal Returns} suggest that all of these political events increase financial volatility.
 However, since stock volatility is not directly observable, one must decide how to best estimate volatility.
-My estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
+Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
 As in \citep{jensen2005market} and \citep{leblang2005government}, we use the GARCH (1,1) specification.
@@
 
-The smaller figure within \autoref{fig:volatility} expands the volatility estimates to the 250 trading days before and after each regime change.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-
 \begin{figure}[htb]
@@
 \end{figure}
+
+The smaller figure within \autoref{fig:volatility} expands the volatility estimates to the 250 trading days before and after each regime change.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
 
@@
 First, one can note that neither the 7-day or the 20-day mean CAR from tables \autoref{tab:AR-coups}, \autoref{tab:AR-ass} or \autoref{tab:AR-resignations} are statistically different than zero at even the 10\% level.
-Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do do not always move in the same direction.
-For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la R?a of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.
+Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction.
+For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.
 
@@
 While the Egyptian Revolution may have positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
-As shown in \autoref{fig:CAR-Egypt}, abnormal returns the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
+As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
 To prevent further decline during the uprising, the Egyptian Stock Exchanged closed at the end of trading on January 27th.
@@
 An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'?tat Events Handbook or the Archigos Version 2.9 data set with available financial data.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 2.9 data set with available financial data.
 In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.

### 2017-08-20 doc/paper.tex
Minor changes to prose and figure placement in Section 3, and changes to visualization of Figure 2

@@
 01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
-04/11/2002 & Venezuela & Failed authoritarian to democratic\\
+04/11/2002 & Venezuela & Partial/failed authoritarian to democratic\\
 \hline
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.
-\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).} \autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002.
+We examine this event as well, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
 
@@
 The average coup has a $-2.5\%$ event day AR.
-Event day ARs for the 1970 coup in Argentina, the 1979 coup in South Korea, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
+Event day ARs for the 1970 coup in Argentina, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
 Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero.
@@
 
-Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez.
-These results provide evidence that that coups can in fact result in positive abnormal returns.
+Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}).
+These results provide evidence that coups can in fact result in positive abnormal returns.
 While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
 The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
+
+\begin{figure}[!ht]
+\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'etat attempt}
+\label{fig:AR-Ven}
+\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'etat attempt}
-\label{fig:AR-Ven}
-\end{figure}
-
 The results in the figure are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
@@
 Kennedy on November 22, 1963; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.
-
-These results are consistent with our hypothesis that the nature of the political event and its expect impact on policy matters.
-While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
-Unlike a coup, an assassination is typically a random event that will not necessarily cause immediate change in economic policy.
-As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
 
@@
 
+These results are consistent with our hypothesis that the nature of the political event and its expect impact on policy matters.
+While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
+Unlike a coup, an assassination is typically a random event that will not necessarily cause immediate change in economic policy.
+As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
+
 There is no evidence of post or pre-event CARs in almost any of the assassinations.
@@
 In any case, the length of this time period is so long that we omitted it when calculating the mean days to rebound in the figure.}
-
-In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
-The mean event day abnormal return is over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011).
-However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.
 
@@
 \end{table}
+
+In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
+The mean event day abnormal return is over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011).
+However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.
 

### 2017-08-20 code/03-event-studies.R

@@ -1,6 +1,7 @@
 rm(list = ls())
 library("xtable")
 library("data.table")
+library("Synth")
 load("data/data-clean.RData")
 theme_set(theme_bw())
 source("code/func.R")

### 2017-08-20 code/04-ar.R

@@ -48,7 +48,10 @@ ven.es <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
 ven.es$ar.treat[, lar := ar - qnorm(.975) * ven.es$sigma.treat]
 ven.es$ar.treat[, uar := ar + qnorm(.975) * ven.es$sigma.treat]
 p <- ggplot(ven.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) + 
-  geom_pointrange(aes(ymin = lar, ymax = uar), size = .2) +
+  geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") +
+  geom_vline(aes(xintercept = 0), linetype = 2, color = "grey") +
+  geom_pointrange(aes(ymin = lar, ymax = uar), size = .3) +
   xlab("Trading days") + ylab("AR (%)") +
-  geom_hline(aes(yintercept = 0), linetype = 2)
+  theme_classic()
+print(p)
 ggsave("figs/venezuela_coup_attempt_2002.pdf", p, height = 5, width = 7)

### 2017-08-21 doc/paper.tex
Updated bibliographic style to APA and made a couple of minor wordsmithing changes.

@@
 \usepackage{setspace}
-\usepackage{natbib}
 \usepackage{enumitem}
@@
 % bibliography packages
-\usepackage{natbib}
+\usepackage[natbibapa]{apacite}
+\bibliographystyle{apacite}
 \bibpunct{(}{)}{;}{a}{}{,}
-\bibliographystyle{apsr}
 \renewcommand{\bibname}{References}
@@
 In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after it.
-This suggests that financial volatility increase during the days surrounding regime changes, although it does not provide any evidence on mean returns.
+This suggests that financial volatility increases during the days surrounding regime changes, although it does not provide any evidence on mean returns.
 
@@
 The second concern is addressed using non-parametric statistical techniques, which are free from distributional assumptions.
-we employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citep{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
+We employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citep{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
 

### 2017-08-22 doc/paper.tex
Updated abstract. Give this a read and see if you like the framing of the argument, description of the methodology, etc.

@@
 We examine the relationship between political instability and daily returns of national stock indices.
-Financial volatility increases dramatically following (and immediately before) ``irregular'' regime changes caused by coup d'etat, assassinations, and resignations.
-Some of the pre-resignation volatility occurs due to actions that precede the resignation such as public protests, riots, and popular demonstrations.
-However, these irregular regime changes have disparate effects on the direction of stock returns.
-Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the temporary ousting of Hugo Chavez during the 2002 Venezuelan coup attempt result in positive abnormal returns of 20\% or more.
+A common hypothesis is that political instability discourages investment and reduces economic growth.
+By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime changes have disparate effects on stock returns.
+We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (6\%), while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
+The impact of coups tends to be negative, but some events such as the 2002 temporary ousting of Hugo Chavez in Venezuela result in positive abnormal returns of 20\% or more.
+We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
 \end{abstract}

### 2017-08-23 doc/paper.tex
Updated Table 1 to explicitly use Polity IV definitions of regime type

@@
 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g.
-a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome in \autoref{tab:coup list} below.
+a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome as defined by the Polity IV Project in \autoref{tab:coup list} below.
 
@@
 \endlastfoot
-06/08/1970 & Argentina & Authoritarian to authoritarian\\
-03/22/1971 & Argentina & Authoritarian to authoritarian\\
-03/24/1976 & Argentina & Democratic to authoritarian\\
-10/06/1976 & Thailand & Democratic to authoritarian\\
-10/20/1977 & Thailand & Authoritarian to authoritarian\\
-12/12/1979 & South Korea & Authoritarian to authoritarian\\
-02/23/1991 & Thailand & Democratic to authoritarian\\
-04/05/1992 & Peru & Democratic to authoritarian\\
-10/12/1999 & Pakistan & Democratic to authoritarian\\
-10/04/2002 & Nepal & Democratic to authoritarian\\
-09/19/2006 & Thailand & Democratic to authoritarian\\
-01/11/2007 & Bangladesh & Authoritarian to authoritarian\\
-04/11/2002 & Venezuela & Partial/failed authoritarian to democratic\\
+06/08/1970 & Argentina & Autocracy to autocracy\\
+03/22/1971 & Argentina & Autocracy to autocracy (democracy by 1973)\\
+03/24/1976 & Argentina & Democracy to autocracy\\
+10/06/1976 & Thailand & Anocracy to autocracy\\
+10/20/1977 & Thailand & Autocracy to autocracy\\
+12/12/1979 & South Korea & Autocracy to autocracy\\
+02/23/1991 & Thailand & Anocracy to anocracy\\
+04/05/1992 & Peru & Democracy to anocracy\\
+10/12/1999 & Pakistan & Democracy to autocracy\\
+10/04/2002 & Nepal & Democracy to autocracy\\
+09/19/2006 & Thailand & Democracy to anocracy\\
+01/11/2007 & Bangladesh & Democracy to autocracy\\
+ & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
+04/11/2002 & Venezuela & Partial/failed anocracy to democracy\\
 \hline

### 2017-08-23 doc/paper.tex
Reviewed most recent Polity IV and Archigos data files. Added two new coups to Table 1. We should add these events (Egypt 2013 and Thailand 2014) to the coup analysis.

@@
 01/11/2007 & Bangladesh & Democracy to autocracy\\
+07/03/2013 & Egypt & Anocracy to anocracy\\
+05/22/2014 & Thailand & Democracy to anocracy\\
  & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
-04/11/2002 & Venezuela & Partial/failed anocracy to democracy\\
+04/11/2002 & Venezuela & Partial/failed democracy to democracy\\
 \hline
@@
 
-We further supplement the CSP data with leadership data from Archigos Version 2.9, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
+We further supplement the CSP data with leadership data from Archigos Version 4.1, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
 coups, revolts and assassinations).
@@
 An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 2.9 data set with available financial data.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
 In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.

### 2017-08-23 doc/paper.tex
Made changes to conclusion and section 4. Also added sub-subsections to section 3. I actually think we should make section 4 a subsection of section 3, but we can discuss before I do that.

@@
 A common hypothesis is that political instability discourages investment and reduces economic growth.
-By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime changes have disparate effects on stock returns.
+By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime change have disparate effects on stock returns.
 We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (6\%), while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events such as the 2002 temporary ousting of Hugo Chavez in Venezuela result in positive abnormal returns of 20\% or more.
+The impact of coups tends to be negative, but some events result in positive abnormal returns of 20\% or more.
+We also find that volatility increases during times of protest preceding resignations, but that no clear directionality is present.
 We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
@@
 
-\section{Irregular Regime Changes} \label{sec: Irregular Regime Changes}
+\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
 \subsection{Abnormal Returns} \label{subsec: Abnormal Returns}
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).} \autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002.
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
+
+\subsubsection{Coups} \label{subsec: Coups}
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002.
 We examine this event as well, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
@@
 While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
-The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
+By 1973 Argentina had transitioned to a democracy.\footnote{Based on Polity IV polity score of 6.
+Values of 6-10 are defined as democracies.} The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
 
@@
 The unexpected nature of the event means that the abnormal returns capture the true value of the regime change from Chavez to Carmona more accurately than they otherwise would.
+
+\subsubsection{Assassinations} \label{subsec: Assassinations}
 
@@
 
-These results are consistent with our hypothesis that the nature of the political event and its expect impact on policy matters.
+These results are consistent with our hypothesis that the nature of the political event and its expected impact on policy matters.
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
@@
 \end{table}
+
+\subsubsection{Resignations} \label{subsec: Resignations}
 
@@
 
-While the Egyptian Revolution may have positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
+While the Egyptian Revolution may have had positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
 As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
@@
 The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
-Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'?tat Events Handbook and Archigos Version 2.9.
+Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
 Additional Lexis Nexis searches were used to verify these descriptions.
@@
 In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
-The variable, \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive are and 0 otherwise.
+The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
 Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
@@
 Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.
+
+We therefore find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
 
@@
 \scriptsize
-Notes: Standard errors clustered by event are in parentheses. Statistical significance at the 10\%, 5\%, and 1\% level is denoted by *, ** and *** respectively.
+Notes: Standard errors clustered by event are in parentheses.
 \end{threeparttable}
@@
 \section{Conclusion}
-This paper has examined the economic effects of irregular regime changes.
+This paper has examined the effects of irregular regime changes on financial returns.
 It uses an event study approach to show that investors expect irregular regime changes to have large effects on equity returns.
@@
 Financial volatility surrounding regime changes, which is often characterized by large positive \textit{and} negative stock returns, suggests that irregular regime changes increase policy uncertainty.
-The variation in the direction of abnormal returns is consistent with the idea that not all governments are created equally.
-Abnormal returns are likely positive following resignations because those leaders were the most likely to be ``bad'' leaders.
+The variation in the direction of abnormal returns is consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.
+Abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership.
 

### 2017-08-25 doc/paper.tex
Added some additional citations.

@@
 The impact of coups tends to be negative, but some events result in positive abnormal returns of 20\% or more.
-This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups}.
+This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
 However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.

### 2017-08-26 doc/paper.tex
Minor wordsmithing and typo corrections.

@@
 These models tend to focus on government policy instruments that affect private rates of return on investment.
-The general argument is that political instability causes governments to act myopically and adopt inefficient policies.
-\footnote{For instance, \citep{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+The general argument is that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citep{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
 Similarly, \citep{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
@@
 
-\autoref{sec: Irregular Regime Changes} tests these results more formally.
+\autoref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
 It will first analyze coups, assassinations and resignations separately and determine whether they increase mean returns.
@@
 We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
-\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
@@
 \subsubsection{Coups} \label{subsec: Coups}
+\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
 \autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002.
@@
 While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
-By 1973 Argentina had transitioned to a democracy.\footnote{Based on Polity IV polity score of 6.
-Values of 6-10 are defined as democracies.} The ultimately failed coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
+In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Polity IV polity score of 6.
+Values of 6-10 are defined as democracies.} The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
 
@@
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
-Unlike a coup, an assassination is typically a random event that will not necessarily cause immediate change in economic policy.
+Unlike a coup, an assassination is typically a random event that may not necessarily cause immediate change in economic policy.
 As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
@@
 This is done to combine events since resignations tend to increase returns while assassinations and coups tend to decrease them.
-The idea that the absolute value of returns might increase during irregular regime changes is similar to the finding that volatility increases and consistent with \autoref{fig:AV-DR}.
+The idea that the absolute value of returns might increase during irregular regime changes is similar to the finding that volatility increases and is consistent with \autoref{fig:AV-DR}.
 
@@
 
-Fianlly, to check whether our results are sensitive to model specificaiton, we estimated market models in addition to the baseline constant returns model.
-We used the MSCI World Index as a proxy for ther market return.
+Finally, to check whether our results are sensitive to model specification, we estimated market models in addition to the baseline constant returns model.
+We used the MSCI World Index as a proxy for their market return.
 [To do: add table for this]

### 2017-08-26 doc/paper.tex
Added PDF to repository

@@
 
+\subsubsection{Public Protests} \label{subsec: Public Protests}
+The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
+While the previous section showed that the resignations themselves had large effects on stock returns, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
+Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
+
+A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
+The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
+Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
+
+While the Egyptian Revolution may have had positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
+As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
+To prevent further decline during the uprising, the Egyptian Stock Exchanged closed at the end of trading on January 27th.
+President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
+
+\begin{figure}[!ht]
+\includegraphics{../figs/egypt-revolution-2011.pdf}
+\caption{Cumulative abnormal returns during the Egyptian revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+An important question is whether other popular uprisings have had similar adverse economic consequences.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
+These events are listed in \autoref{tab:protest-list} in the appendix.
+
+The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
+Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
+Additional Lexis Nexis searches were used to verify these descriptions.
+
+In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
+The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
+Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
+
+Column (1) suggests that public protests have no effect on stock returns.
+However, this occurs because some political movements increase stock prices while others decrease them.
+As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests.
+These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
+To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
+The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests.
+Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}
+
+We therefore find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+
+\begin{table}[!ht]
+\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
+  \hline
+  \hline
+\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
+\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
+ & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
+  \hline
+\ExpandableInput{../tables/protest-regtable.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors clustered by event are in parentheses.
+\end{threeparttable}
+\end{center}
+\end{table}
+
 \subsection{Volatility} \label{subsec: Volatility}
@@
 
-\section{Public Protests} \label{sec: Public Protests}
-The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
-While the previous section showed that the resignations themselves had large effects on stock returns and volatility, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
-Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
-
-The most recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
-The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
-Examples of public discontent included demonstrations, marches, riots and non-violent civil disobedience, and labor strikes.
-
-While the Egyptian Revolution may have had positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
-As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
-To prevent further decline during the uprising, the Egyptian Stock Exchanged closed at the end of trading on January 27th.
-President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
-
-\begin{figure}[!ht]
-\includegraphics{../figs/egypt-revolution-2011.pdf}
-\caption{Cumulative abnormal returns during the Egyptian revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
-In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
-These events are listed in \autoref{tab:protest-list} in the appendix.
-
-The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
-Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
-Additional Lexis Nexis searches were used to verify these descriptions.
-Start dates were determined through similar means.
-
-In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
-The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
-Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
-
-Column (1) suggests that public protests have no effect on stock returns.
-However, this occurs because some political movements increase stock prices while others decrease them.
-As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests.
-These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
-To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
-The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests.
-Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.
-
-We therefore find that both volatility and the absolute value of returns increase during times of protest.
-Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
-
-\begin{table}[!ht]
-\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
-  \hline
-  \hline
-\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
-\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
- & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
-  \hline
-\ExpandableInput{../tables/protest-regtable.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors clustered by event are in parentheses.
-\end{threeparttable}
-\end{center}
-\end{table}
-
 \section{Conclusion}

### 2017-08-27 doc/paper.tex
Changed incorrect uses of citep to citet.

@@
 This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.
-\footnote{In particular, \citep{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-On the other hand, \citep{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
+\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
+On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
 Not all political instability is equivalent - resignations, assassinations, and coups are each examples of political instability, but may have disparate effects on financial returns.
 Further, political instability may be seen as a \textit{positive} event if the current regime is regarded as strongly anti-business or anti-global.
-\citep{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+\citet{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
 
-As in \citep{alesina1996political}, we use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
+As in \citet{alesina1996political}, we use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
 The major innovation of this paper is that, in contrast to the aforementioned cross country studies, we analyze the impact of political instability using daily financial data.
@@
 These models tend to focus on government policy instruments that affect private rates of return on investment.
-The general argument is that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citep{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
-Similarly, \citep{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+The general argument is that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
 The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
@@
 The second looks at how the variance of stock market returns reacts to political events.
-\citep{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
-\citep{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
+\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
+\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
 
 The third strand examines the impact of leaders on political and economic outcomes.
-\citep{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
+\citet{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
 Their results indicate that leaders influence monetary policy and economic growth.
-\citep{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
+\citet{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
 
@@
 We begin our analysis by studying the effect of irregular regime changes on stock returns.
-We follow the standard event study methodology as presented by, among others, \citep{mackinlay1997event} and \citep{campbell1997econometrics}.
+We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
 Normal performance is measured with a constant mean return model\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations (plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995 respectively).
@@
 We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citep{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
 
@@
 Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
-As in \citep{jensen2005market} and \citep{leblang2005government}, we use the GARCH (1,1) specification.
+As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
 In particular, for national stock index $i$,
@@
 
-To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citep{abadie2003economic} and \citep{abadie2010synthetic}.
+To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
 Each country is given a weight which represents its influence in the synthetic control portfolio.
@@
 The second concern is addressed using non-parametric statistical techniques, which are free from distributional assumptions.
-We employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citep{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
+We employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
 
@@
 Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citep{abadie2003economic} for further details.}
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
 

### 2017-08-27 doc/paper.tex
Citation corrections

@@
 The S\&P/IFC index includes securities from emerging markets while the MSCI index includes securities from developed markets only.
-We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citep{jones2009hit}.
+We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
 Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available time series for these stock indices are listed in \autoref{tab:stock list}.

### 2017-08-29 doc/paper.tex
Additional wordsmithing, typo, and citation corrections

@@
 For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.
-In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \textit{World Investment and Political Risk} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability) \citep{wipr2013}.
-In 2011 and 2012, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-\footnote{The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.}
+In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).\footnote{MIGA stopped publishing annual \textit{World Investment and Political Risk} reports in 2013.} In  \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.\footnote{The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.}
 
 A common hypothesis is that political instability discourages investment and reduces economic growth by increasing policy uncertainty.
-This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.
-\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
+This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
 On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
@@
 The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups.\footnote{\citep[p.
+We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g.
@@
 
-The Coup d'etat Events handbook also provides a list of 1) auto-coups, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
+The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime"}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
 Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
@@
 The absolute value of returns on the event day (trading day 0) are significantly larger than on any other day.
-In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after it.
+In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after.
 This suggests that financial volatility increases during the days surrounding regime changes, although it does not provide any evidence on mean returns.
@@
 While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
-In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Polity IV polity score of 6.
+In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Center for System Peace Polity IV polity score of 6.
 Values of 6-10 are defined as democracies.} The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
@@
 While the previous section showed that the resignations themselves had large effects on stock returns, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
-Indeed, corporate investors in the 2011 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
+Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
 

### 2018-07-12 doc/paper.tex
Added additional literature to literature review
Re-runs analysis with new data

@@
 By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime change have disparate effects on stock returns.
-We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (6\%), while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events result in positive abnormal returns of 20\% or more.
+We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (4\%), while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
+The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
 We also find that volatility increases during times of protest preceding resignations, but that no clear directionality is present.
-We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+We therefore find that the expected direction and magnitude of abnormal returns is dependent on the type of political event and its expected impact on economic policy.
 \end{abstract}
@@
 This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.} However, such hypotheses are overly simplistic.
+On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.}
+
+Such hypotheses are overly simplistic.
 Not all political instability is equivalent - resignations, assassinations, and coups are each examples of political instability, but may have disparate effects on financial returns.
@@
 However, unlike the previously mentioned studies, we find that these irregular regime changes have disparate effects on the direction of stock returns.
-Abnormal returns following resignations are large and positive (6\%) while abnormal returns following assassinations are negative and smaller in magnitude (1\%).
-The impact of coups tends to be negative, but some events result in positive abnormal returns of 20\% or more.
+Abnormal returns following resignations are large and positive (4\%) while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
+The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
 This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
@@
 \citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
+\citet{mcgillivray2003redistributive} examines the impact of electoral systems and partisan shifts on stock prices, but is primarily focused on inter-industry variation.
 
@@
 We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
-Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available time series for these stock indices are listed in \autoref{tab:stock list}.
+Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available daily time series for these stock indices are listed in \autoref{tab:stock list}.
 
@@
 \endlastfoot
-Argentina & Beunos Aires SE General Index & Dec-66 & Jan-13\\
-Australia & Australia ASX All Ordinaries & Jan-58 & Jan-13\\
-Bangladesh & Dhaka SE Index & Jan-90 & Apr-09\\
-Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-13\\
-Chile & Santiago IGBC General Index & Jan-75 & Jan-13\\
-Colombia & Colombia IGBC General Index & Jan-92 & Jan-13\\
-Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Nov-11\\
-Egypt & Cairo SE Index & Dec-92 & Jan-13\\
-Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-13\\
-France & France CAC All-Tradable Index & Sep-68 & Jan-13\\
-Greece & Athens SE General Index & Oct-88 & Jan-13\\
-India & Bombday SE SENSEX & Apr-79 & Jan-13\\
-Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-13\\
-Iran & Tehran SE Price Index & Jan-95 & Mar-12\\
-Israel & Tel Aviv 100 Index & May-87 & Jan-13\\
-Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-13\\
-Latin America & Dow Jones Latin America Index & Jan-92 & Jan-13\\
+Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
+Australia & Australia ASX All Ordinaries & Jan-58 & Jan-17\\
+Bangladesh & Dhaka SE Index & Jan-90 & Jan-17\\
+Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-17\\
+Chile & Santiago IGBC General Index & Jan-75 & Jan-17\\
+Colombia & Colombia IGBC General Index & Jan-92 & Jan-17\\
+Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Jan-17\\
+Egypt & Cairo SE Index & Dec-92 & Jan-17\\
+Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-17\\
+Greece & Athens SE General Index & Oct-88 & Jan-17\\
+India & Bombday SE SENSEX & Apr-79 & Jan-17\\
+Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-17\\
+Iran & Tehran SE Price Index & Jan-95 & Jan-17\\
+Israel & Tel Aviv 100 Index & May-87 & Jan-17\\
+Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-17\\
+Latin America & Dow Jones Latin America Index & Jan-92 & Jan-17\\
 Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
-Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-13\\
-Nepal & Nepal NEPSE Stock Index & Jul-97 & Jul-99\\
-Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-13\\
-Pakistan & Karachi SE 100 Index & Jan-89 & Jan-13\\
+Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-17\\
+Nepal & Nepal NEPSE Stock Index & Jan-01 & Jan-17\\
+Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-17\\
+Pakistan & Karachi SE 100 Index & Jan-89 & Jan-17\\
 Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
-Peru & Lima SE General Index & Jan-82 & Jan-13\\
-Philippines & Manila SE Composite Index & Jan-86 & Jan-13\\
-Portugal & Oporto PSI-20 Index & Jan-86 & Jan-13\\
-Singapore & Singapore FTSE ST Index & Jul-65 & Jan-13\\
-South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-13\\
-Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-13\\
-Spain & Madrid SE General Index & Aug-71 & Jan-13\\
-Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-13\\
-Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-13\\
-Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-13\\
-Thailand & Thailand SET General Index & Apr-75 & Jan-13\\
-Tunisia & Tunisia SE Index & Dec-97 & Jan-13\\
-Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-13\\
-Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-13\\
-United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-13\\
-United States & Dow Jones Industrial Average & Feb-1885 & Jan-13\\
-Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jan-13\\
+Peru & Lima SE General Index & Jan-82 & Jan-17\\
+Philippines & Manila SE Composite Index & Jan-86 & Jan-17\\
+Portugal & Oporto PSI-20 Index & Jan-86 & Jan-17\\
+Singapore & Singapore FTSE ST Index & Jul-65 & Jan-17\\
+South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-17\\
+Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-17\\
+Spain & Madrid SE General Index & Aug-71 & Jan-17\\
+Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-17\\
+Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-17\\
+Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-17\\
+Thailand & Thailand SET General Index & Apr-75 & Jan-17\\
+Tunisia & Tunisia SE Index & Dec-97 & Jan-17\\
+Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-17\\
+Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-17\\
+United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-17\\
+United States & Dow Jones Industrial Average & Feb-1885 & Jan-17\\
+Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jul-16\\
 Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
-Venezuela & Caracas SE General Index & Jan-94 & Jan-13\\
-World & MSCI World Price Index & Jan-76 & Jan-13\\
+Venezuela & Caracas SE General Index & Jan-94 & Jan-17\\
+World & MSCI World Price Index & Jan-76 & Jan-17\\
 Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
-Zambia & Zambia LuSE Index & Jan-02 & Apr-06\\
+Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
+
 \hline
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the partial/failed Venezuelan coup attempt of 2002.
-We examine this event as well, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the Argentinian coup of March 24, 1976 and the partial/failed Venezuelan coup attempt of 2002.
+The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}  We later examine the Venezuelan coup attempt of 2002 in detail, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
 
@@
 
-The failed coup attempt against Hugo Chavez is a perfect natural experiment because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+The failed coup attempt against Hugo Chavez allows us to examine the effects of both pro-business and anti-business regime change separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
-The abnormal return on April 12, the first trading day in which investors could react to the coup, was 19.5\%.
-The market reacted similarly, albeit in the opposite direction, to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -14\%.
+The abnormal return on April 12, the first trading day in which investors could react to the coup, was 10\%.
+The market reacted similarly, albeit in the opposite direction, to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
 
 The results in the figure are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
-The only other day in which the ARs are statistically different from zero is on the third trading day after the coup attempt.
+The only days on which the ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
 
@@
 The mean event day abnormal return is negative and statistically different than zero.
-However, the result is driven almost entirely by three events: the shooting of U.S.
+However, the result is driven by five events: the shooting of U.S.
 President William McKinley on September 6, 1901; the assassination of U.S.
 President John F.
-Kennedy on November 22, 1963; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.
+Kennedy on November 22, 1963; the assassination of Indian Prime Minister Indira Gandhi on October 31, 1984; the suicide bombing that killed Sri Lankan president Ranasinghe Premadasa on May 1, 1993; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.
 
@@
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
-Unlike a coup, an assassination is typically a random event that may not necessarily cause immediate change in economic policy.
+Unlike a coup, an assassination is typically an unexpected event that may not necessarily cause immediate change in economic policy.
 As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
@@
 In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
-The mean event day abnormal return is over 6\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in one out of the fifteen resignations (Tunisia on June 31, 2011).
-However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero.
+The mean event day abnormal return is over 4\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in two out of the fifteen resignations (Pakistan on April 19, 1993 and Tunisia on June 31, 2011).
+However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero [[\textit{This doesn't look right to me.
+The positive returns seem persistent and to grow larger over time}]].
 
 These results are also consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns.
-The positive event day abnormal return following resignations is not surprising since resignations occurred because of ``poor performance and/or loss of authority.'' Leaders were often ousted following corruption charges, financial crises, and/or political violence.
-For example, consider Suharto's resignation from office as the President of Indonesia on May 1998, just after the 1997 Asian Financial Crisis.
+The positive event day abnormal return following resignations is not surprising since resignations typically occurr because of poor performance and/or loss of authority.
+Leaders were often ousted following corruption charges, financial crises, and/or political violence.
 
+For example, consider Muhammad Suharto's resignation from office as the President of Indonesia on May 1998, just after the 1997 Asian Financial Crisis.
 Prior to the crisis, the Indonesian economy suffered from a number of ailments including crony capitalism, poor corporate governance, growing short-term debt and a corrupt banking system \citep{radelet2000onset}.
@@
 
-While the Egyptian Revolution may have had positive pro-democracy effects on the Egpytian political system, its short-term impact on the economy was disastrous.
+Despite heralding the beginning of the ``Arab Spring,'' the short-term impact of the Egyptian Revolution on the economy was disastrous.
 As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
@@
 
-As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 5\% level using the rank test statistic and the abnormal returns for coups and resignations are significant at at least the 10\% level using the sign test.
+As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 5\% level using the rank test statistic and the abnormal returns for coups, assassinations, and resignations are significant at at least the 10\% level using the sign test.
 In addition, abnormal absolute returns for all events are statistically significant at the 1\% level using both the rank and sign statistics.
-On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level.
-Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups, resignations and all events combined when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec: Abnormal Returns} are not an artifact of deviations from normality or confounding world events.
+On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level [[\textit{This is not true for all events using the sign test, which seems odd to me}]].
+Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (10\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec: Abnormal Returns} are not an artifact of deviations from normality or confounding world events.
 
 The third concern, which is that the political events in this paper are not unexpected, is addressed in a number of ways.
-First, one can note that neither the 7-day or the 20-day mean CAR from tables \autoref{tab:AR-coups}, \autoref{tab:AR-ass} or \autoref{tab:AR-resignations} are statistically different than zero at even the 10\% level.
+First, one can note that neither the 7-day or the 20-day mean CAR from tables \autoref{tab:AR-coups}, \autoref{tab:AR-ass} or \autoref{tab:AR-resignations} are statistically different than zero at even the 10\% level [[\textit{Not true for resignations 20 day}]].
 Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction.
-For example, there was a negative 11.8\% 7-day CAR preceding the resignation of President Estrada of the Philippines in January of 2001 and a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though both resignations were associated with large positive event day abnormal returns.
+For example, there was a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though the resignation was associated with large positive event day abnormal returns.
 
@@
 We used the MSCI World Index as a proxy for their market return.
-[To do: add table for this]
+[To do: add table for this]  [[\textit{Is this necessary?}]]
 
@@
 
-The results are consistent with the idea that government competence is a random walk and that government changes have large impacts on investor confidence.
-Financial volatility surrounding regime changes, which is often characterized by large positive \textit{and} negative stock returns, suggests that irregular regime changes increase policy uncertainty.
-The variation in the direction of abnormal returns is consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.
+The results are consistent with the idea that perceptions of government competence and changes in government  have large impacts on investor confidence.
+Financial volatility surrounding regime changes, which is often characterized by large negative \textit{and} positive stock returns, suggests that irregular regime changes increase policy uncertainty and volatility, but that uncertainty does not tell the whole story.
+The direction of returns depends on the expected outcome of the irregular regime change.
+The variation in the direction of abnormal returns is therefore consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.
 Abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership.
 
-Although this study is based on only 35 events, the size of the effects suggests that it should not be dismissed.
-Irregular regime changes are important economic events than can drastically alter the economic landscape.
-For instance, the 21.26\% increase in the Venezuelan Stock Index following the temporary ousting of Hugo Chavez in 2002 is its 4th largest increase since 1994.
-In comparison, the Hong Kong Stock Index (Hang Seng Index) decreased by 21.7\% following the 1989 massacre of Chinese protestors in Tiananmen square and the Dow Jones Industrial Average in the United States fell by 22.61\% on Black Monday (1997), the largest one-day drop in its history.
+\newpage
 
@@
 
+\newpage
 \pdfbookmark[1]{References}{References}

### 2018-07-12 code/01-clean.R

@@ -82,6 +82,9 @@ regime.change <- event[type == "Coup" | type == "Assassination" |
                          type == "Resignation", 
                        .(country, ticker, stock_date, type)]
 
+# Drop March 1976 Argentinian coup due to market closure
+regime.change <- regime.change[stock_date != '1976-04-05'] 
+
 # SAVE DATA --------------------------------------------------------------------
 save(country.lookup, event, index, regime.change, rev,
      file = "data/data-clean.RData")

### 2018-07-14 code/01-clean.R
Removed non-daily stock data
Removed all non-daily returns data and re-ran analysis. This fixed the issues with the spikes in volatility, and smoothed out some of the other results as well.

@@ -35,6 +35,23 @@ indices[, year := as.numeric(format(date, format = "%Y"))]
 indices[, dow := day.of.week(month, day, year)]
 event[, stock_date := as.Date(stock_date,"%m/%d/%Y")]
 
+# Remove non-daily values from indices dataframe
+indice_info <- read.csv("data-raw/indices.csv", nrows = 45, header = TRUE, 
+                    stringsAsFactors = FALSE)
+
+indice_info <- as.data.table(indice_info)
+
+indice_info$daily = sub('.*Daily From ', '', indice_info$Periodicity)
+indice_info$daily = gsub("To.*$", "", indice_info$daily)
+
+indice_info$daily = as.Date(paste('01', indice_info$daily), format='%d %b %Y')
+indice_info = indice_info[, c('Ticker', 'daily')]
+
+setnames(indice_info, c("ticker", "daily"))
+indices <- merge(indices, indice_info, by="ticker")
+indices <- indices[date >= daily]
+indices = indices[, daily := NULL]
+
 # Correct Argentina data for shift in indexing in 1983 and 1988
 indices[, real_p := ifelse(date >= "1983-01-01" &
                            date < "1988-01-01" &

### 2018-07-14 doc/paper.tex
Minor updates to doc

@@
 
-The average coup has a $-2.5\%$ event day AR.
+The average coup has a $-2.1\%$ event day AR.
 Event day ARs for the 1970 coup in Argentina, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
@@
 
-Despite heralding the beginning of the ``Arab Spring,'' the short-term impact of the Egyptian Revolution on the economy was disastrous.
+The short-term impact of the Egyptian Revolution on the economy was disastrous.
 As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.

### 2018-07-25 doc/paper.tex
Updated introduction
Updated the introduction to focus on whether political instability is ever good and the debate within current poli sci literature on this topic.

@@
 \begin{abstract}
-We examine the relationship between political instability and daily returns of national stock indices.
+We examine the relationship between political instability and daily returns of national stock indices in every country that experienced a coup, assassination, or resignation for which daily data is available.
 A common hypothesis is that political instability discourages investment and reduces economic growth.
@@
 \section{Introduction} \label{sec:Introduction}
-For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.
-In fact, in the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report, executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).\footnote{MIGA stopped publishing annual \textit{World Investment and Political Risk} reports in 2013.} In  \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.\footnote{The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.}
 
-A common hypothesis is that political instability discourages investment and reduces economic growth by increasing policy uncertainty.
-This hypothesis is supported by cross country empirical evidence that political instability - as measured by regime change frequency or political violence - is negatively correlated with investment, GDP growth, and financial development in cross country regressions \citep{alesina1996political,alesina1996income,roe2011political}.\footnote{In particular, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-On the other hand, \citet{londregan1990poverty} finds that coups have no effect on economic growth.}
+The image of a coup or popular uprising ousting an autocratic ruler and installing a democratic government is an evocative one.
+However, both recent events and prior research suggest that coups rarely lead to democracy.
+In the wake of the Arab Spring - in which rulers were deposed in four countries and major protests occurred in six more - only Tunisia ultimately transitioned to democracy.
+These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
 
-Such hypotheses are overly simplistic.
-Not all political instability is equivalent - resignations, assassinations, and coups are each examples of political instability, but may have disparate effects on financial returns.
-Further, political instability may be seen as a \textit{positive} event if the current regime is regarded as strongly anti-business or anti-global.
-\citet{alesina1996political} takes the possibility of a new government adopting better economic policies seriously, but argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+Political instability is also thought to harm investment.
+For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
+In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These investor sentiments are supported by empirical research that suggests political instability - as measured by regime change frequency or political violence - is negatively correlated with investment and financial development in cross country regressions \citep{alesina1996income,roe2011political}.
+In addition, the variance of stock market returns is also estimated to increase in response to political instability.\footnote{\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain, while \citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility of the Brazilian stock market.}
 
+Political instability is also hypothesized to reduce economic growth by increasing policy uncertainty.
+This hypothesis is once again supported by cross country empirical evidence that political instability is negatively correlated with GDP growth \citep{alesina1996political, fosu1992political, aisen2013does, jong2009measurement}.
+For example, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
+The exception to this conclusion is \citet{londregan1990poverty}, who find that coups have no effect on economic growth.
+Additional research focuses on government policy instruments that affect private rates of return on investment, and argues that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
+
+However, such hypotheses are often overly simplistic.
+Not all political instability is equivalent - resignations, assassinations, and coups are all examples of political instability, but may have disparate effects on financial returns.
+Resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
+Assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
+Coups can occur in the name of democracy or autocracy, and in generally signal relative weakness in the current political system.
+Further, political instability may be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
+\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+
+\bigskip
+
+We use financial performance as an indicator of whether the market views political stability as ``good'' for economic growth.
 As in \citet{alesina1996political}, we use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
@@
 This enables us to use market expectations to quantify the economic impact of each individual type of regime change.
-The advantage of this event study approach is that it allows us to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.
+The advantage of this event study approach is that it allows us to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.\footnote{A growing body of work uses event studies to assess political phenomenon.
+For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.}
 
-We find that financial volatility increases dramatically following (and just before) coup d'etat, assassinations, and resignations.
+We find that financial volatility increases dramatically following (and just before) coups d'etat, assassinations, and resignations.
 However, unlike the previously mentioned studies, we find that these irregular regime changes have disparate effects on the direction of stock returns.
@@
 The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
-This finding is consistent with research that shows that ``good coups'' - coups that lead to democratization and economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
+
+These findings are consistent with research that shows that ``good coups'' - coups that lead to democratization or economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
 However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
@@
 Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule, exacerbate poor economic policies, or merely increase policy uncertainty have the opposite effect.
-
-\bigskip
-
-This paper is closely related to four branches of literature.
-The first analyzes the economic impact of political instability.
-This area contains a number of theoretical models in addition to the empirical work already mentioned.
-These models tend to focus on government policy instruments that affect private rates of return on investment.
-The general argument is that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
-Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
-
-The second looks at how the variance of stock market returns reacts to political events.
-\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain.
-\citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility (but not the mean return) of the Brazilian stock market.
-\citet{mcgillivray2003redistributive} examines the impact of electoral systems and partisan shifts on stock prices, but is primarily focused on inter-industry variation.
-
-The third strand examines the impact of leaders on political and economic outcomes.
-\citet{jones2005leaders} identify exogenous leadership transitions using deaths of leaders from natural causes or accidents.
-Their results indicate that leaders influence monetary policy and economic growth.
-\citet{jones2009hit} find that transitions to democracy are more likely after the assassinations of autocrats.
-
-The fourth uses event studies to assess political phenomenon.
-A growing body of work uses political events to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.
 

### 2018-11-23 code/03-event-studies.R
Modify code so that all statistical models converge. Some minor edits to plots

@@ -3,7 +3,6 @@ library("xtable")
 library("data.table")
 library("Synth")
 load("data/data-clean.RData")
-theme_set(theme_bw())
 source("code/func.R")
 
 # EVENT STUDY ------------------------------------------------------------------
@@ -24,7 +23,8 @@ for (i in 1:n.es){
   }
   
   # use custom V in synth to deal with singular matrix in optim
-  if (regime.change$stock_date[i] == mydate("10/4/2002")){
+  if (regime.change$stock_date[i] == mydate("10/4/2002") |
+      regime.change$stock_date[i] == mydate("5/3/1993")){
       custom.v.i <- rep(1, 2)
   } else{
       custom.v.i <- NULL

### 2018-11-23 code/04-ar.R

@@ -2,6 +2,7 @@ rm(list = ls())
 library("xtable")
 library("data.table")
 library("ggplot2")
+library("scales")
 load("data/data-clean.RData")
 load("output/regime-change-event-study.RData")
 theme_set(theme_bw())
@@ -52,6 +53,8 @@ p <- ggplot(ven.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) +
   geom_vline(aes(xintercept = 0), linetype = 2, color = "grey") +
   geom_pointrange(aes(ymin = lar, ymax = uar), size = .3) +
   xlab("Trading days") + ylab("AR (%)") +
+  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
   theme_classic()
 print(p)
 ggsave("figs/venezuela_coup_attempt_2002.pdf", p, height = 5, width = 7)

### 2018-11-23 code/05-volatility.R

@@ -29,7 +29,8 @@ garch.spec <- ugarchspec(mean.model = list(armaOrder = c(0,0)),
 
 # run models
 for (i in 1:n.rc){
-  rc.garchfit <- ugarchfit(spec = garch.spec, data = dat[[i]]$dr)
+  rc.garchfit <- ugarchfit(spec = garch.spec, data = dat[[i]]$dr,
+                           solver.control = list(tol = 1e-6))
   dat[[i]]$garch_volatility <- rc.garchfit@fit$sigma
   print(i)
 }
@@ -44,6 +45,6 @@ p.volatility <-
   geom_line(color = "grey48") + 
   xlab("Trading days") + 
   ylab("Mean volatility") +
-  theme_classic()
+  theme_minimal()
 
 ggsave("figs/mean-volatility.pdf", p.volatility, height = 5, width = 7)

### 2018-11-23 code/06-sensitivity.R

@@ -4,7 +4,7 @@ load("data/data-clean.RData")
 library("data.table")
 library("ggplot2")
 source("code/func.R")
-theme_set(theme_bw())
+theme_set(theme_minimal())
 
 # NON-PARAMETRIC TESTS ---------------------------------------------------------
 ed <- which(rc.es$td == 0)

### 2018-11-23 code/07-protests.R

@@ -5,7 +5,7 @@ library("data.table")
 library("plm")
 library("lmtest")
 library("broom")
-theme_set(theme_bw())
+theme_set(theme_minimal())
 
 # EGYPTIAN REVOLUTION ----------------------------------------------------------
 egypt.es <-  event_study(ticker = index$ticker, date = index$date, dr = index$dr,
@@ -60,7 +60,8 @@ for (i in 1:length(rev$ticker)){
 garch.spec <- ugarchspec(mean.model = list(armaOrder = c(0,0)), 
                          distribution.model = "norm")
 for (i in 1:length(rev$ticker)){
-  rc.garchfit <- ugarchfit(spec = garch.spec, data = index.rev[[i]]$dr)
+  rc.garchfit <- ugarchfit(spec = garch.spec, data = index.rev[[i]]$dr,
+                           solver.control = list(tol = 1e-12))
   index.rev[[i]]$garch_volatility <- rc.garchfit@fit$sigma
   print(i)
 }

### 2018-12-28 code/06-sensitivity.R
Fixes to non-parametric tests

@@ -3,6 +3,7 @@ load("output/regime-change-event-study.RData")
 load("data/data-clean.RData")
 library("data.table")
 library("ggplot2")
+library("xtable")
 source("code/func.R")
 theme_set(theme_minimal())
 
@@ -15,7 +16,7 @@ colnames(tab.np) <- c("mean_ar_treat", "rank_pval_treat", "sign_pval_treat",
 indx <- list(coup.index = which(regime.change$type == "Coup"),
              ass.index = which(regime.change$type == "Assassination"),
              res.index = which(regime.change$type == "Resignation"))
-sign.dir <- c("negative", "negative", "positive")
+sign.dir <- c("negative", "negative", "positive", "positive")
 
 ## Treatment
 # mean abnormal return
@@ -28,13 +29,14 @@ tab.np[4, 1] <-  mean(rc.abs.es$ar.treat[ed, ])
 for (i in 1:3){
   tab.np[i, 2] <- rank_test(rc.es$ar.treat[, indx[[i]]], rc.es$td)
 }
-tab.np[4, 2] <-  rank_test(rc.abs.es$ar.treat[, indx[[i]]], rc.abs.es$td)
+tab.np[4, 2] <-  rank_test(rc.abs.es$ar.treat[, ], rc.abs.es$td)
 
 # sign test p-value
 for (i in 1:3){
   tab.np[i, 3] <- sign_test(rc.es$ar.treat[ed, indx[[i]]], sign.dir[i])
 }
-tab.np[4, 3] <-  sign_test(rc.abs.es$ar.treat[ed, indx[[i]]], sign.dir[i])
+tab.np[4, 3] <-  sign_test(rc.abs.es$ar.treat[ed, ], sign.dir[4],
+                           alternative = "greater")
 
 ## Control
 # mean abnormal return
@@ -47,13 +49,14 @@ tab.np[4, 4] <-  mean(rc.abs.es$ar.control[ed, ], na.rm = TRUE)
 for (i in 1:3){
   tab.np[i, 5] <- rank_test(rc.es$ar.control[, indx[[i]]] , rc.es$td)
 }
-tab.np[4, 5] <-  rank_test(rc.abs.es$ar.control[, indx[[i]]], rc.abs.es$td)
+tab.np[4, 5] <-  rank_test(rc.abs.es$ar.control[, ], rc.abs.es$td)
 
 # sign test p-value
 for (i in 1:3){
[…]

### 2018-12-28 code/func.R

@@ -317,7 +317,8 @@ rank_test <- function(ar, td){
 }
 
 # SIGN TEST --------------------------------------------------------------------
-sign_test <- function(ar0, direction = c("positive", "negative")){
+sign_test <- function(ar0, direction = c("positive", "negative"),
+                      alternative = c("two.sided", "less", "greater")){
   direction = match.arg(direction)
   ar0 <- ar0[!is.na(ar0)]
   n <- length(ar0)
@@ -326,10 +327,8 @@ sign_test <- function(ar0, direction = c("positive", "negative")){
   } else{
     x <- sum(ar0 < 0)
   }
-  #binom.test <- binom.test(x, n, p = .5)
-  theta <- ((x/n) - 0.5)*(sqrt(n)/0.5)
-  pval <- 2 * (1 - pnorm(abs(theta)))
-  return(pval)
+  binom.test <- binom.test(x, n, p = .5, alternative = alternative)
+  return(binom.test$p.value)
 }
 
 # SYNTHETIC CONTROL GROUP ------------------------------------------------------

### 2018-12-29 doc/paper.tex
Update title of paper
Test overleaf based commit
Some updates to paper including the introduction, data, and results sections

@@
 \author{Devin Incerti and Trevor Incerti}
-\title{\textbf{Political Instability and Financial Markets}}
+\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
 \date{\today}
@@
 
-Political instability is also thought to harm investment.
-For investors, multinational firms, development agencies, and aid organizations, political risk is a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
+Of course, political instability may not only impact a country's political environment but its economy as well.
+For instance, investors, multinational firms, development agencies, and aid organizations, rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
 In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These investor sentiments are supported by empirical research that suggests political instability - as measured by regime change frequency or political violence - is negatively correlated with investment and financial development in cross country regressions \citep{alesina1996income,roe2011political}.
-In addition, the variance of stock market returns is also estimated to increase in response to political instability.\footnote{\citet{leblang2005government} show that right-wing governments increase the mean and volatility of stock prices in the United States and Britain, while \citet{jensen2005market} find that a rise in the popularity of a Brazilian presidential candidate with uncertain future policies increased the volatility of the Brazilian stock market.}
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These investor sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency or political violence---is negatively correlated with investment and financial development in cross country regressions \citep{alesina1996income,roe2011political} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
-Political instability is also hypothesized to reduce economic growth by increasing policy uncertainty.
-This hypothesis is once again supported by cross country empirical evidence that political instability is negatively correlated with GDP growth \citep{alesina1996political, fosu1992political, aisen2013does, jong2009measurement}.
-For example, \citet{alesina1996political} show that countries have lower growth in years in which there are major government changes such as coups.
-The exception to this conclusion is \citet{londregan1990poverty}, who find that coups have no effect on economic growth.
-Additional research focuses on government policy instruments that affect private rates of return on investment, and argues that political instability causes governments to act myopically and adopt inefficient policies.\footnote{For instance, \citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+There is considerable evidence that political risk and policy uncertainty not only impact stock market returns, but economic growth as well.
+For example, cross country empirical evidence suggests that political instability is negatively correlated with GDP growth \citep{alesina1996political, fosu1992political, aisen2013does, jong2009measurement}, which may is likely because governments act myopically and adopt inefficient policies \citep{svensson1998investment,devereux1998political}.\footnote{\citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
 Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation causes the private sector to reduce current investment which reduces future output.}
+The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
 
@@
 Assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
-Coups can occur in the name of democracy or autocracy, and in generally signal relative weakness in the current political system.
+Coups can occur in the name of democracy or autocracy, and in general, signal relative weakness in the current political system.
 Further, political instability may be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
 \citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+Likewise, \citet{londregan1990poverty}, find that coups have no impact on economic growth and hypothesize that this may because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
 
-\bigskip
-
-We use financial performance as an indicator of whether the market views political stability as ``good'' for economic growth.
-As in \citet{alesina1996political}, we use ``irregular'' regime changes such as coups, assassinations and resignations as an indicator for political instability.
-The major innovation of this paper is that, in contrast to the aforementioned cross country studies, we analyze the impact of political instability using daily financial data.
-This enables us to use market expectations to quantify the economic impact of each individual type of regime change.
-The advantage of this event study approach is that it allows us to isolate the effect of irregular regime changes and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.\footnote{A growing body of work uses event studies to assess political phenomenon.
+In this study, examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
+In contrast to the aforementioned cross country studies, we  conduct our analysis using daily financial data.
+Market expectations in the form of stock market returns are therefore used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
+The advantage of this event study approach is that it allows us to use time-series variation in stock returns to estimate treatment effects and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
@@
 We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} As even successful coups can have disparate outcomes (e.g.
-a shift from authoritarian rule to democratic rule, or vica versa), we provide a list of coups and their general outcome as defined by the Polity IV Project in \autoref{tab:coup list} below.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural experiment that allows us to estimate the impact of the forceful removal of a left-wing populist with a pro-business regime.
 
-\singlespacing
+\begin{table}[!ht]
+\caption{Regime changes} \label{tab:regime-changes}
+\vspace{-5pt}
 \footnotesize
 \begin{center}
-\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
-\caption{List of Coup d'Etat}
-\label{tab:coup list}\\
-\vspace{-5pt}\\
-\hline
-\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
-\endfirsthead
-\multicolumn{3}{c}%
-{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
   \hline
   \hline
-\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
+  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
   \hline
-\endhead
-\hline 
-\multicolumn{3}{r}{\textit{Continued on next page}} \\
-\endfoot
-\hline
-\endlastfoot
-06/08/1970 & Argentina & Autocracy to autocracy\\
-03/22/1971 & Argentina & Autocracy to autocracy (democracy by 1973)\\
-03/24/1976 & Argentina & Democracy to autocracy\\
-10/06/1976 & Thailand & Anocracy to autocracy\\
-10/20/1977 & Thailand & Autocracy to autocracy\\
-12/12/1979 & South Korea & Autocracy to autocracy\\
-02/23/1991 & Thailand & Anocracy to anocracy\\
-04/05/1992 & Peru & Democracy to anocracy\\
-10/12/1999 & Pakistan & Democracy to autocracy\\
-10/04/2002 & Nepal & Democracy to autocracy\\
-09/19/2006 & Thailand & Democracy to anocracy\\
-01/11/2007 & Bangladesh & Democracy to autocracy\\
-07/03/2013 & Egypt & Anocracy to anocracy\\
-05/22/2014 & Thailand & Democracy to anocracy\\
- & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
-04/11/2002 & Venezuela & Partial/failed democracy to democracy\\
+   \multicolumn{3}{c}{\textbf{Coups}}\\ 
+\ExpandableInput{../tables/coups.txt} \\
+   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
+\ExpandableInput{../tables/failed_coup.txt}\\
+  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
+\ExpandableInput{../tables/assassinations.txt}\\
+  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
+\ExpandableInput{../tables/resignations.txt}
    \hline
    \hline
-\end{longtable}
+\end{tabular*}
+\scriptsize
+Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
+\end{threeparttable}
 \end{center}
-\doublespacing
-\normalsize
+\end{table}
 
-The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime"}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
+The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime."}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
 Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
@@
 
+A list of the political events in our dataset is shown in \autoref{tab:regime-changes}.
+Coups tend to have the largest impact on the level of democratization as a number of countries have subeqeuently transitioned from democracies to anocracies or autocracies.
+On the other hand, neither assassinations or resignations have much of an impact on the level of democratization.
+
 Financial data are from the Global Financial Data database, which includes the longest available time series of stock prices.
@@
 We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
-Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available daily time series for these stock indices are listed in \autoref{tab:stock list}.
+Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available daily time series for these stock indices are listed in \autoref{tab:stock-list}.
 
-\singlespacing
+\begin{table}[!ht]
+\caption{List of stock indices} \label{tab:stock-list}
+\vspace{-5pt}
 \footnotesize
 \begin{center}
-\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
-\caption{List of stock indices}\label{tab:stock list}\\
-\vspace{-5pt}\\
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lll}
   \hline
   \hline
-\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Stock Index}&\multicolumn{1}{c}{Begin Date}&\multicolumn{1}{c}{End Date}\\
+  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Begin Date} &\multicolumn{1}{c}{Start Date}\\
   \hline
-\endfirsthead
-\multicolumn{4}{c}%
-{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
-\hline
-\hline
-\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Stock Index}&\multicolumn{1}{c}{Begin Date}&\multicolumn{1}{c}{End Date}\\
-\hline
-\endhead
-\hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
-\endfoot
-\hline
-\endlastfoot
 Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
@@
 Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
-
    \hline
    \hline
-\end{longtable}
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
 \end{center}
-\doublespacing
-\normalsize
+\end{table}
 
@@
 \section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
-\subsection{Abnormal Returns} \label{subsec: Abnormal Returns}
+\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
 We begin our analysis by studying the effect of irregular regime changes on stock returns.
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:coup list} with the exception of the Argentinian coup of March 24, 1976 and the partial/failed Venezuelan coup attempt of 2002.
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976 and the partial/failed Venezuelan coup attempt of 2002.
 The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}  We later examine the Venezuelan coup attempt of 2002 in detail, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
@@
 In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
-The mean event day abnormal return is over 4\% and event day abnormal returns are only negative and statistically significant at even the ten percent level in two out of the fifteen resignations (Pakistan on April 19, 1993 and Tunisia on June 31, 2011).
-However, these positive returns are short lived: the 7 day cumulative abnormal return is nearly identical to the event day abnormal return and the 20 day cumulative abnormal return is not statistically different from zero [[\textit{This doesn't look right to me.
-The positive returns seem persistent and to grow larger over time}]].
+The mean event day abnormal return is over 4\% and the positive returns are persistent and grow larger over time (mean 20-day CAR $\approx$ 11\%).
+Furthermore, event day ARs are only negative and statistically significant at even the ten percent level in two out of the fifteen resignations (Pakistan on April 19, 1993 and Tunisia on June 31, 2011).
 
-These results are also consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns.
-The positive event day abnormal return following resignations is not surprising since resignations typically occurr because of poor performance and/or loss of authority.
+These results are consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns.
+The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority.
 Leaders were often ousted following corruption charges, financial crises, and/or political violence.
@@
 \subsection{Volatility} \label{subsec: Volatility}
-Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, the results from \autoref{subsec: Abnormal Returns} suggest that all of these political events increase financial volatility.
+Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, the results from \autoref{subsec:abnormal-returns} suggest that all of these political events increase financial volatility.
 However, since stock volatility is not directly observable, one must decide how to best estimate volatility.
@@
 \subsection{Robustness} \label{subsec: Robustness}
-There are three potential concerns with the results in \autoref{subsec: Abnormal Returns}.
+There are three potential concerns with the results in \autoref{subsec:abnormal-returns}.
 First, the abnormal returns could have been driven by factors unrelated to the regime changes.
@@
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock list}.\footnote{See the appendix for a more formal explanation.}
+The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See the appendix for a more formal explanation.}
 
@@
 \scriptsize
-Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available. 
+Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available. Two-sided 
 \end{threeparttable}
@@
 
-As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 5\% level using the rank test statistic and the abnormal returns for coups, assassinations, and resignations are significant at at least the 10\% level using the sign test.
-In addition, abnormal absolute returns for all events are statistically significant at the 1\% level using both the rank and sign statistics.
-On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level [[\textit{This is not true for all events using the sign test, which seems odd to me}]].
-Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (10\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec: Abnormal Returns} are not an artifact of deviations from normality or confounding world events.
+As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 1\% level using the rank test statistic and the abnormal returns for coups and assassinations are significant at at least the 10\% level using the sign test.
+In addition, abnormal absolute returns for all events are statistically significant at the 5\% level using both the rank and sign statistics.
+On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level.
+Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec:abnormal-returns} are not an artifact of deviations from normality or confounding world events.
 
 The third concern, which is that the political events in this paper are not unexpected, is addressed in a number of ways.
-First, one can note that neither the 7-day or the 20-day mean CAR from tables \autoref{tab:AR-coups}, \autoref{tab:AR-ass} or \autoref{tab:AR-resignations} are statistically different than zero at even the 10\% level [[\textit{Not true for resignations 20 day}]].
-Although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction.
+First, one can note that although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction.
 For example, there was a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though the resignation was associated with large positive event day abnormal returns.
@@
 As shown in \autoref{fig:CAR-mean}, neither the ``positive'' nor ``negative'' events have pre-event CAR's that are statistically different from 0.
-
-It is also worth noting that the post-event CAR(1,k) for $k\in(2,19)$ is not statistically significant for either the ``positive'' or the ``negative'' events.
-Almost all of the stock-market reaction occurs on the first day that the market could react to the event which suggests that markets respond quickly to political events.
-This, in turn, implies that markets are reacting to news efficiently and that an event-driven trading strategy would not be profitable.
-
-Finally, to check whether our results are sensitive to model specification, we estimated market models in addition to the baseline constant returns model.
-We used the MSCI World Index as a proxy for their market return.
-[To do: add table for this]  [[\textit{Is this necessary?}]]
+Furthermore, for negative events, almost all of the stock-market reaction occurs on the first day that the market could react to the event which implies that markets are responding quickly to negative political events.
+On the other hand, the effect of positive event seems to be longer lasting with CARs increasing during the 20-day post-event window.
 
@@
 \subsection{Synthetic Control Portfolio}
-Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock list}.
+Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
 Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}

### 2018-12-29 code/02-desc-stats.R

@@ -2,9 +2,57 @@
 rm(list = ls())
 library("data.table")
 library("ggplot2")
+library("xtable")
 load("data/data-clean.RData")
 source("code/func.R")
 theme_set(theme_bw())
+
+# LIST OF EVENTS ---------------------------------------------------------------
+events <- fread("data-raw/event_list.csv")
+events[, boutcome := cut(bpolity, 
+                         breaks = c(-10.1, -6, 5, 10.1),
+                         labels = c("Autocracy", "Anocracy", "Democracy"))]
+events[, boutcome := as.character(boutcome)]
+events[, eoutcome := cut(epolity, 
+                         breaks = c(-10.1, -6, 5, 10.1),
+                         labels = c("Autocracy", "Anocracy", "Democracy"))]
+events[, eoutcome := as.character(eoutcome)]
+events[, eoutcome := ifelse(country == "Thailand" & date == "10/20/77",
+                            "Autocracy",
+                            eoutcome)]
+events[, outcome := paste0(boutcome, " to ", tolower(eoutcome))]
+
+# Coups
+coups <- events[type == "Coup",  .(date, country, outcome)]
+print(xtable(coups), 
+      include.rownames = FALSE, include.colnames = FALSE,
+      only.contents = TRUE, sanitize.text.function = identity,
+       hline.after = NULL,
+      file = "tables/coups.txt")
+
+# Failed coup
+failed_coup <- events[type == "Partial Coup",  .(date, country, outcome)]
+print(xtable(failed_coup), 
+      include.rownames = FALSE, include.colnames = FALSE,
+      only.contents = TRUE, sanitize.text.function = identity,
+       hline.after = NULL,
+      file = "tables/failed_coup.txt")
+
+# Assassinations
+assassinations <- events[type == "Assassination",  .(date, country, outcome)]
+print(xtable(assassinations), 
+      include.rownames = FALSE, include.colnames = FALSE,
+      only.contents = TRUE, sanitize.text.function = identity,
+       hline.after = NULL,
+      file = "tables/assassinations.txt")
+
+# Resignations
+resignations <- events[type == "Resignation",  .(date, country, outcome)]
+print(xtable(resignations), 
+      include.rownames = FALSE, include.colnames = FALSE,
+      only.contents = TRUE, sanitize.text.function = identity,
+       hline.after = NULL,
+      file = "tables/resignations.txt")
 
[…]

### 2018-12-29 doc/paper.tex
A few more modifications to the intro

@@
 
-Of course, political instability may not only impact a country's political environment but its economy as well.
+Of course, coups and other regime changes not only impact a country's political environment but its economy as well.
 For instance, investors, multinational firms, development agencies, and aid organizations, rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
 In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These investor sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency or political violence---is negatively correlated with investment and financial development in cross country regressions \citep{alesina1996income,roe2011political} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
-
-There is considerable evidence that political risk and policy uncertainty not only impact stock market returns, but economic growth as well.
-For example, cross country empirical evidence suggests that political instability is negatively correlated with GDP growth \citep{alesina1996political, fosu1992political, aisen2013does, jong2009measurement}, which may is likely because governments act myopically and adopt inefficient policies \citep{svensson1998investment,devereux1998political}.\footnote{\citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} Common rationales are that unstable governments act myopically and adopt inefficient policies \citep{svensson1998investment,devereux1998political}\footnote{\citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
 Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
+The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.} and that policy uncertainty depresses business activity \citep{baker2016measuring}.
+Such sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency or political violence---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
 However, such hypotheses are often overly simplistic.
-Not all political instability is equivalent - resignations, assassinations, and coups are all examples of political instability, but may have disparate effects on financial returns.
+Not all political instability is equivalent - resignations, assassinations, and coups are all examples of regime changes, but may have disparate effects on financial returns.
 Resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
@@
 
-In this study, examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
+In this study, we examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
 In contrast to the aforementioned cross country studies, we  conduct our analysis using daily financial data.
@@
 These findings are consistent with research that shows that ``good coups'' - coups that lead to democratization or economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
-However, while ``good coups'' may be the minority, they do exist, and coups that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+However, while ``good coups'' may be the minority, regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
 

### 2018-12-29 doc/paper.tex
Added Philippines example to resignations

@@
 The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority.
-Leaders were often ousted following corruption charges, financial crises, and/or political violence.
+Leaders were often ousted following corruption charges, allegations of fraud, financial crises, and/or political violence.
 
-For example, consider Muhammad Suharto's resignation from office as the President of Indonesia on May 1998, just after the 1997 Asian Financial Crisis.
-Prior to the crisis, the Indonesian economy suffered from a number of ailments including crony capitalism, poor corporate governance, growing short-term debt and a corrupt banking system \citep{radelet2000onset}.
-In addition, Suharto's ill health created considerable policy uncertainty, which only added to the financial panic in Indonesia.
-Indonesia was also hesitant to adopt structural reforms which further weakened its economic image.
-As a result, the crisis gave additional ammunition to opposition leaders, and public opposition culminated in riots in mid-May 1998.
-Suharto eventually lost his military support and was forced to resign.
+For example, consider Ferdinand Marcos' resignation from office as President of the Philippines in February 1986.
+Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
+In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies and possessed one of the worst capital investment to economic output ratios in Asia \citep{overholt1986rise}.
+Marcos held a snap presidential election on February 7, 1986, in which he declared victory despite overwhelming evidence of electoral fraud.
+Public protests ensued, and two weeks later the military withdrew its support of the Marcos regime \citep{lee2009armed}.
+Marcos was replaced by his electoral opponent, Corazon Aquino, who had run on a platform of economic liberalization and elimination of crony capitalism \citep{villegas1987philippines}.
 

### 2019-01-18 doc/paper.tex
Proof reading and conclusion updates
(1) Checked accuracy of description of results and marked where appropriate and (2) expanded conclusion.

@@
 
-Event day ARs are negative for all coups except the 1971 coup in Argentina and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}).
+Event day ARs are negative for all coups except the 1971 coup in Argentina, the 2002 coup in Nepal, and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}).
 These results provide evidence that coups can in fact result in positive abnormal returns.
@@
 In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Center for System Peace Polity IV polity score of 6.
-Values of 6-10 are defined as democracies.} The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
+Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections.
+The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
 
@@
 The only days on which the ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
-
 The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot.
@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 30 trading days prior to and 30 days after each event.
-Volatility appears to increase slowly just before the regime change, which suggests that investors sometimes have information about the events before they occur.
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+This may suggest that investors sometimes have information about the events before they occur.
 Nonetheless, there is still an enormous volatility jump on the day of the regime change.
@@
 \end{figure}
-
-The smaller figure within \autoref{fig:volatility} expands the volatility estimates to the 250 trading days before and after each regime change.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
 
@@
 The third concern, which is that the political events in this paper are not unexpected, is addressed in a number of ways.
-First, one can note that although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction.
+First, one can note that although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction [This is not true for a couple of the coups.
+I am also a bit unclear on the logic of why the directionality being the same is evidence of the event being unexpected?].
 For example, there was a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though the resignation was associated with large positive event day abnormal returns.
@@
 Second, since the direction of the pre-trends is unclear, we examine whether there are different pre-trends for events with positive stock reactions than for events with negative stock reactions.
-As shown in \autoref{fig:CAR-mean}, neither the ``positive'' nor ``negative'' events have pre-event CAR's that are statistically different from 0.
+As shown in \autoref{fig:CAR-mean}, neither the ``positive'' nor ``negative'' events have pre-event CAR's that are statistically different from 0 [We need to address that this is not true for the positive events.
+To me it looks like the Indonesian and Thai resignations are driving the negative pre-event CARs.].
 Furthermore, for negative events, almost all of the stock-market reaction occurs on the first day that the market could react to the event which implies that markets are responding quickly to negative political events.
@@
 The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence.
-Financial volatility surrounding regime changes, which is often characterized by large negative \textit{and} positive stock returns, suggests that irregular regime changes increase policy uncertainty and volatility, but that uncertainty does not tell the whole story.
-The direction of returns depends on the expected outcome of the irregular regime change.
+However, we do not find that irregular regime changes universally discourage investment.
+Instead, financial volatility surrounding regime changes is often characterized by large negative \textit{and} positive stock returns, which suggests that irregular regime changes increase policy uncertainty and volatility, but that uncertainty does not tell the whole story.
+The direction of returns depends on the type of irregular regime change and its expected outcome.
+Abnormal returns following resignations are large and positive (4\%), abnormal returns following assassinations are negative and smaller in magnitude (2\%), and abnormal returns following coups also tend to be negative (2\%).
+However, some coups result in positive abnormal returns of 10\% or more.
 The variation in the direction of abnormal returns is therefore consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.
-Abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership.
+
+Our findings suggest that abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership.
+Conversely, autocratic coups may increase fear of capital appropriation or the institution of poor economic policies, while assassinations may be merely regarded as highly uncertain events.
+However, while our research design allows us to show that different types of irregular regime changes can be expected to result in different financial outcomes on average, it does not allow us to directly test the mechanisms that result in this variation.
+We therefore leave more direct tests of these mechanisms to future research.
 

### 2019-03-02 doc/paper.tex
Removed note from Table 2
Minor edits to draft. Added code for lagged event studies.

@@
 However, both recent events and prior research suggest that coups rarely lead to democracy.
-In the wake of the Arab Spring - in which rulers were deposed in four countries and major protests occurred in six more - only Tunisia ultimately transitioned to democracy.
+In the wake of the Arab Spring - in which rulers were deposed in four countries - only Tunisia ultimately transitioned to democracy.
 These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
@@
 Likewise, \citet{londregan1990poverty}, find that coups have no impact on economic growth and hypothesize that this may because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+\citet{meyersson2016political} provides  support for this hypothesis, finding that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
 
@@
 We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural experiment that allows us to estimate the impact of the forceful removal of a left-wing populist with a pro-business regime.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural experiment that allows us to estimate both the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of left-wing populist.
 
@@
 \end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
 \end{threeparttable}
@@
 We employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
-
 \autoref{tab:non-parametric} compares event day ARs as well as ``abnormal absolute returns'' between the event country and the synthetic control portfolio using the non-parametric methods discussed above.

### 2019-03-02 code/08-event-studies-robustness.R

@@ -1,0 +1,71 @@
+rm(list = ls())
+library("xtable")
+library("data.table")
+library("Synth")
+library("lubridate")
+load("data/data-clean.RData")
+source("code/func.R")
+
+# EVENT STUDY ------------------------------------------------------------------
+# Lag date of event by 60 days
+regime.change$date_lag = regime.change$stock_date %m-% months(3)
+
+# No data for Phillipines prior to 1986: cannot lag data 3 months
+regime.change <- regime.change[stock_date != '1986-02-26'] 
+
+# calculate abnormal returns and days to rebound
+event.window <- 20
+est.window <- 200
+n.es <- nrow(regime.change)
+es <- es.abs <- vector(mode = "list", n.es)
+dtr.treat <- rep(NA, n.es)
+
+# loop
+for (i in 1:n.es){
+  # # no controls for 1901
+  # if(regime.change$date_lag[i] == mydate("06/07/1901")){
+  #     controli <- FALSE
+  # } else{
+  #     controli <- TRUE
+  # }
+  # 
+  # # use custom V in synth to deal with singular matrix in optim
+  # if (regime.change$date_lag[i] == mydate("7/4/2002") |
+  #     regime.change$date_lag[i] == mydate("2/3/1993")){
+  #     custom.v.i <- rep(1, 2)
+  # } else{
+  #     custom.v.i <- NULL
+  # }
+  
+  # run event study
+  es[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                     event_ticker = regime.change$ticker[i],
+                     event_window = event.window, estimation_window = est.window,
+                     event_date = regime.change$date_lag[i], model = "constant",
+                     control = FALSE, custom_v = NULL) 
+  es.abs[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = abs(index$dr),
+                         event_ticker = regime.change$ticker[i],
+                         event_window = event.window, estimation_window = est.window,
+                         event_date = regime.change$date_lag[i], model = "constant",
+                         control = FALSE, custom_v = NULL)
+  
+  # days to rebound
+  dtr.treat[i] <- days_to_rebound(ticker = index$ticker, date = index$date, price = index$p,
+                                  event_ticker = regime.change$ticker[i],
+                                  event_date = regime.change$date_lag[i])
+  
+  # print
+  print(i)
+}
+
+# combine event studies
+rc.es <- combine_event_studies(es, event_country = regime.change$country,
[…]

### 2019-04-23 doc/paper.tex
Update robustness section of manuscript and associated sensitivity analyses

@@
 \usepackage[section]{placeins}
+\usepackage[export]{adjustbox}
 
@@
 \subsection{Robustness} \label{subsec: Robustness}
-There are three potential concerns with the results in \autoref{subsec:abnormal-returns}.
+There are a number of potential concerns with the results in \autoref{subsec:abnormal-returns}.
 First, the abnormal returns could have been driven by factors unrelated to the regime changes.
-Second, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate.
-Third, the true effects of irregular regime changes on firm value may be underestimated if investors had apriori information.
+Second, the true effects of irregular regime changes on firm value may be underestimated if investors had apriori information.
+Third, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate.
 
-To explore the first concern, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
+We explore these concerns in a number of ways.
+First, we reestimate mean CARs on a set of time-shifted placebo dates.
+Means are computed across all events within a given type of regime change.
+We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days).
+In addition, we extend the forward shifted event date out to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
+
+\autoref{fig:mean-car-by-regime-change} compares mean CARs estimated using the actual event date (\autoref{subfig:mean-car-by-regime-change-actual}) to CARs estimated with the event date shifted 1-year (365 days) into the future (\autoref{subfig:mean-car-by-regime-change-placebo}).
+\autoref{subfig:mean-car-by-regime-change-actual}---which reproduces the tabular results presented in \autoref{subsec:abnormal-returns}---shows that assassinations and coups are associated with negative event day ARs while resignations are associated with positive event day ARs.
+For coups and assassinations, most of the stock-market reaction occurs on the first day that the market could react to the event which implies that markets are responding quickly to negative political events.
+On the other hand, the effect of positive event seems to be longer lasting with CARs increasing during the 20-day post-event window.
+The abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo} are considerably different: there is no discernible event day ARs when the event day is shifted forward for any of the regime change types suggesting that the results in this paper are not simply an artifact of the data.
+Moreover, while CARs estimated using the actual event date for resignations trend upwards following the event day, there is no consistent trend in \autoref{subfig:mean-car-by-regime-change-placebo}.
+
+\begin{figure}
+\centering
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[max size={.8\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type.pdf}
+\caption{Actual event date} \label{subfig:mean-car-by-regime-change-actual}
+\end{subfigure}
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[max size={.8\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
+\caption{Event date shifted forward by one year} \label{subfig:mean-car-by-regime-change-placebo}
+\end{subfigure}
+\caption{Mean cumulative abnormal returns by type of regime change}\label{fig:mean-car-by-regime-change}
+\end{figure}
+
+To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
+There are a few instances (e.g., for coups and resignations) in which there are statistically significant ARs in the same direction as those on the actual event day in the post-event window (0 days to 20 days), but they are always smaller in magnitude than the ARs estimated using the actual event date.
+For resignations, there is no consistent pattern in the AR in the post-event window as both positive and negative ARs are observed.
+When estimates are based on dates shifted further into the future (110 days and beyond) the ARs are centered around zero.
+Overall, these results reinforce the main results: the ARs on the actual event date capture most of effect of the regime change, although effects can sometimes persist in the short event window following the event date.
+
+These figures also provide evidence on the extent to which regime changes appear to be unexpected.
+For instance, the CARs prior to assassinations and coups presented in \autoref{subfig:mean-car-by-regime-change-actual} tend to be close to zero, suggesting that investors were unaware that a negative event was likely to occur in the coming days.
+For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
+Overall, there is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+
+Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
 Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See the appendix for a more formal explanation.}
+The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See \autoref{Appendix} for a more formal explanation.}
 
-The second concern is addressed using non-parametric statistical techniques, which are free from distributional assumptions.
-We employ the sign and the rank tests which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
+Non-parametric statistical techniques that are free from distributional assumptions are used to address concerns about inferences from small sample sizes.
+We employ the sign and the rank tests, which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
 \autoref{tab:non-parametric} compares event day ARs as well as ``abnormal absolute returns'' between the event country and the synthetic control portfolio using the non-parametric methods discussed above.
@@
 On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level.
-Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, these results suggests that the results from section~\autoref{subsec:abnormal-returns} are not an artifact of deviations from normality or confounding world events.
-
-The third concern, which is that the political events in this paper are not unexpected, is addressed in a number of ways.
-First, one can note that although some of the irregular regime changes have statistically significant pre-event CAR's, most of them do not, and the ones that do not always move in the same direction [This is not true for a couple of the coups.
-I am also a bit unclear on the logic of why the directionality being the same is evidence of the event being unexpected?].
-For example, there was a positive 14.7\% 7-day CAR preceding the resignation of President Fernando de la Rua of Argentina in December of 2001, even though the resignation was associated with large positive event day abnormal returns.
-
-\begin{figure}[!ht]
-\includegraphics{../figs/mean-car-pos-neg.pdf}
-\caption{Mean cumulative abnormal returns surrounding regime changes}
-\label{fig:CAR-mean}
-\end{figure}
-
-Second, since the direction of the pre-trends is unclear, we examine whether there are different pre-trends for events with positive stock reactions than for events with negative stock reactions.
-As shown in \autoref{fig:CAR-mean}, neither the ``positive'' nor ``negative'' events have pre-event CAR's that are statistically different from 0 [We need to address that this is not true for the positive events.
-To me it looks like the Indonesian and Thai resignations are driving the negative pre-event CARs.].
-Furthermore, for negative events, almost all of the stock-market reaction occurs on the first day that the market could react to the event which implies that markets are responding quickly to negative political events.
-On the other hand, the effect of positive event seems to be longer lasting with CARs increasing during the 20-day post-event window.
+Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, the synthetic control and small sample tests therefore suggest that the main results are not a result of deviations from normality or confounding world events.
 
@@
 \renewcommand\thetable{\Alph{section}.\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
 \section{Appendix} \label{Appendix}
@@
 
+\begin{figure}[!ht]
+\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
+\caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
+\label{fig:mean-event-day-ar-by-regime-change}
+\end{figure}
+
 \subsection{Synthetic Control Portfolio}

### 2019-04-23 code/06-sensitivity.R

@@ -126,39 +126,76 @@ p.meancar <- ggplot(car.mean, aes(x = td, y = car_mean)) + geom_line() +
 ggsave("figs/mean-car-by-regime-change-type.pdf", p.meancar, height = 5, width = 7)
 
 # CAR SURROUNDING REGIME CHANGES: PLACEBO CHECKS --------------------------------
-event.window <- 20
-est.window <- 200
-n.es <- nrow(regime.change)
-es.placebo <- vector(mode = "list", n.es)
-dtr.treat <- rep(NA, n.es)
-event.date.move <- 365
-
-# Run event studies
-for (i in 1:n.es){
-  es.placebo[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
-                                 event_ticker = regime.change$ticker[i],
-                                 event_window = event.window, estimation_window = est.window,
-                                 event_date = regime.change$stock_date[i] + event.date.move, 
-                                 model = "constant",
-                                 control = FALSE, custom_v = NULL)  
+# Run placebo event studies
+run_placebo_tests <- function(event_date_move){
+  # Setup
+  event.window <- 20
+  est.window <- 200
+  n.es <- nrow(regime.change)
+  es.placebo <- vector(mode = "list", n.es)
+  dtr.treat <- rep(NA, n.es)  
+  
+  # Run event studies
+  for (i in 1:n.es){
+    es.placebo[[i]] <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                                   event_ticker = regime.change$ticker[i],
+                                   event_window = event.window, estimation_window = est.window,
+                                   event_date = regime.change$stock_date[i] + event_date_move, 
+                                   model = "constant",
+                                   control = FALSE, custom_v = NULL)  
+  }
+  rc.es.placebo <- combine_event_studies(es.placebo, event_country = regime.change$country,
+                                         event_type = regime.change$type, 
+                                         event_date = regime.change$stock_date + event_date_move)
+  
+  # Create plot data
+  car.mean.coup.placebo <- car_mean_plot_data(rc.es.placebo, coup.events, "Coup")
[…]

### 2019-04-25 doc/paper.tex
Update sensitivity results so trading day 0 is an anchor day

@@
 
-We explore these concerns in a number of ways.
-First, we reestimate mean CARs on a set of time-shifted placebo dates.
-Means are computed across all events within a given type of regime change.
+We explore these concerns in two ways.
+First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events within a given type of regime change.
 We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days).
-In addition, we extend the forward shifted event date out to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
+In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
 

### 2019-04-25 code/06-sensitivity.R

@@ -88,7 +88,6 @@ car_mean_plot_data <- function(rc_es, indices, label = NULL){
 }
 
 # Positive vs negative events
-
 pos.events <- which(rc.es$ar.treat[ed, ] >= 0)
 neg.events <- which(rc.es$ar.treat[ed, ] < 0)
 
@@ -106,15 +105,10 @@ p.meancar <- ggplot(car.mean, aes(x = td, y = car_mean)) + geom_line() +
 ggsave("figs/mean-car-pos-neg.pdf", p.meancar, height = 5, width = 7)
 
 # CAR SURROUNDING REGIME CHANGES: BY EVENT TYPE --------------------------------
-# Indices
-coup.events <- which(regime.change$type == "Coup")
-ass.events <- which(regime.change$type == "Assassination")
-res.events <- which(regime.change$type == "Resignation")
-
 # Create plot data
-car.mean.coup <- car_mean_plot_data(rc.es, coup.events, "Coup")
-car.mean.ass <- car_mean_plot_data(rc.es, ass.events, "Assassination")
-car.mean.res <- car_mean_plot_data(rc.es, res.events, "Resignation")
+car.mean.coup <- car_mean_plot_data(rc.es, indx$coup.index, "Coup")
+car.mean.ass <- car_mean_plot_data(rc.es, indx$ass.index, "Assassination")
+car.mean.res <- car_mean_plot_data(rc.es, indx$res.index, "Resignation")
 car.mean <- rbind(car.mean.coup, car.mean.ass, car.mean.res)
 
 # Plot
@@ -149,9 +143,9 @@ run_placebo_tests <- function(event_date_move){
                                          event_date = regime.change$stock_date + event_date_move)
   
   # Create plot data
-  car.mean.coup.placebo <- car_mean_plot_data(rc.es.placebo, coup.events, "Coup")
-  car.mean.ass.placebo <- car_mean_plot_data(rc.es.placebo, ass.events, "Assassination")
-  car.mean.res.placebo <- car_mean_plot_data(rc.es.placebo, res.events, "Resignation")
+  car.mean.coup.placebo <- car_mean_plot_data(rc.es.placebo, indx$coup.index, "Coup")
+  car.mean.ass.placebo <- car_mean_plot_data(rc.es.placebo, indx$ass.index, "Assassination")
+  car.mean.res.placebo <- car_mean_plot_data(rc.es.placebo, indx$res.index, "Resignation")
[…]

### 2019-04-25 code/func.R

@@ -236,17 +236,16 @@ car_mean <- function(ar, sigma) {
 
 # MEAN CAR PRE AND POST --------------------------------------------------------
 mean_car_prepost <- function(ar, sigma, td){
-  ar.b <-  ar[rev(which(td < -1)), ]
-  car.mean.b <- data.table(car_mean(ar.b, sigma), td = rev(td[td < -1]))
+  ar.b <-  ar[rev(which(td <= -1)), ]
+  car.mean.b <- data.table(car_mean(ar.b, sigma), td = rev(td[td <= -1]))
   ar.f <-  ar[which(td >= 0), ]
   car.mean.f <- data.table(car_mean(ar.f, sigma), td = td[td >= 0])
-  car.mean.fixed <- data.table(car_mean = mean(ar[which(td == -1), ]),
-                               car_mean_se = 0, td = -1)
-  car.mean <- rbind(car.mean.b[nrow(car.mean.b):1 ], car.mean.fixed, car.mean.f)
-  car.mean$car_mean <- car.mean$car_mean - car.mean.fixed$car_mean
+  car.mean.f[, td := td + 1]
+  car.mean.0 <- data.table(car_mean = 0,
+                           car_mean_se = 0, td = 0)
+  car.mean <- rbind(car.mean.b[nrow(car.mean.b):1 ], car.mean.0, car.mean.f)
   return(car.mean)
 }
-  
 
 # REGRESSION TABLE WITH STANDARD ERRORS IN PARENTEHSES -------------------------
 # Regression table with standard errors in parentheses

### 2019-04-26 doc/paper.tex
Some updates to the robustness section of the paper

@@
 \subsection{Robustness} \label{subsec: Robustness}
-There are a number of potential concerns with the results in \autoref{subsec:abnormal-returns}.
+There are some potential concerns with the results in \autoref{subsec:abnormal-returns}.
 First, the abnormal returns could have been driven by factors unrelated to the regime changes.
-Second, the true effects of irregular regime changes on firm value may be underestimated if investors had apriori information.
+Second, the true effects of regime changes on firm value may be underestimated if investors had apriori information.
 Third, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate.
@@
 We explore these concerns in two ways.
-First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events within a given type of regime change.
+First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events for each type of regime change.
 We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days).
@@
 \autoref{subfig:mean-car-by-regime-change-actual}---which reproduces the tabular results presented in \autoref{subsec:abnormal-returns}---shows that assassinations and coups are associated with negative event day ARs while resignations are associated with positive event day ARs.
-For coups and assassinations, most of the stock-market reaction occurs on the first day that the market could react to the event which implies that markets are responding quickly to negative political events.
-On the other hand, the effect of positive event seems to be longer lasting with CARs increasing during the 20-day post-event window.
-The abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo} are considerably different: there is no discernible event day ARs when the event day is shifted forward for any of the regime change types suggesting that the results in this paper are not simply an artifact of the data.
-Moreover, while CARs estimated using the actual event date for resignations trend upwards following the event day, there is no consistent trend in \autoref{subfig:mean-car-by-regime-change-placebo}.
+In contrast, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
+The event day ARs are considerably smaller in magnitude and are not statistically different from zero for either coups or resignations.
+Moreover, while CARs estimated using the actual event date for resignations trend upwards following the event day, there is no consistent trend in the placebo analysis.
+\autoref{fig:mean-car-by-regime-change} therefore suggests that the main results are not merely an artifact of the data.
 
@@
 To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
-There are a few instances (e.g., for coups and resignations) in which there are statistically significant ARs in the same direction as those on the actual event day in the post-event window (0 days to 20 days), but they are always smaller in magnitude than the ARs estimated using the actual event date.
-For resignations, there is no consistent pattern in the AR in the post-event window as both positive and negative ARs are observed.
-When estimates are based on dates shifted further into the future (110 days and beyond) the ARs are centered around zero.
+There are a few instances in which there are statistically significant (at the 95\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
+Most of the statistically significant placebo estimates also occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
+When dates are shifted forward further ($\geq$ 110 days), the event day AR is only statistically significant in one case (day 365 for assassinations).
 Overall, these results reinforce the main results: the ARs on the actual event date capture most of effect of the regime change, although effects can sometimes persist in the short event window following the event date.

### 2019-04-28 code/06-sensitivity.R
Commit updated sensitivity analysis code

@@ -175,7 +175,7 @@ ggsave("figs/mean-car-by-regime-change-type-placebo.pdf", p.meancar.placebo,
        height = 5, width = 7)
 
 # Plot of event day ARs with event day shifted forward 
-ar.mean.placebo <- rbindlist(lapply(car.mean.placebo, function(x) x[td == 0]))
+ar.mean.placebo <- rbindlist(lapply(car.mean.placebo, function(x) x[td == 1]))
 ar.mean.placebo[, shift := rep(event.date.move, each = 3)]
 p.meanar.placebo <- ggplot(ar.mean.placebo, 
                            aes(x = factor(shift), y = car_mean)) +

### 2019-04-28 doc/paper.tex
Update intro

@@
 However, both recent events and prior research suggest that coups rarely lead to democracy.
-In the wake of the Arab Spring - in which rulers were deposed in four countries - only Tunisia ultimately transitioned to democracy.
+In the wake of the Arab Spring---in which rulers were deposed in four countries---only Tunisia ultimately transitioned to democracy.
 These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
@@
 Of course, coups and other regime changes not only impact a country's political environment but its economy as well.
-For instance, investors, multinational firms, development agencies, and aid organizations, rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
+For instance, investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
 In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
@@
 
-However, such hypotheses are often overly simplistic.
+But such hypotheses are often overly simplistic.
 Not all political instability is equivalent - resignations, assassinations, and coups are all examples of regime changes, but may have disparate effects on financial returns.
@@
 \citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
-Likewise, \citet{londregan1990poverty}, find that coups have no impact on economic growth and hypothesize that this may because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-\citet{meyersson2016political} provides  support for this hypothesis, finding that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
+Likewise, \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+More recent studies provide support for this hypothesis.
+\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
+\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with large declines in stock prices while the coup that replaced him boosted them.
 
 In this study, we examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
-In contrast to the aforementioned cross country studies, we  conduct our analysis using daily financial data.
-Market expectations in the form of stock market returns are therefore used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
+In contrast to the aforementioned cross country studies but like \citet{girardi2018institution} we  conduct our analysis using daily financial data.
+Market expectations in the form of stock market returns are used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
 The advantage of this event study approach is that it allows us to use time-series variation in stock returns to estimate treatment effects and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.}
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} We analyze 13 coups, 8 assassinations, 15 forced resignations, 11 public protests, and 1 natural experiment provided by the failed 2002 coup in Venezuela.
+Our study is therefore not only able to use an event-study approach to enhance the reliability of the estimates, but is not limited to a single case study as in \citet{girardi2018institution}.
+The relatively large sample enhances external validity and allows us to show that different types of political events have disparate economic effects.
 
-We find that financial volatility increases dramatically following (and just before) coups d'etat, assassinations, and resignations.
-However, unlike the previously mentioned studies, we find that these irregular regime changes have disparate effects on the direction of stock returns.
+We find that coups, assassinations, resignations, and public protests cause large increases in financial volatility.
 Abnormal returns following resignations are large and positive (4\%) while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
-The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
+The average impact of coups is negative (2\%); however, stock prices increased dramatically during the failed overthrow of Hugo Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
+The effect of public protests on mean stock returns is uncertain, with some protests such as those during the Egpytian Revolution depressing them and others have the opposite effect.
 
-These findings are consistent with research that shows that ``good coups'' - coups that lead to democratization or economic liberalization - are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
+These findings are consistent with research that shows that ``good coups''---coups that lead to democratization or economic liberalization---are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
 However, while ``good coups'' may be the minority, regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
 
-Our main finding is therefore that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+Our main conclusion is therefore that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
 Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule, exacerbate poor economic policies, or merely increase policy uncertainty have the opposite effect.
@@
 
-\section{Conclusion}
+\section{Conclusion and Discussion}
+[Abundance of bad leaders. Coups are still commonplace]
+
+[How we tackle the problem. Strength of our design]
+
+[What our analysis suggest. Summary of findings]
+
+[Compare results to other literature. i.e., magnitude of stock changes. Democratization is not guarantee of positive stock returns]
+
+[Discuss potential mechanisms. Note as a limitation and an avenue for future research.]
+
 This paper has examined the effects of irregular regime changes on financial returns.

### 2019-04-29 doc/paper.tex
Update conclusion and discussion section

@@
 \section{Conclusion and Discussion}
-[Abundance of bad leaders. Coups are still commonplace]
+Max Weber (\citeyear{weber1947theory}) developed the concept of ``charismatic leadership'' whereby a leader's authority stems from their charisma.
+Such rule is often found in autocracies with weak institutions and few constrains placed on the power of leaders.
+\citet{jones2005leaders} has shown that leaders can have particularly large impacts on economic growth in these settings.
+It is therefore not surprising that there is often a strong temptation to overthrow "bad" leaders, even by undemocratic means.
 
-[How we tackle the problem. Strength of our design]
+Coups and other types of regime changes remain common, highlighting their relevance for economic and political development.
+Our sample consists of 5 coups, 1 assassination, 7 resignations, and 7 instances of public protect since 2000.
+The Arab spring is perhaps the most notable, with protests in response to oppressive regimes and low living standards spreading throughout the Middle East in late 2010.
+There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.
+Yet despite their frequency there is little evidence on their economic consequences.
 
-[What our analysis suggest. Summary of findings]
-
-[Compare results to other literature. i.e., magnitude of stock changes. Democratization is not guarantee of positive stock returns]
-
-[Discuss potential mechanisms. Note as a limitation and an avenue for future research.]
-
-This paper has examined the effects of irregular regime changes on financial returns.
-It uses an event study approach to show that investors expect irregular regime changes to have large effects on equity returns.
-This methodology is less susceptible to endogeneity biases than studies that use cross country data.
+This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices.
+This approach provides well-identified estimates of the economic effects of regime changes that are less susceptible to endogeneity bias than prior cross country studies.
+Furthermore, the large sample of political events in our study increases the generalizability of our findings.
 
 The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence.
-However, we do not find that irregular regime changes universally discourage investment.
-Instead, financial volatility surrounding regime changes is often characterized by large negative \textit{and} positive stock returns, which suggests that irregular regime changes increase policy uncertainty and volatility, but that uncertainty does not tell the whole story.
-The direction of returns depends on the type of irregular regime change and its expected outcome.
+But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is less certain.
 Abnormal returns following resignations are large and positive (4\%), abnormal returns following assassinations are negative and smaller in magnitude (2\%), and abnormal returns following coups also tend to be negative (2\%).
-However, some coups result in positive abnormal returns of 10\% or more.
-The variation in the direction of abnormal returns is therefore consistent with the idea that not all types of regime changes are equivalent in terms of expected economic policy outcomes.
+However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that coups can sometimes have large positive economic effects, which is consistent with estimates from \citet{girardi2018institution} showing  the election of Allende in Chile and the subsequent coup replacing him increased stock market valuations.
+In total, the evidence consequently suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones.
+Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.
 
-Our findings suggest that abnormal returns are likely positive following resignations because those leaders were likely to be ``bad'' leaders, and coups may result in positive returns in the event of a transition to more democratic or pro-business leadership.
-Conversely, autocratic coups may increase fear of capital appropriation or the institution of poor economic policies, while assassinations may be merely regarded as highly uncertain events.
-However, while our research design allows us to show that different types of irregular regime changes can be expected to result in different financial outcomes on average, it does not allow us to directly test the mechanisms that result in this variation.
-We therefore leave more direct tests of these mechanisms to future research.
+As in any study, there are a number potential avenues for future research.
+First, more research is needed to identify the pro- and anti-market characteristics of regime changes.
+These may be the types of regime changes used in this paper or more nuanced characteristics.
+Ideally, researchers would be better able to predict the expected effects of future regime changes on stock returns.
+Additionally, it would be useful to identify the mechanisms through which regime changes effect stock returns.
+In the case of Chile,  \citet{girardi2018institution} shows that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
+Research focusing on the mechanisms in other settings would help generalize these findings.
+Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
+\citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
+It would be fruitful to examine whether the direction of the effects of different types of regime changes on these outcomes are consistent with their stock market effects.
+Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
 

### 2019-05-10 doc/paper.tex
Wordsmithing, reformatting, and additions to main text

@@
 \begin{abstract}
+\noindent
 We examine the relationship between political instability and daily returns of national stock indices in every country that experienced a coup, assassination, or resignation for which daily data is available.
@@
 In this study, we examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
-In contrast to the aforementioned cross country studies but like \citet{girardi2018institution} we  conduct our analysis using daily financial data.
+In contrast to the aforementioned cross country studies---but like \citet{girardi2018institution}---we conduct our analysis using daily financial data.
 Market expectations in the form of stock market returns are used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
@@
 The average impact of coups is negative (2\%); however, stock prices increased dramatically during the failed overthrow of Hugo Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
-The effect of public protests on mean stock returns is uncertain, with some protests such as those during the Egpytian Revolution depressing them and others have the opposite effect.
+The effect of public protests on mean stock returns is uncertain, with some protests such as those during the Egyptian Revolution depressing them while others have the opposite effect.
 
@@
 
-The failed coup attempt against Hugo Chavez allows us to examine the effects of both pro-business and anti-business regime change separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+The failed coup attempt against Hugo Chavez provides a natural experiment that allows us to examine the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 The abnormal return on April 12, the first trading day in which investors could react to the coup, was 10\%.
-The market reacted similarly, albeit in the opposite direction, to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
+The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
 
 The results in the figure are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
-The only days on which the ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
+Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
 The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot.
-The unexpected nature of the event means that the abnormal returns capture the true value of the regime change from Chavez to Carmona more accurately than they otherwise would.
+The unexpected nature of the events implies that both regime changes occurred in an as-if random fashion from the perspective of investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
 
@@
 
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those table \autoref{tab:AR-coups} but for successful assassinations rather than coups.
+The results in \autoref{tab:AR-ass} are produced from analyses identical to those in table \autoref{tab:AR-coups} but for successful assassinations rather than coups.
 Like the majority of coups, there is evidence that assassinations decrease stock prices.
@@
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
-Unlike a coup, an assassination is typically an unexpected event that may not necessarily cause immediate change in economic policy.
+Unlike a coup, an assassination may not necessarily be expected to cause immediate change in economic policy, particularly in the presence of an institutionalized line of succession.
 As such, we would expect CARs to be negative due to increased instability and uncertainty, but smaller in magnitude to a coup or resignation due to greater expectations of policy inertia.
@@
 In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
-The mean event day abnormal return is over 4\% and the positive returns are persistent and grow larger over time (mean 20-day CAR $\approx$ 11\%).
+The mean event day abnormal return is over 4\% and the positive returns are persistent and grow larger over time (mean 20-day CAR $\approx$ 12\%).
 Furthermore, event day ARs are only negative and statistically significant at even the ten percent level in two out of the fifteen resignations (Pakistan on April 19, 1993 and Tunisia on June 31, 2011).
@@
 Marcos was replaced by his electoral opponent, Corazon Aquino, who had run on a platform of economic liberalization and elimination of crony capitalism \citep{villegas1987philippines}.
+This event was associated with an approximately 13\% positive event day AR.
 
@@
 As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
-To prevent further decline during the uprising, the Egyptian Stock Exchanged closed at the end of trading on January 27th.
+To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th.
 President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
@@
 
-\begin{figure}[htb]
+\begin{figure}[!htb]
 \includegraphics{../figs/mean-volatility.pdf}
@@
 
-\begin{figure}
+\begin{figure}[!htb]
 \centering
@@
 To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
-There are a few instances in which there are statistically significant (at the 95\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
+There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
 Most of the statistically significant placebo estimates also occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
@@
 For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
-Overall, there is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
 
@@
 \scriptsize
-Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available. Two-sided 
+Notes: Estimates for assassinations do not include the assassination of U.S. president William McKinley in 1901 because no control portfolios are available.
 \end{threeparttable}
@@
 As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 1\% level using the rank test statistic and the abnormal returns for coups and assassinations are significant at at least the 10\% level using the sign test.
-In addition, abnormal absolute returns for all events are statistically significant at the 5\% level using both the rank and sign statistics.
-On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level.
-Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, the synthetic control and small sample tests therefore suggest that the main results are not a result of deviations from normality or confounding world events.
+In addition, abnormal absolute returns for all events are statistically significant at at least the 5\% level using both the rank and sign tests.
+On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level using the rank or sign tests.
+Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, the synthetic control and small sample tests suggest that the main results are not a result of deviations from normality or confounding world events.
 
-\section{Conclusion and Discussion}
+\section{Discussion and Conclusion}
 Max Weber (\citeyear{weber1947theory}) developed the concept of ``charismatic leadership'' whereby a leader's authority stems from their charisma.
-Such rule is often found in autocracies with weak institutions and few constrains placed on the power of leaders.
-\citet{jones2005leaders} has shown that leaders can have particularly large impacts on economic growth in these settings.
-It is therefore not surprising that there is often a strong temptation to overthrow "bad" leaders, even by undemocratic means.
+Such rule is often found in autocracies with weak institutions and few constraints placed on the power of leaders.
+\citet{jones2005leaders} show that leaders can have particularly large impacts on economic growth in these settings.
+It is therefore not surprising that there is often a strong temptation to overthrow ``bad" leaders, even by undemocratic means.
 
@@
 However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that coups can sometimes have large positive economic effects, which is consistent with estimates from \citet{girardi2018institution} showing  the election of Allende in Chile and the subsequent coup replacing him increased stock market valuations.
+
 In total, the evidence consequently suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones.
@@
 First, more research is needed to identify the pro- and anti-market characteristics of regime changes.
-These may be the types of regime changes used in this paper or more nuanced characteristics.
-Ideally, researchers would be better able to predict the expected effects of future regime changes on stock returns.
+There may be features of regime changes that are perceived as pro- or anti-market that are more nuanced than those identified in this paper.
+A greater understanding of these features would allow researchers to better predict the effects of future regime changes on stock returns.
 Additionally, it would be useful to identify the mechanisms through which regime changes effect stock returns.
-In the case of Chile,  \citet{girardi2018institution} shows that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
+In the case of Chile,  \citet{girardi2018institution} show that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
 Research focusing on the mechanisms in other settings would help generalize these findings.
@@
 \citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
-It would be fruitful to examine whether the direction of the effects of different types of regime changes on these outcomes are consistent with their stock market effects.
+It would be fruitful to examine whether the direction of the effects of different types of regime changes on these outcomes are consistent with their stock market effects, or if investor perceptions are at odds with certain development goals.
 Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
@@
 
-\begin{figure}[!ht]
+\pagebreak
+
+\subsection{Time-shifted placebo test}
+
+\begin{figure}[!htb]
 \includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
@@
 
+\pagebreak
+
 \subsection{Synthetic Control Portfolio}
@@
 
-\newpage
+\clearpage
+\pagebreak
+
 \pdfbookmark[1]{References}{References}

### 2019-05-13 doc/paper.tex
Updated natural experiment language in text

@@
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} We analyze 13 coups, 8 assassinations, 15 forced resignations, 11 public protests, and 1 natural experiment provided by the failed 2002 coup in Venezuela.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
+We also examine the ultimately failed 2002 coup in Venezuela, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
 Our study is therefore not only able to use an event-study approach to enhance the reliability of the estimates, but is not limited to a single case study as in \citet{girardi2018institution}.
@@
 We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural experiment that allows us to estimate both the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of left-wing populist.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test\footnote{We refer to this as a natural test rather than a ``natural experiment'' as some definitions of natural experiments would imply as-if random assignment of each regime change to different groups of investors (see for example \citet{dunning2012natural}).
+While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime regime change treatment group while others remained in control.
+This latter scenario is more aligned with many definitions of a natural experiment.} of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
 
@@
 
-The failed coup attempt against Hugo Chavez provides a natural experiment that allows us to examine the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+The failed coup attempt against Hugo Chavez provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot.
-The unexpected nature of the events implies that both regime changes occurred in an as-if random fashion from the perspective of investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
+This implies that both events were unexpected by investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
 

### 2019-05-14 code/01-clean.R
Minor code cleanup
Removed commented out lines for code submission.

@@ -17,9 +17,6 @@ setnames(indices, c("date","ticker","p","dr","real_p"))
 # regime changes
 event <- fread("data-raw/event_list.csv")
 
-# leader duration
-#leaders <- fread("data-raw/leaders_duration.csv") # Is this dataset used in any way?
-
 # revolution dates
 rev <- fread("data-raw/revolutions.csv")
 rev[, num := seq(1, length(country), 1)]

### 2019-05-15 doc/paper.tex
Typo corrections

@@
 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test\footnote{We refer to this as a natural test rather than a ``natural experiment'' as some definitions of natural experiments would imply as-if random assignment of each regime change to different groups of investors (see for example \citet{dunning2012natural}).
-While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime regime change treatment group while others remained in control.
+While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime change treatment group while others remained in control.
 This latter scenario is more aligned with many definitions of a natural experiment.} of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.

### 2019-05-17 doc/paper.tex
Removed footnote explaining why we do not use the term natural experiment.

@@
 We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test\footnote{We refer to this as a natural test rather than a ``natural experiment'' as some definitions of natural experiments would imply as-if random assignment of each regime change to different groups of investors (see for example \citet{dunning2012natural}).
-While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime change treatment group while others remained in control.
-This latter scenario is more aligned with many definitions of a natural experiment.} of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
 

### 2019-05-17 doc/paper.tex
Updated abstract

@@
 \noindent
-We examine the relationship between political instability and daily returns of national stock indices in every country that experienced a coup, assassination, or resignation for which daily data is available.
-A common hypothesis is that political instability discourages investment and reduces economic growth.
-By contrast, we find that while financial volatility increases dramatically following ``irregular'' regime changes, different types of regime change have disparate effects on stock returns.
-We use daily financial data and a constant mean return event study model to show that abnormal returns following resignations are large and positive (4\%), while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
+Political instability is commonly thought to discourage investment and reduce economic growth.
+By contrast, we find that different types of ``irregular'' regime changes - coups, assassinations, or resignations - have disparate effects on stock returns.
+We examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
+Using a constant mean return event study model, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%).
 The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
-We also find that volatility increases during times of protest preceding resignations, but that no clear directionality is present.
+Volatility increases during times of protest preceding resignations, but no clear directionality is present.
 We therefore find that the expected direction and magnitude of abnormal returns is dependent on the type of political event and its expected impact on economic policy.

### 2019-05-17 doc/paper.tex
Updated abstract wording

@@
 We examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
-Using a constant mean return event study model, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%).
+Using an event study approach, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%).
 The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.

### 2019-06-03 doc/paper.tex
Minor updates to conclusion

@@
 \section{Discussion and Conclusion}
-Max Weber (\citeyear{weber1947theory}) developed the concept of ``charismatic leadership'' whereby a leader's authority stems from their charisma.
-Such rule is often found in autocracies with weak institutions and few constraints placed on the power of leaders.
-\citet{jones2005leaders} show that leaders can have particularly large impacts on economic growth in these settings.
-It is therefore not surprising that there is often a strong temptation to overthrow ``bad" leaders, even by undemocratic means.
+
+Markets are said to dislike political instability.
+We show that this is not necessarily the case, as changes in ruler can give markets a boost when a new regime is expected to offer a more pro-business environment than the previous one.
 
@@
 
-In total, the evidence consequently suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones.
+Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones.
 Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.

### 2019-09-09 doc/paper.tex
Updates to theory and examinations of additional events
Added some additional theoretical discussion to address comments, as well as added analysis and visualization of the 1992 Venezuela coup attempt.

@@
 In the wake of the Arab Spring---in which rulers were deposed in four countries---only Tunisia ultimately transitioned to democracy.
-These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
+These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
 
@@
 In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} Common rationales are that unstable governments act myopically and adopt inefficient policies \citep{svensson1998investment,devereux1998political}\footnote{\citet{svensson1998investment} argues that governments are less likely to invest in the legal system and the protection of property rights when political uncertainty is high.
-Similarly, \citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.} and that policy uncertainty depresses business activity \citep{baker2016measuring}.
-Such sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency or political violence---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} Common rationales are that unstable governments act myopically and adopt inefficient policies.
+Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.} Such sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
-But such hypotheses are often overly simplistic.
-Not all political instability is equivalent - resignations, assassinations, and coups are all examples of regime changes, but may have disparate effects on financial returns.
+But such hypotheses may be overly simplistic.
+Not all political instability is equivalent--- resignations, assassinations, and coups are all examples of regime changes, but may have disparate effects on financial returns.
 Resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
@@
 Coups can occur in the name of democracy or autocracy, and in general, signal relative weakness in the current political system.
-Further, political instability may be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
+In other words, investors may view resignations as more stable than coups or assassinations, despite also representing a change in regime.
+Further, political instability may actually be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
 \citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
@@
 Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
+We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.
 We also examine the ultimately failed 2002 coup in Venezuela, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
@@
 
-These findings are consistent with research that shows that ``good coups''---coups that lead to democratization or economic liberalization---are not the norm and therefore on average coups should not be expected to lead to increased economic development and positive market returns \citep{derpanopoulos2015coups, marinov2014coups, powell2011global, thyne2016coup, varol2011democratic}.
-However, while ``good coups'' may be the minority, regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+These findings are consistent with research that shows that ``good coups''---coups that lead to democratization or economic liberalization---are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+However, while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups}, and regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+Previous research therefore suggests that on average coups should not be expected to lead to increased economic development and positive market returns, but that positive returns associated with ``good coups'' should also occasionally be present.
+We provide the first systematic empirical evidence in support of this theory.
 
@@
 \section{Data}
-Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
-The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
-
-\begin{table}[!ht]
-\caption{Regime changes} \label{tab:regime-changes}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
-  \hline
-  \hline
-  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
-  \hline
-   \multicolumn{3}{c}{\textbf{Coups}}\\ 
-\ExpandableInput{../tables/coups.txt} \\
-   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
-\ExpandableInput{../tables/failed_coup.txt}\\
-  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
-\ExpandableInput{../tables/assassinations.txt}\\
-  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
-\ExpandableInput{../tables/resignations.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
-\end{threeparttable}
-\end{center}
-\end{table}
-
-The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime."}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
-Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
-The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.
-
-We further supplement the CSP data with leadership data from Archigos Version 4.1, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
-coups, revolts and assassinations).
-
-A list of the political events in our dataset is shown in \autoref{tab:regime-changes}.
-Coups tend to have the largest impact on the level of democratization as a number of countries have subeqeuently transitioned from democracies to anocracies or autocracies.
-On the other hand, neither assassinations or resignations have much of an impact on the level of democratization.
 
@@
 The S\&P/IFC index includes securities from emerging markets while the MSCI index includes securities from developed markets only.
-We collect stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
+We collect national stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation and for which daily financial data is available.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
 Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available daily time series for these stock indices are listed in \autoref{tab:stock-list}.
@@
 \end{table}
+
+Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
+The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
+We focus on successful coups because it is difficult to classify failed coups.
+\citet[p.
+617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.'' The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+
+\begin{table}[!ht]
+\caption{Regime changes} \label{tab:regime-changes}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
+  \hline
+  \hline
+  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
+  \hline
+   \multicolumn{3}{c}{\textbf{Coups}}\\ 
+\ExpandableInput{../tables/coups.txt} \\
+   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
+\ExpandableInput{../tables/failed_coup.txt}\\
+  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
+\ExpandableInput{../tables/assassinations.txt}\\
+  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
+\ExpandableInput{../tables/resignations.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime."}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
+Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
+The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.
+Note that the Polity IV definition of ``poor performance'' is not synonymous with poor \textit{economic} performance, and in practice the reasons cited for resignation across events are: loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
+
+%loss in conflict/war (Argentina), anti-authoritarian protest (Philippines, Bangladesh, Nepal, Tunisia), corruption scandal (Philippines, Lithuania), constitutional ruling (Pakistan), contested election (Ukraine), abuse of power (Ecuador) Thailand?
+
+We further supplement the CSP data with leadership data from Archigos Version 4.1, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
+coups, revolts and assassinations).
+
+A list of the political events in our dataset is shown in \autoref{tab:regime-changes}.
+Coups tend to have the largest impact on the level of democratization as a number of countries have subeqeuently transitioned from democracies to anocracies or autocracies.
+On the other hand, neither assassinations or resignations have much of an impact on the level of democratization.
 
@@
 Event day ARs are negative for all coups except the 1971 coup in Argentina, the 2002 coup in Nepal, and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}).
-These results provide evidence that coups can in fact result in positive abnormal returns.
+These results provide evidence that coups do not necessarily lead to negative abnormal returns.
 While the 1971 Argentinian coup did result in another military leader, it did so while calling for free and democratic elections and replaced a government that had adopted extreme protectionist economic policies.
@@
 
-The failed coup attempt against Hugo Chavez provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+The failed coup attempt against Hugo Chavez therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
+We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela--- at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see figure \autoref{fig:AR-Ven-1992}).
+These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to attempted and successful overthrows of pro-market leaders.
 
@@
 
+\subsection{Additional graphical depictions of individual events}
+
+\begin{figure}[!htb]
+\includegraphics{../figs/venezuela_coup_attempt_1992.pdf}
+\caption{Abnormal returns surrounding the 1992 Venezuelan coup d'etat attempt}
+\label{fig:AR-Ven-1992}
+\end{figure}
+
+\pagebreak
+
 \subsection{Time-shifted placebo test}

### 2019-09-09 code/04-ar.R

@@ -46,15 +46,43 @@ ven.es <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
                       event_ticker = ven$ticker,
                      event_window = 20, estimation_window = 200,
                      event_date = ven$stock_date, model = "constant", control = FALSE)  
+
 ven.es$ar.treat[, lar := ar - qnorm(.975) * ven.es$sigma.treat]
 ven.es$ar.treat[, uar := ar + qnorm(.975) * ven.es$sigma.treat]
+
 p <- ggplot(ven.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) + 
   geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") +
   geom_vline(aes(xintercept = 0), linetype = 2, color = "grey") +
   geom_pointrange(aes(ymin = lar, ymax = uar), size = .3) +
-  xlab("Trading days") + ylab("Abnormal Returns (%)") +
+  xlab("Trading days") + 
+  ylab("Abnormal Returns (%)") +
   scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
   theme_classic()
 print(p)
+
 ggsave("figs/venezuela_coup_attempt_2002.pdf", p, height = 5, width = 7)
+
+# VENEZUELA 1992 COUP ATTEMPT --------------------------------------------------
+ven92 <- event[ticker == "_VE1" & stock_date == "1992-11-27"]
+ven92.es <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                      event_ticker = ven92$ticker,
+                      event_window = 20, estimation_window = 200,
+                      event_date = ven92$stock_date, model = "constant", control = FALSE)  
+
+ven92.es$ar.treat[, lar := ar - qnorm(.975) * ven92.es$sigma.treat]
+ven92.es$ar.treat[, uar := ar + qnorm(.975) * ven92.es$sigma.treat]
+
+p <- ggplot(ven92.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) + 
+  geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") +
+  geom_vline(aes(xintercept = 0), linetype = 2, color = "grey") +
+  geom_pointrange(aes(ymin = lar, ymax = uar), size = .3) +
+  xlab("Trading days") + 
[…]

### 2019-10-11 doc/paper.tex
Addresed additional reviewer comments
Choices of datasets, coups as a contested concept, and more explanation of event windows.

@@
 But such hypotheses may be overly simplistic.
-Not all political instability is equivalent--- resignations, assassinations, and coups are all examples of regime changes, but may have disparate effects on financial returns.
+Not all political instability is equivalent--- resignations, assassinations, and coups are all examples of unexpected regime changes, but may have disparate effects on financial returns.
 Resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
@@
 Coups can occur in the name of democracy or autocracy, and in general, signal relative weakness in the current political system.
-In other words, investors may view resignations as more stable than coups or assassinations, despite also representing a change in regime.
+Investors may therefore view resignations as more stable than coups or assassinations, despite also representing an abnormal regime change.
 Further, political instability may actually be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
 \citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
-Likewise, \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+\citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
 More recent studies provide support for this hypothesis.
@@
 \citet{girardi2018institution} show that Salvador Allende's socialist government was associated with large declines in stock prices while the coup that replaced him boosted them.
+We add to this literature by showing a systematic demonstration that coups rarely lead to positive abnormal returns, but can in the rare event that a clearly anti-business leader is replaced with a pro-business regime.
 
@@
 Market expectations in the form of stock market returns are used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
-The advantage of this event study approach is that it allows us to use time-series variation in stock returns to estimate treatment effects and mitigate the endogeneity problems that are nearly ubiquitous in cross country regressions.\footnote{A growing body of work uses event studies to assess political phenomenon.
+The advantage of this event study approach is that it allows us to use time-series variation in stock returns to estimate treatment effects and mitigate the endogeneity problems that are nearly ubiquitous in the cross country regression approaches previously used to assess economic response to political instability.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
@@
 
-These findings are consistent with research that shows that ``good coups''---coups that lead to democratization or economic liberalization---are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+These findings are consistent with previous research that suggests that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability \citep{alesina1996income}.
+However, out event study approach also allows us examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
+Previous research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
 However, while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups}, and regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
@@
 
-Financial data are from the Global Financial Data database, which includes the longest available time series of stock prices.
+Financial data are from the Global Financial Data database, which includes the longest available daily time series of stock prices.
 We collect data on national equity indices and two global equity indices, the S\&P/IFC Emerging Market Investable Composite and the Morgan Stanley Capital International (MSCI) World Index.
@@
 The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups.
+We focus on successful coups because it is difficult to classify failed coups, and the choice of dataset and classification methodology would directly alter our findings.
 \citet[p.
-617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.'' The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.'' The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
 
@@
 Returns are for 250 trading days---approximately one calendar year---before and after regime changes.
-
 The absolute value of returns on the event day (trading day 0) are significantly larger than on any other day.
@@
 For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.
+We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$), and the event date plus 19 days $(0,19$).
+In addition, we present results for the pre-event windows $(-1,-7$) and $(-1,-20$).
 
@@
 In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Center for System Peace Polity IV polity score of 6.
-Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections.
+Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections, itself a democratically subversive action.
 The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
@@
 The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela--- at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see figure \autoref{fig:AR-Ven-1992}).
-These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to attempted and successful overthrows of pro-market leaders.
+We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see figure \autoref{fig:AR-Ven-1992}).
+These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
 
@@
 This implies that both events were unexpected by investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
+We see the same story 10 years prior, with pre and post-event CARs statistically indistinguishable from zero on all days except for the day of the Chavez coup attempt, this time demonstrating the market's negative evaluation of a Pérez to Chavez regime change.
 
@@
 
-These results are consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns.
+These results are consistent with the idea that the expected impact of an atypical political event on economic policy is highly important to the directionality of returns.
 The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority.
@@
 Markets are said to dislike political instability.
-We show that this is not necessarily the case, as changes in ruler can give markets a boost when a new regime is expected to offer a more pro-business environment than the previous one.
+We show that this is not necessarily always the case, as unexpected changes in ruler can give markets a boost when a new regime is expected to offer a more pro-business environment than the previous one.
 
@@
 
-Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist governments are replaced with more pro-business ones.
-Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies, while assassinations may be merely regarded as highly uncertain events.
+While our empirical strategy does not allow us to directly test the mechanisms that drive differences in investor response from each individual event, previous theoretical literature and examination of individual cases offer some insights.
+Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist or anti-business governments are replaced with pro-business ones regimes.
+Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies.
+Assassinations may be merely regarded as highly uncertain events.
 

### 2019-10-14 doc/paper.tex
Additions addressing review comments
Addressed comments about a fuller consideration of timing of information available to investors

@@
 \subsection{Robustness} \label{subsec: Robustness}
+
 There are some potential concerns with the results in \autoref{subsec:abnormal-returns}.
@@
 In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
+The general intuition is that we should not observe significant abnormal returns when performing an identical test on dates where no intervention (i.e.
+a politically unstable event) occurred.
+Observing such effects would call the research design and modeling assumptions into question, and raise concerns that the abnormal returns were caused by factors other than the regime changes.
 
@@
 While our empirical strategy does not allow us to directly test the mechanisms that drive differences in investor response from each individual event, previous theoretical literature and examination of individual cases offer some insights.
-Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders, and coups can result in positive returns in settings where socialist or anti-business governments are replaced with pro-business ones regimes.
+Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders whose replacements were expected to adopt better economic policies.
+Our examination the failed 2002 Venezuela coup shows that coups can result in large positive returns in settings where socialist or anti-business governments are replaced with pro-business regimes.
 Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies.
-Assassinations may be merely regarded as highly uncertain events.
+Assassinations may be merely regarded as highly uncertain events, best approximating the classic ``unstable'' event where investors have few priors.
+Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
+CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
 

### 2019-10-15 doc/paper.tex
Added 2016 Turkish coup attempt to appendix

@@
 
-Markets are said to dislike political instability.
-We show that this is not necessarily always the case, as unexpected changes in ruler can give markets a boost when a new regime is expected to offer a more pro-business environment than the previous one.
+While conventional wisdom suggests markets dislike political instability, we show that this is not necessarily always the case.
+Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more pro-business environment than the previous one.
 
@@
 The Arab spring is perhaps the most notable, with protests in response to oppressive regimes and low living standards spreading throughout the Middle East in late 2010.
-There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.
-Yet despite their frequency there is little evidence on their economic consequences.
+There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.\footnote{The Turkish coup attempt led to negative event-day CARs of approximately -7\%.
+See \autoref{fig:AR-Turkey-2016} for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
 
@@
 Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders whose replacements were expected to adopt better economic policies.
+Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
+CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
 Our examination the failed 2002 Venezuela coup shows that coups can result in large positive returns in settings where socialist or anti-business governments are replaced with pro-business regimes.
@@
 Assassinations may be merely regarded as highly uncertain events, best approximating the classic ``unstable'' event where investors have few priors.
-Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
-CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
 
@@
 
-\subsection{Additional graphical depictions of individual events}
+\subsection{Graphical depictions of additional events}
 
 \begin{figure}[!htb]
-\includegraphics{../figs/venezuela_coup_attempt_1992.pdf}
+\centering
+\vspace{-0.4cm}
+\includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
 \caption{Abnormal returns surrounding the 1992 Venezuelan coup d'etat attempt}
@@
 
+\begin{figure}[!htb]
+\centering
+\vspace{-0.8cm}
+\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
+\caption{Abnormal returns surrounding the 2016 Turkish coup d'etat attempt}
+\label{fig:AR-Turkey-2016}
+\end{figure}
+
+\clearpage
 \pagebreak

### 2019-10-15 code/04-ar.R

@@ -86,3 +86,37 @@ p <- ggplot(ven92.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) +
 print(p)
 
 ggsave("figs/venezuela_coup_attempt_1992.pdf", p, height = 5, width = 7)
+
+
+# TURKEY 2016 COUP ATTEMPT -----------------------------------------------------
+
+# Add 2016 Turkey failed coup to data.table
+event = rbind(event,list(85, "Turkey", "_XU100D", "07/15/2016", 
+                 as.Date("07/18/2016", "%m/%d/%Y"),
+                 "Recep Tayyip Erdoğan", "Failed Coup", 
+                 NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA))
+
+
+turk16 <- event[ticker == "_XU100D" & stock_date == "2016-07-18"]
+turk16.es <- event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                      event_ticker = turk16$ticker,
+                      event_window = 20, estimation_window = 200,
+                      event_date = turk16$stock_date, model = "constant", control = FALSE)  
+
+turk16.es$ar.treat[, lar := ar - qnorm(.975) * turk16.es$sigma.treat]
+turk16.es$ar.treat[, uar := ar + qnorm(.975) * turk16.es$sigma.treat]
+
+p <- ggplot(turk16.es$ar.treat[abs(td) <= 10], aes(x = td, y = ar)) + 
+  geom_hline(aes(yintercept = 0), linetype = 2, color = "grey") +
+  geom_vline(aes(xintercept = 0), linetype = 2, color = "grey") +
+  geom_pointrange(aes(ymin = lar, ymax = uar), size = .3) +
+  xlab("Trading days") + 
+  ylab("Abnormal Returns (%)") +
+  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
+  scale_y_continuous(limits = c(-12, 12),
+                     breaks = scales::pretty_breaks(n = 10)) +
+  theme_classic()
+print(p)
+
+ggsave("figs/turkey_coup_attempt_2016.pdf", p, height = 5, width = 7)
+

### 2019-10-17 doc/paper.tex
Reorganized introduction and theory
Added additional theoretical discussion and reorganized the introduction.

@@
 Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.} Such sentiments are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
 
-But such hypotheses may be overly simplistic.
-Not all political instability is equivalent--- resignations, assassinations, and coups are all examples of unexpected regime changes, but may have disparate effects on financial returns.
-Resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
-Assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
-Coups can occur in the name of democracy or autocracy, and in general, signal relative weakness in the current political system.
-Investors may therefore view resignations as more stable than coups or assassinations, despite also representing an abnormal regime change.
-Further, political instability may actually be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
-\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
-\citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-More recent studies provide support for this hypothesis.
-\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
-\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with large declines in stock prices while the coup that replaced him boosted them.
-We add to this literature by showing a systematic demonstration that coups rarely lead to positive abnormal returns, but can in the rare event that a clearly anti-business leader is replaced with a pro-business regime.
+These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
 In this study, we examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
-In contrast to the aforementioned cross country studies---but like \citet{girardi2018institution}---we conduct our analysis using daily financial data.
+In contrast to the aforementioned cross country studies, we conduct our analysis using daily financial data and provide separate estimates by source of instability.
 Market expectations in the form of stock market returns are used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
@@
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.}
+
+We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
 We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.
-We also examine the ultimately failed 2002 coup in Venezuela, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
-Our study is therefore not only able to use an event-study approach to enhance the reliability of the estimates, but is not limited to a single case study as in \citet{girardi2018institution}.
-The relatively large sample enhances external validity and allows us to show that different types of political events have disparate economic effects.
+We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
+Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate economic effects.
 
 We find that coups, assassinations, resignations, and public protests cause large increases in financial volatility.
-Abnormal returns following resignations are large and positive (4\%) while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
-The average impact of coups is negative (2\%); however, stock prices increased dramatically during the failed overthrow of Hugo Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
+However, the magnitude and direction of the effects differ by source of instability.
+On average, abnormal returns following resignations are large and positive (4\%) while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
+The average impact of coups is negative (2\%); however, stock prices increased dramatically (10\%) during the failed overthrow of Hugo Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
 The effect of public protests on mean stock returns is uncertain, with some protests such as those during the Egyptian Revolution depressing them while others have the opposite effect.
 
-These findings are consistent with previous research that suggests that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability \citep{alesina1996income}.
-However, out event study approach also allows us examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
-Previous research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
-However, while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups}, and regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
-Previous research therefore suggests that on average coups should not be expected to lead to increased economic development and positive market returns, but that positive returns associated with ``good coups'' should also occasionally be present.
-We provide the first systematic empirical evidence in support of this theory.
+\subsection{Reexamining how markets respond to irregular regime changes}
 
-Our main conclusion is therefore that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
-Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule, exacerbate poor economic policies, or merely increase policy uncertainty have the opposite effect.
+As noted above, conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns.
+However, there are reasons to believe such hypotheses may be overly simplistic.
+
+First, political instability may be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
+Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+
+An active debate exists on the subject of ``good coups.'' \citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while   \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+However, most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+But while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
+\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth, and \citet{girardi2018institution} show that Salvador Allende's socialist government was associated with large declines in stock prices while the coup that replaced him boosted them.
+
+Previous research therefore suggests that on average coups should not be expected to lead to increased economic development and positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
+We provide the first systematic empirical evidence in support of this theory as our event study approach also allows us examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
+Unlike \citet{girardi2018institution}, we are not limited to a single case study, and can therefore provide both a cross-country and within-case analysis.
+
+Second, not all political instability is equivalent--- resignations, assassinations, and coups are all examples of unexpected regime changes.
+However, resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
+Assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
+Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
+These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
+By contrast---recognizing the different degrees of instability that these events may reflect---we estimate effects separately for coups, assassinations, resignations, and protests.
+Our event study approach affords us this freedom without encountering the power issues that would arise in a regression setting.
+
+Different types and events of instability may therefore have disparate effects on markets or growth.
+Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
+Assassinations should have a neutral or negative impact as they always increase uncertainty, but institutional responses to assassinations vary by country.
+By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader.
+
+Our empirical findings reflect these predictions.
+We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule (e.g.
+military coups), exacerbate poor economic policies, or merely increase policy uncertainty (such as assassinations) have the opposite effect.
 
@@
 \includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup d'etat attempt}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
 \label{fig:AR-Ven}
@@
 CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
-Our examination the failed 2002 Venezuela coup shows that coups can result in large positive returns in settings where socialist or anti-business governments are replaced with pro-business regimes.
+Our examination of the failed 2002 Venezuela coup shows that coups can result in large positive returns in settings where socialist or anti-business governments are replaced with pro-business regimes.
 Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies.
@@
 \includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
-\caption{Abnormal returns surrounding the 1992 Venezuelan coup d'etat attempt}
+\caption{Abnormal returns surrounding the 1992 Venezuelan coup attempt}
 \label{fig:AR-Ven-1992}
@@
 \centering
-\vspace{-0.8cm}
+\vspace{-0.5cm}
 \includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
-\caption{Abnormal returns surrounding the 2016 Turkish coup d'etat attempt}
+\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
 \label{fig:AR-Turkey-2016}

### 2019-12-04 doc/paper.tex
Updates in line with reviewer comments

@@
 
-\subsection{Reexamining how markets respond to irregular regime changes}
+\singlespacing
+\section{Reexamining how markets respond to irregular regime changes}
+\doublespacing
 
-As noted above, conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns.
 However, there are reasons to believe such hypotheses may be overly simplistic.
 
-First, political instability may be seen as a positive event if the current regime is regarded as strongly anti-business or anti-global.
+First, political instability may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
 Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
@@
 
-An active debate exists on the subject of ``good coups.'' \citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while   \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+An active debate exists on the subject of ``good coups''---i.e.
+coups that lead to democratization or economic liberalization.
+\citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
 However, most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
@@
 Previous research therefore suggests that on average coups should not be expected to lead to increased economic development and positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
-We provide the first systematic empirical evidence in support of this theory as our event study approach also allows us examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
-Unlike \citet{girardi2018institution}, we are not limited to a single case study, and can therefore provide both a cross-country and within-case analysis.
+We shed light on this theory as our event study approach also allows us to examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
+As we are not limited to a single case study, we can provide both a cross-country and within-case analysis.
 
@@
 Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
-These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
+These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
 By contrast---recognizing the different degrees of instability that these events may reflect---we estimate effects separately for coups, assassinations, resignations, and protests.
@@
 Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
-Assassinations should have a neutral or negative impact as they always increase uncertainty, but institutional responses to assassinations vary by country.
+Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
 By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader.
@@
 
-The results in the figure are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
+The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
 Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
@@
 
-These results are consistent with our hypothesis that the nature of the political event and its expected impact on policy matters.
+These results are consistent with our hypothesis that the nature of the political event and its expected impact on policy matters, and that assassinations should have a negative effect as they occur seemingly at random and increase uncertainty.
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
@@
 
-These results are consistent with the idea that the expected impact of an atypical political event on economic policy is highly important to the directionality of returns.
-The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority.
-Leaders were often ousted following corruption charges, allegations of fraud, financial crises, and/or political violence.
+These results are again consistent with our hypothesis that different events will have disparate effects, and that resignations may lead to positive returns.
+The positive event day abnormal return following resignations is not surprising as resignations typically occur because of poor performance and/or loss of authority.
+Among our sample of events, leaders were ousted following loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
 
@@
 This event was associated with an approximately 13\% positive event day AR.
+
+By contrast, the largest negative event in our sample (-3\%) is the 1993 resignation of President Ghulam Ishaq Khan and Prime Minister Nawaz Sharif in Pakistan.
+The resignations occurred after months of political infighting when the army demanded the President and Prime Minister resign and call for new elections.
+An interim prime minister was installed, but uncertainty about Pakistan's political and economic future remained high prior to the next round of elections.
 
@@
 However, this occurs because some political movements increase stock prices while others decrease them.
-As shown in column (2), the absolute value of stock returns are over 2\% higher during public protests.
+As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests.
 These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
 To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
-The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 2\% higher during public protests.
-Finally, column (4) shows that stock volatility is more than 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}
+The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
+Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}
 

### 2019-12-05 doc/paper.tex
Corrected some typos

@@
 The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see figure \autoref{fig:AR-Ven-1992}).
+We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see \autoref{fig:AR-Ven-1992}).
 These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
@@
 
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those in table \autoref{tab:AR-coups} but for successful assassinations rather than coups.
+The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for successful assassinations rather than coups.
 Like the majority of coups, there is evidence that assassinations decrease stock prices.

### 2020-05-15 doc/regime_changes_manuscript.tex
JOP Submissions

--- 2019-12-05 doc/paper.tex
@@
 \usepackage[natbibapa]{apacite}
-\bibliographystyle{apacite}
+\bibliographystyle{apsr}
 \bibpunct{(}{)}{;}{a}{}{,}
 \renewcommand{\bibname}{References}
+
+% Footnote double spacing and font size for journal submission
+\usepackage{footmisc}
+\setlength{\footnotesep}{\baselineskip}
+\renewcommand{\footnotelayout}{\normalsize\doublespacing}
 
@@
 \newcommand{\aref}[1]{\hyperref[#1]{Appendix~\ref{#1}}}
+
+\setcounter{secnumdepth}{0}
 
@@
 \begin{document}
-\author{Devin Incerti and Trevor Incerti}
+%\author{Devin Incerti and Trevor Incerti}
 \title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
@@
 \maketitle
+\thispagestyle{empty}
 
@@
 
-\section{Introduction} \label{sec:Introduction}
+\clearpage
+\pagenumbering{arabic}
+
+%\section{Introduction} \label{sec:Introduction}
+\newpage
 
@@
 
-\autoref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
+\nameref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
 It will first analyze coups, assassinations and resignations separately and determine whether they increase mean returns.
@@
 \section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
-\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
+%\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
 We begin our analysis by studying the effect of irregular regime changes on stock returns.
@@
 
-\subsubsection{Coups} \label{subsec: Coups}
+\subsection{Coups} \label{subsec: Coups}
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
@@
 The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see \autoref{fig:AR-Ven-1992}).
+We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see Figure A1).
 These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
@@
 
-\subsubsection{Assassinations} \label{subsec: Assassinations}
+\subsection{Assassinations} \label{subsec: Assassinations}
 
@@
 
-\subsubsection{Resignations} \label{subsec: Resignations}
+\subsection{Resignations} \label{subsec: Resignations}
 
@@
 
-\subsubsection{Public Protests} \label{subsec: Public Protests}
+\subsection{Public Protests} \label{subsec: Public Protests}
 The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
@@
 
-The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
+The start and end dates in Table A.1 are the dates that protests began and leader's resigned respectively.
 Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
@@
 The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
-Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
+Non-protest dates are the 250 days prior to the start dates and after the end dates listed in Table A.1.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
 
@@
 The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
-Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}
+Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
 
@@
 \subsection{Volatility} \label{subsec: Volatility}
-Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, the results from \autoref{subsec:abnormal-returns} suggest that all of these political events increase financial volatility.
+Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, our results suggest that all of these political events increase financial volatility.
 However, since stock volatility is not directly observable, one must decide how to best estimate volatility.
@@
 
-\subsection{Robustness} \label{subsec: Robustness}
+\section{Robustness} \label{subsec: Robustness}
 
-There are some potential concerns with the results in \autoref{subsec:abnormal-returns}.
+There are some potential concerns with the results in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections.
 First, the abnormal returns could have been driven by factors unrelated to the regime changes.
@@
 \autoref{fig:mean-car-by-regime-change} compares mean CARs estimated using the actual event date (\autoref{subfig:mean-car-by-regime-change-actual}) to CARs estimated with the event date shifted 1-year (365 days) into the future (\autoref{subfig:mean-car-by-regime-change-placebo}).
-\autoref{subfig:mean-car-by-regime-change-actual}---which reproduces the tabular results presented in \autoref{subsec:abnormal-returns}---shows that assassinations and coups are associated with negative event day ARs while resignations are associated with positive event day ARs.
+\autoref{subfig:mean-car-by-regime-change-actual}---which reproduces the tabular results presented in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections---shows that assassinations and coups are associated with negative event day ARs while resignations are associated with positive event day ARs.
 In contrast, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
@@
 
-To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
+To ensure that results of the placebo test based on 1-year did not occur by chance, Figure A3 plots event-day abnormal against the number of days shifted.
 There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
@@
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See \autoref{Appendix} for a more formal explanation.}
+The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See Appendix A for a more formal explanation.}
 
@@
 There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.\footnote{The Turkish coup attempt led to negative event-day CARs of approximately -7\%.
-See \autoref{fig:AR-Turkey-2016} for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
+See Figure A2 for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
 
@@
 
-\newpage
-
-\appendix
-\setcounter{table}{0}
-\renewcommand\thetable{\Alph{section}.\arabic{table}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-
-\section{Appendix} \label{Appendix}
-\begin{table}[!ht]
-\caption{List of public protests preceding resignations} \label{tab:protest-list}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}llll}
-  \hline
-    \hline
-\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Name}&\multicolumn{1}{c}{Start Date}&\multicolumn{1}{c}{End Date}\\
-  \hline
-Philippines & EDSA 1/Yellow Revolution & 2/22/1986 & 2/25/1986\\
-Bangladesh & Bangladeshi Spring of 1990 & 11/27/1990 & 12/7/1990\\
-Thailand & Black May & 5/17/1992 & 5/20/1992\\
-Indonesia & Indonesian Riots & 5/12/1998 & 5/21/1998\\
-Philippines & EDSA II & 1/17/2001 & 1/20/2001\\
-Argentina & Argentina Riots & 12/16/2001 & 12/20/2001\\
-Ukraine & Orange Revolution & 11/22/2004 & 1/23/2005\\
-Ecuador & Ecuadorian Protests & 4/13/2005 & 4/20/2005\\
-Nepal & Nepalese People's Revolution & 4/6/2006 & 4/24/2006\\
-Tunisia & Tunisian Revolution & 12/18/2010 & 1/14/2011\\
-Egypt & Egyptian Revolution & 1/25/2011 & 2/11/2001\\
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\pagebreak
-
-\subsection{Graphical depictions of additional events}
-
-\begin{figure}[!htb]
-\centering
-\vspace{-0.4cm}
-\includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
-\caption{Abnormal returns surrounding the 1992 Venezuelan coup attempt}
-\label{fig:AR-Ven-1992}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\vspace{-0.5cm}
-\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
-\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
-\label{fig:AR-Turkey-2016}
-\end{figure}
-
-\clearpage
-\pagebreak
-
-\subsection{Time-shifted placebo test}
-
-\begin{figure}[!htb]
-\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
-\caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
-\label{fig:mean-event-day-ar-by-regime-change}
-\end{figure}
-
-\pagebreak
-
-\subsection{Synthetic Control Portfolio}
-Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
-
 \clearpage

### 2020-05-19 doc/paper.tex
Prose updates and addition of mechanisms analysis and section

@@
 \usepackage[natbibapa]{apacite}
-\bibliographystyle{apacite}
+\bibliographystyle{apsr}
 \bibpunct{(}{)}{;}{a}{}{,}
 \renewcommand{\bibname}{References}
+
+% Footnote double spacing and font size for journal submission
+%\usepackage{footmisc}
+%\setlength{\footnotesep}{\baselineskip}
+%\renewcommand{\footnotelayout}{\normalsize\doublespacing}
 
@@
 \begin{document}
-\author{Devin Incerti and Trevor Incerti}
-\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
+\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
+devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
+PhD Candidate in the Department of Political Science, Yale University.
+trevor.incerti@yale.edu.}}
+\title{\textbf{Are regime changes always bad for markets?
+Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
+Authors are listed in alphabetic order, implying equal authorship.
+Any and all errors are our own.}}}
 \date{\today}
 \maketitle
+\thispagestyle{empty}
 
@@
 Political instability is commonly thought to discourage investment and reduce economic growth.
-By contrast, we find that different types of ``irregular'' regime changes - coups, assassinations, or resignations - have disparate effects on stock returns.
-We examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
-Using an event study approach, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%).
-The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more.
-Volatility increases during times of protest preceding resignations, but no clear directionality is present.
-We therefore find that the expected direction and magnitude of abnormal returns is dependent on the type of political event and its expected impact on economic policy.
+However, we find that different types of ``irregular'' regime changes have disparate effects on stock returns.
+Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
+We show that abnormal returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
+The impact of coups tends to be negative (-2\%), but examination of the 2002 failed coup against Hugo Chavez reveals returns of +10\%.
+We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to be perceived negatively by investors than democratic or pro-business changes.
+The expected direction and magnitude of abnormal returns is therefore dependent on the type of regime change and its expected impact on economic policy.
+
 \end{abstract}
@@
 
-In this study, we examine the impact of ``irregular'' regime changes and public protests on economic performance and remain agnostic about the direction of the effect.
-In contrast to the aforementioned cross country studies, we conduct our analysis using daily financial data and provide separate estimates by source of instability.
-Market expectations in the form of stock market returns are used as an indicator of whether the market views different types of potentially destabilizing political events as ``good'' for economic growth.
-The advantage of this event study approach is that it allows us to use time-series variation in stock returns to estimate treatment effects and mitigate the endogeneity problems that are nearly ubiquitous in the cross country regression approaches previously used to assess economic response to political instability.\footnote{A growing body of work uses event studies to assess political phenomenon.
+In this study, we examine the impact of ``irregular'' regime changes and public protests on market performance, but remain agnostic about the direction of the effect.
+Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns and by extension economic growth.
+Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
+
+In contrast to the aforementioned cross country studies, we conduct our analysis using event studies of daily financial data and provide separate estimates by source of instability.
+Event studies examine the behavior of stock prices around specific unexpected events, and therefore seek to determine if returns at the time of event are abnormal (i.e., systematically different from predicted).
+An ``abnormal return'' therefore reflects the difference between the observed return and the predicted return.
+We use daily data as it allows for more precise measurement of abnormal returns.
+The advantage of this approach is that it uses time-series variation in stock returns to estimate treatment effects and mitigates the endogeneity problems that are nearly ubiquitous in the cross country regression approaches often used to assess economic response to political instability.
+In other words, an event study does not require a correct specification of controls to establish a causal effect.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
@@
 We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
-Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate economic effects.
+Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
 
 We find that coups, assassinations, resignations, and public protests cause large increases in financial volatility.
-However, the magnitude and direction of the effects differ by source of instability.
-On average, abnormal returns following resignations are large and positive (4\%) while abnormal returns following assassinations are negative and smaller in magnitude (2\%).
-The average impact of coups is negative (2\%); however, stock prices increased dramatically (10\%) during the failed overthrow of Hugo Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
-The effect of public protests on mean stock returns is uncertain, with some protests such as those during the Egyptian Revolution depressing them while others have the opposite effect.
+However, the magnitude and direction of the effects differ by type of regime change.
+On average, abnormal returns following resignations are large and positive (+4\%) while abnormal returns following assassinations and coups tend to be negative and smaller in magnitude (-2\%).
+We also find suggestive evidence that authoritarian regime changes are more likely to lead to negative returns that democratic regime changes.
+Finally, we examine the effect of pro versus anti business regime change via an in-depth examination of the seemingly successful but ultimately failed coup against Hugo Chavez in 2002.
+Stock prices increased dramatically (+10\%) after the failed overthrow of Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
 
@@
 
-Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns.
-However, there are reasons to believe such hypotheses may be overly simplistic.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
+However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
 
-First, political instability may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
+First, a change in regime may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
 Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
-\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
 
 An active debate exists on the subject of ``good coups''---i.e.
-coups that lead to democratization or economic liberalization.
+coups that lead to democratization or economic liberalization---and their effect on economic growth.
+\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
 \citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
@@
 But while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
-\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth, and \citet{girardi2018institution} show that Salvador Allende's socialist government was associated with large declines in stock prices while the coup that replaced him boosted them.
+\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
+In another study examining the outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
 
-Previous research therefore suggests that on average coups should not be expected to lead to increased economic development and positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
+Previous research therefore suggests that on average coups should not be expected to lead to increased economic development or positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
 We shed light on this theory as our event study approach also allows us to examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
@@
 
-Second, not all political instability is equivalent--- resignations, assassinations, and coups are all examples of unexpected regime changes.
-However, resignations typically occur when an unpopular leader steps down and may signal the coming of a more effective leader.
-Assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
+Second, not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
+However, some regime changes may actually lead to increased stability.
+Resignations, for example, often occur when an ineffective leader steps down.
+Assassinations, by contrast, are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
 Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
@@
 By contrast---recognizing the different degrees of instability that these events may reflect---we estimate effects separately for coups, assassinations, resignations, and protests.
-Our event study approach affords us this freedom without encountering the power issues that would arise in a regression setting.
+Our event study approach affords us this freedom without encountering the statistical power issues that would arise in a regression setting.
 
-Different types and events of instability may therefore have disparate effects on markets or growth.
+Different types of regime changes may therefore have disparate effects on markets, just as they may differentially effect overall economic growth.
 Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
@@
 
-Our empirical findings reflect these predictions.
-We therefore find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+Our empirical findings validate these predictions.
+We find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
 Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule (e.g.
@@
 \citet[p.
-617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.'' The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''
 
@@
 A list of the political events in our dataset is shown in \autoref{tab:regime-changes}.
-Coups tend to have the largest impact on the level of democratization as a number of countries have subeqeuently transitioned from democracies to anocracies or autocracies.
+Coups tend to have the largest impact on the level of democratization as a number of countries have subsequently transitioned from democracies to anocracies or autocracies.
 On the other hand, neither assassinations or resignations have much of an impact on the level of democratization.
 
+The discussion above shows that there is considerable debate about classification of regime changes.
+We recognize that some readers may feel that certain events are missing based on their own substantive knowledge.
+However, we choose to rely on commonly used third-party classifications in order to minimize the possibility that our results are driven by our own subjective classifications.
+The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+
 To gain perspective on the relationship between irregular regime changes and the stock market, \autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events.
-Returns are for 250 trading days---approximately one calendar year---before and after regime changes.
+Returns are for 200 trading days before and after regime changes.
 The absolute value of returns on the event day (trading day 0) are significantly larger than on any other day.
@@
 
-\autoref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
-It will first analyze coups, assassinations and resignations separately and determine whether they increase mean returns.
-It will then combine all irregular regime changes and estimate the effect of regime changes on the variance of returns.
+\nameref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
+It will first formally estimate the amount of volatility surrounding all irregular regime changes, then analyze coups, assassinations and resignations separately and determine what impact they have on mean returns.
 
@@
 \section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
+
+\subsection{Volatility} \label{subsec: Volatility}
+
+We begin our analysis by studying the effect of irregular regime changes on financial volatility.
+Since stock volatility is not directly observable, one must decide how to best estimate volatility.
+Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
+As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
+In particular, for national stock index $i$,
+\begin{align*}
+R_{it}=\mu_i + \epsilon_{it},\hspace{1cm} \epsilon_{it}\sim \mathcal{N}\left(0,\sigma_{it}^2\right),
+\end{align*}
+where $\mu_i$ is a constant and,
+\begin{align*}
+\sigma_{it}^2&=\gamma_{i}+\alpha_{i}\epsilon_{i,t-1}^2+\beta_{i}\sigma_{i,t-1}^2.
+\end{align*}
+
+The key parameter of interest is the conditional variance, $\sigma_{it}^2$.
+The one-period-ahead volatility forecasts, $\sigma_{it}$, are larger when $\epsilon_{i,t-1}^2$ and $\sigma_{i,t-1}^2$ are larger.
+In other words, the model predicts that large shocks will be followed by other large shocks.
+
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+This may suggest that investors sometimes have information about the events before they occur.
+Nonetheless, there is still an enormous volatility jump on the day of the regime change.
+Volatility then decreases to normal levels within a month of the event.
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
 \subsection{Abnormal Returns} \label{subsec:abnormal-returns}
-We begin our analysis by studying the effect of irregular regime changes on stock returns.
+
+We now turn to the magnitude and direction of the effect of irregular regime changes on stock returns.
 We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
-Normal performance is measured with a constant mean return model\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations (plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995 respectively).
-That said, results are insensitive to the use of a market model.},
+Normal performance is measured with a constant mean return model,\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations.
+Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.}
 \begin{align} \label{eqn:market-model}
@@
 
-We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
+As we hypothesize that different types of regime changes will have disparate effects on markets, we report abnormal returns separately for coups, assassinations and resignations.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
 
-\subsubsection{Coups} \label{subsec: Coups}
+\subsection{Coups} \label{subsec: Coups}
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976 and the partial/failed Venezuelan coup attempt of 2002.
-The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}  We later examine the Venezuelan coup attempt of 2002 in detail, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976.
+The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
 
@@
 Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero.
-In all of these cases, the coup in question either overthrew a democratically elected government or changed governance from one military ruler to another.
+In all of these cases, the coup either overthrew a democratically elected government or changed governance from one military ruler to another.
 The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.
 
-Event day ARs are negative for all coups except the 1971 coup in Argentina, the 2002 coup in Nepal, and the 2002 failed coup d'etat attempt against Hugo Chavez (\autoref{fig:AR-Ven}).
+The only events with positive ARs are the 1971 coup in Argentina and the 2002 coup in Nepal.
 These results provide evidence that coups do not necessarily lead to negative abnormal returns.
@@
 Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections, itself a democratically subversive action.
-The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
 
-\begin{figure}[!ht]
-\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
-\label{fig:AR-Ven}
-\end{figure}
-
-The failed coup attempt against Hugo Chavez therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
-On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
-Pedro Carmona, a Venezuelan economist and business leader, was named the transitional President of Venezuela.
-Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.
-This provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
-By extension, it provides an estimate of the impact of a shift from a left-wing populist government to a pro business regime in an emerging market.
-
-\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt.
-The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
-The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
-The abnormal return on April 12, the first trading day in which investors could react to the coup, was 10\%.
-The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see \autoref{fig:AR-Ven-1992}).
-These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
-
-The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
-Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
-The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot.
-This implies that both events were unexpected by investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
-We see the same story 10 years prior, with pre and post-event CARs statistically indistinguishable from zero on all days except for the day of the Chavez coup attempt, this time demonstrating the market's negative evaluation of a Pérez to Chavez regime change.
-
-\subsubsection{Assassinations} \label{subsec: Assassinations}
+\subsection{Assassinations} \label{subsec: Assassinations}
 
@@
 As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days, or almost 4 calendar years.
-However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death (although the assassination may have exacerbated the panic).
-In any case, the length of this time period is so long that we omitted it when calculating the mean days to rebound in the figure.}
+However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death (although the assassination may have exacerbated the panic).}
 
@@
 
-\subsubsection{Public Protests} \label{subsec: Public Protests}
 The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
-While the previous section showed that the resignations themselves had large effects on stock returns, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
-Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
+It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent in \nameref{subsec: Public Protests} in the appendix.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.} When taking directionality into account, it appears that public protests have no effect on stock returns.
+However, this occurs because some political movements increase stock prices while others decrease them, and the absolute value of stock returns are approximately 1.5\% higher during public protests (see \autoref{tab:protest-stocks}).\footnote{These results hold when controlling for emerging market index fluctuations.}
 
-A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
-The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
-Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
+\section{Exploring possible mechanisms} \label{subsec: mechanisms}
 
-The short-term impact of the Egyptian Revolution on the economy was disastrous.
-As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
-To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th.
-President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
+While markets may generally dislike political instability, the immediate effect of regime changes on markets may not always be unpredictable.
+For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation \citep{przeworski1982structure, north1989constitutions, svensson1998investment}.
+In addition, when the successor in an irregular regime change is clear, investors may have strong priors about the effect of the new leader on economic and/or market performance.
+Two possible mechanisms that could be driving the differences may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift in governance, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
 
-\begin{figure}[!ht]
-\includegraphics{../figs/egypt-revolution-2011.pdf}
-\caption{Cumulative abnormal returns during the Egyptian revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
-In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
-These events are listed in \autoref{tab:protest-list} in the appendix.
-
-The start and end dates in \autoref{tab:protest-list} are the dates that protests began and leader's resigned respectively.
-Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
-Additional Lexis Nexis searches were used to verify these descriptions.
-
-In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
-The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
-Non-protest dates are the 250 days prior to the start dates and after the end dates listed in \autoref{tab:protest-list}.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
-
-Column (1) suggests that public protests have no effect on stock returns.
-However, this occurs because some political movements increase stock prices while others decrease them.
-As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests.
-These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
-To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
-The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
-Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \autoref{subsec: Volatility}.}
-
-We therefore find that both volatility and the absolute value of returns increase during times of protest.
-Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
+We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
+We observe ten cases associated with an authoritarian shift in governance.
+Only two of these events result in positive CARs, and neither are significantly different from zero.
+Five cases resulted in a democratic shift in governance.
+Three of these five cases result in positive CARs.
+Of the two negative CARs, one is not significantly different from zero, and the other is associated with a forced market closure that lasted 17 days.
+However, the majority of the positive returns from democratic regime changes come from the 12\% positive CAR associated with the resignation of Ferdinand Marcos in the Philippines in 1986.
 
 \begin{table}[!ht]
-\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
+\caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
 \vspace{-5pt}
@@
 \begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
   \hline
   \hline
-\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
-\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
- & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
   \hline
-\ExpandableInput{../tables/protest-regtable.txt}
+\ExpandableInput{../tables/artable-auth-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-auth-car-mean.txt}
    \hline
@@
 \scriptsize
-Notes: Standard errors clustered by event are in parentheses.
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
 \end{threeparttable}
@@
 
-\subsection{Volatility} \label{subsec: Volatility}
-Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, the results from \autoref{subsec:abnormal-returns} suggest that all of these political events increase financial volatility.
-However, since stock volatility is not directly observable, one must decide how to best estimate volatility.
-Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
-As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
-In particular, for national stock index $i$,
-\begin{align*}
-R_{it}=\mu_i + \epsilon_{it},\hspace{1cm} \epsilon_{it}\sim \mathcal{N}\left(0,\sigma_{it}^2\right),
-\end{align*}
-where $\mu_i$ is a constant and,
-\begin{align*}
-\sigma_{it}^2&=\gamma_{i}+\alpha_{i}\epsilon_{i,t-1}^2+\beta_{i}\sigma_{i,t-1}^2.
-\end{align*}
-The key parameter of interest is the conditional variance, $\sigma_{it}^2$.
-The one-period-ahead volatility forecasts, $\sigma_{it}$, are larger when $\epsilon_{i,t-1}^2$ and $\sigma_{i,t-1}^2$ are larger.
-In other words, the model predicts that large shocks will be followed by other large shocks.
+\begin{table}[!ht]
+\caption{Abnormal returns following democratic regime changes} \label{tab:AR-dem}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-dem-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-dem-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
-This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
+A similar analysis is not possible for shifts from pro or anti business leaders, as examples of such clear and plausibly exogenous shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
+In all cases, no clear economic ideological shift can be identified.} We therefore look outside of the sample above and conduct an in-depth case study of a seemingly pro-business and anti-socialist coup followed by the reinstatement of a socialist government: the 2002 failed coup against Hugo Chavez in Venezuela.
 
-\begin{figure}[!htb]
-\includegraphics{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
+\begin{figure}[!ht]
+\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
+\label{fig:AR-Ven}
 \end{figure}
 
-\subsection{Robustness} \label{subsec: Robustness}
+The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
+Pedro Carmona, a Venezuelan economist and business leader, was named the transitional President of Venezuela.
+Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.
+This provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
+By extension, it provides an estimate of the impact of a shift from a left-wing populist government to a pro business regime in an emerging market.
 
-There are some potential concerns with the results in \autoref{subsec:abnormal-returns}.
+\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt.
+The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
+The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
+The abnormal return on April 12, the first trading day in which investors could react to the coup, was +10\%.
+The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
+
+The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
+Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
+The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were completely unaware of the coup plot, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
+This failed coup therefore demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
+
+%We also note that Chavez's own failed attempt to overthrow the democratically elected government of Carlos Andrés Pérez---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see \autoref{fig:AR-Ven-1992}).
+Here too, pre and post-event CARs are statistically indistinguishable from zero on all days except for the day of the Chavez coup attempt, this time demonstrating the market's negative evaluation of a Pérez to Chavez regime change.
+These two failed coups therefore demonstrate one positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
+
+\section{Robustness} \label{subsec: Robustness}
+
+There are some potential concerns with the results in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections.
 First, the abnormal returns could have been driven by factors unrelated to the regime changes.
@@
 
-While conventional wisdom suggests markets dislike political instability, we show that this is not necessarily always the case.
-Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more pro-business environment than the previous one.
+While conventional wisdom suggests markets dislike the political instability associated with regime changes, we show that this is not necessarily always the case.
+Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
 
@@
 There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.\footnote{The Turkish coup attempt led to negative event-day CARs of approximately -7\%.
-See \autoref{fig:AR-Turkey-2016} for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
+See Figure A2 for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
 
 This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices.
-This approach provides well-identified estimates of the economic effects of regime changes that are less susceptible to endogeneity bias than prior cross country studies.
+This approach provides well-identified estimates of an economic effect of regime changes that is less susceptible to endogeneity bias than prior cross country studies.
 Furthermore, the large sample of political events in our study increases the generalizability of our findings.
@@
 But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is less certain.
-Abnormal returns following resignations are large and positive (4\%), abnormal returns following assassinations are negative and smaller in magnitude (2\%), and abnormal returns following coups also tend to be negative (2\%).
-However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that coups can sometimes have large positive economic effects, which is consistent with estimates from \citet{girardi2018institution} showing  the election of Allende in Chile and the subsequent coup replacing him increased stock market valuations.
-
-While our empirical strategy does not allow us to directly test the mechanisms that drive differences in investor response from each individual event, previous theoretical literature and examination of individual cases offer some insights.
-Taken together, the evidence suggests that abnormal returns tend to be positive following resignations because the regime change likely replaced ``bad'' leaders whose replacements were expected to adopt better economic policies.
+Abnormal returns following resignations are large and positive (+4\%), abnormal returns following assassinations are negative and smaller in magnitude (-2\%), and abnormal returns following coups also tend to be negative (-2\%).
 Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
 CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
-Our examination of the failed 2002 Venezuela coup shows that coups can result in large positive returns in settings where socialist or anti-business governments are replaced with pro-business regimes.
-Conversely, autocratic coups may increase fear of capital appropriation or the implementation of poor economic policies.
-Assassinations may be merely regarded as highly uncertain events, best approximating the classic ``unstable'' event where investors have few priors.
 
-As in any study, there are a number potential avenues for future research.
-First, more research is needed to identify the pro- and anti-market characteristics of regime changes.
-There may be features of regime changes that are perceived as pro- or anti-market that are more nuanced than those identified in this paper.
-A greater understanding of these features would allow researchers to better predict the effects of future regime changes on stock returns.
-Additionally, it would be useful to identify the mechanisms through which regime changes effect stock returns.
+A preliminary test of mechanisms suggests that democratic regime changes are typically preferable to authoritarian regime changes to investors.
+However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that even democratically subversive coups can have positive effects if the instigators are clearly pro-business.
+These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
+
+There are a number potential avenues for future research.
+First, more research is needed to identify the pro and anti market characteristics of regime changes.
+There may be pro or anti market features of regime changes that are more nuanced than those identified in this paper.
+Similarly, it would be useful to identify additional mechanisms through which regime changes effect stock returns.
 In the case of Chile,  \citet{girardi2018institution} show that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
@@
 \newpage
+\appendix
+\setcounter{secnumdepth}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand\thetable{\Alph{section}.\arabic{table}}
+\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
 
-\appendix
-\setcounter{table}{0}
-\renewcommand\thetable{\Alph{section}.\arabic{table}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
+\section{Appendix} \label{sec: appendix}
 
-\section{Appendix} \label{Appendix}
+\subsection{Public Protests} \label{subsec: Public Protests}
+
+The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
+It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}
+
 \begin{table}[!ht]
@@
 
-\pagebreak
+A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
+The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
+Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
 
-\subsection{Graphical depictions of additional events}
+The short-term impact of the Egyptian Revolution on the economy was disastrous.
+As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
+To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th.
+President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
 
-\begin{figure}[!htb]
-\centering
-\vspace{-0.4cm}
-\includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
-\caption{Abnormal returns surrounding the 1992 Venezuelan coup attempt}
-\label{fig:AR-Ven-1992}
+\begin{figure}[!ht]
+\includegraphics{../figs/egypt-revolution-2011.pdf}
+\caption{Cumulative abnormal returns during the Egyptian revolution}
+\label{fig:CAR-Egypt}
 \end{figure}
 
-\begin{figure}[!htb]
-\centering
-\vspace{-0.5cm}
-\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
-\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
-\label{fig:AR-Turkey-2016}
-\end{figure}
+An important question is whether other popular uprisings have had similar adverse economic consequences.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
+We find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+
+The start and end dates in \autoref{tab:protest-stocks} are the dates that protests began and leader's resigned respectively.
+Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
+Additional Lexis Nexis searches were used to verify these descriptions.
+
+In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
+The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
+Non-protest dates are the 250 days prior to the start dates and after the end dates listed in Table A.1.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
+
+Column (1) suggests that public protests have no effect on stock returns.
+However, this occurs because some political movements increase stock prices while others decrease them.
+As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests.
+These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
+To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
+The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
+Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
+
+We therefore find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+
+\begin{table}[!ht]
+\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
+  \hline
+  \hline
+\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
+\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
+ & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
+  \hline
+\ExpandableInput{../tables/protest-regtable.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors clustered by event are in parentheses.
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 \pagebreak
+\newpage
 
@@
 \label{fig:mean-event-day-ar-by-regime-change}
+\end{figure}
+
+\clearpage
+\pagebreak
+
+\subsection{Graphical depictions of additional events}
+
+%\begin{figure}[!htb]
+%\centering
+%\vspace{-0.4cm}
+%\includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
+%\caption{Abnormal returns surrounding the 1992 Venezuelan coup attempt}
+%\label{fig:AR-Ven-1992}
+%\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
+\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
+\label{fig:AR-Turkey-2016}
 \end{figure}

### 2020-05-19 doc/regime_changes_manuscript.tex
Prose updates and addition of mechanisms analysis and section

@@
 % Footnote double spacing and font size for journal submission
-\usepackage{footmisc}
-\setlength{\footnotesep}{\baselineskip}
-\renewcommand{\footnotelayout}{\normalsize\doublespacing}
+%\usepackage{footmisc}
+%\setlength{\footnotesep}{\baselineskip}
+%\renewcommand{\footnotelayout}{\normalsize\doublespacing}
 
@@
 %\author{Devin Incerti and Trevor Incerti}
-\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
+\title{\textbf{Are regime changes always bad for markets? Evidence from daily financial data}}
 \date{\today}
@@
 \nameref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
-It will first analyze coups, assassinations and resignations separately and determine whether they increase mean returns.
-It will then combine all irregular regime changes and estimate the effect of regime changes on the variance of returns.
+It will first formally estimate the amount of volatility surrounding all irregular regime changes, then analyze coups, assassinations and resignations separately and determine what impact they have on mean returns.
 
@@
 \section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
-%\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
-We begin our analysis by studying the effect of irregular regime changes on stock returns.
+
+\subsection{Volatility} \label{subsec: Volatility}
+
+We begin our analysis by studying the effect of irregular regime changes on financial volatility.
+Since stock volatility is not directly observable, one must decide how to best estimate volatility.
+Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
+As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
+In particular, for national stock index $i$,
+\begin{align*}
+R_{it}=\mu_i + \epsilon_{it},\hspace{1cm} \epsilon_{it}\sim \mathcal{N}\left(0,\sigma_{it}^2\right),
+\end{align*}
+where $\mu_i$ is a constant and,
+\begin{align*}
+\sigma_{it}^2&=\gamma_{i}+\alpha_{i}\epsilon_{i,t-1}^2+\beta_{i}\sigma_{i,t-1}^2.
+\end{align*}
+
+The key parameter of interest is the conditional variance, $\sigma_{it}^2$.
+The one-period-ahead volatility forecasts, $\sigma_{it}$, are larger when $\epsilon_{i,t-1}^2$ and $\sigma_{i,t-1}^2$ are larger.
+In other words, the model predicts that large shocks will be followed by other large shocks.
+
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+This may suggest that investors sometimes have information about the events before they occur.
+Nonetheless, there is still an enormous volatility jump on the day of the regime change.
+Volatility then decreases to normal levels within a month of the event.
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
+\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
+
+We now turn to the magnitude and direction of the effect of irregular regime changes on stock returns.
 We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
-Normal performance is measured with a constant mean return model\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations (plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995 respectively).
-That said, results are insensitive to the use of a market model.},
+Normal performance is measured with a constant mean return model,\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations.
+Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.}
 \begin{align} \label{eqn:market-model}
@@
 
-We report abnormal returns separately for coups, assassinations and resignations because they may have distinct effects on stock returns.
+As we hypothesize that different types of regime changes will have disparate effects on markets, we report abnormal returns separately for coups, assassinations and resignations.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
@@
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976 and the partial/failed Venezuelan coup attempt of 2002.
-The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}  We later examine the Venezuelan coup attempt of 2002 in detail, but do not include it in the sample in \autoref{tab:AR-coups} as it does not match our definition of a successful coup.
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976.
+The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
 
@@
 Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections, itself a democratically subversive action.
-The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president.
-
-\begin{figure}[!ht]
-\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
-\caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
-\label{fig:AR-Ven}
-\end{figure}
-
-The failed coup attempt against Hugo Chavez therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
-On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
-Pedro Carmona, a Venezuelan economist and business leader, was named the transitional President of Venezuela.
-Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.
-This provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
-By extension, it provides an estimate of the impact of a shift from a left-wing populist government to a pro business regime in an emerging market.
-
-\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt.
-The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
-The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
-The abnormal return on April 12, the first trading day in which investors could react to the coup, was 10\%.
-The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-We also note that Chavez's own failed attempt to overthrow the democratically elected government of Venezuela---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see Figure A1).
-These events therefore demonstrate a positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
-
-The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
-Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
-The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were unaware of the coup plot.
-This implies that both events were unexpected by investors, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
-We see the same story 10 years prior, with pre and post-event CARs statistically indistinguishable from zero on all days except for the day of the Chavez coup attempt, this time demonstrating the market's negative evaluation of a Pérez to Chavez regime change.
 
@@
 
-\subsection{Public Protests} \label{subsec: Public Protests}
 The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
-While the previous section showed that the resignations themselves had large effects on stock returns, it is not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
-Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.
+It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent in \nameref{subsec: Public Protests} in the appendix.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.} When taking directionality into account, it appears that public protests have no effect on stock returns.
+However, this occurs because some political movements increase stock prices while others decrease them, and the absolute value of stock returns are approximately 1.5\% higher during public protests (see \autoref{tab:protest-stocks}).\footnote{These results hold when controlling for emerging market index fluctuations.}
 
-A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
-The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
-Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
+\section{Exploring possible mechanisms} \label{subsec: mechanisms}
 
-The short-term impact of the Egyptian Revolution on the economy was disastrous.
-As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
-To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th.
-President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
+While markets may generally dislike political instability, the immediate effect of regime changes on markets may not always be unpredictable.
+For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation \citep{przeworski1982structure, north1989constitutions, svensson1998investment}.
+In addition, when the successor in an irregular regime change is clear, investors may have strong priors about the effect of the new leader on economic and/or market performance.
+Two possible mechanisms that could be driving the differences may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift in governance, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
 
-\begin{figure}[!ht]
-\includegraphics{../figs/egypt-revolution-2011.pdf}
-\caption{Cumulative abnormal returns during the Egyptian revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-An important question is whether other popular uprisings have had similar adverse economic consequences.
-To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
-In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
-These events are listed in \autoref{tab:protest-list} in the appendix.
-
-The start and end dates in Table A.1 are the dates that protests began and leader's resigned respectively.
-Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
-Additional Lexis Nexis searches were used to verify these descriptions.
-
-In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
-The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
-Non-protest dates are the 250 days prior to the start dates and after the end dates listed in Table A.1.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
-
-Column (1) suggests that public protests have no effect on stock returns.
-However, this occurs because some political movements increase stock prices while others decrease them.
-As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests.
-These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
-To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
-The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
-Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
-
-We therefore find that both volatility and the absolute value of returns increase during times of protest.
-Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
+We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
+We observe ten cases associated with an authoritarian shift in governance.
+Only two of these events result in positive CARs, and neither are significantly different from zero.
+Five cases resulted in a democratic shift in governance.
+Three of these five cases result in positive CARs.
+Of the two negative CARs, one is not significantly different from zero, and the other is associated with a forced market closure that lasted 17 days.
+However, the majority of the positive returns from democratic regime changes come from the 12\% positive CAR associated with the resignation of Ferdinand Marcos in the Philippines in 1986.
 
 \begin{table}[!ht]
-\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
+\caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
 \vspace{-5pt}
@@
 
-\subsection{Volatility} \label{subsec: Volatility}
-Although irregular regime changes have disparate effects on the direction of stock returns depending on expected policy outcomes, our results suggest that all of these political events increase financial volatility.
-However, since stock volatility is not directly observable, one must decide how to best estimate volatility.
-Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
-As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
-In particular, for national stock index $i$,
-\begin{align*}
-R_{it}=\mu_i + \epsilon_{it},\hspace{1cm} \epsilon_{it}\sim \mathcal{N}\left(0,\sigma_{it}^2\right),
-\end{align*}
-where $\mu_i$ is a constant and,
-\begin{align*}
-\sigma_{it}^2&=\gamma_{i}+\alpha_{i}\epsilon_{i,t-1}^2+\beta_{i}\sigma_{i,t-1}^2.
-\end{align*}
-The key parameter of interest is the conditional variance, $\sigma_{it}^2$.
-The one-period-ahead volatility forecasts, $\sigma_{it}$, are larger when $\epsilon_{i,t-1}^2$ and $\sigma_{i,t-1}^2$ are larger.
-In other words, the model predicts that large shocks will be followed by other large shocks.
+\begin{table}[!ht]
+\caption{Abnormal returns following democratic regime changes} \label{tab:AR-dem}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-dem-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-dem-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
-This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
+A similar analysis is not possible for shifts from pro or anti business leaders, as examples of such clear and plausibly exogenous shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
+In all cases, no clear economic ideological shift can be identified.} We therefore look outside of the sample above and conduct an in-depth case study of a seemingly pro-business and anti-socialist coup followed by the reinstatement of a socialist government: the 2002 failed coup against Hugo Chavez in Venezuela.
 
-\begin{figure}[!htb]
-\includegraphics{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
+\begin{figure}[!ht]
+\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
+\caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
+\label{fig:AR-Ven}
 \end{figure}
+
+The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
+Pedro Carmona, a Venezuelan economist and business leader, was named the transitional President of Venezuela.
+Two days later, on April 13, 2002, a popular uprising led to Chavez's reinstatement as president.
+This provides an estimate of the market's valuation of a transition from the Chavez regime to the Carmona regime and its valuation of a transition from the Carmona regime back to the Chavez regime.
+By extension, it provides an estimate of the impact of a shift from a left-wing populist government to a pro business regime in an emerging market.
+
+\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt.
+The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
+The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
+The abnormal return on April 12, the first trading day in which investors could react to the coup, was +10\%.
+The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
+
+The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
+Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
+The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were completely unaware of the coup plot, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
+This failed coup therefore demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
+
+%We also note that Chavez's own failed attempt to overthrow the democratically elected government of Carlos Andrés Pérez---at the time pursuing deficit reduction efforts in order to obtain IMF loans---in 1992 was similarly viewed negatively by investors, resulting in an approximately -6\% AR (see \autoref{fig:AR-Ven-1992}).
+Here too, pre and post-event CARs are statistically indistinguishable from zero on all days except for the day of the Chavez coup attempt, this time demonstrating the market's negative evaluation of a Pérez to Chavez regime change.
+These two failed coups therefore demonstrate one positive market reaction to the attempted overthrow of a socialist leader, as well as two examples of negative reactions to an attempted and successful overthrow of pro-market leaders.
 
@@
 
-To ensure that results of the placebo test based on 1-year did not occur by chance, Figure A3 plots event-day abnormal against the number of days shifted.
+To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
 There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
@@
 This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices.
-This approach provides well-identified estimates of the economic effects of regime changes that are less susceptible to endogeneity bias than prior cross country studies.
+This approach provides well-identified estimates of an economic effect of regime changes that is less susceptible to endogeneity bias than prior cross country studies.
 Furthermore, the large sample of political events in our study increases the generalizability of our findings.
@@
 Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
+
+\newpage
+\appendix
+\setcounter{secnumdepth}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand\thetable{\Alph{section}.\arabic{table}}
+\renewcommand\thefigure{\Alph{section}.\arabic{figure}}
+
+\section{Appendix} \label{sec: appendix}
+
+\subsection{Public Protests} \label{subsec: Public Protests}
+
+The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
+It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}
+
+\begin{table}[!ht]
+\caption{List of public protests preceding resignations} \label{tab:protest-list}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}llll}
+  \hline
+    \hline
+\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Name}&\multicolumn{1}{c}{Start Date}&\multicolumn{1}{c}{End Date}\\
+  \hline
+Philippines & EDSA 1/Yellow Revolution & 2/22/1986 & 2/25/1986\\
+Bangladesh & Bangladeshi Spring of 1990 & 11/27/1990 & 12/7/1990\\
+Thailand & Black May & 5/17/1992 & 5/20/1992\\
+Indonesia & Indonesian Riots & 5/12/1998 & 5/21/1998\\
+Philippines & EDSA II & 1/17/2001 & 1/20/2001\\
+Argentina & Argentina Riots & 12/16/2001 & 12/20/2001\\
+Ukraine & Orange Revolution & 11/22/2004 & 1/23/2005\\
+Ecuador & Ecuadorian Protests & 4/13/2005 & 4/20/2005\\
+Nepal & Nepalese People's Revolution & 4/6/2006 & 4/24/2006\\
+Tunisia & Tunisian Revolution & 12/18/2010 & 1/14/2011\\
+Egypt & Egyptian Revolution & 1/25/2011 & 2/11/2001\\
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+\end{threeparttable}
+\end{center}
+\end{table}
+
+A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
+The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
+Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
+
+The short-term impact of the Egyptian Revolution on the economy was disastrous.
+As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
+To prevent further decline during the uprising, the Egyptian Stock Exchange closed at the end of trading on January 27th.
+President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
+
+\begin{figure}[!ht]
+\includegraphics{../figs/egypt-revolution-2011.pdf}
+\caption{Cumulative abnormal returns during the Egyptian revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+An important question is whether other popular uprisings have had similar adverse economic consequences.
+To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent.
+We find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+
+The start and end dates in \autoref{tab:protest-stocks} are the dates that protests began and leader's resigned respectively.
+Resignations caused by popular uprisings were identified by examining the descriptions in the Coup d'etat Events Handbook and Archigos Version 4.1.
+Additional Lexis Nexis searches were used to verify these descriptions.
+
+In \autoref{tab:protest-stocks}, we examine whether public protests influence stock prices.
+The variable \textit{Protest} is equal to 1 during the dates in which citizens participate in political activities demanding the resignation of the executive and 0 otherwise.
+Non-protest dates are the 250 days prior to the start dates and after the end dates listed in Table A.1.\footnote{The volatility estimates used as the dependent variable in column (4) are estimated on the 250 days prior to the start date, the protest dates, and the 250 days following the end date.}
+
+Column (1) suggests that public protests have no effect on stock returns.
+However, this occurs because some political movements increase stock prices while others decrease them.
+As shown in column (2), the absolute value of stock returns are approximately 1.5\% higher during public protests.
+These estimates would be biased if protest dates are correlated with higher world or regional stock market indices.
+To address this potential confounder, column (3) controls for returns on the S\&P/IFC Emerging Markets Investable Composite Stock Index.
+The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
+Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
+
+We therefore find that both volatility and the absolute value of returns increase during times of protest.
+Similarly to coups, however, the direction of returns is dependent upon the nature of the protest in question.
+
+\begin{table}[!ht]
+\caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}d{1.3}d{1.3}d{1.3}d{1.3}}
+  \hline
+  \hline
+\multicolumn{1}{c}{}&\multicolumn{1}{c}{Returns} & \multicolumn{2}{c}{Absolute Value of Returns}&\multicolumn{1}{c}{Volatility}\\
+\cmidrule(r){2-2} \cmidrule(r){3-4} \cmidrule(r){5-5}
+ & \multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}\\
+  \hline
+\ExpandableInput{../tables/protest-regtable.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors clustered by event are in parentheses.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\clearpage
+\pagebreak
+\newpage
+
+\subsection{Time-shifted placebo test}
+
+\begin{figure}[!htb]
+\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
+\caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
+\label{fig:mean-event-day-ar-by-regime-change}
+\end{figure}
+
+\clearpage
+\pagebreak
+
+\subsection{Graphical depictions of additional events}
+
+%\begin{figure}[!htb]
+%\centering
+%\vspace{-0.4cm}
+%\includegraphics[scale=0.75]{../figs/venezuela_coup_attempt_1992.pdf}
+%\caption{Abnormal returns surrounding the 1992 Venezuelan coup attempt}
+%\label{fig:AR-Ven-1992}
+%\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
+\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
+\label{fig:AR-Turkey-2016}
+\end{figure}
+
+\pagebreak
+
+\subsection{Synthetic Control Portfolio}
+Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
 

### 2020-05-19 code/03-event-studies.R

@@ -6,6 +6,14 @@ load("data/data-clean.RData")
 source("code/func.R")
 
 # EVENT STUDY ------------------------------------------------------------------
+# Add authoritarian versus democratic shift information to data
+auth_dem <- event[type == "Coup" | type == "Assassination" |
+                  type == "Resignation", 
+                  .(country, ticker, stock_date, `auth shift`, `dem shift`)]
+
+regime.change <- merge(regime.change, auth_dem, 
+                       by = c("country", "ticker", "stock_date"))
+
 # calculate abnormal returns and days to rebound
 event.window <- 20
 est.window <- 200
@@ -51,7 +59,7 @@ for (i in 1:n.es){
   print(i)
 }
 
-# combine event studies
+# combine event studies: by type of regime change
 rc.es <- combine_event_studies(es, event_country = regime.change$country,
                                           event_type = regime.change$type, 
                                           event_date = regime.change$stock_date)
@@ -60,5 +68,24 @@ rc.abs.es <- combine_event_studies(es.abs, event_country = regime.change$country
                                           event_type = regime.change$type, 
                                           event_date = regime.change$stock_date)
 
+# combine event studies: by authoritarian shift
+rc.es.auth <- combine_event_studies(es, event_country = regime.change$country,
+                                          event_type = regime.change$`auth shift`, 
+                                          event_date = regime.change$stock_date)
+rc.es.auth <- c(rc.es, list(dtr.treat = dtr.treat))
+rc.abs.es.auth <- combine_event_studies(es.abs, event_country = regime.change$country,
+                                          event_type = regime.change$`auth shift`, 
+                                          event_date = regime.change$stock_date)
+
+# combine event studies: by democratic shift
+rc.es.dem <- combine_event_studies(es, event_country = regime.change$country,
+                                          event_type = regime.change$`dem shift`, 
+                                          event_date = regime.change$stock_date)
+rc.es.dem <- c(rc.es, list(dtr.treat = dtr.treat))
+rc.abs.es.dem <- combine_event_studies(es.abs, event_country = regime.change$country,
+                                          event_type = regime.change$`dem shift`, 
+                                          event_date = regime.change$stock_date)
+
 # save 
-save(rc.es, rc.abs.es, file = "output/regime-change-event-study.RData")
+save(rc.es, rc.abs.es, rc.es.auth, rc.abs.es.auth, rc.es.dem, rc.abs.es.dem,
+     file = "output/regime-change-event-study.RData")

### 2020-05-19 code/04-ar.R

@@ -9,6 +9,14 @@ theme_set(theme_bw())
 source("code/func.R")
 
 # ABNORMAL RETURNS TABLES ------------------------------------------------------
+# Add authoritarian versus democratic shift information to data
+auth_dem <- event[type == "Coup" | type == "Assassination" |
+                  type == "Resignation", 
+                  .(country, ticker, stock_date, `auth shift`, `dem shift`)]
+
+regime.change <- merge(regime.change, auth_dem, 
+                       by = c("country", "ticker", "stock_date"))
+
 # coups
 coup.index <- which(regime.change$type == "Coup")
 artable.coups <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, coup.index],
@@ -40,6 +48,28 @@ artable.res <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, res.index],
 myprint.xtable(artable.res$car, file = "tables/artable-res-car.txt")
 myprint.xtable(artable.res$car.mean, file = "tables/artable-res-car-mean.txt")
 
+# Authoritarian
+auth.index <- which(regime.change$`auth shift` == 1)
+artable.auth <- ar_table(td = rc.es.auth$td, ar = rc.es.auth$ar.treat[, auth.index],
+                          sigma = rc.es.auth$sigma.treat[auth.index], 
+                          dtr = rc.es.auth$dtr.treat[auth.index],
+                          country = regime.change[auth.index, country],
+                          date = regime.change[auth.index, stock_date], 
+                          coup = FALSE)
+myprint.xtable(artable.auth$car, file = "tables/artable-auth-car.txt")
+myprint.xtable(artable.auth$car.mean, file = "tables/artable-auth-car-mean.txt")
+
+# Democratic
+dem.index <- which(regime.change$`dem shift` == 1)
+artable.dem <- ar_table(td = rc.es.dem$td, ar = rc.es.dem$ar.treat[, dem.index],
+                          sigma = rc.es.dem$sigma.treat[dem.index], 
+                          dtr = rc.es.dem$dtr.treat[dem.index],
+                          country = regime.change[dem.index, country],
+                          date = regime.change[dem.index, stock_date], 
+                          coup = FALSE)
+myprint.xtable(artable.dem$car, file = "tables/artable-dem-car.txt")
+myprint.xtable(artable.dem$car.mean, file = "tables/artable-dem-car-mean.txt")
+
[…]

### 2021-06-29 doc/regime_changes_manuscript.tex
Begin rewriting manuscript as note

@@
 \begin{document}
-%\author{Devin Incerti and Trevor Incerti}
+%\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
+devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
+PhD Candidate in the Department of Political Science, Yale University.
+trevor.incerti@yale.edu.}}
 \title{\textbf{Are regime changes always bad for markets? Evidence from daily financial data}} 
@@
 In this study, we examine the impact of ``irregular'' regime changes and public protests on market performance, but remain agnostic about the direction of the effect.
-Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns and by extension economic growth.
+Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
 Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
@@
 In contrast to the aforementioned cross country studies, we conduct our analysis using event studies of daily financial data and provide separate estimates by source of instability.
-Event studies examine the behavior of stock prices around specific unexpected events, and therefore seek to determine if returns at the time of event are abnormal (i.e., systematically different from predicted).
+Event studies examine the effect of an unexpected event on stock prices \textit{at the time of the event} (i.e.
+a local average treatment effect), and seek to determine if returns at the time of event are abnormal (i.e., systematically different from predicted).
 An ``abnormal return'' therefore reflects the difference between the observed return and the predicted return.
 We use daily data as it allows for more precise measurement of abnormal returns.
-The advantage of this approach is that it uses time-series variation in stock returns to estimate treatment effects and mitigates the endogeneity problems that are nearly ubiquitous in the cross country regression approaches often used to assess economic response to political instability.
-In other words, an event study does not require a correct specification of controls to establish a causal effect.\footnote{A growing body of work uses event studies to assess political phenomenon.
+This interrupted time-series approach mitigates the endogeneity problems ubiquitous in the cross country regression approaches---confounding events would need to also occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
@@
 We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
-Normal performance is measured with a constant mean return model,\footnote{A constant mean return model is used instead of a market model in order to maximize the number of observations.
-Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.}
+Normal performance is measured with a constant mean return model,
 \begin{align} \label{eqn:market-model}
@@
 The abnormal returns are then used to generate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
+
+A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns.
 
@@
 
-We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
+We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project.} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
 We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
@@
 This failed coup therefore demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
+More generally, the large magnitudes and precision of these effects suggest that  investors primarily value transition to a pro-business government regime, regardless of how the regime change is achieved.
 
@@
 Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
+
+\clearpage
+\pagebreak
+
+\pdfbookmark[1]{References}{References}
+\bibliography{bibliography}
 
@@
 
-\clearpage
-\pagebreak
-
-\pdfbookmark[1]{References}{References}
-\bibliography{bibliography}
-
 \end{document}

### 2021-06-29 doc/regime_changes_note.tex
Begin rewriting manuscript as note

--- 2020-05-19 doc/paper.tex
@@
 trevor.incerti@yale.edu.}}
-\title{\textbf{Are regime changes always bad for markets?
+\title{\textbf{Are regime changes always bad economics?
 Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
@@
 Political instability is commonly thought to discourage investment and reduce economic growth.
-However, we find that different types of ``irregular'' regime changes have disparate effects on stock returns.
+We challenge this theory by finding that different types of instability have disparate effects on stock returns.
 Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
-We show that abnormal returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
+Abnormal returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
 The impact of coups tends to be negative (-2\%), but examination of the 2002 failed coup against Hugo Chavez reveals returns of +10\%.
@@
 \end{abstract}
-\doublespacing
+%\doublespacing
 
@@
 
-The image of a coup or popular uprising ousting an autocratic ruler and installing a democratic government is an evocative one.
-However, both recent events and prior research suggest that coups rarely lead to democracy.
-In the wake of the Arab Spring---in which rulers were deposed in four countries---only Tunisia ultimately transitioned to democracy.
-These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+Investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the \citet{wipr2013} report (most recent), executives of multinational enterprises ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries (after macroeconomic instability).
+In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.}
 
-Of course, coups and other regime changes not only impact a country's political environment but its economy as well.
-For instance, investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
-In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} Common rationales are that unstable governments act myopically and adopt inefficient policies.
-Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
+Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.
+This is supported by empirical research showing that political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
-These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+In contrast to these cross country studies, we: (1) examine the impact of various types of instability (coups, resignations, assassinations, and protests) separately, and (2) conduct our analysis using event studies of daily financial data.
+Event studies examine the effect of an unexpected event on stock prices \textit{at the time of the event} (i.e.
+a local average treatment effect) to determine if returns are systematically different from predicted.
+This interrupted time-series approach mitigates the endogeneity problems ubiquitous in previous cross country regressions.
+Confounding events would need to also occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
+For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.,][]{fisman2001estimating,faccio2006politically,goldman2009politically}.}
 
-In this study, we examine the impact of ``irregular'' regime changes and public protests on market performance, but remain agnostic about the direction of the effect.
-Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns and by extension economic growth.
+%Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
 Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
 
-In contrast to the aforementioned cross country studies, we conduct our analysis using event studies of daily financial data and provide separate estimates by source of instability.
-Event studies examine the behavior of stock prices around specific unexpected events, and therefore seek to determine if returns at the time of event are abnormal (i.e., systematically different from predicted).
-An ``abnormal return'' therefore reflects the difference between the observed return and the predicted return.
-We use daily data as it allows for more precise measurement of abnormal returns.
-The advantage of this approach is that it uses time-series variation in stock returns to estimate treatment effects and mitigates the endogeneity problems that are nearly ubiquitous in the cross country regression approaches often used to assess economic response to political instability.
-In other words, an event study does not require a correct specification of controls to establish a causal effect.\footnote{A growing body of work uses event studies to assess political phenomenon.
-For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.}
+%An ``abnormal return'' therefore reflects the difference between the observed return and the predicted return. We use daily data as it allows for more precise measurement of abnormal returns.
 
-We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
-We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.
-We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
-Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
+We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests---the full sample of events for which national-level daily financial data is available.
+Like previous research, we find that coups, assassinations, resignations, and public protests all cause large increases in financial volatility.
+However, we also find that abnormal returns are large and positive (+4\%) following resignations and tend to be negative and smaller in magnitude following assassinations and coups (-2\%).
+We also examine the failed 2002 Venezuelan coup, as it allows us to estimate the effects of both a pro-business coup (+10\%), and the reinstatement of a left-wing populist (-8\%) on the same market.
 
-We find that coups, assassinations, resignations, and public protests cause large increases in financial volatility.
-However, the magnitude and direction of the effects differ by type of regime change.
-On average, abnormal returns following resignations are large and positive (+4\%) while abnormal returns following assassinations and coups tend to be negative and smaller in magnitude (-2\%).
-We also find suggestive evidence that authoritarian regime changes are more likely to lead to negative returns that democratic regime changes.
-Finally, we examine the effect of pro versus anti business regime change via an in-depth examination of the seemingly successful but ultimately failed coup against Hugo Chavez in 2002.
-Stock prices increased dramatically (+10\%) after the failed overthrow of Chavez's socialist regime and decreased by approximately the same magnitude following his return to leadership.
+Our primary contributions are empirical and methodological.
+Empirically, we show that while political instability concerns investors, instability does not systematically depress investment.
+Investors recognize when instability may be in their favor.
+Methodologically, we employ a method less susceptible to endogeneity concerns, and integrate event studies with synthetical control methods to allow for control portfolios in situations where an obvious control portfolio candidate is not present.
+While we do not view theoretical development as our main contribution, we do find evidence that authoritarian regime changes are more likely to lead to negative returns, and that leaders who are clearly pro-business can be rewarded by investors, even if they use extra-judicial methods to take power.
 
-\singlespacing
+%Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
+
 \section{Reexamining how markets respond to irregular regime changes}
-\doublespacing
 
 Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
-However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
+However, if market returns reflect investor expectations about future economic growth and expected returns, such hypotheses may be overly simplistic.
+Investors may view even a coup as a ``positive'' event if the current regime is anti-business or anti-global.
 
-First, a change in regime may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
-Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
+An active debate exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
+Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, and others argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions \citep{alesina1996political}, or that the expected impact of coups on economic growth is neutral as some enhance growth and others depress it \citep{londregan1990poverty}.
+But while ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
+Previous research therefore suggests that on average coups should not be expected to lead to increased economic development or positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
+As our event study approach also allows us to individual coups separately from others, we can evaluate this prediction.
 
-An active debate exists on the subject of ``good coups''---i.e.
-coups that lead to democratization or economic liberalization---and their effect on economic growth.
-\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
-\citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-However, most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
-But while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
-\citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
-In another study examining the outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
+Not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
+Some regime changes---such as the sudden resignation of an ineffective leader---may even lead to increased stability.
+By contrast, assassinations can occur seemingly at random, and a successor may be unclear.
+Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
+These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
 
-Previous research therefore suggests that on average coups should not be expected to lead to increased economic development or positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
-We shed light on this theory as our event study approach also allows us to examine ``good coups''---coups that lead to democratization or economic liberalization---separately from others.
-As we are not limited to a single case study, we can provide both a cross-country and within-case analysis.
-
-Second, not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
-However, some regime changes may actually lead to increased stability.
-Resignations, for example, often occur when an ineffective leader steps down.
-Assassinations, by contrast, are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
-Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
-These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
-By contrast---recognizing the different degrees of instability that these events may reflect---we estimate effects separately for coups, assassinations, resignations, and protests.
-Our event study approach affords us this freedom without encountering the statistical power issues that would arise in a regression setting.
-
-Different types of regime changes may therefore have disparate effects on markets, just as they may differentially effect overall economic growth.
+Different types of regime changes may therefore have disparate effects on markets and/or economic growth.
 Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
@@
 Financial data are from the Global Financial Data database, which includes the longest available daily time series of stock prices.
-We collect data on national equity indices and two global equity indices, the S\&P/IFC Emerging Market Investable Composite and the Morgan Stanley Capital International (MSCI) World Index.
-The S\&P/IFC index includes securities from emerging markets while the MSCI index includes securities from developed markets only.
 We collect national stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation and for which daily financial data is available.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
@@
 
-\begin{table}[!ht]
-\caption{List of stock indices} \label{tab:stock-list}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lll}
-  \hline
-  \hline
-  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Begin Date} &\multicolumn{1}{c}{Start Date}\\
-  \hline
-Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
-Australia & Australia ASX All Ordinaries & Jan-58 & Jan-17\\
-Bangladesh & Dhaka SE Index & Jan-90 & Jan-17\\
-Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-17\\
-Chile & Santiago IGBC General Index & Jan-75 & Jan-17\\
-Colombia & Colombia IGBC General Index & Jan-92 & Jan-17\\
-Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Jan-17\\
-Egypt & Cairo SE Index & Dec-92 & Jan-17\\
-Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-17\\
-Greece & Athens SE General Index & Oct-88 & Jan-17\\
-India & Bombday SE SENSEX & Apr-79 & Jan-17\\
-Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-17\\
-Iran & Tehran SE Price Index & Jan-95 & Jan-17\\
-Israel & Tel Aviv 100 Index & May-87 & Jan-17\\
-Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-17\\
-Latin America & Dow Jones Latin America Index & Jan-92 & Jan-17\\
-Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
-Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-17\\
-Nepal & Nepal NEPSE Stock Index & Jan-01 & Jan-17\\
-Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-17\\
-Pakistan & Karachi SE 100 Index & Jan-89 & Jan-17\\
-Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
-Peru & Lima SE General Index & Jan-82 & Jan-17\\
-Philippines & Manila SE Composite Index & Jan-86 & Jan-17\\
-Portugal & Oporto PSI-20 Index & Jan-86 & Jan-17\\
-Singapore & Singapore FTSE ST Index & Jul-65 & Jan-17\\
-South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-17\\
-Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-17\\
-Spain & Madrid SE General Index & Aug-71 & Jan-17\\
-Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-17\\
-Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-17\\
-Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-17\\
-Thailand & Thailand SET General Index & Apr-75 & Jan-17\\
-Tunisia & Tunisia SE Index & Dec-97 & Jan-17\\
-Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-17\\
-Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-17\\
-United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-17\\
-United States & Dow Jones Industrial Average & Feb-1885 & Jan-17\\
-Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jul-16\\
-Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
-Venezuela & Caracas SE General Index & Jan-94 & Jan-17\\
-World & MSCI World Price Index & Jan-76 & Jan-17\\
-Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
-Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
-   \hline
-   \hline
-\end{tabular*}
-\end{threeparttable}
-\end{center}
-\end{table}
-
 Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
 The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups, and the choice of dataset and classification methodology would directly alter our findings.
-\citet[p.
-617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''
-
-\begin{table}[!ht]
-\caption{Regime changes} \label{tab:regime-changes}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
-  \hline
-  \hline
-  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
-  \hline
-   \multicolumn{3}{c}{\textbf{Coups}}\\ 
-\ExpandableInput{../tables/coups.txt} \\
-   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
-\ExpandableInput{../tables/failed_coup.txt}\\
-  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
-\ExpandableInput{../tables/assassinations.txt}\\
-  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
-\ExpandableInput{../tables/resignations.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
-\end{threeparttable}
-\end{center}
-\end{table}
+We focus on successful coups because it is difficult to classify failed coups, and the choice of dataset and classification methodology would directly alter our findings.\footnote{\citet[p.
+617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''}
 
@@
 Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
-The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.
-Note that the Polity IV definition of ``poor performance'' is not synonymous with poor \textit{economic} performance, and in practice the reasons cited for resignation across events are: loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
+The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.\footnote{Note that the Polity IV definition of ``poor performance'' is not synonymous with poor \textit{economic} performance, and in practice the reasons cited for resignation across events are: loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.}
 
@@
 We recognize that some readers may feel that certain events are missing based on their own substantive knowledge.
-However, we choose to rely on commonly used third-party classifications in order to minimize the possibility that our results are driven by our own subjective classifications.
-The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+We rely on commonly used third-party classifications in order to minimize the possibility that our results are driven by our own subjective classifications.
+The one exception is that we separately analyze the failed coup attempt in Venezuela in April 2002 in which President Hugo Chavez was removed from office for two days, as it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
 
-To gain perspective on the relationship between irregular regime changes and the stock market, \autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events.
-Returns are for 200 trading days before and after regime changes.
-The absolute value of returns on the event day (trading day 0) are significantly larger than on any other day.
+\autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events and show that the absolute value of returns on the event day (day 0) are significantly larger than on any other day.
 In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after.
 This suggests that financial volatility increases during the days surrounding regime changes, although it does not provide any evidence on mean returns.
-
 \nameref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
@@
 \begin{figure}[!ht]
-\includegraphics{../figs/daily_mean_absreturn.pdf}
+\includegraphics[width = 17cm]{../figs/daily_mean_absreturn.pdf}
 \caption{Absolute value of daily returns}
@@
 
-We begin our analysis by studying the effect of irregular regime changes on financial volatility.
-Since stock volatility is not directly observable, one must decide how to best estimate volatility.
+We first examine the effect of irregular regime changes on financial volatility.
 Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
@@
 \section{Appendix} \label{sec: appendix}
+\newpage
+
+\subsection{Data} \label{subsec: data}
+
+\begin{table}[!htb]
+\caption{List of stock indices} \label{tab:stock-list}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}lll}
+  \hline
+  \hline
+  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Begin Date} &\multicolumn{1}{c}{Start Date}\\
+  \hline
+Argentina & Beunos Aires SE General Index & Dec-66 & Jan-17\\
+Australia & Australia ASX All Ordinaries & Jan-58 & Jan-17\\
+Bangladesh & Dhaka SE Index & Jan-90 & Jan-17\\
+Canada & Canada S\&P/TSX 300 Composite & Jan-76 & Jan-17\\
+Chile & Santiago IGBC General Index & Jan-75 & Jan-17\\
+Colombia & Colombia IGBC General Index & Jan-92 & Jan-17\\
+Ecuador & Ecuador Bolsa de Valores de Guayaquil (BVG) & Jan-94 & Jan-17\\
+Egypt & Cairo SE Index & Dec-92 & Jan-17\\
+Emerging Market & S\&P/IFC Emerging Markets Investable Composite & Jul-95 & Jan-17\\
+Greece & Athens SE General Index & Oct-88 & Jan-17\\
+India & Bombday SE SENSEX & Apr-79 & Jan-17\\
+Indonesia & Jakarta SE Composite Index & Apr-83 & Jan-17\\
+Iran & Tehran SE Price Index & Jan-95 & Jan-17\\
+Israel & Tel Aviv 100 Index & May-87 & Jan-17\\
+Japan & Tokyo SE Price Index (TOPIX) & Jan-53 & Jan-17\\
+Latin America & Dow Jones Latin America Index & Jan-92 & Jan-17\\
+Lithuania & Lithuania Lit-10 Index & Jan-99 & May-05\\
+Malaysia & Malaysia KLSE Composite & Jan-80 & Jan-17\\
+Nepal & Nepal NEPSE Stock Index & Jan-01 & Jan-17\\
+Netherlands & Netherlands All-Share Price Index & Jan-80 & Jan-17\\
+Pakistan & Karachi SE 100 Index & Jan-89 & Jan-17\\
+Paraguay & Asuncion SE PDV General Index & Oct-93 & Sep-08\\
+Peru & Lima SE General Index & Jan-82 & Jan-17\\
+Philippines & Manila SE Composite Index & Jan-86 & Jan-17\\
+Portugal & Oporto PSI-20 Index & Jan-86 & Jan-17\\
+Singapore & Singapore FTSE ST Index & Jul-65 & Jan-17\\
+South Korea & Korea SE Stock Price Index  & Jan-62 & Jan-17\\
+Southeast Asia & Dow Jones Southeast Asia Index & Jan-92 & Jan-17\\
+Spain & Madrid SE General Index & Aug-71 & Jan-17\\
+Sri Lanka & Colombo SE All-Share Index & Dec-84 & Jan-17\\
+Sweden & Sweden OMX Affarsvarlden General Index & Jan-80 & Jan-17\\
+Taiwan & Taiwan SE Capitalization Weighted Index & Jan-67 & Jan-17\\
+Thailand & Thailand SET General Index & Apr-75 & Jan-17\\
+Tunisia & Tunisia SE Index & Dec-97 & Jan-17\\
+Turkey & Instanbul IMKB 100 Price Index & Oct-87 & Jan-17\\
+Ukraine & Ukraine PFTS OTC Index & Jan-98 & Jan-17\\
+United Kingdom & UK FTSE All-Share Index & Nov-62 & Jan-17\\
+United States & Dow Jones Industrial Average & Feb-1885 & Jan-17\\
+Uruguay & Bolsa de Valores de Montevideo Index & Jan-08 & Jul-16\\
+Venezuela & Dow Jones Venezuela Stock Index & Jan-92 & Jul-07\\
+Venezuela & Caracas SE General Index & Jan-94 & Jan-17\\
+World & MSCI World Price Index & Jan-76 & Jan-17\\
+Zambia & Lusaka SE Index & Jan-02 & Apr-06\\
+Zambia & Lusaka SE Index & Jul-11 & Jan-17\\
+   \hline
+   \hline
+\end{tabular*}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Regime changes} \label{tab:regime-changes}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ll}
+  \hline
+  \hline
+  \multicolumn{1}{c}{Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Political Outcome}\\
+  \hline
+   \multicolumn{3}{c}{\textbf{Coups}}\\ 
+\ExpandableInput{../tables/coups.txt} \\
+   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
+\ExpandableInput{../tables/failed_coup.txt}\\
+  \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
+\ExpandableInput{../tables/assassinations.txt}\\
+  \multicolumn{3}{c}{\textbf{Resignations}}\\ 
+\ExpandableInput{../tables/resignations.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: The Polity score is used to classify political outcomes as follows: autocracy = $-10 \leq \rm{score} \leq -6$, anocracy = $-5 \leq \rm{score} \leq 5$, and democracy = $6 \leq \rm{score} \leq 10$.
+\end{threeparttable}
+\end{center}
+\end{table}
 

### 2021-07-01 doc/regime_changes_note.tex
Further note revisions/edits/cuts

@@
 
-\section{Reexamining how markets respond to irregular regime changes}
+\section{Reexamining market response to irregular regime changes}
 
-Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
-However, if market returns reflect investor expectations about future economic growth and expected returns, such hypotheses may be overly simplistic.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
+However, if market returns reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
 Investors may view even a coup as a ``positive'' event if the current regime is anti-business or anti-global.
 
-An active debate exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
-Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, and others argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions \citep{alesina1996political}, or that the expected impact of coups on economic growth is neutral as some enhance growth and others depress it \citep{londregan1990poverty}.
-But while ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
-Previous research therefore suggests that on average coups should not be expected to lead to increased economic development or positive market returns, but that positive returns associated with ``good coups'' could occasionally be present.
-As our event study approach also allows us to individual coups separately from others, we can evaluate this prediction.
+%Previous research therefore suggests that coups should on average not lead to positive economic development or market returns, but that ``good coups'' could occasionally create positive returns.
+As our event study approach allows us to analyze individual coups separately from others, we can test this prediction.
 
-Not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
-Some regime changes---such as the sudden resignation of an ineffective leader---may even lead to increased stability.
-By contrast, assassinations can occur seemingly at random, and a successor may be unclear.
-Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
+Not all regime changes are equivalent.
+Resignations, assassinations, and coups have all been used as proxies for instability in previous research.
+However, some regime changes---such as the sudden resignation of an ineffective leader---may lead to increased stability.
+By contrast, assassinations can occur seemingly at random and a successor may be unclear.
+Coups can occur in the name of democracy or autocracy.
 These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
 
+An active debate also exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
+Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, others argue that the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the expected impact of coups  is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
+But while ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
+
 Different types of regime changes may therefore have disparate effects on markets and/or economic growth.
-Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
+The theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro-market than the regime they replace.
+As our event study approach allows us to analyze individual coups separately from others, we can test this prediction.
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
@@
 
-Our empirical findings validate these predictions.
+%Our empirical findings validate these predictions.
 We find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
@@
 Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
-The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots.
-We focus on successful coups because it is difficult to classify failed coups, and the choice of dataset and classification methodology would directly alter our findings.\footnote{\citet[p.
+The Coup d'etat dataset includes the date of successful, attempted, plotted, and alleged coups.
+We focus on successful coups because the other classifications are contentious, and the choice of dataset and classification methodology would directly alter our findings.\footnote{\citet[p.
 617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''}
@@
 
-A list of the political events in our dataset is shown in \autoref{tab:regime-changes}.
+A list of the political events in our dataset and whether they resulted in democratic or autocratic shifts is shown in \autoref{tab:regime-changes}.
 Coups tend to have the largest impact on the level of democratization as a number of countries have subsequently transitioned from democracies to anocracies or autocracies.
-On the other hand, neither assassinations or resignations have much of an impact on the level of democratization.
+On the other hand, neither assassinations nor resignations tend to have much impact on the level of democratization.
 
 The discussion above shows that there is considerable debate about classification of regime changes.
-We recognize that some readers may feel that certain events are missing based on their own substantive knowledge.
+We recognize that some readers may feel certain events are missing based on their own substantive knowledge.
 We rely on commonly used third-party classifications in order to minimize the possibility that our results are driven by our own subjective classifications.
@@
 
-\autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events and show that the absolute value of returns on the event day (day 0) are significantly larger than on any other day.
+\autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events and shows that the absolute value of returns on the event day (day 0) are significantly larger than on any other day.
 In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after.
@@
 \begin{figure}[!ht]
-\includegraphics[width = 17cm]{../figs/daily_mean_absreturn.pdf}
+\begin{centering}
+\includegraphics[width = 15cm]{../figs/daily_mean_absreturn.pdf}
 \caption{Absolute value of daily returns}
 \label{fig:AV-DR}
+\end{centering}
 \end{figure}
@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+Volatility stays between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations.
 This may suggest that investors sometimes have information about the events before they occur.
@@
 
-\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
+\subsection{Estimation strategy: abnormal returns} \label{subsec:abnormal-returns}
 
@@
 The abnormal returns are then used to generate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
 
-A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns.
-
-We define the event date as the first trading day in which the market could have reacted to news of the event.
-For example, during the October 12, 1999 coup d'etat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
-We code October 14th, the day in which the market re-opened, as the event day.
-When events occurred on weekends, we change the event date to the following Monday.
-
-$(0,\tau-1)$ is used to denote the $\tau$-day period beginning with the event day and $(-1,\tau)$ to denote the negative $\tau$-day period beginning with the day prior to the event day.
-In other words, for cumulative abnormal returns prior to the event date, we aggregate backwards starting at the day of the event.
-For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.
-We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$), and the event date plus 19 days $(0,19$).
+We define the event date as the first trading day in which the market could have reacted to news of the event.\footnote{For example, during the October 12, 1999 coup d'etat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
+We code October 14th, the day in which the market re-opened, as the event day.} When events occurred on weekends, we change the event date to the following Monday.
+$(0,\tau-1)$ is used to denote the $\tau$-day period beginning with the event day and $(-1,\tau)$ to denote the negative $\tau$-day period beginning with the day prior to the event day.\footnote{In other words, for cumulative abnormal returns prior to the event date, we aggregate backwards starting at the day of the event.
+For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.} We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$), and the event date plus 19 days $(0,19$).
 In addition, we present results for the pre-event windows $(-1,-7$) and $(-1,-20$).
 
-As we hypothesize that different types of regime changes will have disparate effects on markets, we report abnormal returns separately for coups, assassinations and resignations.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
+We use a constant mean return model instead of a market model to maximize the number of observations and because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we integrate synthetic control methodology \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
+In short, we create a ``synthetic'' control portfolio for each event and compare observed returns to the synthetic returns.
+Each country is given a weight which represents its influence in the synthetic control portfolio.
+The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
+
+More formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}, and the results are presented in \nameref{subsec: Robustness}.
 
 \subsection{Coups} \label{subsec: Coups}
+
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes} with the exception of the Argentinian coup of March 24, 1976.
-The March 24, 1976 Argentinian coup is excluded from our analysis because the stock market remained closed from March 24 to April 5, 1976, or a period of twelve days.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes}, with the exception of the Argentinian coup of March 24, 1976 which is excluded from our analysis because the stock market remained closed for twelve days following the event.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
 
-\begin{table}[!ht]
+\begin{table}[!htb]
 \caption{Abnormal returns following coups} \label{tab:AR-coups}
@@
 The mean event day abnormal return is negative and statistically different than zero.
-However, the result is driven by five events: the shooting of U.S.
+
+%However, the result is driven by five events: the shooting of U.S.
 President William McKinley on September 6, 1901; the assassination of U.S.
@@
 
-\begin{table}[!ht]
+\begin{table}[!htb]
 \caption{Abnormal returns following assassinations} \label{tab:AR-ass}
@@
 
-These results are consistent with our hypothesis that the nature of the political event and its expected impact on policy matters, and that assassinations should have a negative effect as they occur seemingly at random and increase uncertainty.
+These results are consistent with our hypothesis that assassinations should have a negative effect as they occur seemingly at random and increase uncertainty.
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
@@
 
-These results are again consistent with our hypothesis that different events will have disparate effects, and that resignations may lead to positive returns.
-The positive event day abnormal return following resignations is not surprising as resignations typically occur because of poor performance and/or loss of authority.
+These results are again consistent with our hypothesis that different events will have disparate effects, and that resignations may lead to positive returns as resignations typically occur because of poor performance and/or loss of authority.
 Among our sample of events, leaders were ousted following loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
 
-For example, consider Ferdinand Marcos' resignation from office as President of the Philippines in February 1986.
+For example, the resignation of Ferdinand Marcos as President of the Philippines in February 1986 was associated with an approximately 13\% positive event day AR.
+Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
+In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies \citep{overholt1986rise}.
+
+%For example, consider Ferdinand Marcos' resignation from office as President of the Philippines in February 1986.
 Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
@@
 
-By contrast, the largest negative event in our sample (-3\%) is the 1993 resignation of President Ghulam Ishaq Khan and Prime Minister Nawaz Sharif in Pakistan.
+%By contrast, the largest negative event in our sample (-3\%) is the 1993 resignation of President Ghulam Ishaq Khan and Prime Minister Nawaz Sharif in Pakistan.
 The resignations occurred after months of political infighting when the army demanded the President and Prime Minister resign and call for new elections.
@@
 
-\begin{table}[!ht]
-\caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-auth-car.txt}
-  \hline
-\ExpandableInput{../tables/artable-auth-car-mean.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Abnormal returns following democratic regime changes} \label{tab:AR-dem}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-dem-car.txt}
-  \hline
-\ExpandableInput{../tables/artable-dem-car-mean.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
 A similar analysis is not possible for shifts from pro or anti business leaders, as examples of such clear and plausibly exogenous shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
 In all cases, no clear economic ideological shift can be identified.} We therefore look outside of the sample above and conduct an in-depth case study of a seemingly pro-business and anti-socialist coup followed by the reinstatement of a socialist government: the 2002 failed coup against Hugo Chavez in Venezuela.
+The coup replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 
@@
 
-The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+%The ultimately failed Venezuelan coup against Hugo Chavez replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 On the evening of April 11, 2002, coup plotters removed Chavez from office and later detained him.
@@
 
-\autoref{fig:AR-Ven} provides graphical evidence on the effect of the coup attempt.
-The top panel shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
-The daily ARs and corresponding confidence intervals are displayed in the bottom panel.
+\autoref{fig:AR-Ven} shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
 The abnormal return on April 12, the first trading day in which investors could react to the coup, was +10\%.
 The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-
 The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
@@
 
+\subsection{Democratic vs. authoritarian regime changes}
+
+\begin{table}[!ht]
+\caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-auth-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-auth-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Abnormal returns following democratic regime changes} \label{tab:AR-dem}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-dem-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-dem-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\clearpage
+\pagebreak
+\newpage
+
 \subsection{Time-shifted placebo test}

### 2021-07-01 doc/regime_changes_note.tex
Additional edits to change to research note format
Create separate sections for estimation strategy and results. Also  moved tabular results to appendix and now display primary results as visualization.

@@
 
-\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
+\section{Estimation strategy} \label{sec: estimation}
 
@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-Volatility stays between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations.
-This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
+\subsection{Abnormal returns} \label{subsec:abnormal-returns}
 
-\begin{figure}[!htb]
-\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
-\end{figure}
-
-\subsection{Estimation strategy: abnormal returns} \label{subsec:abnormal-returns}
-
-We now turn to the magnitude and direction of the effect of irregular regime changes on stock returns.
-We follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
+For the magnitude and direction of the effect of irregular regime changes on stock returns, we follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
 Normal performance is measured with a constant mean return model,
@@
 
+\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
+
+\subsection{Volatility} \label{subsec: volatility}
+
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+Volatility stays between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations.
+This may suggest that investors sometimes have information about the events before they occur.
+Nonetheless, there is still an enormous volatility jump on the day of the regime change.
+Volatility then decreases to normal levels within a month of the event.
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.8]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
 \subsection{Coups} \label{subsec: Coups}
 
-\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
-\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes}, with the exception of the Argentinian coup of March 24, 1976 which is excluded from our analysis because the stock market remained closed for twelve days following the event.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
+\begin{figure}[!htb]
+\centering
+\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type.pdf}
+\caption{Mean cumulative abnormal returns by type of regime change}\label{fig:mean-car-by-regime-change}
+\end{figure}
 
-\begin{table}[!htb]
-\caption{Abnormal returns following coups} \label{tab:AR-coups}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-coups-car.txt}
-  \hline
-\ExpandableInput{../tables/artable-coups-car-mean.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
+\autoref{fig:mean-car-by-regime-change} shows the mean cumulative abnormal returns by each type of regime change we analyze.
 
+Individual results for all coups in our sample and mean results for all coups can be found in \autoref{tab:AR-coups}.
 The average coup has a $-2.1\%$ event day AR.
@@
 
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for successful assassinations rather than coups.
-Like the majority of coups, there is evidence that assassinations decrease stock prices.
+Like the majority of coups, there is evidence that assassinations decrease stock prices ( see \autoref{fig:mean-car-by-regime-change}).
+The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for assassinations rather than coups.
 The mean event day abnormal return is negative and statistically different than zero.
@@
 Kennedy on November 22, 1963; the assassination of Indian Prime Minister Indira Gandhi on October 31, 1984; the suicide bombing that killed Sri Lankan president Ranasinghe Premadasa on May 1, 1993; and the assassination of Israeli Prime Minister Yitzhak Rabin on the evening of November 4, 1995.
-
-\begin{table}[!htb]
-\caption{Abnormal returns following assassinations} \label{tab:AR-ass}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-ass-car.txt}
-  \hline
-\ExpandableInput{../tables/artable-ass-car-mean.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
 
@@
 
-\begin{table}[!ht]
-\caption{Abnormal returns following resignations} \label{tab:AR-resignations}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-res-car.txt}
-  \hline
-\ExpandableInput{../tables/artable-res-car-mean.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
 \subsection{Resignations} \label{subsec: Resignations}
 
-In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{tab:AR-resignations}).
+In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-resignations}).
 The mean event day abnormal return is over 4\% and the positive returns are persistent and grow larger over time (mean 20-day CAR $\approx$ 12\%).
@@
 \begin{figure}[!ht]
-\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
+\begin{centering}
+\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/venezuela_coup_attempt_2002.pdf}
 \caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
 \label{fig:AR-Ven}
+\end{centering}
 \end{figure}
@@
 In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
-The general intuition is that we should not observe significant abnormal returns when performing an identical test on dates where no intervention (i.e.
+The intuition is that we should not observe significant abnormal returns when performing an identical test on dates where no intervention (i.e.
 a politically unstable event) occurred.
@@
 
-\autoref{fig:mean-car-by-regime-change} compares mean CARs estimated using the actual event date (\autoref{subfig:mean-car-by-regime-change-actual}) to CARs estimated with the event date shifted 1-year (365 days) into the future (\autoref{subfig:mean-car-by-regime-change-placebo}).
-\autoref{subfig:mean-car-by-regime-change-actual}---which reproduces the tabular results presented in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections---shows that assassinations and coups are associated with negative event day ARs while resignations are associated with positive event day ARs.
-In contrast, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
+\autoref{subfig:mean-car-by-regime-change-placebo} shows CARs estimated with the event date shifted 1-year (365 days) into the future.
+In contrast to \autoref{fig:mean-car-by-regime-change}, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
 The event day ARs are considerably smaller in magnitude and are not statistically different from zero for either coups or resignations.
@@
 \centering
-\begin{subfigure}{\textwidth}
-\centering
-\includegraphics[max size={.8\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type.pdf}
-\caption{Actual event date} \label{subfig:mean-car-by-regime-change-actual}
-\end{subfigure}
-\begin{subfigure}{\textwidth}
-\centering
-\includegraphics[max size={.8\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
+\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
 \caption{Event date shifted forward by one year} \label{subfig:mean-car-by-regime-change-placebo}
-\end{subfigure}
-\caption{Mean cumulative abnormal returns by type of regime change}\label{fig:mean-car-by-regime-change}
 \end{figure}
@@
 To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
-There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date.
-Most of the statistically significant placebo estimates also occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
+There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date and most  occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
 When dates are shifted forward further ($\geq$ 110 days), the event day AR is only statistically significant in one case (day 365 for assassinations).
@@
 
+\subsection{Coups} \label{subsec: coups appendix}
+
+\autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
+\autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes}, with the exception of the Argentinian coup of March 24, 1976 which is excluded from our analysis because the stock market remained closed for twelve days following the event.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
+
+\begin{table}[H]
+\caption{Abnormal returns following coups} \label{tab:AR-coups}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-coups-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-coups-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\subsection{Assassinations} \label{subsec: ass appendix}
+
+\begin{table}[H]
+\caption{Abnormal returns following assassinations} \label{tab:AR-ass}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-ass-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-ass-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\subsection{Resignations} \label{subsec: resignation appendix}
+
+\begin{table}[H]
+\caption{Abnormal returns following resignations} \label{tab:AR-resignations}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-res-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-res-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\newpage
+
 \subsection{Public Protests} \label{subsec: Public Protests}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 \caption{List of public protests preceding resignations} \label{tab:protest-list}

### 2021-08-11 doc/regime_changes_note.tex
Additional research note edits
Made additional edits to reformat paper to research note length.

@@
 Political instability is commonly thought to discourage investment and reduce economic growth.
-We challenge this theory by finding that different types of instability have disparate effects on stock returns.
+We challenge this consensus by showing that instability does not systematically depress investment as investors recognize when instability may be in their favor.
 Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
-Abnormal returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
-The impact of coups tends to be negative (-2\%), but examination of the 2002 failed coup against Hugo Chavez reveals returns of +10\%.
+Returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
+The impact of coups tends to be negative (-2\%), but we show that a pro-capitalist coup results in large positive returns.
 We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to be perceived negatively by investors than democratic or pro-business changes.
-The expected direction and magnitude of abnormal returns is therefore dependent on the type of regime change and its expected impact on economic policy.
+The impact of political instability on investment is therefore dependent on the type of regime change and its expected impact on economic policy.
 
@@
 
-Investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the \citet{wipr2013} report (most recent), executives of multinational enterprises ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries (after macroeconomic instability).
-In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.}
+Investors rank political risk as a top consideration when investing in emerging markets.\footnote{Executives of multinational enterprises rank political risk as among the most important constraint for foreign direct investment (FDI) in developing countries \citep{wipr2011, wipr2012, wipr2013}.} Research shows that political instability is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, and that stock market variance increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
-Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.
-This is supported by empirical research showing that political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+%Unstable governments have been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.
 
-In contrast to these cross country studies, we: (1) examine the impact of various types of instability (coups, resignations, assassinations, and protests) separately, and (2) conduct our analysis using event studies of daily financial data.
-Event studies examine the effect of an unexpected event on stock prices \textit{at the time of the event} (i.e.
-a local average treatment effect) to determine if returns are systematically different from predicted.
-This interrupted time-series approach mitigates the endogeneity problems ubiquitous in previous cross country regressions.
-Confounding events would need to also occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
-For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.,][]{fisman2001estimating,faccio2006politically,goldman2009politically}.}
+%---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---
+
+However, how different types of political instability affect markets remains unknown.
+In contrast to aforementioned cross country studies, we: (1) examine the impact of various types of instability (coups, resignations, assassinations, and protests) separately, and (2) conduct event studies of daily financial data.
+Event studies estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
+This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.
 
@@
 
-We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests---the full sample of events for which national-level daily financial data is available.
-Like previous research, we find that coups, assassinations, resignations, and public protests all cause large increases in financial volatility.
-However, we also find that abnormal returns are large and positive (+4\%) following resignations and tend to be negative and smaller in magnitude following assassinations and coups (-2\%).
+We analyze the full sample of politically unstable events for which national-level daily financial data is available.\footnote{13 coups, 8 assassinations, 15 forced resignations, and 11 public protests.}  Like previous research, we find that all types of political instability cause large increases in financial volatility.
+However, we find that abnormal returns are large and positive (+4\%) following resignations and tend to be negative and smaller in magnitude following assassinations and coups (-2\%).
 We also examine the failed 2002 Venezuelan coup, as it allows us to estimate the effects of both a pro-business coup (+10\%), and the reinstatement of a left-wing populist (-8\%) on the same market.
@@
 Our primary contributions are empirical and methodological.
-Empirically, we show that while political instability concerns investors, instability does not systematically depress investment.
+Empirically, we provide the first estimates of financial market reactions disaggregated by type of political instability.
+We show that while political instability concerns investors, it does not systematically depress investment.
 Investors recognize when instability may be in their favor.
-Methodologically, we employ a method less susceptible to endogeneity concerns, and integrate event studies with synthetical control methods to allow for control portfolios in situations where an obvious control portfolio candidate is not present.
-While we do not view theoretical development as our main contribution, we do find evidence that authoritarian regime changes are more likely to lead to negative returns, and that leaders who are clearly pro-business can be rewarded by investors, even if they use extra-judicial methods to take power.
+The capital flows we document are not insubstantial---in many cases they represent larger shocks than the 2008 stock market crash.
+Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios in situations where an obvious control portfolio is not present.
+We do not view theoretical development as our main contribution, but find evidence that authoritarian regime changes are more likely to lead to negative returns, and that leaders who are clearly pro-business can be rewarded by investors, even if they use extra-judicial methods to take power.
 
@@
 Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
-However, if market returns reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
+But if market returns reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
 Investors may view even a coup as a ``positive'' event if the current regime is anti-business or anti-global.
@@
 Not all regime changes are equivalent.
-Resignations, assassinations, and coups have all been used as proxies for instability in previous research.
-However, some regime changes---such as the sudden resignation of an ineffective leader---may lead to increased stability.
-By contrast, assassinations can occur seemingly at random and a successor may be unclear.
-Coups can occur in the name of democracy or autocracy.
-These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
+Some regime changes---e.g., the resignation of an ineffective leader---may foreshadow better policy.
+Assassinations can occur seemingly at random, and a successor may be unclear.
+Coups can be democratic or autocratic.
+These differences are often overlooked in past studies, which have proxied for instability using the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or combined events into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
 
-An active debate also exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
-Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, others argue that the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the expected impact of coups  is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
+Debate also exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
+Most research suggests ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+Others argue the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the expected impact of coups is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
 But while ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
@@
 Different types of regime changes may therefore have disparate effects on markets and/or economic growth.
-The theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro-market than the regime they replace.
-As our event study approach allows us to analyze individual coups separately from others, we can test this prediction.
+Previous research suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro-market than the regime they replace.
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
@@
 
-Financial data are from the Global Financial Data database, which includes the longest available daily time series of stock prices.
-We collect national stock index data on every country in which there was a coup or coup attempt, an assassination or failed assassination, or a forced resignation and for which daily financial data is available.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
-Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} The longest available daily time series for these stock indices are listed in \autoref{tab:stock-list}.
+Financial data is from the Global Financial Data database---the longest available daily time series of stock prices.
+We collect national stock index data for every country in which there was a coup, assassination, or resignation and daily financial data is available.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
+Coup attempts are those in category 2 in the CSP Coup d'etat dataset.} These stock indices are listed in \autoref{tab:stock-list}.
 
 Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
-The Coup d'etat dataset includes the date of successful, attempted, plotted, and alleged coups.
-We focus on successful coups because the other classifications are contentious, and the choice of dataset and classification methodology would directly alter our findings.\footnote{\citet[p.
-617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''}
+We form a list of ``irregular'' regime changes from successful coups,\footnote{For example, \citet[p.
+617]{needler1966political} states that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the CSP is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''} assassinations of the executive, and resignations of the executive\footnote{Resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.Note that the Polity IV definition of ``poor performance'' is not synonymous with poor \textit{economic} performance, and in practice the reasons cited for resignation across events are: loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.} as daily financial data is available for countries in these categories.
+We supplement the CSP data with Archigos Version 4.1 leadership data, which allows us to identify some additional cases of coups, assassinations, and protests.
+A list of the political events in our dataset and whether they resulted in democratic or autocratic shifts is shown in \autoref{tab:regime-changes}.
 
-The Coup d'etat Events handbook also provides a list of 1) auto-coups\footnote{Defined by Center for Systemic Peace as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime."}, 2) the ouster of leadership by foreign forces, 3) the ouster of leadership by rebel forces, 4) assassinations of the executive and 5) resignations of the executive due to poor performance and/or loss of authority.
-Daily financial data is available for countries in categories 4 and 5, so we supplement the coups with assassinations and resignations to form a list of ``irregular'' regime changes.
-The resignations are those in which the ruling executive was coerced to resign due to poor performance, public discontent and popular demonstrations.\footnote{Note that the Polity IV definition of ``poor performance'' is not synonymous with poor \textit{economic} performance, and in practice the reasons cited for resignation across events are: loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.}
+%in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
+coups, revolts and assassinations).
+
+There is considerable debate about classification of regime changes.
+We recognize that some readers may feel certain events are missing.
+We rely on common third-party classifications to minimize the possibility our results are driven by our own classifications.
+The one exception is that we separately analyze the 2002 failed coup  in Venezuela, as it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+
+%in which President Hugo Chavez was removed from office for two days
+
+%\footnote{Defined by CSP as the ``occurrence of subversion of the constitutional order by a ruling (usually elected) executive and the imposition of an autocratic regime."}
 
@@
 
-We further supplement the CSP data with leadership data from Archigos Version 4.1, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g.
-coups, revolts and assassinations).
-
-A list of the political events in our dataset and whether they resulted in democratic or autocratic shifts is shown in \autoref{tab:regime-changes}.
-Coups tend to have the largest impact on the level of democratization as a number of countries have subsequently transitioned from democracies to anocracies or autocracies.
+%Coups tend to have the largest impact on the level of democratization as a number of countries have subsequently transitioned from democracies to anocracies or autocracies.
 On the other hand, neither assassinations nor resignations tend to have much impact on the level of democratization.
 
-The discussion above shows that there is considerable debate about classification of regime changes.
-We recognize that some readers may feel certain events are missing based on their own substantive knowledge.
-We rely on commonly used third-party classifications in order to minimize the possibility that our results are driven by our own subjective classifications.
-The one exception is that we separately analyze the failed coup attempt in Venezuela in April 2002 in which President Hugo Chavez was removed from office for two days, as it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+%\autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events.
+The returns on the event day (day 0) are significantly larger than on any other day.
+The magnitude of returns begins increasing just before the event day and remains high for a short period after.
+This suggests that financial volatility increases during the days surrounding regime changes, but says nothing about mean returns.
+\nameref{sec: Impact of Political Instability on Stock Returns} will first formally estimate the volatility surrounding all irregular regime changes, then analyze coups, assassinations and resignations separately and determine their impact on mean returns.
 
-\autoref{fig:AV-DR} plots the absolute value of daily stock returns averaged across all events and shows that the absolute value of returns on the event day (day 0) are significantly larger than on any other day.
-In addition, the magnitude of returns begins increasing just before the event day and remains high for a short period after.
-This suggests that financial volatility increases during the days surrounding regime changes, although it does not provide any evidence on mean returns.
-\nameref{sec: Impact of Political Instability on Stock Returns} tests these results more formally.
-It will first formally estimate the amount of volatility surrounding all irregular regime changes, then analyze coups, assassinations and resignations separately and determine what impact they have on mean returns.
-
-\begin{figure}[!ht]
-\begin{centering}
-\includegraphics[width = 15cm]{../figs/daily_mean_absreturn.pdf}
-\caption{Absolute value of daily returns}
-\label{fig:AV-DR}
-\end{centering}
-\end{figure}
-
-\section{Estimation strategy} \label{sec: estimation}
+\section{Estimation} \label{sec: estimation}
 
@@
 
-We first examine the effect of irregular regime changes on financial volatility.
-Our estimates are obtained from a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
+To examine the effect of irregular regime changes on financial volatility, we use a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
 As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
@@
 
-For the magnitude and direction of the effect of irregular regime changes on stock returns, we follow the standard event study methodology as presented by, among others, \citet{mackinlay1997event} and \citet{campbell1997econometrics}.
+%\footnote{A growing body of work uses event studies to assess political phenomenon.
+For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.,][]{fisman2001estimating,faccio2006politically,goldman2009politically}.}
+
+To estimate the magnitude and direction of the effect of irregular regime changes on stock returns, we follow standard event study methodology \citep{mackinlay1997event, campbell1997econometrics}.
 Normal performance is measured with a constant mean return model,
@@
 where $R_{it}$ is the logged return of national stock index $i$ on trading day $t$ and $\epsilon_{it}$ is the error term.
-We calculate abnormal returns (ARs), in an ``event window'' surrounding the date of each coup, $AR_{i\tau}=R_{i\tau}-\widehat{\mu}_i$, where $\tau$ is a date in the event window, and $\widehat{\mu}_i$ is estimated in an ``estimation window'' preceding the event window with \autoref{eqn:market-model}.
-We use a 41 day event window (i.e.
-20 pre-event trading days, the event day, and 20 post-event trading days).
-The estimation window is the 250 trading days prior to the start of the event window.
-The abnormal returns are then used to generate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
+We calculate abnormal returns (ARs) in an ``event window'' around the date of each event, $AR_{i\tau}=R_{i\tau}-\widehat{\mu}_i$, where $\tau$ is a date in the event window, and $\widehat{\mu}_i$ is estimated in an ``estimation window'' preceding the event window with \autoref{eqn:market-model}.
+We use a 41 trading day event window (20 pre-event days, event day, and 20 post-event days) and 250 trading day estimation window.
+The ARs are then used to calculate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
 Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
 
-We define the event date as the first trading day in which the market could have reacted to news of the event.\footnote{For example, during the October 12, 1999 coup d'etat in Pakistan led by General Pervez Musharraf, the army announced that Prime Minister Nawaz Sharif had been dismissed after market hours at 10:15 pm.
-We code October 14th, the day in which the market re-opened, as the event day.} When events occurred on weekends, we change the event date to the following Monday.
-$(0,\tau-1)$ is used to denote the $\tau$-day period beginning with the event day and $(-1,\tau)$ to denote the negative $\tau$-day period beginning with the day prior to the event day.\footnote{In other words, for cumulative abnormal returns prior to the event date, we aggregate backwards starting at the day of the event.
-For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.} We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$), and the event date plus 19 days $(0,19$).
-In addition, we present results for the pre-event windows $(-1,-7$) and $(-1,-20$).
+The event date is the first trading day a market could react to news of the event.
+$(0,\tau-1)$ denotes the $\tau$-day period beginning with the event day and $(-1,\tau)$ denotes the negative $\tau$-day period beginning with the day prior to the event day.
+We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$) and 19 days $(0,19$), and the pre-event windows $(-1,-7$) and $(-1,-20$).
 
-We use a constant mean return model instead of a market model to maximize the number of observations and because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we integrate synthetic control methodology \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
-In short, we create a ``synthetic'' control portfolio for each event and compare observed returns to the synthetic returns.
-Each country is given a weight which represents its influence in the synthetic control portfolio.
+%\footnote{In other words, for cumulative abnormal returns prior to the event date, we aggregate backwards starting at the day of the event.
+For example, $CAR(-1,-2$) is the sum of the abnormal returns on event date $-1$ and event day $-2$.}
+
+%If an event occurred on a weekend, the event date is the following Monday.
+
+We do not use a market model (where a market index is included as a control) to maximize the number of observations and because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we combine synthetic control methods \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
+We create a ``synthetic'' control portfolio for each event, where each country is given a weight representing its influence in the control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
 
-More formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}, and the results are presented in \nameref{subsec: Robustness}.
+Formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+
+%and the results are presented in \nameref{subsec: Robustness}.
 
@@
 \begin{figure}[!htb]
-\includegraphics[scale = 0.8]{../figs/mean-volatility.pdf}
+\includegraphics[scale = 0.75]{../figs/mean-volatility.pdf}
 \caption{Mean of volatility estimates from GARCH(1,1) models}
@@
 
+\autoref{fig:mean-car-by-regime-change} shows the mean CARs by each type of regime change we analyze for the event day, as well 20 days before and after the event.
+Individual results for all coups in our sample and mean results for all coups can be found in \autoref{tab:AR-coups}.
+
 \begin{figure}[!htb]
 \centering
-\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type.pdf}
+\includegraphics[scale = 0.75]{../figs/mean-car-by-regime-change-type.pdf}
 \caption{Mean cumulative abnormal returns by type of regime change}\label{fig:mean-car-by-regime-change}
@@
 
-\autoref{fig:mean-car-by-regime-change} shows the mean cumulative abnormal returns by each type of regime change we analyze.
-
-Individual results for all coups in our sample and mean results for all coups can be found in \autoref{tab:AR-coups}.
 The average coup has a $-2.1\%$ event day AR.
@@
 
-Like the majority of coups, there is evidence that assassinations decrease stock prices ( see \autoref{fig:mean-car-by-regime-change}).
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for assassinations rather than coups.
+Like the majority of coups, we find that assassinations decrease stock prices (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-coups}).
 The mean event day abnormal return is negative and statistically different than zero.
@@
 This is consistent with expectations as assassinations are typically not predictable.
-As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days, or almost 4 calendar years.
-However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death (although the assassination may have exacerbated the panic).}
+As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days.
+However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death.}
+
+% (although the assassination may have exacerbated the panic)
 
@@
 
-In contrast to coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-resignations}).
-The mean event day abnormal return is over 4\% and the positive returns are persistent and grow larger over time (mean 20-day CAR $\approx$ 12\%).
-Furthermore, event day ARs are only negative and statistically significant at even the ten percent level in two out of the fifteen resignations (Pakistan on April 19, 1993 and Tunisia on June 31, 2011).
+Unlike coups and assassinations, abnormal returns following resignations are large and positive (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-resignations}).
+The mean event day abnormal return is over 4\%, and the positive returns grow larger over time (mean 20-day CAR $\approx$ 12\%).
+Event day ARs are only negative and significant at even the ten percent level in two of the fifteen resignations.
 
-These results are again consistent with our hypothesis that different events will have disparate effects, and that resignations may lead to positive returns as resignations typically occur because of poor performance and/or loss of authority.
+These results are consistent with our hypothesis that resignations may lead to positive returns as they typically occur due to poor performance and/or loss of authority.
 Among our sample of events, leaders were ousted following loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
 
-For example, the resignation of Ferdinand Marcos as President of the Philippines in February 1986 was associated with an approximately 13\% positive event day AR.
-Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
-In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies \citep{overholt1986rise}.
+%For example, the resignation of Ferdinand Marcos as President of the Philippines in February 1986 was associated with an approximately 13\% positive event day AR.
+Prior to his resignation, the Philippine regime was the least preferred site for foreign investment amongst East Asian capitalist economies due to rampant corruption, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
+
+%In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies \citep{overholt1986rise}.
 
@@
 
-The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
-It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent in \nameref{subsec: Public Protests} in the appendix.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
-In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.} When taking directionality into account, it appears that public protests have no effect on stock returns.
-However, this occurs because some political movements increase stock prices while others decrease them, and the absolute value of stock returns are approximately 1.5\% higher during public protests (see \autoref{tab:protest-stocks}).\footnote{These results hold when controlling for emerging market index fluctuations.}
+The resignations analyzed encompass leaders who left office because of poor performance, public discontent and popular protests.
+Protests preceding these resignations may therefore also affect financial markets\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.}, so we analyze all protests that preceded the resignations in \nameref{subsec: Public Protests}.
+Including directionality, public protests have no effect on stock returns as some increase stock prices while others decrease them (see \autoref{tab:protest-stocks}).
+In absolute terms, stock returns are approximately 1.5\% higher during public protests.
 
-\section{Exploring possible mechanisms} \label{subsec: mechanisms}
+%\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}
+
+%\footnote{These results hold when controlling for emerging market index fluctuations.}
+
+\section{Mechanisms} \label{subsec: mechanisms}
 
@@
 For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation \citep{przeworski1982structure, north1989constitutions, svensson1998investment}.
-In addition, when the successor in an irregular regime change is clear, investors may have strong priors about the effect of the new leader on economic and/or market performance.
-Two possible mechanisms that could be driving the differences may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift in governance, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
+Investors may also have priors about a new leader's economic ideology.
+Two mechanisms that could be driving positive or negative returns may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
 
-We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
-We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
-We observe ten cases associated with an authoritarian shift in governance.
-Only two of these events result in positive CARs, and neither are significantly different from zero.
-Five cases resulted in a democratic shift in governance.
-Three of these five cases result in positive CARs.
+We therefore first aggregate the events in our sample by whether they resulted in an authoritarian or democratic shift.\footnote{As defined by the Polity project.} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while democratic shifts are perceived positively (see \autoref{tab:AR-dem}).
+Of ten authoritarian shifts, only two result in positive CARs, and neither are significantly different from zero.
+Three of five cases involving democratic shifts result in positive CARs, and the positive CARs persist in the follows weeks.
 Of the two negative CARs, one is not significantly different from zero, and the other is associated with a forced market closure that lasted 17 days.
-However, the majority of the positive returns from democratic regime changes come from the 12\% positive CAR associated with the resignation of Ferdinand Marcos in the Philippines in 1986.
 
-A similar analysis is not possible for shifts from pro or anti business leaders, as examples of such clear and plausibly exogenous shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
-In all cases, no clear economic ideological shift can be identified.} We therefore look outside of the sample above and conduct an in-depth case study of a seemingly pro-business and anti-socialist coup followed by the reinstatement of a socialist government: the 2002 failed coup against Hugo Chavez in Venezuela.
-The coup replaced a left-wing populist government with a new pro-business president, and therefore provides a natural test of the effects of both pro-business and anti-business regime changes separately from simple uncertainty because investors reacted to an expected regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
+%However, the majority of the positive returns from democratic regime changes come from the 12\% positive CAR associated with the resignation of Ferdinand Marcos in the Philippines in 1986.
+
+%We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
+
+A similar aggregated analysis is not possible for shifts from pro or anti business leaders, as examples of clear shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
+In all cases, no clear economic ideological shift can be identified.} We therefore look outside our sample and examine a (failed) pro-business coup followed by the reinstatement of a socialist leader: the 2002 failed coup against Hugo Chavez in Venezuela.
+This provides a natural test of the effects of both pro and anti business regime changes separately from simple uncertainty because investors reacted to a regime change twice: first, when Chavez was ousted, and second, when he was reinstated.
 
@@
 \begin{centering}
-\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/venezuela_coup_attempt_2002.pdf}
+\includegraphics[max size={0.8\textwidth}{.8\textheight}]{../figs/venezuela_coup_attempt_2002.pdf}
 \caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
@@
 
-\autoref{fig:AR-Ven} shows CARs for the 10 days prior to and following the event, along with 95\% confidence intervals.
-The abnormal return on April 12, the first trading day in which investors could react to the coup, was +10\%.
-The market reacted in the opposite direction to Chavez's reinstatement as president: the abnormal return on the next trading day, April 15, 2002, was -8\%.
-The results in \autoref{fig:AR-Ven} are particularly striking given the discrepancy between the ARs on event days 0 and 1 and all other days.
-Consistent with our earlier findings that coups tend to have pre and post-event CARs that are statistically indistinguishable from zero, the only days on which the 2002 Venezuelan coup d'etat attempt ARs are statistically different from zero is on event days 0 and 1 after the coup attempt.
-The almost 0\% 10-day CAR preceding the coup makes this an ideal case as it implies that investors were completely unaware of the coup plot, increasing our confidence that the abnormal returns capture the true effect of the Chavez to Carmona and Carmona to Chavez regime changes on stock returns.
-This failed coup therefore demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
-More generally, the large magnitudes and precision of these effects suggest that  investors primarily value transition to a pro-business government regime, regardless of how the regime change is achieved.
+\autoref{fig:AR-Ven} shows CARs and 95\% confidence intervals for the 20 days surrounding the event.
+The abnormal return on the first trading day investors could react to the coup was +10\%.
+When Chavez was reinstated, the abnormal return was -8\%.
+The 0\% 10-day CAR preceding the coup implies that investors were completely unaware of the coup plot, increasing our confidence that the abnormal returns capture the true effect of the regime changes.
+This failed coup demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
+The large magnitudes and precision of these effects suggest that investors value transition to a pro-business government regime, regardless of how the regime change is achieved.
 
@@
 
+\vspace{-0.05cm}
 \section{Robustness} \label{subsec: Robustness}
 
-There are some potential concerns with the results in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections.
-First, the abnormal returns could have been driven by factors unrelated to the regime changes.
-Second, the true effects of regime changes on firm value may be underestimated if investors had apriori information.
-Third, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate.
+Potential concerns with the results in the \nameref{subsec: Coups}, \nameref{subsec: Assassinations}, and \nameref{subsec: Resignations} sections are that: (1) the ARs could be driven by factors unrelated to the regime changes, (2) the effects of regime changes may be underestimated if investors had apriori information, and (3) confidence intervals based on normally distributed ARs may be inappropriate.
 
@@
 First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events for each type of regime change.
-We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days).
-In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
-The intuition is that we should not observe significant abnormal returns when performing an identical test on dates where no intervention (i.e.
-a politically unstable event) occurred.
-Observing such effects would call the research design and modeling assumptions into question, and raise concerns that the abnormal returns were caused by factors other than the regime changes.
+We should not observe significant CARs when performing an identical test on dates where no event occurred.
+This would call the research design and modeling assumptions into question, and raise concerns that the abnormal returns were caused by factors other than the regime changes.
+The results reinforce the main results: the ARs on the actual event date capture most of effect of the regime change, although effects can sometimes persist in the short event window following the event date.
+For a detailed descriptions of this analysis and results, see \nameref{subsec: robustness appendix}.
 
-\autoref{subfig:mean-car-by-regime-change-placebo} shows CARs estimated with the event date shifted 1-year (365 days) into the future.
-In contrast to \autoref{fig:mean-car-by-regime-change}, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
-The event day ARs are considerably smaller in magnitude and are not statistically different from zero for either coups or resignations.
-Moreover, while CARs estimated using the actual event date for resignations trend upwards following the event day, there is no consistent trend in the placebo analysis.
-\autoref{fig:mean-car-by-regime-change} therefore suggests that the main results are not merely an artifact of the data.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
-\caption{Event date shifted forward by one year} \label{subfig:mean-car-by-regime-change-placebo}
-\end{figure}
-
-To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
-There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date and most  occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
-When dates are shifted forward further ($\geq$ 110 days), the event day AR is only statistically significant in one case (day 365 for assassinations).
-Overall, these results reinforce the main results: the ARs on the actual event date capture most of effect of the regime change, although effects can sometimes persist in the short event window following the event date.
-
-These figures also provide evidence on the extent to which regime changes appear to be unexpected.
-For instance, the CARs prior to assassinations and coups presented in \autoref{subfig:mean-car-by-regime-change-actual} tend to be close to zero, suggesting that investors were unaware that a negative event was likely to occur in the coming days.
-For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
-There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
-
-Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
+Second, we create a synthetic control portfolio for each event.
 Each country is given a weight which represents its influence in the synthetic control portfolio.
@@
 
-Non-parametric statistical techniques that are free from distributional assumptions are used to address concerns about inferences from small sample sizes.
-We employ the sign and the rank tests, which are based on the sign and the rank of the event day ARs respectively.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier in this paper.
-\autoref{tab:non-parametric} compares event day ARs as well as ``abnormal absolute returns'' between the event country and the synthetic control portfolio using the non-parametric methods discussed above.
-The ``abnormal absolute returns'' are abnormal returns for the absolute value of stock returns.
+Third, non-parametric statistical techniques (sign and rank tests) free from distributional assumptions address concerns about inferences from small sample sizes.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} \autoref{tab:non-parametric} compares event day ARs and the absolute value of all combined returns (since some events increase returns while others decrease them) to the synthetic control portfolio using the non-parametric methods discussed above.
+The synthetic control and small sample tests suggest that the main results are not a result of deviations from normality or confounding world events (see \nameref{subsec: robustness appendix} for a full discussion).
+
+%The ``abnormal absolute returns'' are abnormal returns for the absolute value of stock returns.
 This is done to combine events since resignations tend to increase returns while assassinations and coups tend to decrease them.
 The idea that the absolute value of returns might increase during irregular regime changes is similar to the finding that volatility increases and is consistent with \autoref{fig:AV-DR}.
+
+%Both tests are less influenced by departures from normality than statistics based on traditional t-tests such as those reported earlier.
+
+%We employ the sign and the rank tests, which are based on the sign and the rank of the event day ARs respectively.
 
@@
 
-As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 1\% level using the rank test statistic and the abnormal returns for coups and assassinations are significant at at least the 10\% level using the sign test.
-In addition, abnormal absolute returns for all events are statistically significant at at least the 5\% level using both the rank and sign tests.
-On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level using the rank or sign tests.
-Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, the synthetic control and small sample tests suggest that the main results are not a result of deviations from normality or confounding world events.
+\section{Conclusion}
 
-\section{Discussion and Conclusion}
+Conventional theory suggests markets dislike political instability.
+We show that this is not always the case.
+Unexpected changes in ruler virtually always increase market volatility, but returns are not always negative.
+Markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
 
-While conventional wisdom suggests markets dislike the political instability associated with regime changes, we show that this is not necessarily always the case.
-Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
+Despite their frequency, there is little evidence on the economic consequences of various types of political instability.
+We show that market returns following resignations are large and positive on average, but negative and smaller in magnitude following assassinations and coups.
+We also find evidence that investors tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost markets if the instigators are clearly pro-business.
 
-Coups and other types of regime changes remain common, highlighting their relevance for economic and political development.
-Our sample consists of 5 coups, 1 assassination, 7 resignations, and 7 instances of public protect since 2000.
-The Arab spring is perhaps the most notable, with protests in response to oppressive regimes and low living standards spreading throughout the Middle East in late 2010.
-There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.\footnote{The Turkish coup attempt led to negative event-day CARs of approximately -7\%.
-See Figure A2 for a visual depiction.} Yet despite their frequency there is little evidence on their economic consequences.
+There are a number of avenues for future research.
+First, more research is needed to identify the pro and anti market characteristics of regime changes.
+Second, more work is needed to determine the extent to which stock market returns translate to broader economic development outcomes.
+It remains unclear whether the direction of the effects of different types of regime changes on outcomes such as economic growth, investment, debt, inflation, infant mortality, and years of schooling are consistent with their stock market effects, or if investor perceptions are at odds with certain development goals.
 
+%\citet{meyersson2016political} examined the impact of coups on economic growth, investment, debt, inflation, infant mortality, and years of schooling.
+
+%We demonstrate that investors clearly disliked the socialist regime in Venezuela, and \citet{girardi2018institution} show that in Chile increasing stock market valuations were caused by changes in private property rights, but it would be helpful to identify such mechanisms in additional settings.
+
+%The Venezuelan example shows that investors clearly recognized one unstable event would benefit them while the other would harm them.
+
+%Our results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor actions.
+But although the effect of regime changes on stock volatility is substantial, the effect on the direction of stock returns is less certain.
+
+%Coups and other types of irregular regime changes remain common. Our sample consists of 5 coups, 1 assassination, and 7 resignations since 2000.
+
+%Despite their frequency, there is little evidence on the economic consequences of various types of political instability.
 This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices.
 This approach provides well-identified estimates of an economic effect of regime changes that is less susceptible to endogeneity bias than prior cross country studies.
-Furthermore, the large sample of political events in our study increases the generalizability of our findings.
+The large sample of political events in our study increases the generalizability of our findings.
 
-The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence.
-But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is less certain.
-Abnormal returns following resignations are large and positive (+4\%), abnormal returns following assassinations are negative and smaller in magnitude (-2\%), and abnormal returns following coups also tend to be negative (-2\%).
-Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
+%The Arab spring is perhaps the most notable, with protests spreading throughout the Middle East in late 2010.
+There have also been a number of failed coups such as the 2002 coup attempt against Hugo Chavez and the 2016 failed coup in Turkey.\footnote{The Turkish coup attempt led to negative event-day CARs of approximately -7\%.
+See Figure A2 for a visual depiction.}
+
+%Our examination of pre-event trends in abnormal returns suggests that the positive returns we observe following resignations are not driven by investors anticipating resignations, but not coups or assassinations.
 CARs trend downward in the days preceding resignations, but if investors anticipated a resignation that brought a more competent leader and increased stability, pre-event CARs should also trend positive.
 
-A preliminary test of mechanisms suggests that democratic regime changes are typically preferable to authoritarian regime changes to investors.
-However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that even democratically subversive coups can have positive effects if the instigators are clearly pro-business.
-These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
+%These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
 
-There are a number potential avenues for future research.
-First, more research is needed to identify the pro and anti market characteristics of regime changes.
-There may be pro or anti market features of regime changes that are more nuanced than those identified in this paper.
-Similarly, it would be useful to identify additional mechanisms through which regime changes effect stock returns.
-In the case of Chile,  \citet{girardi2018institution} show that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
-Research focusing on the mechanisms in other settings would help generalize these findings.
-Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
-\citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
-It would be fruitful to examine whether the direction of the effects of different types of regime changes on these outcomes are consistent with their stock market effects, or if investor perceptions are at odds with certain development goals.
-Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
+%Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
+
+\clearpage
+\pagebreak
+
+\pdfbookmark[1]{References}{References}
+\bibliography{bibliography}
 
@@
 \section{Appendix} \label{sec: appendix}
-\newpage
 
@@
 
-\begin{table}[!htb]
+\begin{table}[H]
 \caption{List of stock indices} \label{tab:stock-list}
@@
 
-\begin{table}[!ht]
+\begin{table}[H]
 \caption{Regime changes} \label{tab:regime-changes}
@@
 
-\subsection{Coups} \label{subsec: coups appendix}
+\begin{figure}[!ht]
+\begin{centering}
+\includegraphics[width = 15cm]{../figs/daily_mean_absreturn.pdf}
+\caption{Absolute value of daily returns}
+\label{fig:AV-DR}
+\end{centering}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Event-level estimates: coups} \label{subsec: coups appendix}
 
@@
 
-\subsection{Assassinations} \label{subsec: ass appendix}
+\subsection{Event-level estimates: assassinations} \label{subsec: ass appendix}
 
@@
 
-\subsection{Resignations} \label{subsec: resignation appendix}
+\subsection{Event-level estimates: resignations} \label{subsec: resignation appendix}
 
@@
 
-\subsection{Democratic vs. authoritarian regime changes}
+\subsection{Event-level estimates: democratic vs. authoritarian regime changes}
 
@@
 
-\subsection{Time-shifted placebo test}
+\subsection{Robustness details} \label{subsec: robustness appendix}
+
+We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days) (shown in \autoref{fig:mean-car-by-regime-change}).
+In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
+
+\autoref{subfig:mean-car-by-regime-change-placebo} shows CARs estimated with the event date shifted 1-year (365 days) into the future.
+In contrast to \autoref{fig:mean-car-by-regime-change}, there are no discernible abnormal returns in \autoref{subfig:mean-car-by-regime-change-placebo}.
+To ensure that results of the placebo test based on 1-year did not occur by chance, \autoref{fig:mean-event-day-ar-by-regime-change} plots event-day abnormal against the number of days shifted.
+There are a few instances in which there are statistically significant ARs in the same direction as the event day, but they are always smaller in magnitude than the ARs estimated using the actual event date and occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
+Overall, these results reinforce the main results: the ARs on the actual event date capture most of effect of the regime change, although effects can sometimes persist in the short event window following the event date.
+These figures also provide evidence that regime changes appear to be unexpected.
+For instance, the CARs prior to assassinations and coups presented in \autoref{fig:mean-car-by-regime-change} tend to be close to zero, suggesting that investors were unaware that a negative event was likely to occur in the coming days.
+For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
+There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+
+There are a few instances in which there are statistically significant (at the 5\% level) ARs in the same direction as those on the actual event day, but they are always smaller in magnitude than the ARs estimated using the actual event date and most occur when dates are shifted within the post-event window (days 0-20), a period during which stock returns remain volatile and, in the case of resignations, there is a consistent upward trend in the CARs.
+When dates are shifted forward further ($\geq$ 110 days), the event day AR is only statistically significant in one case (day 365 for assassinations).
+The event day ARs are considerably smaller in magnitude and are not statistically different from zero for either coups or resignations.
+Moreover, while CARs estimated using the actual event date for resignations trend upwards following the event day, there is no consistent trend in the placebo analysis.
+\autoref{fig:mean-car-by-regime-change} therefore suggests that the main results are not merely an artifact of the data.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
+\caption{Event date shifted forward by one year} \label{subfig:mean-car-by-regime-change-placebo}
+\end{figure}
 
@@
 \end{figure}
+
+As shown in \autoref{tab:non-parametric}, the mean event day abnormal returns for coups, assassinations and resignations are all statistically different from zero at the 1\% level using the rank test statistic and the abnormal returns for coups and assassinations are significant at at least the 10\% level using the sign test.
+In addition, abnormal absolute returns for all events are statistically significant at at least the 5\% level using both the rank and sign tests.
+On the other hand, the event day abnormal returns for the control portfolio are never statistically different from zero at even the 10\% level using the rank or sign tests.
+Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.}
 
@@
 
-\pagebreak
-
-\subsection{Synthetic Control Portfolio}
-Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+%\pagebreak
+%
+%\subsection{Synthetic Control Portfolio}
+%Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
 Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
 
-\clearpage
-\pagebreak
-
-\pdfbookmark[1]{References}{References}
-\bibliography{bibliography}
-
 \end{document}

### 2021-10-25 doc/regime_changes_note.tex
Updates to research note version of paper

@@
 \title{\textbf{Are regime changes always bad economics?
-Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
+Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, Frances Rosenbluth, and Hikaru Yamagishi for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
@@
 Political instability is commonly thought to discourage investment and reduce economic growth.
-We challenge this consensus by showing that instability does not systematically depress investment as investors recognize when instability may be in their favor.
+We challenge this consensus by showing that instability does not systematically depress access to financial capital.
 Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
@@
 The impact of coups tends to be negative (-2\%), but we show that a pro-capitalist coup results in large positive returns.
-We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to be perceived negatively by investors than democratic or pro-business changes.
-The impact of political instability on investment is therefore dependent on the type of regime change and its expected impact on economic policy.
+We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to lead to capital flight than democratic or pro-business changes.
+The immediate impact of political instability on capital access is therefore dependent on the type of regime change and its expected impact on economic policy.
 
@@
 
-Investors rank political risk as a top consideration when investing in emerging markets.\footnote{Executives of multinational enterprises rank political risk as among the most important constraint for foreign direct investment (FDI) in developing countries \citep{wipr2011, wipr2012, wipr2013}.} Research shows that political instability is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, and that stock market variance increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+Economies are now global, financialized, and integrated, with domestic economies intrinsically linked to international investment.
+Political instability is negatively correlated with investment, financial development, and GDP growth \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, as well as associated with increases in stock market variance \citep{leblang2005government, jensen2005market, liu2015economic}.
+
+% Investors rank political risk as a top consideration when investing in emerging markets \citep{wipr2011, wipr2012, wipr2013}.
 
@@
 
-However, how different types of political instability affect markets remains unknown.
-In contrast to aforementioned cross country studies, we: (1) examine the impact of various types of instability (coups, resignations, assassinations, and protests) separately, and (2) conduct event studies of daily financial data.
-Event studies estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
+However, how different types of political instability affect a country's access to capital remains unknown.
+In contrast to the aforementioned cross country studies, we therefore separately examine the effect of various types of instability (coups, resignations, assassinations, and protests) on domestic access to financial capital.
+Specifically, we examine whether changes in financial capital flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
+democratic and pro vs.
+anti business shifts.
+
+To test our concept, we examine shifts in capital market flows surrounding politically unstable domestic events.
+Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
 This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.
@@
 
-We analyze the full sample of politically unstable events for which national-level daily financial data is available.\footnote{13 coups, 8 assassinations, 15 forced resignations, and 11 public protests.}  Like previous research, we find that all types of political instability cause large increases in financial volatility.
-However, we find that abnormal returns are large and positive (+4\%) following resignations and tend to be negative and smaller in magnitude following assassinations and coups (-2\%).
-We also examine the failed 2002 Venezuelan coup, as it allows us to estimate the effects of both a pro-business coup (+10\%), and the reinstatement of a left-wing populist (-8\%) on the same market.
+We analyze the full sample of politically unstable events for which national-level daily financial data is available.\footnote{13 coups, 8 assassinations, 15 forced resignations, and 11 public protests.}  Like previous research, we find that all types of political instability in our sample cause large increases in financial volatility.
+However, we find that capital flows are large and positive (+4\%) following resignations and negative and smaller in magnitude following assassinations and coups (-2\%).
+We also find that the failed pro-business 2002 Venezuelan coup caused large positive capital inflows (+10\%), followed by immediate capital flight (-8\%) following the reinstatement of a left-wing populist.
 
 Our primary contributions are empirical and methodological.
-Empirically, we provide the first estimates of financial market reactions disaggregated by type of political instability.
-We show that while political instability concerns investors, it does not systematically depress investment.
-Investors recognize when instability may be in their favor.
-The capital flows we document are not insubstantial---in many cases they represent larger shocks than the 2008 stock market crash.
-Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios in situations where an obvious control portfolio is not present.
-We do not view theoretical development as our main contribution, but find evidence that authoritarian regime changes are more likely to lead to negative returns, and that leaders who are clearly pro-business can be rewarded by investors, even if they use extra-judicial methods to take power.
+Empirically, we provide the first estimates of capital market reactions disaggregated by type of political instability, and show that instability does not systematically depress investment.
+The capital flows we document are not insubstantial---in many cases they represent larger shocks than the 2008 stock market crash on their respective domestic economies.
+Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios when a control candidate is not present.
+Theoretically, we find evidence that authoritarian regime changes are more likely to lead to negative returns, but that leaders who are clearly pro-business can be rewarded by financial markets, even if they use extra-judicial methods to take power.
+
+%Investors recognize when instability may be in their favor.
 
@@
 Coups can be democratic or autocratic.
-These differences are often overlooked in past studies, which have proxied for instability using the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or combined events into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
+These differences are often overlooked in past studies, which have proxied for instability using the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or combined events into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.
+By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
+
+% \footnote{These studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.}
 
@@
 
-Different types of regime changes may therefore have disparate effects on markets and/or economic growth.
-Previous research suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro-market than the regime they replace.
+%Different types of regime changes may therefore have disparate effects on markets and/or economic growth.
+
+Previous research therefore suggests that coups should on average cause negative financial flows, but sometimes lead to positive flows when the coup's instigators are more pro-market than the regime they replace.
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
@@
 
-Financial data is from the Global Financial Data database---the longest available daily time series of stock prices.
+%---the longest available daily time series of stock prices
+
+Financial data is from the Global Financial Data database.
 We collect national stock index data for every country in which there was a coup, assassination, or resignation and daily financial data is available.\footnote{The list of failed assassinations are from \citet{jones2009hit}.
@@
 
-Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
+Political data are drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook.
 We form a list of ``irregular'' regime changes from successful coups,\footnote{For example, \citet[p.
@@
 We supplement the CSP data with Archigos Version 4.1 leadership data, which allows us to identify some additional cases of coups, assassinations, and protests.
-A list of the political events in our dataset and whether they resulted in democratic or autocratic shifts is shown in \autoref{tab:regime-changes}.
+A list of the political events in our dataset and whether they were democratic or autocratic shifts is shown in \autoref{tab:regime-changes}.
 
@@
 We rely on common third-party classifications to minimize the possibility our results are driven by our own classifications.
-The one exception is that we separately analyze the 2002 failed coup  in Venezuela, as it provides a natural test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
+The exception is that we separately analyze the 2002 failed coup  in Venezuela, as it provides a test of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
 
@@
 
-To examine the effect of irregular regime changes on financial volatility, we use a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
+To estimate the effect of irregular regime changes on financial volatility, we use a generalized autoregressive conditional heteroskedasticity (GARCH) model estimated using 1000 pre-event days, the event day and 1000 post-event days.
 As in \citet{jensen2005market} and \citet{leblang2005government}, we use the GARCH (1,1) specification.
@@
 
-To estimate the magnitude and direction of the effect of irregular regime changes on stock returns, we follow standard event study methodology \citep{mackinlay1997event, campbell1997econometrics}.
+%  the magnitude and direction of
+
+To estimate the effect of irregular regime changes on financial flows, we follow standard event study methodology \citep{mackinlay1997event, campbell1997econometrics}.
 Normal performance is measured with a constant mean return model,
@@
 The ARs are then used to calculate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).}
-
-The event date is the first trading day a market could react to news of the event.
-$(0,\tau-1)$ denotes the $\tau$-day period beginning with the event day and $(-1,\tau)$ denotes the negative $\tau$-day period beginning with the day prior to the event day.
-We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$) and 19 days $(0,19$), and the pre-event windows $(-1,-7$) and $(-1,-20$).
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).} The event date is the first trading day a market could react to news of the event.
 
@@
 
-We do not use a market model (where a market index is included as a control) to maximize the number of observations and because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we combine synthetic control methods \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
+We do not use a market model (where a market index is included as a control) because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we combine synthetic control methods \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
 We create a ``synthetic'' control portfolio for each event, where each country is given a weight representing its influence in the control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-
-Formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+A more formal exposition of the methodology can be found in \nameref{subsec: synth}.
+
+% to maximize the number of observations and
 
@@
 
+We first confirm that our sample of events shows the same increases in volatility suggested by previous literature.
 \autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates across all irregular regime changes for 250 trading days prior to and 250 days after each event.
 Volatility stays between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations.
+There is an enormous volatility jump on the day of the regime change, with levels then decreasing to normal within a month of the event.
+
+%Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations.
 This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
-
-\begin{figure}[!htb]
-\includegraphics[scale = 0.75]{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
-\end{figure}
 
@@
 Event day ARs for the 1970 coup in Argentina, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
-Moreover, all of these cases except Thailand have negative post-event CARs and pre-event CARs that are statistically indistinguishable from zero.
+Moreover, all of these cases except Thailand have negative pre-event CARs that are statistically indistinguishable from zero, suggesting they were not foreseen.
 In all of these cases, the coup either overthrew a democratically elected government or changed governance from one military ruler to another.
 The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.
+
+%  post-event CARs and
 
@@
 
-These results are consistent with our hypothesis that assassinations should have a negative effect as they occur seemingly at random and increase uncertainty.
+These results are consistent with our hypothesis that assassinations should have a negative effect as they occur seemingly at random\footnote{There is no evidence of post or pre-event CARs in almost any of the assassinations, consistent with the expectation that assassinations are typically not predictable.} and increase uncertainty.
 While the mean effect of assassinations is negative, it is smaller in magnitude than for coups.
@@
 
-There is no evidence of post or pre-event CARs in almost any of the assassinations.
-This is consistent with expectations as assassinations are typically not predictable.
-As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days.
+%As with coups, the number of days that it took the stock market to rebound to pre-event levels is fairly low.\footnote{One exception is the assassination of William Mckinley in which the stock market didn't fully recover for 963 days.
 However, this was likely caused by the Panic of 1901, which began when the stock market crashed on May 17th, 1901, and not by McKinley's death.}
@@
 Protests preceding these resignations may therefore also affect financial markets\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.}, so we analyze all protests that preceded the resignations in \nameref{subsec: Public Protests}.
-Including directionality, public protests have no effect on stock returns as some increase stock prices while others decrease them (see \autoref{tab:protest-stocks}).
-In absolute terms, stock returns are approximately 1.5\% higher during public protests.
+Including directionality, public protests appear to have no effect on stock returns as some increase stock prices while others decrease them (see \autoref{tab:protest-stocks}), but in absolute terms,  returns are approximately 1.5\% higher during public protests.
 
@@
 
-While markets may generally dislike political instability, the immediate effect of regime changes on markets may not always be unpredictable.
+While investors may generally dislike political instability, the immediate effect of regime changes on financial flows may not always be unpredictable.
 For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation \citep{przeworski1982structure, north1989constitutions, svensson1998investment}.
 Investors may also have priors about a new leader's economic ideology.
-Two mechanisms that could be driving positive or negative returns may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
-
-We therefore first aggregate the events in our sample by whether they resulted in an authoritarian or democratic shift.\footnote{As defined by the Polity project.} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while democratic shifts are perceived positively (see \autoref{tab:AR-dem}).
+Two mechanisms that may therefore drive the direction of capital flows are: (1) whether the regime change is associated with an authoritarian or democratic shift, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
+
+We therefore aggregate the events in our sample by whether they resulted in an authoritarian or democratic shift.\footnote{As defined by the Polity project.} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while democratic shifts are perceived positively (see \autoref{tab:AR-dem}).
 Of ten authoritarian shifts, only two result in positive CARs, and neither are significantly different from zero.
@@
 
-A similar aggregated analysis is not possible for shifts from pro or anti business leaders, as examples of clear shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
+A similar analysis is not possible for pro and anti business shifts, as examples of clear shifts in leader economic ideology do not exist in our sample.\footnote{Based on matching our cases with codings from the The Ideology of Heads of Government (HOG) database, as well as surveys of news reports on the day of each event.
 In all cases, no clear economic ideological shift can be identified.} We therefore look outside our sample and examine a (failed) pro-business coup followed by the reinstatement of a socialist leader: the 2002 failed coup against Hugo Chavez in Venezuela.
@@
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See Appendix A for a more formal explanation.}
-
-Third, non-parametric statistical techniques (sign and rank tests) free from distributional assumptions address concerns about inferences from small sample sizes.\footnote{See section 8 in \citet{mackinlay1997event} for more details.} \autoref{tab:non-parametric} compares event day ARs and the absolute value of all combined returns (since some events increase returns while others decrease them) to the synthetic control portfolio using the non-parametric methods discussed above.
+The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+
+Third, non-parametric statistical techniques (sign and rank tests) free from distributional assumptions address concerns about inferences from small sample sizes.
+\autoref{tab:non-parametric} compares event day ARs and the absolute value of all combined returns (since some events increase returns while others decrease them) to the synthetic control portfolio using the non-parametric methods discussed above.
 The synthetic control and small sample tests suggest that the main results are not a result of deviations from normality or confounding world events (see \nameref{subsec: robustness appendix} for a full discussion).
+
+% \footnote{See section 8 in \citet{mackinlay1997event} for more details.}
 
@@
 
-Conventional theory suggests markets dislike political instability.
+Conventional theory suggests political instability causes capital flight.
 We show that this is not always the case.
-Unexpected changes in ruler virtually always increase market volatility, but returns are not always negative.
-Markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
+Unexpected changes in ruler virtually always increase volatility, but returns are not always negative.
+Capital markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
 
@@
 We show that market returns following resignations are large and positive on average, but negative and smaller in magnitude following assassinations and coups.
-We also find evidence that investors tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost markets if the instigators are clearly pro-business.
+We also find evidence that capital markets tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost markets if the instigators are clearly pro-business.
 
@@
 First, more research is needed to identify the pro and anti market characteristics of regime changes.
-Second, more work is needed to determine the extent to which stock market returns translate to broader economic development outcomes.
+Second, more work is needed to determine the extent to which financial market flows translate to broader economic development outcomes.
 It remains unclear whether the direction of the effects of different types of regime changes on outcomes such as economic growth, investment, debt, inflation, infant mortality, and years of schooling are consistent with their stock market effects, or if investor perceptions are at odds with certain development goals.
@@
 
+\subsection{Synthetic control methods} \label{subsec: synth}
+
+Formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
+
+\newpage
+
+\subsection{Volatility} \label{subsec: volatility}
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.75]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
+\newpage
+
 \subsection{Event-level estimates: coups} \label{subsec: coups appendix}
@@
 \autoref{tab:AR-coups} contains all coups presented in \autoref{tab:regime-changes}, with the exception of the Argentinian coup of March 24, 1976 which is excluded from our analysis because the stock market remained closed for twelve days following the event.\footnote{Treating this twelve day period as a single day CARs results in a positive abnormal return of 58\%, a fluctuation that seems qualitatively unreasonable.}
+
+ $(0,\tau-1)$ denotes the $\tau$-day period beginning with the event day and $(-1,\tau)$ denotes the negative $\tau$-day period beginning with the day prior to the event day.
+We present results for the sum of abnormal returns over the post-event windows of the event date only $(0,0$), the event date plus 6 days $(0,6$) and 19 days $(0,19$), and the pre-event windows $(-1,-7$) and $(-1,-20$).
 

### 2021-11-16 doc/regime_changes_note.tex
Additional edits to note draft

@@
 Economies are now global, financialized, and integrated, with domestic economies intrinsically linked to international investment.
-Political instability is negatively correlated with investment, financial development, and GDP growth \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, as well as associated with increases in stock market variance \citep{leblang2005government, jensen2005market, liu2015economic}.
+However, political instability appears to jeopardize access to capital---instability is negatively correlated with investment, financial development, and GDP growth \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, as well as associated with increases in stock market variance \citep{leblang2005government, jensen2005market, liu2015economic}.
 
@@
 
-However, how different types of political instability affect a country's access to capital remains unknown.
-In contrast to the aforementioned cross country studies, we therefore separately examine the effect of various types of instability (coups, resignations, assassinations, and protests) on domestic access to financial capital.
-Specifically, we examine whether changes in financial capital flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
+However, how different \textit{types} of political instability affect domestic capital access remains unclear.
+In contrast to the aforementioned cross country studies, we therefore separately examine the effect of different types of instability on domestic firms' access to financial capital.
+Specifically, we examine whether changes in financial flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
 democratic and pro vs.
@@
 
-To test our concept, we examine shifts in capital market flows surrounding politically unstable domestic events.
+To test our concept, we examine changes in market returns surrounding politically unstable domestic events.
 Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
@@
 We analyze the full sample of politically unstable events for which national-level daily financial data is available.\footnote{13 coups, 8 assassinations, 15 forced resignations, and 11 public protests.}  Like previous research, we find that all types of political instability in our sample cause large increases in financial volatility.
-However, we find that capital flows are large and positive (+4\%) following resignations and negative and smaller in magnitude following assassinations and coups (-2\%).
-We also find that the failed pro-business 2002 Venezuelan coup caused large positive capital inflows (+10\%), followed by immediate capital flight (-8\%) following the reinstatement of a left-wing populist.
+However, we find that market returns are large and positive (+4\%) following resignations and negative and smaller in magnitude following assassinations and coups (-2\%).
+We also find that the failed pro-business 2002 Venezuelan coup caused large positive market returns (+10\%), followed by immediate capital flight (-8\%) following the reinstatement of a left-wing populist.
 
 Our primary contributions are empirical and methodological.
-Empirically, we provide the first estimates of capital market reactions disaggregated by type of political instability, and show that instability does not systematically depress investment.
-The capital flows we document are not insubstantial---in many cases they represent larger shocks than the 2008 stock market crash on their respective domestic economies.
+Empirically, we provide the first estimates of the effects of different types of political instability on domestic capital access, and show that instability does not systematically depress investment.
+The capital flows we document are not insubstantial---they are in many cases larger shocks than the 2008 stock market crash on their respective domestic economies.
 Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios when a control candidate is not present.
@@
 
-Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
-But if market returns reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
-Investors may view even a coup as a ``positive'' event if the current regime is anti-business or anti-global.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}, and increases in volatility \citep{irshad2017relationship, bialkowski2008stock, leblang2005government, jensen2005market, liu2015economic}.
+But if capital flows reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
+For example, capital access may increase in response to a coup if the current regime is anti-business or anti-global.
 
@@
 
-Not all regime changes are equivalent.
-Some regime changes---e.g., the resignation of an ineffective leader---may foreshadow better policy.
+Not all irregular regime changes are equivalent.
+Some---e.g., the resignation of an ineffective leader---may foreshadow better policy.
 Assassinations can occur seemingly at random, and a successor may be unclear.
@@
 These differences are often overlooked in past studies, which have proxied for instability using the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or combined events into single indices \citep{alesina1996income, venieris1986income, gupta1990economics, jong2009measurement}.
-By contrast, we estimate effects separately for coups, assassinations, resignations, and protests.
 
@@
 
-Debate also exists on the subject of ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
-Most research suggests ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+Debate also exists on ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
+Most research suggests these are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
 Others argue the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the expected impact of coups is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
@@
 
-Previous research therefore suggests that coups should on average cause negative financial flows, but sometimes lead to positive flows when the coup's instigators are more pro-market than the regime they replace.
+Previous research therefore suggests coups should on average cause capital flight, but lead to positive flows if the coup's instigators are more pro-market than the regime they replace.
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
-By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader.
+By contrast, resignations may be viewed positively on average, as they often signal the departure of an ineffective leader.
 
@@
 The ARs are then used to calculate cumulative abnormal returns (CARs) between event day $\tau_1$ and event day $\tau_2$: $CAR(\tau_1,\tau_2)=\sum_{\tau=\tau_1}^{\tau_2}AR_{i\tau}$.
-Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{It is appropriate to use the standard normal distribution to calculate test statistics because the length of the estimation window is sufficiently long (250 trading days).} The event date is the first trading day a market could react to news of the event.
+Standard errors and p-values are calculated using asymptotic t-statistics as in \citet{mackinlay1997event}.\footnote{This is appropriate because the length of the estimation window is sufficiently long (250 trading days).} The event date is the first trading day a market could react to news of the event.
 
@@
 
-We do not use a market model (where a market index is included as a control) because our unit of analysis \textit{is} the country-wide market index (not firms).\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we combine synthetic control methods \citep{abadie2003economic, abadie2010synthetic} with event study estimation.
-We create a ``synthetic'' control portfolio for each event, where each country is given a weight representing its influence in the control portfolio.
+We do not use a market model (where a market index is included as a control) as our unit of analysis \textit{is} the country-wide market index (i.e., not a firm).
+To address concerns regarding use of a constant mean return model, we combine synthetic control methods \citep{abadie2010synthetic} with event study estimation.
+We create a ``synthetic'' control portfolio for each event, where each country is given a weight representing its influence in the portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+The possible countries in the control portfolio are all countries listed in \autoref{tab:stock-list}.
 A more formal exposition of the methodology can be found in \nameref{subsec: synth}.
 
+This interrupted time series approach implies that the ``control group'' being compared against is not, for example, regular regime changes or failed regime changes, but the expected returns in the same country on the same day in a but-for world in which no regime change occurred.
+We report abnormal returns separately for coups, assassinations and resignations.
+However, each event CAR is by itself also a valid causal estimate of the effect of a specific regime change.
+
 % to maximize the number of observations and
@@
 
-We first confirm that our sample of events shows the same increases in volatility suggested by previous literature.
+We first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
 \autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates across all irregular regime changes for 250 trading days prior to and 250 days after each event.
@@
 
-The average coup has a $-2.1\%$ event day AR.
-Event day ARs for the 1970 coup in Argentina, the 1991 coup in Thailand, the 1992 coup in Peru, and the 1999 coup in Pakistan are all negative and statistically different than zero.
+The average coup has a -2.1\% event day AR.
+ARs for the 1970 coup in Argentina,  1991 coup in Thailand, 1992 coup in Peru, and 1999 coup in Pakistan are all negative and significantly different than zero.
 Moreover, all of these cases except Thailand have negative pre-event CARs that are statistically indistinguishable from zero, suggesting they were not foreseen.
 In all of these cases, the coup either overthrew a democratically elected government or changed governance from one military ruler to another.
-The initial negative reaction followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.
+This initial capital flight followed by additional post-event negativity is consistent with the expected market reaction from a successful authoritarian coup followed by post-event consolidation of power.
 
@@
 In fact, by 1973 Argentina had transitioned to a democracy.\footnote{Based on Center for System Peace Polity IV polity score of 6.
-Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the country's prime minister postponed general elections, itself a democratically subversive action.
+Values of 6-10 are defined as democracies.} The 2002 coup in Nepal resulted in a monarchical restoration, but occurred after the prime minister postponed general elections, itself a democratically subversive action.
 
@@
 
-Like the majority of coups, we find that assassinations decrease stock prices (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-coups}).
+Like the majority of coups, we find that assassinations lead to capital flight (see \autoref{fig:mean-car-by-regime-change} and \autoref{tab:AR-coups}).
 The mean event day abnormal return is negative and statistically different than zero.
@@
 
-These results are consistent with our hypothesis that resignations may lead to positive returns as they typically occur due to poor performance and/or loss of authority.
+These results are consistent with our hypothesis that resignations may lead to increased capital access as they typically occur due to poor performance and/or loss of authority.
 Among our sample of events, leaders were ousted following loss in conflict/war, anti-authoritarian protest, corruption scandals, Supreme Court ruling against unconstitutional actions, contested elections, and abuse of power.
@@
 The resignations analyzed encompass leaders who left office because of poor performance, public discontent and popular protests.
-Protests preceding these resignations may therefore also affect financial markets\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.}, so we analyze all protests that preceded the resignations in \nameref{subsec: Public Protests}.
-Including directionality, public protests appear to have no effect on stock returns as some increase stock prices while others decrease them (see \autoref{tab:protest-stocks}), but in absolute terms,  returns are approximately 1.5\% higher during public protests.
+Protests preceding these resignations may therefore also affect capital access,\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} so we analyze all protests that preceded the resignations in \nameref{subsec: Public Protests}.
+Including directionality, public protests appear to have no effect on returns as some increase stock prices while others decrease them (see \autoref{tab:protest-stocks}), but in absolute terms, returns are approximately 1.5\% higher during public protests.
 
@@
 Of the two negative CARs, one is not significantly different from zero, and the other is associated with a forced market closure that lasted 17 days.
+While this evidence is suggestive, it comports with previous research showing that political risk to markets declines with higher levels of democracy \citep{lehkonen2015democracy}.
 
@@
 The 0\% 10-day CAR preceding the coup implies that investors were completely unaware of the coup plot, increasing our confidence that the abnormal returns capture the true effect of the regime changes.
-This failed coup demonstrates a large positive market reaction to the attempted overthrow of a socialist leader, and an equally large negative reaction to his reinstatement.
+This failed coup demonstrates a large influx of capital in response to the attempted overthrow of a socialist leader, and equally large capital flight following his reinstatement.
 The large magnitudes and precision of these effects suggest that investors value transition to a pro-business government regime, regardless of how the regime change is achieved.
@@
 Unexpected changes in ruler virtually always increase volatility, but returns are not always negative.
-Capital markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
+Domestic capital access can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
 
 Despite their frequency, there is little evidence on the economic consequences of various types of political instability.
-We show that market returns following resignations are large and positive on average, but negative and smaller in magnitude following assassinations and coups.
-We also find evidence that capital markets tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost markets if the instigators are clearly pro-business.
+We show that resignations increase capital access on average, but assassinations and coups tend to cause capital flight.
+We also find evidence that capital markets tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost capital access if the instigators are clearly pro-business.
 
@@
 Second, more work is needed to determine the extent to which financial market flows translate to broader economic development outcomes.
-It remains unclear whether the direction of the effects of different types of regime changes on outcomes such as economic growth, investment, debt, inflation, infant mortality, and years of schooling are consistent with their stock market effects, or if investor perceptions are at odds with certain development goals.
+It remains unclear whether the direction of the effects of different types of regime changes on outcomes such as economic growth, investment, debt, inflation, infant mortality, and years of schooling are consistent with their impact on financial flows, or if investor perceptions are at odds with certain development goals.
 

### 2021-11-17 doc/regime_changes_note.tex
Updates to intro, conclusion, and lit review

@@
 \begin{document}
-\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
+\author{Devin Incerti\thanks{Principal Data Scientist, Genentech.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
@@
 \title{\textbf{Are regime changes always bad economics?
-Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, Frances Rosenbluth, and Hikaru Yamagishi for helpful feedback and suggestions.
+Evidence from daily financial data \thanks{We are grateful to P.M.
+Aronow, Matthew Graham, Frances Rosenbluth, and Hikaru Yamagishi for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
@@
 Returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
-The impact of coups tends to be negative (-2\%), but we show that a pro-capitalist coup results in large positive returns.
+The impact of coups tends to be negative (-2\%), but we show that a pro-capitalist coup results in large positive returns (+10\%).
 We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to lead to capital flight than democratic or pro-business changes.
@@
 
-To test our concept, we examine changes in market returns surrounding politically unstable domestic events.
+To test whether there are meaningful differences in capital flows following different types of political instability, we examine changes in stock market returns surrounding politically unstable domestic events.
 Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
@@
 However, we find that market returns are large and positive (+4\%) following resignations and negative and smaller in magnitude following assassinations and coups (-2\%).
-We also find that the failed pro-business 2002 Venezuelan coup caused large positive market returns (+10\%), followed by immediate capital flight (-8\%) following the reinstatement of a left-wing populist.
+We also find that the failed pro-business 2002 Venezuelan coup caused large positive market returns (+10\%), followed by immediate capital flight (-8\%) after the reinstatement of a left-wing populist.
 
 Our primary contributions are empirical and methodological.
+We provide the first estimates of the effects of different types of political instability on domestic capital access.
+We show that instability does not systematically depress investment, and find evidence that authoritarian regime changes are more likely to lead to negative returns, but that leaders who are clearly pro-business can be rewarded by financial markets even if they use extra-judicial methods to take power.
+The capital flows we document are not insubstantial---they are in some cases larger shocks than the 2008 stock market crash on their respective domestic economies.
+Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios when a control candidate is not present.
+
+%Our primary contributions are empirical and methodological.
 Empirically, we provide the first estimates of the effects of different types of political instability on domestic capital access, and show that instability does not systematically depress investment.
@@
 
-\section{Reexamining market response to irregular regime changes}
-
-Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}, and increases in volatility \citep{irshad2017relationship, bialkowski2008stock, leblang2005government, jensen2005market, liu2015economic}.
+\section{Reexamining capital response to political instability}
+
+Stable capital flows are highly important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
+High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth \citep{koepke2019drives}.
+
+Conventional theory and cross-country empirical evidence suggests that political instability increases country risk and therefore depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}, and increases volatility \citep{irshad2017relationship, bialkowski2008stock, leblang2005government, jensen2005market, liu2015economic}.
 But if capital flows reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
@@
 We show that this is not always the case.
-Unexpected changes in ruler virtually always increase volatility, but returns are not always negative.
+Unexpected changes in ruler virtually always increase volatility, but when political instability is broken down into types, evidence emerges that some types of instability increase capital access while other types lead to capital flight.
 Domestic capital access can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
 
-Despite their frequency, there is little evidence on the economic consequences of various types of political instability.
+%Despite their frequency, there is little evidence on the economic consequences of various types of political instability.
+
 We show that resignations increase capital access on average, but assassinations and coups tend to cause capital flight.

### 2021-11-17 doc/archive/paper.tex
Additional changes to note manuscript and organization
- Minor changes to abstract, theory, and conclusion.
- Created anonymous note manuscript.
- Moved old .tex files to archive folder.

--- 2021-06-29 doc/regime_changes_manuscript.tex
@@
 \begin{document}
-%\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
+\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
@@
 trevor.incerti@yale.edu.}}
-\title{\textbf{Are regime changes always bad for markets? Evidence from daily financial data}} 
+\title{\textbf{Are regime changes always bad economics?
+Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
+Authors are listed in alphabetic order, implying equal authorship.
+Any and all errors are our own.}}}
 \date{\today}
@@
 
-We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project.} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
+We first attempt to explore these mechanisms by aggregating all of the events in our sample by whether they resulted in a shift in an authoritarian or democratic direction.\footnote{As defined by the Polity project} We find suggestive evidence that regime changes associated with authoritarian shifts are on average perceived negatively by investors (see \autoref{tab:AR-auth}), while those that move governance in a democratic direction are on average perceived positively (see \autoref{tab:AR-dem}).
 We refer to this evidence as suggestive despite statistical significance due to the small sample of cases which fit these criteria, particularly with regard to democratic shifts.
@@
 
-\clearpage
-\pagebreak
-
-\pdfbookmark[1]{References}{References}
-\bibliography{bibliography}
-
 \newpage
@@
 
+\clearpage
+\pagebreak
+
+\pdfbookmark[1]{References}{References}
+\bibliography{bibliography}
+
 \end{document}

### 2021-11-17 doc/regime_changes_note_anonymous.tex
Additional changes to note manuscript and organization
- Minor changes to abstract, theory, and conclusion.
- Created anonymous note manuscript.
- Moved old .tex files to archive folder.

--- 2021-11-17 doc/regime_changes_note.tex
@@
 \begin{document}
-\author{Devin Incerti\thanks{Principal Data Scientist, Genentech.
+%\author{Devin Incerti\thanks{Principal Data Scientist, Genentech.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
@@
 trevor.incerti@yale.edu.}}
-\title{\textbf{Are regime changes always bad economics?
-Evidence from daily financial data \thanks{We are grateful to P.M.
-Aronow, Matthew Graham, Frances Rosenbluth, and Hikaru Yamagishi for helpful feedback and suggestions.
-Authors are listed in alphabetic order, implying equal authorship.
-Any and all errors are our own.}}}
+\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
 \date{\today}
@@
 We challenge this consensus by showing that instability does not systematically depress access to financial capital.
-Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
+Using an event study approach, we examine daily returns of national financial indices in every country that experienced an irregular regime change subject to data availability.
 Returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
 The impact of coups tends to be negative (-2\%), but we show that a pro-capitalist coup results in large positive returns (+10\%).
-We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to lead to capital flight than democratic or pro-business changes.
-The immediate impact of political instability on capital access is therefore dependent on the type of regime change and its expected impact on economic policy.
+We also find evidence that authoritarian or anti-capitalist regime changes are more likely to lead to capital flight than democratic or pro-business changes.
+The immediate impact of political instability on capital access is therefore dependent on the type of regime change and its expected impact on future growth.
 
@@
 Conventional theory and cross-country empirical evidence suggests that political instability increases country risk and therefore depresses financial returns and economic growth \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}, and increases volatility \citep{irshad2017relationship, bialkowski2008stock, leblang2005government, jensen2005market, liu2015economic}.
-But if capital flows reflect investor expectations about future economic growth and returns, such hypotheses may be too simplistic.
+But if capital flows reflect expectations of future economic growth and returns, such hypotheses may be too simplistic.
 For example, capital access may increase in response to a coup if the current regime is anti-business or anti-global.
@@
 
-Debate also exists on ``good coups''---i.e., coups that lead to democratization or economic liberalization---and their effect on economic growth.
+Debate also exists on coups that lead to democratization or economic liberalization and their effect on economic growth.
 Most research suggests these are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
-Others argue the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the expected impact of coups is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
-But while ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
+Others argue the negative effects of uncertainty dominate any positive effects \citep{alesina1996political}, or that the impact of coups is neutral as some enhance growth while others depress it \citep{londregan1990poverty}.
+But while these ``good coups'' may be the minority, they have become more frequent \citep{marinov2014coups} and could have positive economic effects \citep{meyersson2016political, girardi2018institution}.
+Regular regime changes such as elections have been found to boost markets following opposition victories in weak democracies \citep{pantzalis2000political}, and coups may exhibit the same pattern.
 
@@
 
-Previous research therefore suggests coups should on average cause capital flight, but lead to positive flows if the coup's instigators are more pro-market than the regime they replace.
+Previous research therefore suggests coups may on average cause capital flight, but lead to positive flows if the coup's instigators are more democratic or pro-market than the regime they replace.
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
@@
 
-This interrupted time series approach implies that the ``control group'' being compared against is not, for example, regular regime changes or failed regime changes, but the expected returns in the same country on the same day in a but-for world in which no regime change occurred.
+This interrupted time series approach implies that the ``control group'' being compared against is not, for example, regular regime\footnote{Past studies have examined market reactions to regular regime changes.
+This work finds that volatility increases around elections---particularly close elections and those that lead to a change in government political orientation \citep{bialkowski2008stock} ---and that positive returns tend to precede elections \citep{pantzalis2000political}.} changes or failed regime changes, but the expected returns in the same country on the same day in a but-for world in which no regime change occurred.
 We report abnormal returns separately for coups, assassinations and resignations.
@@
 Of the two negative CARs, one is not significantly different from zero, and the other is associated with a forced market closure that lasted 17 days.
-While this evidence is suggestive, it comports with previous research showing that political risk to markets declines with higher levels of democracy \citep{lehkonen2015democracy}.
+While this evidence is suggestive, it comports with previous research showing that political risk to markets declines with higher levels of democracy \citep{lehkonen2015democracy}, and that markets tend to react favorably to opposition victories in weak democracies \citep{pantzalis2000political}.
 
@@
 Unexpected changes in ruler virtually always increase volatility, but when political instability is broken down into types, evidence emerges that some types of instability increase capital access while other types lead to capital flight.
-Domestic capital access can be given a boost when a new regime is expected to offer a more democratic or pro-business environment.
 
@@
 
-We show that resignations increase capital access on average, but assassinations and coups tend to cause capital flight.
+We examine changes in stock market returns surrounding politically unstable domestic events to show that resignations increase capital access on average, but assassinations and coups usually cause capital flight.
 We also find evidence that capital markets tend to prefer democratic regime changes to authoritarian shifts, but that even democratically subversive coups can boost capital access if the instigators are clearly pro-business.

### 2021-12-13 doc/regime_changes_note_anonymous.tex
Reduced appendix to under 10 pages in manuscript

@@
 \vspace{-5pt}
-\footnotesize
+\scriptsize
 \begin{center}
@@
 \begin{centering}
-\includegraphics[width = 15cm]{../figs/daily_mean_absreturn.pdf}
+\includegraphics[width = 0.6\textwidth]{../figs/daily_mean_absreturn.pdf}
 \caption{Absolute value of daily returns}
@@
 
-\clearpage
-\newpage
-
-\subsection{Synthetic control methods} \label{subsec: synth}
-
-Formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
-Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
-
-\newpage
-
-\subsection{Volatility} \label{subsec: volatility}
-
 \begin{figure}[!htb]
-\includegraphics[scale = 0.75]{../figs/mean-volatility.pdf}
+\centering
+\includegraphics[width = 0.6\textwidth]{../figs/mean-volatility.pdf}
 \caption{Mean of volatility estimates from GARCH(1,1) models}
@@
 
-\newpage
-
-\subsection{Event-level estimates: coups} \label{subsec: coups appendix}
+%\clearpage
+%\newpage
+
+\subsection{Synthetic control methods} \label{subsec: synth}
+
+Formally, let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
+Then $\boldsymbol{W}^*$ is chosen to minimize $(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})'\boldsymbol{V}(\boldsymbol{X}_1-\boldsymbol{X}_0\boldsymbol{W})$ subject to $w_i\geq0$ $(i = 1,2,\ldots,N-1)$ and $\sum_i^{N-1} w_i = 1$, and the vector $\boldsymbol{V}$ is chosen so that stock returns for the control portfolio during the estimation window are are close as possible to the event country.\footnote{See \citet{abadie2003economic} for further details.}
+
+%\newpage
+
+%\subsection{Volatility} \label{subsec: volatility}
+
+%\newpage
+
+\subsection{Event-level estimates} \label{subsec: coups appendix}
 
@@
 
-\subsection{Event-level estimates: assassinations} \label{subsec: ass appendix}
+%\subsection{Event-level estimates: assassinations} \label{subsec: ass appendix}
 
@@
 
-\subsection{Event-level estimates: resignations} \label{subsec: resignation appendix}
+%\subsection{Event-level estimates: resignations} \label{subsec: resignation appendix}
 
@@
 
-\newpage
+%\newpage
 
@@
 
-The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
-It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.\footnote{Indeed, corporate investors in the 2013 MIGA \textit{World Investment and Political Risk} ranked civil disturbances as the fourth most concerning type of political risk.} To examine this, we explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
+%The resignations studied in this paper are those in which leaders left office because of poor performance, public discontent and popular protests.
+It is therefore not unreasonable to expect the political actions preceding the resignations to have similarly large effects on financial markets.
+To examine this,
+
+We explore all resignations that were driven by significant popular demonstrations, riots, non-violent civil resistance and other forms of public discontent (see \autoref{tab:protest-list}).\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
 In practice, this is the 2011 Egyptian Revolution and the list of resignations in \autoref{tab:AR-resignations}.}
 
-\begin{table}[H]
+\begin{table}[!htb]
 \caption{List of public protests preceding resignations} \label{tab:protest-list}
 \vspace{-5pt}
-\footnotesize
+\scriptsize
 \begin{center}
@@
 
-A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
+%A recent example of a popular uprising preceding a resignation is the 2011 Egyptian Revolution that resulted in the overthrow of President Hosni Mubarak's regime.\footnote{Abnormal returns for this event are not shown in \autoref{tab:AR-resignations} because the stock market was closed on the day of Mubarak's resignation.} Clashes between security forces and protestors led to the deaths of hundreds of citizens and injuries to thousands more.
 The uprising began on January 25, 2011 when millions of protestors demanded the overthrow of the Egyptian leadership.
 Examples of public discontent included demonstrations, marches, riots, non-violent civil disobedience, and labor strikes.
-
-The short-term impact of the Egyptian Revolution on the economy was disastrous.
+%
+%The short-term impact of the Egyptian Revolution on the economy was disastrous.
 As shown in \autoref{fig:CAR-Egypt}, abnormal returns on the Egyptian Stock Exchange Index (EGX 30) were around -7\% on January 26th and -10\% the day after.
@@
 President Mubarak resigned on February 11, but the market remained closed until March 23, when CARs declined by another 9\%, before rebounding slightly thereafter.
-
-\begin{figure}[!ht]
-\includegraphics{../figs/egypt-revolution-2011.pdf}
-\caption{Cumulative abnormal returns during the Egyptian revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-An important question is whether other popular uprisings have had similar adverse economic consequences.
+%
+%\begin{figure}[!ht]
+%\centering
+%\includegraphics[width = 0.6\textwidth]{../figs/egypt-revolution-2011.pdf}
+%\caption{Cumulative abnormal returns during the Egyptian revolution}
+%\label{fig:CAR-Egypt}
+%\end{figure}
+%
+%An important question is whether other popular uprisings have had similar adverse economic consequences.
 To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data.
@@
 The coefficient on \textit{Protest} barely changes and the absolute value of returns are still about 1.5\% higher during public protests.
-Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
+Finally, column (4) shows that stock volatility is approximately 1 percentage point higher during political movements.
+
+%\footnote{Volatility estimation methodology is described in detail in \nameref{subsec: Volatility}.}
 
@@
 
-\begin{table}[!ht]
+\begin{table}[!htb]
 \caption{Effect of public protests on stock prices} \label{tab:protest-stocks}
 \vspace{-5pt}
-\footnotesize
+\scriptsize
 \begin{center}
@@
 
-\clearpage
-\pagebreak
-\newpage
-
-\subsection{Event-level estimates: democratic vs. authoritarian regime changes}
-
-\begin{table}[!ht]
+%\clearpage
+%\pagebreak
+%\newpage
+
+%\subsection{Event-level estimates: democratic vs. authoritarian regime changes}
+
+\begin{table}[!htb]
 \caption{Abnormal returns following authoritarian regime changes} \label{tab:AR-auth}
 \vspace{-5pt}
-\footnotesize
+\scriptsize
 \begin{center}
@@
 
-\begin{table}[!ht]
+\begin{table}[!htb]
 \caption{Abnormal returns following democratic regime changes} \label{tab:AR-dem}
 \vspace{-5pt}
-\footnotesize
+\scriptsize
 \begin{center}
@@
 
-\clearpage
-\pagebreak
-\newpage
+%\clearpage
+%\pagebreak
+%\newpage
 
@@
 \centering
-\includegraphics[max size={\textwidth}{.8\textheight}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
+\includegraphics[max size={0.75\textwidth}]{../figs/mean-car-by-regime-change-type-placebo.pdf}
 \caption{Event date shifted forward by one year} \label{subfig:mean-car-by-regime-change-placebo}
@@
 \begin{figure}[!htb]
-\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
+\centering
+\includegraphics[width = 0.75\textwidth]{../figs/mean-ar-by-regime-change-type-placebo.pdf}
 \caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
@@
 Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.}
-
-\clearpage
-\pagebreak
-
-\subsection{Graphical depictions of additional events}
+%
+%\clearpage
+%\pagebreak
+
+%\subsection{Graphical depictions of additional events}
 
@@
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
-\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
-\label{fig:AR-Turkey-2016}
-\end{figure}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[scale=0.75]{../figs/turkey_coup_attempt_2016.pdf}
+%\caption{Abnormal returns surrounding the 2016 Turkish coup attempt}
+%\label{fig:AR-Turkey-2016}
+%\end{figure}
 

### 2023-04-26 doc/regime_changes_bp_rr.tex
Create r&r document

--- 2021-11-17 doc/archive/paper.tex
@@
 
+\pagestyle{empty}
+
 \setlength{\mathindent}{1cm}
@@
 \begin{document}
-\author{Devin Incerti\thanks{Senior Data Scientist, Genentech.
+\author{Devin Incerti\thanks{Independent researcher.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
-PhD Candidate in the Department of Political Science, Yale University.
-trevor.incerti@yale.edu.}}
+Assistant Professor, Department of Political Science, University of Amsterdam.
+t.n.incerti@uva.nl.}}
 \title{\textbf{Are regime changes always bad economics?
@@
 Political instability is commonly thought to discourage investment and reduce economic growth.
-However, we find that different types of ``irregular'' regime changes have disparate effects on stock returns.
-Using an event study approach, we examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability.
-We show that abnormal returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
-The impact of coups tends to be negative (-2\%), but examination of the 2002 failed coup against Hugo Chavez reveals returns of +10\%.
-We find suggestive evidence that authoritarian or anti-capitalist regime changes are more likely to be perceived negatively by investors than democratic or pro-business changes.
-The expected direction and magnitude of abnormal returns is therefore dependent on the type of regime change and its expected impact on economic policy.
+We challenge this consensus by showing that instability does not systematically depress investment.
+Using an event study approach, we examine daily returns of national financial indices in every country that experienced an irregular regime change subject to data availability.
+Returns following resignations are large and positive (+4\%), while those following assassinations are negative and smaller in magnitude (-2\%).
+The impact of coups tends to be negative (-2\%), but we show that a pro-business coup results in large positive returns (+10\%).
+We also find evidence that authoritarian or anti-business regime changes are more likely to lead to capital flight than democratic or pro-business changes.
+The immediate impact of political instability on investment is therefore dependent on the type of regime change and its expected impact on future growth.
 
@@
 
-The image of a coup or popular uprising ousting an autocratic ruler and installing a democratic government is an evocative one.
+Economies are now global, financialized, and integrated, with domestic economies intrinsically linked to international investment.
+However, political instability such as coups and other regimes changes appear to jeopardize access to capital.
+Investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
+In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These considerations of political risk are reflected in research showing that political instability is negatively correlated with investment, financial development, and GDP growth \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, as well as associated with increases in stock market variance \citep{leblang2005government, jensen2005market, liu2015economic}.
+Common rationales are that unstable governments act myopically and adopt inefficient policies.
+Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
+
+%The image of a coup or popular uprising ousting an autocratic ruler and installing a democratic government is an evocative one.
 However, both recent events and prior research suggest that coups rarely lead to democracy.
@@
 
-Of course, coups and other regime changes not only impact a country's political environment but its economy as well.
-For instance, investors, multinational firms, development agencies, and aid organizations rank political risk as a top consideration when making investment decisions in emerging markets.\footnote{In the 2013 Multilateral Investment Guarantee Agency (MIGA) \citet{wipr2013} report (the last report published), executives of multinational enterprises (MNEs) ranked political risk as the second most important constraint for foreign direct investment (FDI) in developing countries over the next three years (after macroeconomic instability).
-In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} Common rationales are that unstable governments act myopically and adopt inefficient policies.
-Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
-The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
+%These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
 
-These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+In this study, we examine the impact of ``irregular'' regime changes and public protests on investment in a country's firms.
+However, unlike previous studies, we (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
+Specifically, we examine whether changes in financial flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
+democratic and pro vs.
+anti business shifts.
 
-In this study, we examine the impact of ``irregular'' regime changes and public protests on market performance, but remain agnostic about the direction of the effect.
-Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
-Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
+%Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
 
-In contrast to the aforementioned cross country studies, we conduct our analysis using event studies of daily financial data and provide separate estimates by source of instability.
-Event studies examine the effect of an unexpected event on stock prices \textit{at the time of the event} (i.e.
-a local average treatment effect), and seek to determine if returns at the time of event are abnormal (i.e., systematically different from predicted).
-An ``abnormal return'' therefore reflects the difference between the observed return and the predicted return.
-We use daily data as it allows for more precise measurement of abnormal returns.
-This interrupted time-series approach mitigates the endogeneity problems ubiquitous in the cross country regression approaches---confounding events would need to also occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
+%Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
+
+We also provide methodological advancements when compared to the aforementioned cross country studies.
+Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
+This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.}
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply market-model event studies even when a suitable control portfolio is absent.
 
-We analyze 13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.
-We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.
-We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
+We analyze the full sample of politically unstable events for which national-level daily financial data is available---13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.\footnote{We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.} We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
 Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
@@
 
+Our primary contributions are empirical and methodological.
+We provide the first estimates of the effects of different types of political instability on domestic capital access.
+We show that instability does not systematically depress investment, and find evidence that authoritarian regime changes are more likely to lead to negative returns, but that leaders who are clearly pro-business can be rewarded by financial markets even if they use extra-judicial methods to take power.
+The capital flows we document are not insubstantial---they are in some cases larger shocks than the 2008 stock market crash on their respective domestic economies.
+Methodologically, we (1) employ a method less susceptible to endogeneity concerns than previous studies, and (2) integrate synthetic control and event study methods to allow for control portfolios when a control candidate is not present.
+
 \singlespacing
@@
 
-Conventional theory and cross-country empirical evidence suggests that political instability depresses financial returns \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
+Stable capital flows are highly important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
+High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth \citep{koepke2019drives}.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
 However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
@@
 
-Different types of regime changes may therefore have disparate effects on markets, just as they may differentially effect overall economic growth.
+Different types of regime changes may therefore have disparate effects on investment, just as they may differentially effect overall economic growth.
 Taken together, the theory and research above suggests that coups should on average lead to negative returns, but sometimes lead to positive returns when the coup's instigators are clearly more pro market than the regime they replace.
@@
 Our empirical findings validate these predictions.
-We find that the type of political event and its expected impact on economic policy determines the direction of abnormal returns.
+We find that the type of political event and its expected impact on economic policy determines the direction of investment.
 Events expected to lead to more stable governance, economic liberalization, or democratization (such as willful resignations and coups that overthrow protectionist or leftist autocrats) are associated with positive returns, while those that consolidate authoritarian rule (e.g.
@@
 
-We begin our analysis by studying the effect of irregular regime changes on financial volatility.
+We first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
 Since stock volatility is not directly observable, one must decide how to best estimate volatility.
@@
 \begin{figure}[!ht]
-\includegraphics{../figs/venezuela_coup_attempt_2002.pdf}
+\includegraphics[width = \textwidth]{../figs/venezuela_coup_attempt_2002.pdf}
 \caption{Abnormal returns surrounding the 2002 Venezuelan coup attempt}
@@
 Each country is given a weight which represents its influence in the synthetic control portfolio.
-The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.
-The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.\footnote{See Appendix A for a more formal explanation.}
+The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
 
@@
 
-While conventional wisdom suggests markets dislike the political instability associated with regime changes, we show that this is not necessarily always the case.
+While conventional wisdom suggests investors dislike political instability, we show that this is not necessarily always the case.
 Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
@@
 This paper helps fill the evidence gap by using an event study approach that exploits daily returns of national stock market indices.
-This approach provides well-identified estimates of an economic effect of regime changes that is less susceptible to endogeneity bias than prior cross country studies.
+This approach provides well-identified estimates of the effect of regime changes on investment that is less susceptible to endogeneity bias than prior cross country studies.
 Furthermore, the large sample of political events in our study increases the generalizability of our findings.
@@
 The results are consistent with the idea that perceptions of government competence and changes in government have large impacts on investor confidence.
-But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is less certain.
+But although the effect of regime changes and protests on stock volatility is substantial, the effect on the direction of stock returns is not uniformly negative.
 Abnormal returns following resignations are large and positive (+4\%), abnormal returns following assassinations are negative and smaller in magnitude (-2\%), and abnormal returns following coups also tend to be negative (-2\%).
@@
 
-A preliminary test of mechanisms suggests that democratic regime changes are typically preferable to authoritarian regime changes to investors.
+A test of mechanisms suggests that democratic regime changes are typically preferable to authoritarian regime changes to investors.
 However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that even democratically subversive coups can have positive effects if the instigators are clearly pro-business.
@@
 There may be pro or anti market features of regime changes that are more nuanced than those identified in this paper.
-Similarly, it would be useful to identify additional mechanisms through which regime changes effect stock returns.
+Similarly, it would be useful to identify additional mechanisms through which regime changes effect investment.
 In the case of Chile,  \citet{girardi2018institution} show that increasing stock market valuations were caused by changes in private property rights rather than economic growth prospects or wage costs.
@@
 Such research can help enlarge the body of evidence on the extent to which regime changes cause institutional and political change, and, in turn, have significant consequences for economic development.
+
+\newpage
+
+\pdfbookmark[1]{References}{References}
+\bibliography{bibliography}
 
@@
 
-\subsection{Synthetic Control Portfolio}
+\subsection{Synthetic Control Portfolio}\label{synthetic}
 Let $\boldsymbol{R}_{k}$ be the vector of returns for the event country in the estimation window, $\boldsymbol{R}_{-k}$ be the vector of returns for all other countries in the estimation window, $\boldsymbol{X}_1=(\boldsymbol{R}_{k},\var(\boldsymbol{R}_{k}))$, $\boldsymbol{X}_0=(\boldsymbol{R}_{-k},\var(\boldsymbol{R}_{-k}))$, and $\boldsymbol{W}_{-k}$ be a $((N-1) \times 1)$ vector of weights where $N$ is the number of countries listed in \autoref{tab:stock-list}.
@@
 
-\pdfbookmark[1]{References}{References}
-\bibliography{bibliography}
-
 \end{document}

### 2023-05-17 doc/regime_changes_bp_rr.tex
Add analysis subsetting to insig pre-trends

@@
 \usepackage{lipsum}
+\usepackage{etoc}
 
@@
 
-\setcounter{tocdepth}{1}
+%\setcounter{tocdepth}{1}
 \begin{document}
@@
 
+\newpage
+
+\begin{centering}
+\LARGE
+\textbf{\textit{Supplementary Appendix:}} \\
+ \vspace{0.5cm}
+\textbf{Are regime changes always bad economics? Evidence from daily financial data} \\
+
+\vspace{0.5cm}
+
+\large
+Devin Incerti and Trevor Incerti
+
+\end{centering}
+
 \section{Appendix} \label{sec: appendix}
+
+\localtableofcontents
+\pagenumbering{arabic}% resets `page` counter to 1
+\renewcommand*{\thepage}{A\arabic{page}}
+
+\newpage
 
@@
 
-\subsection{Time-shifted placebo test}
-
-\begin{figure}[!htb]
+\subsection{Additional robustness tests}
+
+\subsubsection{Abnormal returns for events with insignificant 7-day pre-trends only}
+
+\begin{table}[H]
+\caption{Abnormal returns following coups} \label{tab:AR-coups-pre}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-coups-car-pre.txt}
+  \hline
+\ExpandableInput{../tables/artable-coups-car-mean-pre.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{Abnormal returns following assassinations} \label{tab:AR-ass-pre}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-ass-car-pre.txt}
+  \hline
+\ExpandableInput{../tables/artable-ass-car-mean-pre.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{Abnormal returns following resignations} \label{tab:AR-resignations-pre}
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-res-car-pre.txt}
+  \hline
+\ExpandableInput{../tables/artable-res-car-mean-pre.txt}
+   \hline
+   \hline
+\end{tabular*}
+\scriptsize
+Notes: Standard errors are in parentheses.
+``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
+Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\subsubsection{Time-shifted placebo test}
+
+\begin{figure}[H]
 \includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}

### 2023-05-17 code/04-ar.R

@@ -28,6 +28,18 @@ artable.coups <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, coup.index],
 myprint.xtable(artable.coups$car, file = "tables/artable-coups-car.txt")
 myprint.xtable(artable.coups$car.mean, file = "tables/artable-coups-car-mean.txt")
 
+# coups - insignificant 7 day pre-trends only
+coup.index.pre <- which(regime.change$type == "Coup" & regime.change$stock_date != "1977-10-20")
+artable.coups.pre <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, coup.index.pre],
+                          sigma = rc.es$sigma.treat[coup.index.pre], 
+                          dtr = rc.es$dtr.treat[coup.index.pre],
+                          country = regime.change[coup.index.pre, country],
+                          date = regime.change[coup.index.pre, stock_date], 
+                          coup = FALSE)
+
+myprint.xtable(artable.coups.pre$car, file = "tables/artable-coups-car-pre.txt")
+myprint.xtable(artable.coups.pre$car.mean, file = "tables/artable-coups-car-mean-pre.txt")
+
 # assassinations
 ass.index <- which(regime.change$type == "Assassination")
 artable.ass <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, ass.index],
@@ -38,6 +50,20 @@ artable.ass <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, ass.index],
 myprint.xtable(artable.ass$car, file = "tables/artable-ass-car.txt")
 myprint.xtable(artable.ass$car.mean, file = "tables/artable-ass-car-mean.txt")
 
+# assassinations - insignificant 7 day pre-trends only
+ass.index.pre <- which(regime.change$type == "Assassination" &
+                         regime.change$stock_date != "1963-11-22" &
+                         regime.change$stock_date != "1984-11-05")
+
+artable.ass.pre <- ar_table(td = rc.es$td, ar = rc.es$ar.treat[, ass.index.pre],
+                        sigma = rc.es$sigma.treat[ass.index.pre], 
+                        dtr = rc.es$dtr.treat[ass.index.pre],
+                        country = regime.change[ass.index.pre, country],
+                        date = regime.change[ass.index.pre, stock_date])
+
+myprint.xtable(artable.ass.pre$car, file = "tables/artable-ass-car-pre.txt")
[…]

### 2023-05-17 doc/regime_changes_bp_rr.tex
Add eGarch and tGarch volatility estimates

@@
 \title{\textbf{Are regime changes always bad economics?
-Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
+Evidence from daily financial data \thanks{We are grateful to P.M.
+Aronow, Matthew Graham, Frances Rosenbluth, and four anonymous reviewers for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
@@
 
+\begin{figure}[H]
+\includegraphics[scale = 0.75]{../figs/mean-volatility-egarch.pdf}
+\caption{Mean of volatility estimates from exponential GARCH models}
+\label{fig:volatility}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale = 0.75]{../figs/mean-volatility-tgarch.pdf}
+\caption{Mean of volatility estimates from threshold GARCH models}
+\label{fig:volatility}
+\end{figure}
+
 \subsubsection{Abnormal returns for events with insignificant 7-day pre-trends only}

### 2023-05-17 code/05-volatility.R

@@ -22,8 +22,9 @@ for (i in 1:n.rc){
 } 
 nobs <- do.call("c", lapply(dat, nrow))
 
-# GARCH MODEL ------------------------------------------------------------------
-# model spects
+# GARCH MODELS -----------------------------------------------------------------
+# Garch (1,1)
+# model specs
 garch.spec <- ugarchspec(mean.model = list(armaOrder = c(0,0)), 
                          distribution.model = "norm")
 
@@ -35,10 +36,34 @@ for (i in 1:n.rc){
   print(i)
 }
 
+# EGARCH
+# model specs
+egarch.spec = ugarchspec(variance.model=list(model="eGARCH",garchOrder=c(1,1)), 
+                         mean.model=list(armaOrder=c(0,0))) 
+
+# run models
+for (i in 1:n.rc){
+  rc.egarchfit <- ugarchfit(spec = egarch.spec, data = dat[[i]]$dr)
+  dat[[i]]$egarch_volatility <- rc.egarchfit@fit$sigma
+  print(i)
+}
+
+#TGARCH
+tgarch.spec = ugarchspec(variance.model = list(model="fGARCH", submodel="TGARCH", garchOrder=c(1,1)), 
+                           mean.model = list(armaOrder=c(0,0)))
+
+for (i in 1:n.rc){
+  rc.tgarchfit <- ugarchfit(spec = tgarch.spec, data = dat[[i]]$dr)
+  dat[[i]]$tgarch_volatility <- rc.tgarchfit@fit$sigma
+  print(i)
+}
+
 # VOLATILITY PLOTS -------------------------------------------------------------
 dat <- rbindlist(dat, fill = TRUE)
-volatility.mean <- dat[, .(mean_garch_volatility = mean(garch_volatility, na.rm = TRUE)),
-                             by = c("td")]
+
+# GARCH
+volatility.mean <- dat[, .(mean_garch_volatility = mean(garch_volatility, na.rm = TRUE)), by = c("td")]
+
 p.volatility <- 
   ggplot(volatility.mean[td >= -250 & td <= 250],
          aes(x = td, y = mean_garch_volatility)) + 
@@ -49,4 +74,37 @@ p.volatility <-
                      breaks = round(seq(min(1), max(2.5), by = 0.5),1)) +
   theme_classic()
 
-ggsave("figs/mean-volatility.pdf", p.volatility, height = 5, width = 7)
[…]

### 2023-05-17 code/05-volatility.R
Added FiGARCH model

@@ -58,6 +58,18 @@ for (i in 1:n.rc){
   print(i)
 }
 
+#FIGARCH
+figarch.spec <-ugarchspec(variance.model = list(model = "fiGARCH", garchOrder = c(1, 1))) 
+
+for (i in 1:n.rc){
+  rc.figarchfit <- ugarchfit(spec = figarch.spec, data = dat[[i]]$dr)
+  dat[[i]]$figarch_volatility <- rc.figarchfit@fit$sigma
+  print(i)
+}
+
+# FRACTIONAL INTEGRATION -------------------------------------------------------
+
+
 # VOLATILITY PLOTS -------------------------------------------------------------
 dat <- rbindlist(dat, fill = TRUE)
 
@@ -108,3 +120,16 @@ t.volatility <-
 
 ggsave("figs/mean-volatility-tgarch.pdf", t.volatility, height = 5, width = 7)
 
+# FiGARCH
+volatility.mean <- dat[, .(mean_figarch_volatility = mean(figarch_volatility, na.rm = TRUE)),
+                       by = c("td")]
+
+fi.volatility <- 
+  ggplot(volatility.mean[td >= -250 & td <= 250],
+         aes(x = td, y = mean_figarch_volatility)) + 
+  geom_line(color = "grey48") + 
+  xlab("Trading days") + 
+  ylab("Mean volatility") +
+  scale_y_continuous(limits = c(1, 3),
+                     breaks = round(seq(min(1), max(3), by = 0.5),1)) +
+  theme_classic()

### 2023-06-12 doc/regime_changes_bp_rr.tex
Updates to R&R draft

@@
 In this study, we examine the impact of ``irregular'' regime changes and public protests on investment in a country's firms.
-However, unlike previous studies, we (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
+However, unlike previous studies, \textcolor{red}{we theorize that investors will not be uniformly discouraged by sudden regime change, but will instead recognize some politically unstable events as ``good'' for future returns}.
+We therefore (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
 Specifically, we examine whether changes in financial flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
@@
 anti business shifts.
-
-%Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
+\textcolor{red}{Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' or ``bad'' for future profits.
+Importantly, expected future profits may differ from general economic performance, as stock prices only reflect the expected future profits of existing publicly-held firms.}
 
@@
 We also provide methodological advancements when compared to the aforementioned cross country studies.
-Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
+Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the exact time of the event}.
 This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
@@
 
-Stable capital flows are highly important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
+Stable capital flows are important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
 High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth \citep{koepke2019drives}.
-Conventional theory and cross-country empirical evidence suggests that political instability depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
+Conventional theory and cross-country empirical evidence suggests that political instability---as measured by events such as protests, strikes, assassinations, number of regime changes, and ongoing elections---depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
 However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
 
-First, a change in regime may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
+First, a change in regime may be seen as a positive event for future economic performance if the current regime is regarded as anti-business or anti-global.
 Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
-
-An active debate exists on the subject of ``good coups''---i.e.
-coups that lead to democratization or economic liberalization---and their effect on economic growth.
-\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
-\citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-However, most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
-But while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
+For example, there is an active debate on whether ``good coups'' that lead to democratization or economic liberalization can be good for economic growth.
+\citet{alesina1996political} argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions, while \citet{alesina1996income} submit that ``unconstitutional'' regime changes such as coups are worse for economic growth than other types of political instability.
+\citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, but some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
 \citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
-In another study examining the outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
+In another study examining the same outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
 
@@
 
-Second, not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
-However, some regime changes may actually lead to increased stability.
-Resignations, for example, often occur when an ineffective leader steps down.
-Assassinations, by contrast, are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
+\textcolor{red}{Second, it is not necessarily the case that even a sudden, extra-legal, or unexpected regime change will result in higher levels of instability}.
+Not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
+However, resignations often occur when an ineffective leader steps down.
+By contrast, assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
 Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
@@
 
+\textcolor{red}{Third, the theoretical linkage through which political events have an impact on daily stock prices is changes in the broader macroeconomic environment that influence the expected stream of future profits of existing publicly-held firms.
+Examples of expected changes in the macroeconomic environment that can be influenced by sudden political events include: shifts in monetary policy, changes in trade or FDI openness, shifts in regulatory policy, changes in the share of output going to capital, transfer and convertibility restrictions, degree of resource nationalism, and heightened risk of capital expropriation or breach of contracts.
+Not all shocks to the political system will result in similar shifts in these macroeconomic variables depending on the actors involved, their ideological preferences, and their expected ability to enact policy changes.}
+
 Different types of regime changes may therefore have disparate effects on investment, just as they may differentially effect overall economic growth.
@@
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
-By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader.
+By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader and may in fact signal \textit{increased} stability.
+\textcolor{red}{Using immediate, day-of shocks to stock prices as our outcome variable, we investigate the hypothesis that investors will positively update their perceptions of future economic performance when a sudden political event clearly shifts a country in a pro-democratic or pro-business direction, and negatively update when an event merely exacerbates instability or uncertainty.}
 
@@
 military coups), exacerbate poor economic policies, or merely increase policy uncertainty (such as assassinations) have the opposite effect.
+\textcolor{red}{Of course, changes in stock prices reflect investor's \textit{expected} changes in the macroeconomic environment, and these expectations may differ from realized future economic performance.
+Nevertheless, it is clear from our results that even sudden and extra-legal regime changes can be viewed as a ``positive'' event by investors under the right circumstances.}
 
@@
 
-\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
-
-\subsection{Volatility} \label{subsec: Volatility}
-
-We first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
+\section{Estimation strategy} \label{sec: estimation}
+
+\textcolor{red}{We estimate the effect of irregular regime changes on financial flows using an interrupted time series---also known as event study---approach, and examine the impact of political events on stock returns using daily financial data.
+Additional explanation of the theoretical logic of why mean \textit{daily} stock market returns would be influenced by politically unstable events is warranted.
+Event studies rely on the theoretical assumption that investors anticipate the effect of sudden events (e.g., corporate announcements, regulatory policy changes, political events, etc.) on future profitability of a firm or firms in a market, and importantly, that these anticipated changes in profitability are \textit{immediately} reflected in stock market prices.
+The approach therefore implicitly relies on the efficient market hypothesis, or the idea that in an efficient market, stocks instantly incorporate publicly available information into their prices \citep{fama1965behavior, samuelson1965proof}.
+The immediate nature of this effect allows us to use the magnitude and direction of sudden fluctuations in granular daily data as a proxy for investors' expected valuation of the event in terms of future profits.
+This in turn allows us to examine how global financial actors value different kinds of politically unstable events---for example, pro-vs-anti business coups.}
+
+\textcolor{red}{The focus on \textit{immediate} fluctuations in daily financial data implies that we are examining the effect of ``one shot'' regime changes akin to a sudden day-of shock.
+Our estimates therefore capture the effect of these sudden, unexpected shocks on stock prices on the same day of the shock.
+Importantly, this implies that we are not estimating the effect of any larger underlying political conditions surrounding the event, but rather only the immediate event itself, independent of other surrounding conditions.
+Further, as this approach provides an estimate \textit{at the exact time of the event}, confounding events would need to occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.
+We recognize that broader definitions of political instability may encompass broader political volatility over a wider range of time.
+In an attempt to address this concern, we also examine the impact of periods of protest on financial returns in the appendix.}
+
+\textcolor{red}{The key identifying assumption behind our interrupted time-series approach is that the events are unpredicted in an immediate temporal sense.
+In other words, for an event to be plausibly exogenous, the exact timing of the event must be unknown to investors.
+If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the stock during the estimation window.}
+
+\subsection{Volatility} \label{subsec: Volatility_estimation}
+
+Before examining the magnitude and direction of returns, we first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
 Since stock volatility is not directly observable, one must decide how to best estimate volatility.
@@
 In other words, the model predicts that large shocks will be followed by other large shocks.
-
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
-This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
-
-\begin{figure}[!htb]
-\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
-\end{figure}
-
-\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
+\textcolor{red}{As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, and fractionally integrated GARCH models in the appendix}.
+
+\subsection{Abnormal Returns} \label{subsec:abnormal-returns_estimation}
 
@@
 
-\subsection{Coups} \label{subsec: Coups}
+\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
+
+\subsection{Volatility} \label{subsec: Volatility}
+
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+This may suggest that investors sometimes have information about the events before they occur.
+Nonetheless, there is still an enormous volatility jump on the day of the regime change.
+Volatility then decreases to normal levels within a month of the event.
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
+\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
+
+\subsubsection{Coups} \label{subsec: Coups}
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
@@
 
-\subsection{Assassinations} \label{subsec: Assassinations}
+\subsubsection{Assassinations} \label{subsec: Assassinations}
 
@@
 
-\subsection{Resignations} \label{subsec: Resignations}
+\subsubsection{Resignations} \label{subsec: Resignations}
 
@@
 For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
-There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+\textcolor{red}{For coups, there is suggestive evidence of a negative pre-trend in the run up to the event.
+However, the overall 7-day and 20-day pre-trends are both insignificant at conventional levels.
+There is also a much larger jump in negative CARs on the day of the event.
+This therefore implies that even if investors had some expectation of a negative event occurring, they were unaware of its timing, and at worst a portion of the negative change in investment was already priced into the day-of shift.}There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
 

### 2023-06-21 doc/regime_changes_bp_rr.tex
Additional reviewer response updates

@@
 Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
-Each country is given a weight which represents its influence in the synthetic control portfolio.
+\textcolor{red}{This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
+We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.} Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
+\textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are [add percentage difference in magnitude] and never significantly different from zero for coups, assassinations, or resignations (or overall).}
 
@@
 
-While conventional wisdom suggests investors dislike political instability, we show that this is not necessarily always the case.
+While conventional wisdom suggests investors dislike unexpected regime changes, we show that this is not necessarily always the case.
 Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
@@
 These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
+
+\textcolor{red}{Our findings have a number of potential implications for policymakers.
+First, our finding that even democratically subversive irregular regime changes can have a positive impact on investment when the replacement government is clearly pro-business  implies that investor goals and actions may be at odds with regime stability.
+Second, the immediate nature and large magnitude of the financial outflows we observe in the wake of the majority of coups and assassinations suggests that a weakened financial system and economy are likely to accompany these kinds of regime changes.
+More optimistically, however, we also find suggestive evidence that in the event of a democratic extra-legal regime change, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
 

### 2023-07-03 doc/regime_changes_bp_rr.tex
Add charts of individual protest events

@@
 
+In addition, we independently plot the CARs during each period of protest preceding a resignation for each event.\footnote{An expception is the 1998 Yellow Revolution in the Philippines, as markets remained closed from the start of the protest until after Marcos' resignation}.
+This analysis also shows that volatility and the absolute value of returns increase during times of protest, but also reveals that the resignations themselves constitute distinct events that are clearly distinguishable from the general period of protest.
+
 \begin{table}[!ht]
@@
 \end{table}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/bangla-1990.pdf}
+\caption{CARs during the 1998 Indonesian revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/indonesia-1998.pdf}
+\caption{CARs during the 1998 Indonesian revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/phil-2001.pdf}
+\caption{CARs during the 1998 Indonesian revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/argentina-2001.pdf}
+\caption{CARs during the 2001 Argentinian riots}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/ukraine-2004.pdf}
+\caption{CARs during the 2004 Orange Revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/ecuador-2005.pdf}
+\caption{CARs during the 2006 Nepalese Democracy Movement}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/nepal-2006.pdf}
+\caption{CARs during the 2006 Nepalese Democracy Movement}
+\label{fig:CAR-Egypt}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[scale=0.8]{../figs/tunisia-2011.pdf}
+\caption{CARs during the 2011 Tunisian Revolution}
+\label{fig:CAR-Egypt}
+\end{figure}
 

### 2023-07-03 code/07-protests.R

@@ -5,9 +5,12 @@ library("data.table")
 library("plm")
 library("lmtest")
 library("broom")
+library(ggplot2)
+library(rugarch)
 theme_set(theme_minimal())
 
 # EGYPTIAN REVOLUTION ----------------------------------------------------------
+# Model estimation
 egypt.es <-  event_study(ticker = index$ticker, date = index$date, dr = index$dr,
                          event_ticker = "_EFGID",
                     event_window = 20, estimation_window = 200,
@@ -19,6 +22,8 @@ egypt.es <- data.table(date = egypt.es$ar.treat$date, td = egypt.es$ar.treat$td,
                        car = egypt.es$car, car.se = egypt.es$car.se)
 egypt.es[, lcar := car - qnorm(.975) * car.se]
 egypt.es[, ucar := car + qnorm(.975) * car.se]
+
+# Plot 
 p <- ggplot(egypt.es, aes(x = date, y = car)) + geom_line() +
   geom_point(size = .8) +
   geom_ribbon(aes(ymin = lcar, ymax = ucar), alpha=0.2) +
@@ -42,7 +47,294 @@ p <- ggplot(egypt.es, aes(x = date, y = car)) + geom_line() +
                    xend = as.Date("2011-03-23"), 
                    yend = 1.01 * egypt.es[date == as.Date("2011-03-23"), car]),
                arrow = arrow(length = unit(0.01, "npc")))
+
 ggsave("figs/egypt-revolution-2011.pdf", p, height = 5, width = 7)
+
+# INDONESIAN UPRISING ----------------------------------------------------------
+# Model estimation
+indonesia.es <-  event_study(ticker = index$ticker, date = index$date, dr = index$dr,
+                         event_ticker = "_JKSED",
+                         event_window = 20, estimation_window = 200,
+                         event_date = rev[name == "Indonesian Revolution", start_date],
+                         model = "constant", control = FALSE)   
+indonesia.es <- c(indonesia.es, car_prepost(indonesia.es$ar.treat$td, indonesia.es$ar.treat$ar,
+                                            indonesia.es$sigma.treat))
+indonesia.es <- data.table(date = indonesia.es$ar.treat$date, td = indonesia.es$ar.treat$td,  
+                       car = indonesia.es$car, car.se = indonesia.es$car.se)
[…]

### 2023-07-04 doc/regime_changes_bp_rr.tex
Updates to rr manuscript

@@
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply market-model event studies even when a suitable control portfolio is absent.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply a method akin to market-model event studies even when a suitable control portfolio is absent.
 
@@
 In other words, for an event to be plausibly exogenous, the exact timing of the event must be unknown to investors.
-If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the stock during the estimation window.}
+If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the index during the estimation window.}
 
@@
 
-A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns.
+A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns as a robustness check.
 
@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
-As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH and threshold GARCH models can be found in \autoref{fig:egarch} and \autoref{fig:tgarch}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
 Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
@@
 
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for successful assassinations rather than coups.
+The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for assassinations rather than coups.
 Like the majority of coups, there is evidence that assassinations decrease stock prices.
@@
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
-\textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are [add percentage difference in magnitude] and never significantly different from zero for coups, assassinations, or resignations (or overall).}
+\textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are never significantly different from zero for coups, assassinations, or resignations (or overall).}
 
@@
 Second, the immediate nature and large magnitude of the financial outflows we observe in the wake of the majority of coups and assassinations suggests that a weakened financial system and economy are likely to accompany these kinds of regime changes.
-More optimistically, however, we also find suggestive evidence that in the event of a democratic extra-legal regime change, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
+More optimistically, however, we also find suggestive evidence that in the event of a democratic regime change or revolution, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
 
@@
 Research focusing on the mechanisms in other settings would help generalize these findings.
-Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
+\textcolor{red}{Second, it remains unclear how markets react to successful irregular regime change conditional on attempt.
+A future study could therefore examine how markets react to successful assassinations or coups when compared to failed attempts.} Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
 \citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/bangla-1990.pdf}
-\caption{CARs during the 1998 Indonesian revolution}
+\caption{CARs during the 1990 Bangladesh uprising}
 \label{fig:CAR-Egypt}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/indonesia-1998.pdf}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/phil-2001.pdf}
-\caption{CARs during the 1998 Indonesian revolution}
+\caption{CARs during the Philippines Second People Power Revolution}
 \label{fig:CAR-Egypt}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/argentina-2001.pdf}
-\caption{CARs during the 2001 Argentinian riots}
+\caption{CARs during the 2001 Argentine crisis}
 \label{fig:CAR-Egypt}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/ukraine-2004.pdf}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/ecuador-2005.pdf}
-\caption{CARs during the 2006 Nepalese Democracy Movement}
+\caption{CARs during the Ecuadorian Revolution of 2005}
 \label{fig:CAR-Egypt}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/nepal-2006.pdf}
@@
 \begin{figure}[!ht]
+\centering
 \includegraphics[scale=0.8]{../figs/tunisia-2011.pdf}
@@
 \caption{Mean of volatility estimates from exponential GARCH models}
-\label{fig:volatility}
+\label{fig:egarch}
 \end{figure}
@@
 \caption{Mean of volatility estimates from threshold GARCH models}
-\label{fig:volatility}
+\label{fig:tgarch}
 \end{figure}

### 2023-07-05 doc/regime_changes_bp_rr.tex
Add structural breaks analysis

@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH and threshold GARCH models can be found in \autoref{fig:egarch} and \autoref{fig:tgarch}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH, threshold GARCH, and GARCH(1,1) controlling for structural breaks can be found in \autoref{fig:egarch}, \autoref{fig:tgarch}, and \autoref{fig:garch_sb}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
 Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
@@
 
+\begin{figure}[H]
+\includegraphics[scale = 0.75]{../figs/mean-volatility-sb.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models, with adjustment for structural breaks}
+\label{fig:garch_sb}
+\end{figure}
+
 \subsubsection{Abnormal returns for events with insignificant 7-day pre-trends only}

### 2023-07-05 code/09-structural-breaks.R

@@ -1,0 +1,134 @@
+rm(list = ls())
+
+# Libraries
+library("xtable")
+library("data.table")
+library("ggplot2")
+library("rugarch")
+library("changepoint")
+library("strucchange")
+library("tidyverse")
+source("code/func.R")
+
+# Import data
+load("data/data-clean.RData")
+
+# Global options
+theme_set(theme_bw())
+
+# DATA SETUP -------------------------------------------------------------------
+post.days <- pre.days <- 1000
+n.rc <- nrow(regime.change)
+dat <- vector(mode = "list", n.rc)
+for (i in 1:n.rc){
+  dat[[i]] <- index[ticker == regime.change$ticker[i], .(ticker, date, dr)]
+  dat[[i]] <- calc_td(stockdata = dat[[i]], 
+                      event_date = regime.change$stock_date[i])
+  dat[[i]] <- dat[[i]][td >= -pre.days & td <= post.days]
+  dat[[i]] <- dat[[i]][complete.cases(dat[[i]])]
+  dat[[i]]$event_date <- regime.change$stock_date[i]
+  dat[[i]]$event_num <- i
+} 
+nobs <- do.call("c", lapply(dat, nrow))
+
+# EXAMINE CHANGE POINTS --------------------------------------------------------
+# Examine mean across all indices
+index_mean <- index %>% 
+  group_by(date) %>% 
+  summarize(dr = mean(dr)) %>%
+  filter(!is.na(dr))
+
+# Examine change points: mean and variance
+meanvar <- cpt.meanvar(index_mean$dr, method = "PELT")
+plot(meanvar, type = "l", col = "grey", cpt.col = "steelblue2", 
+     xlab = "Date", ylab = "Daily return", cpt.width = 2, ylim = c(-10, 10))
+
+# Loop through all indices: Binary segmentation
+par(mfrow=c(6,6), mai = c(0.3, 0.3, 0.3, 0.3))
+for (i in 1:n.rc){
+  data = dat[[i]]
+  m_binseg <- cpt.mean(data$dr, penalty = "BIC", method = "BinSeg", Q = 5)
+  plot(m_binseg, type = "l", col = "grey", cpt.col = "steelblue2", 
+       xlab = "Date", ylab = "Daily return", cpt.width = 2)
+  abline(v=as.Date(data$event_date[[i]]), col = 'firebrick2')
+}
+
+# Loop through all indices: PELT
[…]

### 2023-07-08 doc/regime_changes_bp_rr.tex
Updates to GARCH figures
Placed all figures on common y-axis scale

--- 2023-07-04 doc/regime_changes_bp_rr.tex
@@
 In other words, the model predicts that large shocks will be followed by other large shocks.
-\textcolor{red}{As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, and fractionally integrated GARCH models in the appendix}.
+\textcolor{red}{As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, fractionally integrated GARCH, and GARCH(1,1) accounting for structural breaks in the time series data in the appendix}.
 
@@
 
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH and threshold GARCH models can be found in \autoref{fig:egarch} and \autoref{fig:tgarch}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH, threshold GARCH, FIGARCH, and GARCH(1,1) controlling for structural breaks can be found in \autoref{fig:egarch}, \autoref{fig:tgarch}, \autoref{fig:figarch}, and \autoref{fig:garch_sb}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
 Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
@@
 
+\subsubsection{Volatility}
+
 \begin{figure}[H]
@@
 \label{fig:tgarch}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale = 0.75]{../figs/mean-volatility-figarch.pdf}
+\caption{Mean of volatility estimates from FIGARCH models}
+\label{fig:figarch}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale = 0.75]{../figs/mean-volatility-sb.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models with adjustment for structural breaks}
+\label{fig:garch_sb}
 \end{figure}

### 2023-07-08 code/05-volatility.R

@@ -67,9 +67,6 @@ for (i in 1:n.rc){
   print(i)
 }
 
-# FRACTIONAL INTEGRATION -------------------------------------------------------
-
-
 # VOLATILITY PLOTS -------------------------------------------------------------
 dat <- rbindlist(dat, fill = TRUE)
 

### 2023-07-08 code/05-volatility.R
Updates to GARCH figures
Placed all figures on common y-axis scale

@@ -79,11 +79,11 @@ p.volatility <-
   geom_line(color = "grey48") + 
   xlab("Trading days") + 
   ylab("Mean volatility") +
-  scale_y_continuous(limits = c(1, 2.5),
-                     breaks = round(seq(min(1), max(2.5), by = 0.5),1)) +
+  scale_y_continuous(limits = c(1, 3),
+                     breaks = round(seq(min(1), max(3), by = 0.5),1)) +
   theme_classic()
 
-#ggsave("figs/mean-volatility.pdf", p.volatility, height = 5, width = 7)
+ggsave("figs/mean-volatility.pdf", p.volatility, height = 5, width = 7)
 
 # EGARCH
 volatility.mean <- dat[, .(mean_egarch_volatility = mean(egarch_volatility, na.rm = TRUE)),
@@ -95,11 +95,11 @@ e.volatility <-
   geom_line(color = "grey48") + 
   xlab("Trading days") + 
   ylab("Mean volatility") +
-  scale_y_continuous(limits = c(1, 2.5),
-                     breaks = round(seq(min(1), max(2.5), by = 0.5),1)) +
+  scale_y_continuous(limits = c(1, 3),
+                     breaks = round(seq(min(1), max(3), by = 0.5),1)) +
   theme_classic()
 
-#ggsave("figs/mean-volatility-egarch.pdf", e.volatility, height = 5, width = 7)
+ggsave("figs/mean-volatility-egarch.pdf", e.volatility, height = 5, width = 7)
 
 # TGARCH
 volatility.mean <- dat[, .(mean_tgarch_volatility = mean(tgarch_volatility, na.rm = TRUE)),
@@ -111,8 +111,8 @@ t.volatility <-
   geom_line(color = "grey48") + 
   xlab("Trading days") + 
   ylab("Mean volatility") +
-  scale_y_continuous(limits = c(1, 2.5),
-                     breaks = round(seq(min(1), max(2.5), by = 0.5),1)) +
+  scale_y_continuous(limits = c(1, 3),
+                     breaks = round(seq(min(1), max(3), by = 0.5),1)) +
   theme_classic()
 
 ggsave("figs/mean-volatility-tgarch.pdf", t.volatility, height = 5, width = 7)
@@ -130,3 +130,6 @@ fi.volatility <-
   scale_y_continuous(limits = c(1, 3),
                      breaks = round(seq(min(1), max(3), by = 0.5),1)) +
[…]

### 2023-11-13 doc/regime_changes_bp_rr.tex
R&R files

@@
 
-\pagestyle{empty}
-
 \setlength{\mathindent}{1cm}
@@
 \begin{document}
+%\author{  }
+%\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
 \author{Devin Incerti\thanks{Independent researcher.
@@
 In this study, we examine the impact of ``irregular'' regime changes and public protests on investment in a country's firms.
-However, unlike previous studies, \textcolor{red}{we theorize that investors will not be uniformly discouraged by sudden regime change, but will instead recognize some politically unstable events as ``good'' for future returns}.
+However, unlike previous studies, we theorize that investors will not be uniformly discouraged by sudden regime change, but will instead recognize some sudden political shocks as ``good'' for future returns.
 We therefore (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
@@
 anti business shifts.
-\textcolor{red}{Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' or ``bad'' for future profits.
-Importantly, expected future profits may differ from general economic performance, as stock prices only reflect the expected future profits of existing publicly-held firms.}
+Stock market returns are used as an indicator of whether investors view different types of sudden political shocks as ``good'' or ``bad'' for future profits.
+Importantly, expected future profits may differ from general economic performance, as stock prices only reflect the expected future profits of existing publicly-held firms.
 
@@
 
-\textcolor{red}{Second, it is not necessarily the case that even a sudden, extra-legal, or unexpected regime change will result in higher levels of instability}.
+Second, it is not necessarily the case that even a sudden, extra-legal, or unexpected regime change will result in higher levels of instability.
 Not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
@@
 
-\textcolor{red}{Third, the theoretical linkage through which political events have an impact on daily stock prices is changes in the broader macroeconomic environment that influence the expected stream of future profits of existing publicly-held firms.
+Third, the theoretical link through which political events are expected to have an impact on daily stock prices is changes in the broader macroeconomic environment that influence the expected stream of future profits of existing publicly-held firms.
 Examples of expected changes in the macroeconomic environment that can be influenced by sudden political events include: shifts in monetary policy, changes in trade or FDI openness, shifts in regulatory policy, changes in the share of output going to capital, transfer and convertibility restrictions, degree of resource nationalism, and heightened risk of capital expropriation or breach of contracts.
-Not all shocks to the political system will result in similar shifts in these macroeconomic variables depending on the actors involved, their ideological preferences, and their expected ability to enact policy changes.}
+Not all shocks to the political system will result in similar shifts in these macroeconomic variables depending on the actors involved, their ideological preferences, and their expected ability to enact policy changes.
 
@@
 By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader and may in fact signal \textit{increased} stability.
-\textcolor{red}{Using immediate, day-of shocks to stock prices as our outcome variable, we investigate the hypothesis that investors will positively update their perceptions of future economic performance when a sudden political event clearly shifts a country in a pro-democratic or pro-business direction, and negatively update when an event merely exacerbates instability or uncertainty.}
+Using immediate, day-of shocks to stock prices as our outcome variable, we investigate the hypothesis that investors will positively update their perceptions of future economic performance when a sudden political event clearly shifts a country in a pro-democratic or pro-business direction, and negatively update when an event merely exacerbates instability or uncertainty.
 
@@
 military coups), exacerbate poor economic policies, or merely increase policy uncertainty (such as assassinations) have the opposite effect.
-\textcolor{red}{Of course, changes in stock prices reflect investor's \textit{expected} changes in the macroeconomic environment, and these expectations may differ from realized future economic performance.
-Nevertheless, it is clear from our results that even sudden and extra-legal regime changes can be viewed as a ``positive'' event by investors under the right circumstances.}
+Of course, changes in stock prices reflect investor's \textit{expected} changes in the macroeconomic environment, and these expectations may differ from realized future economic performance.
+Nevertheless, it is clear from our results that even sudden and extra-legal regime changes can be viewed as a ``positive'' event by investors under the right circumstances.
 
@@
 
-\textcolor{red}{We estimate the effect of irregular regime changes on financial flows using an interrupted time series---also known as event study---approach, and examine the impact of political events on stock returns using daily financial data.
+We estimate the effect of irregular regime changes on financial flows using an interrupted time series---also known as event study---approach, and examine the impact of political events on stock returns using daily financial data.
 Additional explanation of the theoretical logic of why mean \textit{daily} stock market returns would be influenced by politically unstable events is warranted.
@@
 The immediate nature of this effect allows us to use the magnitude and direction of sudden fluctuations in granular daily data as a proxy for investors' expected valuation of the event in terms of future profits.
-This in turn allows us to examine how global financial actors value different kinds of politically unstable events---for example, pro-vs-anti business coups.}
-
-\textcolor{red}{The focus on \textit{immediate} fluctuations in daily financial data implies that we are examining the effect of ``one shot'' regime changes akin to a sudden day-of shock.
+This in turn allows us to examine how global financial actors value different kinds of politically unstable events---for example, pro-vs-anti business coups.
+
+The focus on \textit{immediate} fluctuations in daily financial data implies that we are examining the effect of ``one shot'' regime changes akin to a sudden day-of shock.
 Our estimates therefore capture the effect of these sudden, unexpected shocks on stock prices on the same day of the shock.
-Importantly, this implies that we are not estimating the effect of any larger underlying political conditions surrounding the event, but rather only the immediate event itself, independent of other surrounding conditions.
+Importantly, this implies that we are not estimating the effect of any larger underlying political conditions surrounding the event, but rather only the immediate event itself independent of other surrounding conditions.
 Further, as this approach provides an estimate \textit{at the exact time of the event}, confounding events would need to occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.
-We recognize that broader definitions of political instability may encompass broader political volatility over a wider range of time.
-In an attempt to address this concern, we also examine the impact of periods of protest on financial returns in the appendix.}
-
-\textcolor{red}{The key identifying assumption behind our interrupted time-series approach is that the events are unpredicted in an immediate temporal sense.
+We recognize that broader definitions of political instability may encompass political volatility over a wider range of time.
+In an attempt to address this concern, we also examine the impact of periods of protest on financial returns in the appendix.
+
+The key identifying assumption behind our interrupted time-series approach is that the events are unpredicted in an immediate temporal sense.
 In other words, for an event to be plausibly exogenous, the exact timing of the event must be unknown to investors.
-If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the index during the estimation window.}
+If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the index during the estimation window.
 
@@
 In other words, the model predicts that large shocks will be followed by other large shocks.
-\textcolor{red}{As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, fractionally integrated GARCH, and GARCH(1,1) accounting for structural breaks in the time series data in the appendix}.
+As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, fractionally integrated GARCH, and GARCH(1,1) accounting for structural breaks in the time series data in the appendix.
 
@@
 For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
-\textcolor{red}{For coups, there is suggestive evidence of a negative pre-trend in the run up to the event.
+By contrast, a clear break exists between the negative pre-event trend and positive event day jump and post-event trend.
+For coups, there is suggestive evidence of a negative pre-trend in the run up to the event.
 However, the overall 7-day and 20-day pre-trends are both insignificant at conventional levels.
 There is also a much larger jump in negative CARs on the day of the event.
-This therefore implies that even if investors had some expectation of a negative event occurring, they were unaware of its timing, and at worst a portion of the negative change in investment was already priced into the day-of shift.}There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+This therefore implies that even if investors had some expectation of a negative event occurring, they were unaware of its timing, and at worst a portion of the negative change in investment was already priced into the day-of shift.
+There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
 
 Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
-\textcolor{red}{This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
-We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.} Each country is given a weight which represents its influence in the synthetic control portfolio.
+This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
+We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.
+Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
-\textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are never significantly different from zero for coups, assassinations, or resignations (or overall).}
+In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are never significantly different from zero for coups, assassinations, or resignations (or when aggregated together).
 
@@
 While conventional wisdom suggests investors dislike unexpected regime changes, we show that this is not necessarily always the case.
-Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
+Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more stable, democratic, or pro-business environment than the previous one.
 
@@
 
-\textcolor{red}{Our findings have a number of potential implications for policymakers.
+Our findings have a number of potential policy implications.
 First, our finding that even democratically subversive irregular regime changes can have a positive impact on investment when the replacement government is clearly pro-business  implies that investor goals and actions may be at odds with regime stability.
 Second, the immediate nature and large magnitude of the financial outflows we observe in the wake of the majority of coups and assassinations suggests that a weakened financial system and economy are likely to accompany these kinds of regime changes.
-More optimistically, however, we also find suggestive evidence that in the event of a democratic regime change or revolution, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
+More optimistically, however, we also find suggestive evidence that in the event of a democratic regime change or revolution, clearly signaling a commitment to democracy may result in increased investment in a country's firms.
 
@@
 Research focusing on the mechanisms in other settings would help generalize these findings.
-\textcolor{red}{Second, it remains unclear how markets react to successful irregular regime change conditional on attempt.
-A future study could therefore examine how markets react to successful assassinations or coups when compared to failed attempts.} Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
+Second, it remains unclear how markets react to successful irregular regime change conditional on attempt.
+A future study could therefore examine how markets react to successful assassinations or coups when compared to failed attempts.
+Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
 \citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
@@
 \large
-Devin Incerti and Trevor Incerti
+%Devin Incerti and Trevor Incerti
 
@@
 
-In addition, we independently plot the CARs during each period of protest preceding a resignation for each event.\footnote{An expception is the 1998 Yellow Revolution in the Philippines, as markets remained closed from the start of the protest until after Marcos' resignation}.
-This analysis also shows that volatility and the absolute value of returns increase during times of protest, but also reveals that the resignations themselves constitute distinct events that are clearly distinguishable from the general period of protest.
+In addition, we independently plot the CARs during each period of protest preceding a resignation for each event.\footnote{An expception is the 1998 Yellow Revolution in the Philippines, as markets remained closed from the start of the protest until after Marcos' resignation} This analysis also shows that volatility and the absolute value of returns increase during times of protest, but also reveals that the resignations themselves typically constitute distinct events that are clearly distinguishable from the general period of protest.
 

### 2023-11-13 code/09-structural-breaks.R

@@ -127,8 +127,8 @@ sb.volatility <-
   geom_line(color = "grey48") + 
   xlab("Trading days") + 
   ylab("Mean volatility") +
-  scale_y_continuous(limits = c(1, 2.5),
-                     breaks = round(seq(min(1), max(2.5), by = 0.5),1)) +
+  scale_y_continuous(limits = c(1, 3),
+                     breaks = round(seq(min(1), max(3), by = 0.5),1)) +
   theme_classic()
 
 ggsave("figs/mean-volatility-sb.pdf", sb.volatility, height = 5, width = 7)

### 2024-02-09 doc/regime_changes_bp_final.tex
Update manuscript for publication

--- 2023-11-13 doc/regime_changes_bp_rr.tex
@@
 
+% footnote citations
+\newcommand*{\footcite}[1]{\footnote{\cite{#1}.}}
+
 % file paths and definitions
@@
 \begin{document}
-%\author{  }
-%\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
+\author{  }
+\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
 \author{Devin Incerti\thanks{Independent researcher.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
-Assistant Professor, Department of Political Science, University of Amsterdam.
+Assistant Professor of Political Economy, Department of Political Science, University of Amsterdam.
 t.n.incerti@uva.nl.}}
@@
 Evidence from daily financial data \thanks{We are grateful to P.M.
-Aronow, Matthew Graham, Frances Rosenbluth, and four anonymous reviewers for helpful feedback and suggestions.
+Aronow, Matthew Graham, Frances Rosenbluth, Hikaru Yamagishi, and four anonymous reviewers for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
+Replication data and code can be found at \url{https://github.com/dincerti/political-instability}.
 Any and all errors are our own.}}}
@@
 In \citet{wipr2011} and  \citet{wipr2012}, political risk was ranked the most important constraint for FDI in developing countries - even greater than macroeconomic instability.
-The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These considerations of political risk are reflected in research showing that political instability is negatively correlated with investment, financial development, and GDP growth \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring}, as well as associated with increases in stock market variance \citep{leblang2005government, jensen2005market, liu2015economic}.
-Common rationales are that unstable governments act myopically and adopt inefficient policies.
-Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights \citep{svensson1998investment}, and to be more likely to increases taxes \citep{devereux1998political}.\footnote{\citet{devereux1998political} proposes a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
+The types of political risk of most concern to investors in developing countries (ranked in order of importance) were 1) adverse regulatory changes, 2) breaches of contract, 3) transfers and convertibility restrictions, 4) civil disturbances, 5) non-honoring of government guarantees, 6) expropriation nationalization, 7) terrorism and 8) war.} These considerations of political risk are reflected in research showing that political instability is negatively correlated with investment, financial development, and GDP growth,\footcite{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} as well as associated with increases in stock market variance.\footcite{leblang2005government, jensen2005market, liu2015economic} Common rationales are that unstable governments act myopically and adopt inefficient policies.
+Unstable governments have, for example, been argued to be less likely to invest in the legal system and the protection of property rights,\footcite{svensson1998investment} and to be more likely to increases taxes.\footcite{devereux1998political} \footnote{\citet{devereux1998political} propose a model in which political instability causes governments to leave fewer assets to their successors which forces them into increasing capital taxes.
 The knowledge of future taxation then causes the private sector to reduce current investment which reduces future output.}
@@
 In the wake of the Arab Spring---in which rulers were deposed in four countries---only Tunisia ultimately transitioned to democracy.
-These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
-
-%These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \citep{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \citep{leblang2005government, jensen2005market, liu2015economic}.
+These results are in line with prior research that claims that in autocracies coups rarely lead to democratization, and in democracies they cause instability \footcite{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+
+%These theories are supported by empirical research that suggests political instability---as measured by regime change frequency, political violence, or indices of uncertainty derived from news reports---is negatively correlated with investment, financial development, and GDP growth in cross country regressions \footcite{aisen2013does, alesina1996income, alesina1996political, fosu1992political, jong2009measurement, roe2011political, baker2016measuring} and that the variance of stock market returns increases in response to economic policy uncertainty \footcite{leblang2005government, jensen2005market, liu2015economic}.
 
@@
 
-%Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \citep{schwert1990stock, fama1990stock}.
+%Beyond the large changes in real wealth created by extreme stock market volatility, empirical research has tied future production growth rates to variation in stock returns \footcite{schwert1990stock, fama1990stock}.
 
@@
 This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
-For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
+For example, political events have been used to estimate the effect of political connections on firm value \citep{fisman2001estimating,faccio2006politically,goldman2009politically}.
 Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply a method akin to market-model event studies even when a suitable control portfolio is absent.
 
-We analyze the full sample of politically unstable events for which national-level daily financial data is available---13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.\footnote{We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.} We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
+We analyze the full sample of politically unstable events for which national-level daily financial data is available---13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.\footnote{We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.} In addition, we examine 24 failed coups in order to compare the impact of successful coups that resulted in regime change to coups attempts that did not.
+We also engage in a closer examination of the failed 2002 Venezuelan coup, as it provides a special case that allows us to observe the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
 Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
@@
 
-Stable capital flows are important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
-High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth \citep{koepke2019drives}.
-Conventional theory and cross-country empirical evidence suggests that political instability---as measured by events such as protests, strikes, assassinations, number of regime changes, and ongoing elections---depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
-However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
+Stable capital flows are important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital.\footcite{koepke2019drives, obstfeld2012financial, cohen2017global} High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth.\footcite{koepke2019drives} Conventional theory and cross-country empirical evidence suggests that political instability---as measured by events such as protests, strikes, assassinations, number of regime changes, and ongoing elections---depresses investment.\footcite{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy} However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
 
@@
 \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, but some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
+
+Most research suggests that ``good coups'' are not the norm,\footcite{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic} but some evidence suggests that they have become more frequent\footcite{marinov2014coups} and could have positive economic effects.
 \citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
@@
 Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
-These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups \citep{londregan1990poverty, alesina1996political}, assassinations or revolutions \citep{barro1991economic}, or have combined various metrics into single indices \citep{alesina1996income, venieris1986income, gupta1990economics}.\footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
+These differences are often overlooked in past empirical strategies, which have proxied for instability in terms of the number of coups,\footcite{londregan1990poverty, alesina1996political} assassinations or revolutions,\footcite{barro1991economic} or have combined various metrics into single indices.\footcite{alesina1996income, venieris1986income, gupta1990economics} \footnote{Note that these studies vary by metrics included in the indices, method of aggregation, and outcome variable of interest.} In another cross-country regression study, \citet{jong2009measurement} disaggregates instability into four main metrics, one of which is regime changes, but does not subset below this metric.
 By contrast---recognizing the different degrees of instability that these events may reflect---we estimate effects separately for coups, assassinations, resignations, and protests.
@@
 \citet[p.
-617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''
+617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.'' With this caveat in mind, we nevertheless additionally construct a database of failed coups from the Colpus dataset\footcite{chin2021varieties} in order to test for robustness to inclusion of ambiguous coup cases, which can be found in \autoref{tab:AR-coups-failed} in the appendix.
 
@@
 \ExpandableInput{../tables/coups.txt} \\
-   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
-\ExpandableInput{../tables/failed_coup.txt}\\
+%   \multicolumn{3}{c}{\textbf{Failed coup}}\\ 
+% \ExpandableInput{../tables/failed_coup.txt}\\
   \multicolumn{3}{c}{\textbf{Assassinations}}\\ 
@@
 Event studies rely on the theoretical assumption that investors anticipate the effect of sudden events (e.g., corporate announcements, regulatory policy changes, political events, etc.) on future profitability of a firm or firms in a market, and importantly, that these anticipated changes in profitability are \textit{immediately} reflected in stock market prices.
-The approach therefore implicitly relies on the efficient market hypothesis, or the idea that in an efficient market, stocks instantly incorporate publicly available information into their prices \citep{fama1965behavior, samuelson1965proof}.
-The immediate nature of this effect allows us to use the magnitude and direction of sudden fluctuations in granular daily data as a proxy for investors' expected valuation of the event in terms of future profits.
+The approach therefore implicitly relies on the efficient market hypothesis, or the idea that in an efficient market, stocks instantly incorporate publicly available information into their prices.\footcite{fama1965behavior, samuelson1965proof} The immediate nature of this effect allows us to use the magnitude and direction of sudden fluctuations in granular daily data as a proxy for investors' expected valuation of the event in terms of future profits.
 This in turn allows us to examine how global financial actors value different kinds of politically unstable events---for example, pro-vs-anti business coups.
@@
 We recognize that broader definitions of political instability may encompass political volatility over a wider range of time.
-In an attempt to address this concern, we also examine the impact of periods of protest on financial returns in the appendix.
+In an attempt to address this concern, we also examine the impact of periods of protest and failed coup attempts on financial returns in the appendix.
 
@@
 For example, consider Ferdinand Marcos' resignation from office as President of the Philippines in February 1986.
-Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}.
-In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies and possessed one of the worst capital investment to economic output ratios in Asia \citep{overholt1986rise}.
-Marcos held a snap presidential election on February 7, 1986, in which he declared victory despite overwhelming evidence of electoral fraud.
-Public protests ensued, and two weeks later the military withdrew its support of the Marcos regime \citep{lee2009armed}.
-Marcos was replaced by his electoral opponent, Corazon Aquino, who had run on a platform of economic liberalization and elimination of crony capitalism \citep{villegas1987philippines}.
-This event was associated with an approximately 13\% positive event day AR.
+Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy.\footcite{overholt1986rise, traywick2014} In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies and possessed one of the worst capital investment to economic output ratios in Asia.\footcite{overholt1986rise} Marcos held a snap presidential election on February 7, 1986, in which he declared victory despite overwhelming evidence of electoral fraud.
+Public protests ensued, and two weeks later the military withdrew its support of the Marcos regime.\footcite{lee2009armed} Marcos was replaced by his electoral opponent, Corazon Aquino, who had run on a platform of economic liberalization and elimination of crony capitalism.\footcite{villegas1987philippines} This event was associated with an approximately 13\% positive event day AR.
 
@@
 While markets may generally dislike political instability, the immediate effect of regime changes on markets may not always be unpredictable.
-For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation \citep{przeworski1982structure, north1989constitutions, svensson1998investment}.
-In addition, when the successor in an irregular regime change is clear, investors may have strong priors about the effect of the new leader on economic and/or market performance.
+For example, investors may generally value democracy if it is perceived to provide stronger property rights and lower susceptibility to capital appropriation.\footcite{przeworski1982structure, north1989constitutions, svensson1998investment} In addition, when the successor in an irregular regime change is clear, investors may have strong priors about the effect of the new leader on economic and/or market performance.
 Two possible mechanisms that could be driving the differences may therefore be: (1) whether the regime change is associated with an authoritarian or democratic shift in governance, and (2) whether a new leader is clearly more pro or anti business than their predecessor.
@@
 Third, the reported means are based on small sample sizes so confidence intervals based on normally distributed abnormal returns may be inappropriate.
-
-We explore these concerns in two ways.
+Finally, for coups, it may also be useful to compare successful coups to  unsuccessful events (rather than no coup), as the latter may adjust for selection into unstable events.
+
+We explore these concerns in the following ways.
 First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events for each type of regime change.
@@
 This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
-We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.
-Each country is given a weight which represents its influence in the synthetic control portfolio.
+We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.\footnote{Greater political risk is associated with higher within-country financial volatility \footcite{boutchkova2012precarious}.
+As our synthetic control portfolio contains data from countries at both high and low levels of general political risk, some countries in the synthetic control reference market  have higher levels of baseline financial volatility than an event country, while others have lower levels of baseline volatility.
+Note, however, that this does not impact the main event study estimates, as the relevant comparison is the financial returns on the event day and \textit{within}-country financial volatility in the period preceding the event.} Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
@@
 
+Finally, we supplement our list of successful coups with a list of failed coups from the Colpus data set\footcite{chin2021varieties} and show robustness to including and excluding ambiguous cases by reestimating our models while also including failed coups.
+This analysis demonstrates that including failed coups reduces the magnitude of the negative effect of coups overall, but that the estimates remain negative and statistically significant (see \autoref{tab:AR-coups-failed-success}).
+This result is clarified by analyzing failed coups independently of successful coups, which reveals a slightly negative but null impact of failed coups on returns, suggesting that ambiguous cases and plots tend not to have the same level of directed impact on average as successful regime changes (see \autoref{tab:AR-coups-failed}).
+
 \section{Discussion and Conclusion}
@@
 However, the returns surrounding the failed 2002 coup that temporarily ousted Hugo Chavez from power in Venezuela show that even democratically subversive coups can have positive effects if the instigators are clearly pro-business.
-These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
+These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations.\footcite{girardi2018institution}
 
@@
 \large
-%Devin Incerti and Trevor Incerti
+Devin Incerti and Trevor Incerti
 
@@
 \caption{Abnormal returns following coups} \label{tab:AR-coups-pre}
+\singlespacing
 \vspace{-5pt}
@@
 \caption{Abnormal returns following assassinations} \label{tab:AR-ass-pre}
+\singlespacing
 \vspace{-5pt}
@@
 \caption{Abnormal returns following resignations} \label{tab:AR-resignations-pre}
+\singlespacing
 \vspace{-5pt}
@@
 Returns are inflation adjusted.
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\subsubsection{Abnormal returns for failed coups}
+
+\begin{table}[H]
+\caption{Abnormal returns following failed coups} \label{tab:AR-coups-failed}
+\singlespacing
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\resizebox{!}{.35\paperheight}{%
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-failed-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-failed-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{Abnormal returns following failed and successful coups} \label{tab:AR-coups-failed-success}
+\singlespacing
+\vspace{-5pt}
+\footnotesize
+\begin{center}
+\begin{threeparttable}
+\resizebox{!}{.39\paperheight}{%
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
+  \hline
+  \hline
+\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
+\cmidrule(r){3-5} \cmidrule(r){6-7}
+\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
+  \hline
+\ExpandableInput{../tables/artable-failed-success-car.txt}
+  \hline
+\ExpandableInput{../tables/artable-failed-success-car-mean.txt}
+   \hline
+   \hline
+\end{tabular*}}
 \end{threeparttable}

### 2024-02-09 doc/archive/regime_changes.tex
Clean up file and directory names

--- 2023-07-05 doc/regime_changes_bp_rr.tex
@@
 \usepackage{lipsum}
-\usepackage{etoc}
 
@@
 
-%\setcounter{tocdepth}{1}
+\setcounter{tocdepth}{1}
 \begin{document}
@@
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
-Assistant Professor, Department of Political Science, University of Amsterdam.
-t.n.incerti@uva.nl.}}
+Postdoctoral Fellow, Weatherhead Center for International Affairs, Harvard University.
+trevorincerti@fas.harvard.edu.}}
 \title{\textbf{Are regime changes always bad economics?
-Evidence from daily financial data \thanks{We are grateful to P.M.
-Aronow, Matthew Graham, Frances Rosenbluth, and four anonymous reviewers for helpful feedback and suggestions.
+Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
@@
 In this study, we examine the impact of ``irregular'' regime changes and public protests on investment in a country's firms.
-However, unlike previous studies, \textcolor{red}{we theorize that investors will not be uniformly discouraged by sudden regime change, but will instead recognize some politically unstable events as ``good'' for future returns}.
-We therefore (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
+However, unlike previous studies, we (1) remain agnostic about the direction of the effect of political instability, and (2) separately examine the effect of different types of instability on domestic firms' access to financial capital.
 Specifically, we examine whether changes in financial flows differ for coups, resignations, assassinations, and protests, as well as for authoritarian vs.
@@
 anti business shifts.
-\textcolor{red}{Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' or ``bad'' for future profits.
-Importantly, expected future profits may differ from general economic performance, as stock prices only reflect the expected future profits of existing publicly-held firms.}
+
+%Stock market returns are used as an indicator of whether investors view different types of potentially destabilizing political events as ``good'' for future returns.
 
@@
 We also provide methodological advancements when compared to the aforementioned cross country studies.
-Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the exact time of the event}.
+Specifically, we conduct event studies of daily financial data, which estimate a local average treatment effect of an unexpected event on stock prices \textit{at the time of the event}.
 This interrupted time-series approach mitigates the endogeneity problems in previous cross country regressions---confounding events would need to occur on the same day as instability, and do so for a large portion of all of our independently tested events in order to influence our estimates.\footnote{A growing body of work uses event studies to assess political phenomenon.
 For example, political events have been used to estimate the effect of political connections on firm value \citep[e.g.][]{fisman2001estimating,faccio2006politically,goldman2009politically}.
-Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply a method akin to market-model event studies even when a suitable control portfolio is absent.
+Studies in ``forensic economics" have used abnormal returns from political events to locate or examine transactions such as insider trading \citep{dube2011coups}, illegal arms trading \citep{dellavigna2010detecting}, and the impact of hostilities on the financial performance of diamond mining firms in Angola \citep{guidolin2007diamonds}.} In addition, we integrate synthetic control and event study methods and demonstrate how ``synthetic'' control portfolios can be used to apply market-model event studies even when a suitable control portfolio is absent.
 
@@
 
-Stable capital flows are important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
+Stable capital flows are highly important to financial stability in emerging markets, which are particularly exposed to shifts in the availability of foreign capital \citep{koepke2019drives, obstfeld2012financial, cohen2017global}.
 High country risk reduces capital flows, which in turn has been shown to reduce domestic output growth \citep{koepke2019drives}.
-Conventional theory and cross-country empirical evidence suggests that political instability---as measured by events such as protests, strikes, assassinations, number of regime changes, and ongoing elections---depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
+Conventional theory and cross-country empirical evidence suggests that political instability depresses investment \citep{irshad2017relationship, le2006political, lensink2000capital, boutchkova2012precarious, lehkonen2015democracy}.
 However, if market returns reflect investor expectations about future economic growth and expected returns, there are reasons to believe such hypotheses may be overly simplistic.
 
-First, a change in regime may be seen as a positive event for future economic performance if the current regime is regarded as anti-business or anti-global.
+First, a change in regime may be seen as a positive event if the current regime is regarded as anti-business or anti-global.
 Regime changes that attempt to overthrow anti-business autocrats may be expected to result in positive abnormal returns as investors see little risk of a replacement government ``worse'' than the status quo.
-For example, there is an active debate on whether ``good coups'' that lead to democratization or economic liberalization can be good for economic growth.
-\citet{alesina1996political} argues that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions, while \citet{alesina1996income} submit that ``unconstitutional'' regime changes such as coups are worse for economic growth than other types of political instability.
-\citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
-Most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}, but some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
+
+An active debate exists on the subject of ``good coups''---i.e.
+coups that lead to democratization or economic liberalization---and their effect on economic growth.
+\citet{alesina1996political} take the possibility of a new government adopting better economic policies seriously, but argue that the negative effects of uncertainty dominate the positive effects of coups staged by pro growth factions.
+\citet{alesina1996income} argue that ``unconstitional'' regime changes such as coups are worse for economic growth than other types of political instability, while \citet{londregan1990poverty} find that coups have no impact on economic growth and hypothesize that this may be because there is a bimodal distribution of coups, some of which enhance growth and others which restrict it.
+However, most research suggests that ``good coups'' are not the norm \citep{derpanopoulos2015coups, powell2011global, thyne2016coup, varol2011democratic}.
+But while ``good coups'' may be the minority, some evidence suggests that they have become more frequent \citep{marinov2014coups} and could have positive economic effects.
 \citet{meyersson2016political} finds that coup attempts that occur in democratic regimes are associated with negative GDP growth, while those that occur in autocratic regimes are associated with positive GDP growth.
-In another study examining the same outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
+In another study examining the outcome variable as our own---financial returns---\citet{girardi2018institution} show that Salvador Allende's socialist government was associated with declines in stock prices while the coup that replaced him boosted them.
 
@@
 
-\textcolor{red}{Second, it is not necessarily the case that even a sudden, extra-legal, or unexpected regime change will result in higher levels of instability}.
-Not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
-However, resignations often occur when an ineffective leader steps down.
-By contrast, assassinations are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
+Second, not all regime changes are equivalent---resignations, assassinations, and coups are all examples of sudden regime changes and have been used as proxies for instability in previous research.
+However, some regime changes may actually lead to increased stability.
+Resignations, for example, often occur when an ineffective leader steps down.
+Assassinations, by contrast, are not always related to the effectiveness of a leader, can occur seemingly at random, and the successor to the assassinated leader may be unclear.
 Coups can occur in the name of democracy or autocracy, and in general signal relative weakness in the current political system.
@@
 
-\textcolor{red}{Third, the theoretical linkage through which political events have an impact on daily stock prices is changes in the broader macroeconomic environment that influence the expected stream of future profits of existing publicly-held firms.
-Examples of expected changes in the macroeconomic environment that can be influenced by sudden political events include: shifts in monetary policy, changes in trade or FDI openness, shifts in regulatory policy, changes in the share of output going to capital, transfer and convertibility restrictions, degree of resource nationalism, and heightened risk of capital expropriation or breach of contracts.
-Not all shocks to the political system will result in similar shifts in these macroeconomic variables depending on the actors involved, their ideological preferences, and their expected ability to enact policy changes.}
-
 Different types of regime changes may therefore have disparate effects on investment, just as they may differentially effect overall economic growth.
@@
 Assassinations should have a neutral or negative impact as they increase uncertainty, but institutional responses to assassinations vary by country.
-By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader and may in fact signal \textit{increased} stability.
-\textcolor{red}{Using immediate, day-of shocks to stock prices as our outcome variable, we investigate the hypothesis that investors will positively update their perceptions of future economic performance when a sudden political event clearly shifts a country in a pro-democratic or pro-business direction, and negatively update when an event merely exacerbates instability or uncertainty.}
+By contrast, resignations may be viewed positively on average, as they typically signal the departure of an ineffective leader.
 
@@
 military coups), exacerbate poor economic policies, or merely increase policy uncertainty (such as assassinations) have the opposite effect.
-\textcolor{red}{Of course, changes in stock prices reflect investor's \textit{expected} changes in the macroeconomic environment, and these expectations may differ from realized future economic performance.
-Nevertheless, it is clear from our results that even sudden and extra-legal regime changes can be viewed as a ``positive'' event by investors under the right circumstances.}
 
@@
 
-\section{Estimation strategy} \label{sec: estimation}
-
-\textcolor{red}{We estimate the effect of irregular regime changes on financial flows using an interrupted time series---also known as event study---approach, and examine the impact of political events on stock returns using daily financial data.
-Additional explanation of the theoretical logic of why mean \textit{daily} stock market returns would be influenced by politically unstable events is warranted.
-Event studies rely on the theoretical assumption that investors anticipate the effect of sudden events (e.g., corporate announcements, regulatory policy changes, political events, etc.) on future profitability of a firm or firms in a market, and importantly, that these anticipated changes in profitability are \textit{immediately} reflected in stock market prices.
-The approach therefore implicitly relies on the efficient market hypothesis, or the idea that in an efficient market, stocks instantly incorporate publicly available information into their prices \citep{fama1965behavior, samuelson1965proof}.
-The immediate nature of this effect allows us to use the magnitude and direction of sudden fluctuations in granular daily data as a proxy for investors' expected valuation of the event in terms of future profits.
-This in turn allows us to examine how global financial actors value different kinds of politically unstable events---for example, pro-vs-anti business coups.}
-
-\textcolor{red}{The focus on \textit{immediate} fluctuations in daily financial data implies that we are examining the effect of ``one shot'' regime changes akin to a sudden day-of shock.
-Our estimates therefore capture the effect of these sudden, unexpected shocks on stock prices on the same day of the shock.
-Importantly, this implies that we are not estimating the effect of any larger underlying political conditions surrounding the event, but rather only the immediate event itself, independent of other surrounding conditions.
-Further, as this approach provides an estimate \textit{at the exact time of the event}, confounding events would need to occur on the same day, and do so for a large portion of all of our independently tested events in order to influence our estimates.
-We recognize that broader definitions of political instability may encompass broader political volatility over a wider range of time.
-In an attempt to address this concern, we also examine the impact of periods of protest on financial returns in the appendix.}
-
-\textcolor{red}{The key identifying assumption behind our interrupted time-series approach is that the events are unpredicted in an immediate temporal sense.
-In other words, for an event to be plausibly exogenous, the exact timing of the event must be unknown to investors.
-If information about the event has leaked prior to occurrence of the event, a portion of the change in investment will already be priced into the index during the estimation window.}
-
-\subsection{Volatility} \label{subsec: Volatility_estimation}
-
-Before examining the magnitude and direction of returns, we first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
+\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
+
+\subsection{Volatility} \label{subsec: Volatility}
+
+We first confirm that our sample of events exhibits the increases in volatility suggested by previous literature.
 Since stock volatility is not directly observable, one must decide how to best estimate volatility.
@@
 In other words, the model predicts that large shocks will be followed by other large shocks.
-\textcolor{red}{As robustness checks, we also estimate volatility using exponential GARCH, threshold GARCH, and fractionally integrated GARCH models in the appendix}.
-
-\subsection{Abnormal Returns} \label{subsec:abnormal-returns_estimation}
+
+\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.
+As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
+Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
+This may suggest that investors sometimes have information about the events before they occur.
+Nonetheless, there is still an enormous volatility jump on the day of the regime change.
+Volatility then decreases to normal levels within a month of the event.
+
+\begin{figure}[!htb]
+\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
+\caption{Mean of volatility estimates from GARCH(1,1) models}
+\label{fig:volatility}
+\end{figure}
+
+\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
 
@@
 
-A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns as a robustness check.
+A constant mean return model is used instead of a market model in order to maximize the number of observations and because our unit of analysis is country-wide market indices rather than firms.\footnote{Plausible market indices such as the MSCI World Index and the S\&P/IFC Emerging Markets Investable Composite Index only begin in 1976 and 1995, respectively.} To address concerns regarding use of a constant mean return model, we also create a synthetic control portfolio for each event and compare observed returns to the synthetic returns.
 
@@
 
-\section{Impact of Political Instability on Stock Returns} \label{sec: Impact of Political Instability on Stock Returns}
-
-\subsection{Volatility} \label{subsec: Volatility}
-
-\autoref{fig:volatility} shows the mean volatility ($\overline{\sigma_t}$) estimates from the GARCH (1,1) model across all irregular regime changes for 250 trading days prior to and 250 days after each event.\footnote{Robustness checks using exponential GARCH, threshold GARCH, and GARCH(1,1) controlling for structural breaks can be found in \autoref{fig:egarch}, \autoref{fig:tgarch}, and \autoref{fig:garch_sb}, respectively.} As expected, the volatility estimates stay between a narrow range at nearly all dates except those surrounding the regime change.
-Volatility appears to increase slowly just before the regime change, albeit not to a degree out of line with previous fluctuations in volatility.
-This may suggest that investors sometimes have information about the events before they occur.
-Nonetheless, there is still an enormous volatility jump on the day of the regime change.
-Volatility then decreases to normal levels within a month of the event.
-
-\begin{figure}[!htb]
-\includegraphics[scale = 0.9]{../figs/mean-volatility.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models}
-\label{fig:volatility}
-\end{figure}
-
-\subsection{Abnormal Returns} \label{subsec:abnormal-returns}
-
-\subsubsection{Coups} \label{subsec: Coups}
+\subsection{Coups} \label{subsec: Coups}
 \autoref{tab:AR-coups} shows abnormal returns for national stock indices both preceding and following coup d'etat.
@@
 
-\subsubsection{Assassinations} \label{subsec: Assassinations}
-
-The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for assassinations rather than coups.
+\subsection{Assassinations} \label{subsec: Assassinations}
+
+The results in \autoref{tab:AR-ass} are produced from analyses identical to those in \autoref{tab:AR-coups} but for successful assassinations rather than coups.
 Like the majority of coups, there is evidence that assassinations decrease stock prices.
@@
 For resignations, CARs trend downward in the 10 days prior to the event; however, if investors were aware that a resignation were about to occur one would expect the pre-event CARs to be positive given the positive CARs observed in the post-event window.
-\textcolor{red}{For coups, there is suggestive evidence of a negative pre-trend in the run up to the event.
-However, the overall 7-day and 20-day pre-trends are both insignificant at conventional levels.
-There is also a much larger jump in negative CARs on the day of the event.
-This therefore implies that even if investors had some expectation of a negative event occurring, they were unaware of its timing, and at worst a portion of the negative change in investment was already priced into the day-of shift.}There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
+There is thus little evidence that the CARs in the post-event window are not capturing most of the effect caused by the regime changes.
 
 Second, we create a synthetic control portfolio for each event based on the techniques introduced in \citet{abadie2003economic} and \citet{abadie2010synthetic}.
-\textcolor{red}{This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
-We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.} Each country is given a weight which represents its influence in the synthetic control portfolio.
+Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
-\textcolor{red}{In contrast with the large and significant abnormal returns in the actual countries of study, the returns in the synthetic control portfolio are never significantly different from zero for coups, assassinations, or resignations (or overall).}
 
@@
 
-While conventional wisdom suggests investors dislike unexpected regime changes, we show that this is not necessarily always the case.
+While conventional wisdom suggests investors dislike political instability, we show that this is not necessarily always the case.
 Unexpected changes in ruler virtually always increase market volatility, but the directionality is not always negative as markets can be given a boost when a new regime is expected to offer a more democratic or pro-business environment than the previous one.
@@
 These results are consistent with previous research showing that the coup replacing Allende in Chile increased stock market valuations \citep{girardi2018institution}.
-
-\textcolor{red}{Our findings have a number of potential implications for policymakers.
-First, our finding that even democratically subversive irregular regime changes can have a positive impact on investment when the replacement government is clearly pro-business  implies that investor goals and actions may be at odds with regime stability.
-Second, the immediate nature and large magnitude of the financial outflows we observe in the wake of the majority of coups and assassinations suggests that a weakened financial system and economy are likely to accompany these kinds of regime changes.
-More optimistically, however, we also find suggestive evidence that in the event of a democratic regime change or revolution, clearly signalling a commitment to democracy may result in increased investment in a country's firms.}
 
@@
 Research focusing on the mechanisms in other settings would help generalize these findings.
-\textcolor{red}{Second, it remains unclear how markets react to successful irregular regime change conditional on attempt.
-A future study could therefore examine how markets react to successful assassinations or coups when compared to failed attempts.} Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
+Lastly, it would be helpful to determine the extent to which stock market returns translate to broader economic development outcomes.
 \citet{meyersson2016political} has made progress on this front by examining the impact of coups on a number of outcomes in addition to economic growth including investment, debt, inflation, infant mortality, and years of schooling.
@@
 
-\newpage
-
-\begin{centering}
-\LARGE
-\textbf{\textit{Supplementary Appendix:}} \\
- \vspace{0.5cm}
-\textbf{Are regime changes always bad economics? Evidence from daily financial data} \\
-
-\vspace{0.5cm}
-
-\large
-Devin Incerti and Trevor Incerti
-
-\end{centering}
-
 \section{Appendix} \label{sec: appendix}
-
-\localtableofcontents
-\pagenumbering{arabic}% resets `page` counter to 1
-\renewcommand*{\thepage}{A\arabic{page}}
-
-\newpage
 
@@
 
-In addition, we independently plot the CARs during each period of protest preceding a resignation for each event.\footnote{An expception is the 1998 Yellow Revolution in the Philippines, as markets remained closed from the start of the protest until after Marcos' resignation}.
-This analysis also shows that volatility and the absolute value of returns increase during times of protest, but also reveals that the resignations themselves constitute distinct events that are clearly distinguishable from the general period of protest.
-
 \begin{table}[!ht]
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/bangla-1990.pdf}
-\caption{CARs during the 1990 Bangladesh uprising}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/indonesia-1998.pdf}
-\caption{CARs during the 1998 Indonesian revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/phil-2001.pdf}
-\caption{CARs during the Philippines Second People Power Revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/argentina-2001.pdf}
-\caption{CARs during the 2001 Argentine crisis}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/ukraine-2004.pdf}
-\caption{CARs during the 2004 Orange Revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/ecuador-2005.pdf}
-\caption{CARs during the Ecuadorian Revolution of 2005}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/nepal-2006.pdf}
-\caption{CARs during the 2006 Nepalese Democracy Movement}
-\label{fig:CAR-Egypt}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[scale=0.8]{../figs/tunisia-2011.pdf}
-\caption{CARs during the 2011 Tunisian Revolution}
-\label{fig:CAR-Egypt}
-\end{figure}
-
 \clearpage
@@
 
-\subsection{Additional robustness tests}
-
-\begin{figure}[H]
-\includegraphics[scale = 0.75]{../figs/mean-volatility-egarch.pdf}
-\caption{Mean of volatility estimates from exponential GARCH models}
-\label{fig:egarch}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[scale = 0.75]{../figs/mean-volatility-tgarch.pdf}
-\caption{Mean of volatility estimates from threshold GARCH models}
-\label{fig:tgarch}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[scale = 0.75]{../figs/mean-volatility-sb.pdf}
-\caption{Mean of volatility estimates from GARCH(1,1) models, with adjustment for structural breaks}
-\label{fig:garch_sb}
-\end{figure}
-
-\subsubsection{Abnormal returns for events with insignificant 7-day pre-trends only}
-
-\begin{table}[H]
-\caption{Abnormal returns following coups} \label{tab:AR-coups-pre}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-coups-car-pre.txt}
-  \hline
-\ExpandableInput{../tables/artable-coups-car-mean-pre.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{table}[H]
-\caption{Abnormal returns following assassinations} \label{tab:AR-ass-pre}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-ass-car-pre.txt}
-  \hline
-\ExpandableInput{../tables/artable-ass-car-mean-pre.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\begin{table}[H]
-\caption{Abnormal returns following resignations} \label{tab:AR-resignations-pre}
-\vspace{-5pt}
-\footnotesize
-\begin{center}
-\begin{threeparttable}
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
-  \hline
-  \hline
-\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
-\cmidrule(r){3-5} \cmidrule(r){6-7}
-\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
-  \hline
-\ExpandableInput{../tables/artable-res-car-pre.txt}
-  \hline
-\ExpandableInput{../tables/artable-res-car-mean-pre.txt}
-   \hline
-   \hline
-\end{tabular*}
-\scriptsize
-Notes: Standard errors are in parentheses.
-``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative).
-Returns are inflation adjusted.
-\end{threeparttable}
-\end{center}
-\end{table}
-
-\subsubsection{Time-shifted placebo test}
-
-\begin{figure}[H]
+\subsection{Time-shifted placebo test}
+
+\begin{figure}[!htb]
 \includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}

### 2024-02-09 doc/archive/regime_changes_bp_rr_2.tex
Clean up file and directory names

--- 2023-11-13 doc/regime_changes_bp_rr.tex
@@
 \begin{document}
-%\author{  }
-%\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
-\author{Devin Incerti\thanks{Independent researcher.
+\author{  }
+\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data}}
+%\author{Devin Incerti\thanks{Independent researcher.
 devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author.
@@
 t.n.incerti@uva.nl.}}
-\title{\textbf{Are regime changes always bad economics?
+%\title{\textbf{Are regime changes always bad economics?
 Evidence from daily financial data \thanks{We are grateful to P.M.
-Aronow, Matthew Graham, Frances Rosenbluth, and four anonymous reviewers for helpful feedback and suggestions.
+Aronow, Matthew Graham, Frances Rosenbluth, Hikaru Yamagishi, and four anonymous reviewers for helpful feedback and suggestions.
 Authors are listed in alphabetic order, implying equal authorship.
@@
 
-We analyze the full sample of politically unstable events for which national-level daily financial data is available---13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.\footnote{We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.} We also examine the failed 2002 Venezuelan coup, as it provides a case that allows us to estimate the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
+We analyze the full sample of politically unstable events for which national-level daily financial data is available---13 successful coups, 8 assassinations, 15 forced resignations, and 11 public protests.\footnote{We recognize that this does not represent a full list of historical coups, assassinations, resignations, and public protests, but are restricted to the sample of events for which national-level daily financial data is available.} In addition, we examine 24 failed coups in order to compare the impact of successful coups that resulted in regime change to coups attempts that did not.
+We also engage in a closer examination of the failed 2002 Venezuelan coup, as it provides a special case that allows us to observe the effects of both a seemingly successful pro-business coup, and the immediate reinstatement of a left-wing populist.
 Our study therefore not only uses an event-study approach to enhance the reliability of our estimates, but simultaneously examines a relatively large sample that enhances external validity and allows us to show that different types of political events have disparate effects.
@@
 \citet[p.
-617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.''
+617]{needler1966political} has gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting,'' the Center for Systemic Peace states that it is ``confident that [its] list of successful coups is comprehensive'' but does not extend this confidence to attempted or failed coups, and \citet{powell2011global} state that it is ``difficult to identify more ambiguous forms of coup activity, such as coup failures, plots, and rumors.'' With this caveat in mind, we nevertheless additionally construct a database of failed coups from the Colpus dataset \citep{chin2021varieties} in order to test for robustness to inclusion of ambiguous coup cases, which can be found in \autoref{tab:AR-coups-failed} in the appendix.
 
@@
 This approach creates a ``synthetic'' time series of daily financial returns based on the returns in a basket of countries which did \textit{not} experience tumultuous political events on the day of the event.
-We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.
-Each country is given a weight which represents its influence in the synthetic control portfolio.
+We are then able to compare the returns in the country which experienced the unexpected regime change with the actual returns of a reference market---in this case all countries that did not experience an unexpected regime change.\footnote{Greater political risk is associated with higher within-country financial volatility \citep{boutchkova2012precarious}.
+As our synthetic control portfolio contains data from countries at both high and low levels of general political risk, some countries in the synthetic control reference market  have higher levels of baseline financial volatility than an event country, while others have lower levels of baseline volatility.
+Note, however, that this does not impact the main event study estimates, as the relevant comparison is the financial returns on the event day and \textit{within}-country financial volatility in the period preceding the event.} Each country is given a weight which represents its influence in the synthetic control portfolio.
 The weight is chosen so that the daily returns and the variance of the daily returns of the control portfolio and the event country are most similar in the estimation window.\footnote{See ``Synthetic Control Portfolio'' in the Appendix for mathematical formalization.} The set of possible countries in the control portfolio consists of all countries listed in \autoref{tab:stock-list}.
@@
 Finally, the difference in means between the regime change country and the control portfolio are statistically different from zero for coups (1\% level), assassinations (10\% level), resignations (5\% level), and all events combined (1\% level) when using two-sided p-values from the Wilcoxon rank test.\footnote{The Wilcoxon rank test is a non-parametric statistical technique that can be used to compare differences between matched samples.} In sum, the synthetic control and small sample tests suggest that the main results are not a result of deviations from normality or confounding world events.
+
+Finally, we supplement our list of successful coups with a list of failed coups from the Colpus data set \citep{chin2021varieties} and show robustness to including and excluding ambiguous cases by reestimating our models while also including failed coups.
+This analysis demonstrates that including failed coups reduces the magnitude of the negative effect of coups overall, but that the estimates remain negative and statistically significant (see \autoref{tab:AR-coups-failed-success}).
+This result is clarified by analyzing failed coups independently of successful coups, which reveals a slightly negative but null impact of failed coups on returns, suggesting that ambiguous cases and plots tend not to have the same level of directed impact on average as successful regime changes (see \autoref{tab:AR-coups-failed}).
 
